### 2019-12-27 Other/FSD_templates/Latex_Template/Template.tex
Template added, Simulink model updated (Ts changed from 0.01 to 1/500)

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% Compile Template in following order:
%
% pdflatex Template
% makeindex Template.nlo -s nomencl.ist -o Template.nls
% makeindex Template.acn -s Template.ist -t Template.alg -o Template.acr
% makeindex Template.glo -s Template.ist -t Template.glg -o Template.gls
% pdflatex Template
% pdflatex Template
%
%
%#################################################################################
%#################################################################################
%#################################################################################

% Preamble
\documentclass[11pt, a4paper, twoside]{report}

% Define page layout
\usepackage[
 left=2.5cm,
 right=2.5cm,
 top=2.5cm,
 bottom=3cm]
{geometry}

% Package for defining the default font size
% We use Helvetica as an alternative to Arial
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
%alternatively one can use Arial package and compile with XeLaTEX
%\usepackage{fontspec}
%\setmainfont{Arial}

% Set line spacing to 1.15pt
\renewcommand{\baselinestretch}{1.15}

% Set spacing between paragraphs to be 10pt
\setlength{\parskip}{10pt}

% Set paragraph intendation (here 0pt, no intendation)
\setlength{\parindent}{0pt}

% Package for estimating the last page
\usepackage{pageslts}

% Package and settings for adding header/footer
\usepackage{fancyhdr}

% Set style for pages with arabic numbering 
% This block prints only the chapter number and the chapter name, not the word "Chapter"
%\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\ \thechapter. \ #1}}{}}
% Clear current page style 
\fancyhf{}
% Head (11 pt font size and 12 pt line spacing)
\fancyhf[HRE,HLO]{\includegraphics[width=2.5cm]{figs/fsd}}
\fancyhf[HRO,HLE]{\fontsize{11}{12}\selectfont \leftmark}
% Foot (11 pt font size and 12 pt line spacing)
\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Title\\First Name Last Name}
\fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage \thinspace / \lastpageref{LastPages}}
% Line settings
\renewcommand{\headrulewidth}{0.1pt}	%upper line
\renewcommand{\footrulewidth}{0.1pt}	%lower line

% Set style for pages with roman numbering 
\fancypagestyle{fancy_beginning}{%
%\pagestyle{fancy}
% Clear current page style 
\fancyhf{}%
% Head
\fancyhf[HRE,HLO]{\includegraphics[width=2.5cm]{figs/fsd}}%
\fancyhf[HRO,HLE]{\fontsize{11}{12}\selectfont \leftmark}%
% Foot
\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Title\\First Name Last Name}%
\fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage}%
% Line settings
\renewcommand{\headrulewidth}{0.1pt}%	%upper line
\renewcommand{\footrulewidth}{0.1pt}%	%lower line
}

% Package for inserting titel page
\usepackage{pdfpages}

% Package for changing distance between sections
\usepackage{titlesec}

% Package for setting up the caption options of figures
\usepackage{subcaption}

% Package prevents placing floats before a section (for not mooving figures)
\usepackage{float}

% TODO
% Package for using acronyms 
%\usepackage[printonlyused]{acronym}
%\renewcommand\acsfont{\textnormal}	% Set non-bold font of the acronym units

% This patch removes the insertion of \addvspace to both the LoF and the LoT; the cause of the additional gap between entries on a per-chapter basis
\usepackage{etoolbox}% http://ctan.org/pkg/etoolbox
\makeatletter
% \patchcmd{<cmd>}{<search>}{<replace>}{<succes>}{<failure>}
\patchcmd{\@chapter}{\addtocontents{lof}{\protect\addvspace{10\p@}}}{}{}{}% LoF
\patchcmd{\@chapter}{\addtocontents{lot}{\protect\addvspace{10\p@}}}{}{}{}% LoT
\makeatother

% Set chapter font size and spacing
\newcommand{\chapfnt}{\fontsize{14}{19}}
\titleformat{\chapter}
{\normalfont\chapfnt\bfseries}{\thechapter}{1em}{\chapfnt} 	% set font size
\titlespacing{\chapter}{0cm}{-1.2cm}{0cm}					% set spacing

% Set section font size (13pt) and spacing
\newcommand{\secfnt}{\fontsize{13}{19}}
\titleformat{\section}
{\normalfont\secfnt\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0cm}{0.3cm}{0cm}					% set spacing

% Package for edditing TOC, LOF and LOT
\usepackage[titles]{tocloft}

% Package for setting itemization/description parameters like indentation of items
\usepackage{enumitem}

% Package for acronyms
\usepackage[acronym, automake, nopostdot, nogroupskip]{glossaries}
\setlength{\LTleft}{-0.15cm}			% left justified
\renewcommand*{\arraystretch}{1.4}		% vertical distance between entries, default is 1
% List
\newacronym{ADF}{ADF}{Automatic Direction Finder}
\newacronym{ADI}{ADI}{Automatic Direction Indicator}
% Make gls
\renewcommand*\entryname{Acronym}
\makeglossaries

% Package for setting up the list of symbols
%https://tex.stackexchange.com/questions/112884/how-to-achieve-nomenclature-entries-like-symbol-description-dimension-and-uni
\usepackage{nomencl,etoolbox,ragged2e,siunitx}
%
\newcommand{\DimensUnits}[2]{\makebox[1em]{#1}\makebox[4em]{#2\hfill}\ignorespaces}
\newcommand{\insertnomheaders}{\item[\bfseries Symbol]\DimensUnits{}{\textbf{Unit}}\textbf{Description}}
%
\renewcommand\nomgroup[1]{%
  \item[\large\bfseries
  \ifstrequal{#1}{A}{Acronyms}{%
  \ifstrequal{#1}{B}{Latin Letters}{%
  \ifstrequal{#1}{G}{Greek Letters}{%
  \ifstrequal{#1}{S}{Indices}{% 
  \ifstrequal{#1}{U}{Subscripts}{%   
  \ifstrequal{#1}{X}{Other Symbols}{}}}}}}]
  \insertnomheaders
  }
%
\renewcommand*{\nompreamble}{\markboth{\nomname}{\nomname}}
% parbox - Description
\newcommand{\nomdescr}[1]{\parbox[t]{10cm}{\RaggedRight #1}}
\newcommand{\nomwithdim}[5]{\nomenclature[#1]{#2}{\DimensUnits{}{#5}\nomdescr{#3}}}
%
\makenomenclature

%#################################################################################%#################################################################################%#################################################################################

\begin{document}

% Activate roman page numbering
\pagenumbering{roman}

% Insert title page
\includepdf[pages={1}]{figs/Title_page.pdf}

%Insert empty page after title page
\newpage\null\thispagestyle{empty}\newpage

% For some reason fisrt chapter has a different vert. spacing from the top, so we add additional 0.8cm, starred command makes sure it will not be suppressed at the beginning or at the end of the page
\vspace*{-0.8cm}
\section*{Statutory Declaration}
I, , declare on oath towards the Institute of Flight System Dynamics of Technische Universität München, that I have prepared the present BA/SA/MA independently and with the aid of nothing but the resources listed in the bibliography.
\\
\\
This thesis has neither as-is nor similarly been submitted to any other university.
\bigskip
\\
\\
Garching,

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Statutory Declaration}

%Insert empty page after statutory declaration section
\newpage\null\thispagestyle{empty}\newpage

\section*{Kurzfassung} \label{sec:kurzfassung}
% Start cursive block
\begin{itshape}
Deutsche Kurzfassung der Arbeit.
\end{itshape}

% Add Abstract chapter to the same page as Kurzfassung
{\let\clearpage\relax\section*{Abstract}}
% Start cursive block
\begin{itshape}
English abstract of the thesis.
\end{itshape}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Abstract}

%Insert empty page after abstract page
\newpage\null\thispagestyle{empty}\newpage

% Add Table of Contents 
\setlength{\cftbeforechapskip}{0.2cm}			% space before chapters
\renewcommand\cftchapafterpnum{\vskip-0.4cm}	% space after chapters
\renewcommand\cftsecafterpnum{\vskip-0.4cm}		% space after sections
\renewcommand\cftsubsecafterpnum{\vskip-0.4cm}	% space after subsections	
\renewcommand{\cftchapfont}{\normalfont}		% set normal font, not bold
%\titleformat{\section}{\fontsize{14}{19}}	 	% ?

\renewcommand*\contentsname{Table of Contents}  % Change the defaulf name "Contents" to "Table of Contents"  
\tableofcontents								% Generate Table of Contents

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Contents}

%Insert empty page after table of contents
\newpage\null\thispagestyle{empty}\newpage

% Add List of Figures  
\renewcommand{\cftfigfont}{Figure }				% Add "Figure" to the LOF
\renewcommand\cftfigaftersnum{:} 				% Put ":" after the figure num 
\setlength{\cftfigindent}{0pt}					% Remove left indent 
\setlength\cftbeforefigskip{-0.2cm}				% Space between figures 
\addtocontents{lof}{\vspace*{10pt}}			    % Set distance between LOF title and list
\listoffigures
%\setlength{\cftbeforeloftitleskip}{0cm}		% ? 
%\setlength\cftafterloftitleskip{-2cm}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{List of Figures}

%Insert empty page after table the list of figures
\newpage\null\thispagestyle{empty}\newpage

% Add List of Tables
\renewcommand{\cfttabfont}{Table }				% Add "Figure" to the LOF
\renewcommand\cfttabaftersnum{:} 				% Put ":" after the figure num 
\setlength{\cfttabindent}{0pt}					% Remove left indent
\setlength\cftbeforetabskip{-0.2cm}				% Space between tables
\addtocontents{lot}{\vspace*{10pt}}			    % Set distance between LOT title and list
\listoftables{}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{List of Tables}

%Insert empty page after the list of tables 
\newpage\null\thispagestyle{empty}\newpage

% Print table of acronyms
\printglossary[type=\acronymtype, title={Table of Acronyms}, nonumberlist, style=longheader]

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Acronyms}

%Insert empty page after table of acronyms
\newpage\null\thispagestyle{empty}

% Add Table of Symbols
%\chapter*{Table of Symbols} \label{sec:symbols}
\mbox{}
\nomwithdim{B}{\( F \)}{Force}{L}{$N$}
\nomwithdim{B}{\( g \)}{Gravitational acceleration}{}{$m/s^2$}
\nomwithdim{G}{\( \alpha \)}{Angle of attack}{}{$rad$}
\nomwithdim{G}{\( \zeta \)}{Damping of a linear second order system}{}{--}
\nomwithdim{S}{\( m \)}{Variable related to pitch moment}{}{}
\nomwithdim{S}{\( W \)}{Wind}{}{}
\renewcommand{\nomname}{Table of Symbols}
\printnomenclature[6em]

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Symbols}

%Insert empty page after table of symbols
\newpage\null\thispagestyle{empty}\newpage

% Beginning of the core text 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Activate arabic page numbering from here on
\pagenumbering{arabic}

% Delete the word "Chapter" leaving only the number of the chapter
\titleformat{\chapter}
{\normalfont\chapfnt\bfseries}{\thechapter}{1em}{\chapfnt} 	% set font size
\titlespacing*{\chapter}{0cm}{-1.2cm}{0cm}					% set spacing

% Set subsection font size (11pt) and spacing
\newcommand{\ssecfnt}{\fontsize{11}{14}}
\titleformat{\subsection}
{\normalfont\ssecfnt\bfseries}{\thesubsection}{1em}{}
\titlespacing*{\subsection}{0cm}{-0cm}{0cm}					% set spacing

% Activate default fancy design (chapter number, chapter)
\pagestyle{fancy} 
\renewcommand{\chaptermark}[1]{\markboth{\ \thechapter \ #1}{}}

% Change separator in the figure and table captures from "." to "-"
\renewcommand{\thefigure}{\thechapter-\arabic{figure}}
\renewcommand{\thetable}{\thechapter-\arabic{table}}

\chapter{Introduction} \label{cha:introduction}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy}
\chaptermark{Introduction}

The Introduction shall give a short overview over the chapters. Here, this section is used to explain the formatting of thesis papers at FSD.

\section{General} \label{sec:general}

This template works best, when using “English” as Language in Word, since otherwise some references to styles might not be processed correctly. 
First of all, enter your name and the title of the thesis in the word ‘file’ tab (see Figure \ref{fig:word}). By doing this, all occurrences of the name and tile in this document will be replaced accordingly when refreshing the document.

\begin{figure}[H]
  \centering 
  \includegraphics[width=1 \linewidth]{figs/fig_word.pdf}
  % Figure description is left aligned)
  \captionsetup{justification=raggedright, singlelinecheck=off, font=bf, belowskip=-0.5cm}
  \caption[Titel und Autor als Dokumenteigenschaften]{Titel und Autor als Dokumenteigenschaften}
  \label{fig:word}
\end{figure}

Enter the German title of the thesis on the first page, and choose the appropriate type from the drop-down menu. Matriculation number and supervisor have to be filled in, and the date when the thesis is handed in can be chosen via an interactive element.

In the text of the Statutory Declaration, the type of work and hand-in date have to be filled in.

On the following page, a German and an English Abstract have to be included, followed by a table of contents for all headings Furthermore, tables for figures and tables have to be included, and the explanation of abbreviations and the nomenclature have to be included in the form of tables.

The text of all chapter is to be written in justified alignment, with a font size of 11 and in ‘Arial’. The font color is black, and the line spacing is to be set to 1.15 (the “Normal” Style in this template). Names (file names, name of bus objects etc.) are to be written in italics (“Emphasis” Style in this template).

Headings are numerated with Arabic characters and are again to be written in Arial. The font sizes are as follows (Microsoft standard with black font and written in Arial):
\begin{description}[labelindent=1cm, topsep=0pt, noitemsep]
	%\setlength{\itemsep}{-10pt}
	\item First level = Chapters: 14, bold (Style “Heading 1”)
	\item Second level: 13, bold (Style “Heading 2”)
	\item Third level: 11, bold (Style “Heading 3”)
	\item Fourth level: 11, bold, italic (Style “Heading 4”)
	\item Fifth level: 11, non-bold, non-italic (Style “Heading 5”)
\end{description}
Every chapter (style ``Heading 1'') automatically starts on a new page. Abstracts, Contents and Lists, the first chapter and the bibliography have to start on an uneven page ($\rightarrow$ ``section break (odd page)'')

References to sections, figures, tables and equations are to be done as cross references. Examples for references can be found in section \textbf{Fehler! Verweisquelle konnte nicht gefunden werden..}

The bibliography is to be included according to the IEEE style, and references to sources are preferably to be included in square brackets \cite{Handbook}, \cite{Cooper}. The respective bibliography item has to describe the source clearly without ambiguity and citations from sources have to be marked with quotation marks.

Headers and footers are different for even and uneven pages. The header contains the FSD and TUM logo, the current heading number and heading text for the first level. The footer contains the topic, name of the author and page number.

The page numbers of the chapters (introduction until conclusion) are numerated in Arabic characters. The rest are numerated with Latin characters, where the enumeration starts anew from 1 with the Bibliography.

\section{Figures, tables and equations} \label{sec:figs_tabs_eqs}

Figures, tables and equations are to be centered in a separate line. The file format for figures should be *.emf (enhanced windows metafile) and captions for figures and tables are to be inserted below and centered. The font of the caption is Arial (bold) and the font size is 9. Equations are centered with the aid of invisible tables: The middle column contains the equation, the right column the equation number. The font of the equation number is Arial (bold) and the font-size is 9. In every caption, the chapter number is to be included, and with the beginning of every new chapter, the enumeration starts again at 1. Due to the complexity of this layout element, the best way to create new equations is by copying and pasting an existing equation. The equation then first is displayed to be the same as the one copied from. This is updated when performing printing or print preview, or by selecting the equation number and pressing the F9-key.

\begin{figure}[H]
  \centering 
  \includegraphics[width=1 \linewidth]{figs/fig_sample_1.pdf}
  % Figure description is left aligned
  \captionsetup{justification=raggedright, singlelinecheck=off, font=bf, belowskip=-0.5cm}
  \caption[Sample figure 1]{Sample figure 1}
  \label{fig:sample_1}
\end{figure}

Here, it is referenced to Figure \ref{fig:sample_1} (cross-reference, Reference Type: Figure, Insert reference to: only label and number)

% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  \centering
  \begin{tabular}{c c} 
    Column 1 & Column 2  \\ [0.5ex] 
    Content & Content \\ 
    Content & Content \\
    Content & Content \\
    Content & Content \\ [1ex] 
  \end{tabular}
  \captionsetup{font=bf, belowskip=-0.5cm}
  \caption[Sample table 1]{Sample table 1}
  \label{table:tab_1}
\end{table}

This is a reference to Table \ref{table:tab_1}. (Cross-reference, Reference Type: Figure, Insert reference to: only label and number)

% Insert equation
\begin{equation}
	R_m = 10 + \Big(\frac{1}{-8.3^{n-1}}\Big) \displaystyle\prod_{i=1}^{n} (R_i-10)
	\label{eq:eq_1}
\end{equation}

Reference to equation \ref{eq:eq_1}. (Cross-reference, Reference Type: Equation, Insert reference to: entire caption) 
The following section 2 contains further example text, figures, tables and equations. 
In section 3 some concluding remarks can be found. Here, we use the acronym \acrfull{ADF}. The second acronym is \acrfull{ADI}. After the first usage of the 1st acronym, only the short version is used: \acrshort{ADF}.

\chapter{Section 2} \label{sec:section_2}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy}
\chaptermark{Section 2}

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.

\section{Subsection 2.1} \label{sec:subsection_21}

\subsection{Subsection 2.1.1} \label{sec:subsection_211}

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.

\begin{figure}[H]
  \centering 
  \includegraphics[width=1 \linewidth]{figs/fig_sample_1.pdf}
  % Figure description is left aligned
  \captionsetup{justification=raggedright, singlelinecheck=off, font=bf, belowskip=-0.5cm}
  \caption[Sample figure 2]{Sample figure 2}
  \label{fig:sample_2}
\end{figure}

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.

Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.

% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  \centering
  % Spacing added between columns
  \begin{tabular}{c c@{\hskip 1.5in} c} 
    & Column 1 & Column 2  \\ [0.5ex] 
    Line 1 & Content & Content \\ 
    Line 2 & Content & Content \\
    Line 3 & Content & Content \\ [1ex] 
  \end{tabular}
  \captionsetup{font=bf, belowskip=-0.5cm}
  \caption[Sample table 2]{Sample table 2}
  \label{table:tab_2}

\end{table}
Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.

\subsection{Subsection 2.1.2} \label{sec:subsection_212}

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.

% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  \centering
  % Spacing added between columns
  \begin{tabular}{c c@{\hskip 1in} c} 
    & Column 1 & Column 2  \\ [0.5ex] 
    Line 1 & Content & Content \\ 
    Line 2 & Content & Content \\
    Line 3 & Content & Content \\
    Line 4 & Content & Content \\ [1ex] 
  \end{tabular}
  \captionsetup{font=bf, belowskip=-0.5cm}
  \caption[Sample table 3]{Sample table 3}
  \label{table:tab_3}
\end{table}

Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat. Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.

% Insert equation
\begin{equation}
	R_m = 10 + \Big(\frac{1}{-8.3^{n-1}}\Big) \displaystyle\prod_{i=1}^{n} (R_i-10)
	\label{eq:eq_2}
\end{equation}

Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.

% Insert equation
\begin{equation}
	R_m = 10 + \Big(\frac{1}{-8.3^{n-1}}\Big) \displaystyle\prod_{i=1}^{n} (R_i-10)
	\label{eq:eq_3}
\end{equation}

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat. Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.

\section{Subsection 2.2} \label{sec:subsection_22}

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.

\chapter{Conclusions and perspective} \label{sec:conclusions}

In this chapter, concluding remarks should be mentioned and an outlook to future work shall be given.

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy}
\chaptermark{Conclusions and Perspective}

\newpage

% Activate and reset roman page numbering
\pagenumbering{roman}
\setcounter{page}{1}

% Add references
\renewcommand\bibname{References}		% Rename Bibliography to References
\bibliographystyle{plain}
\bibliography{Literature}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{References}

\chapter*{Appendix} \label{sec:appendix}
% Add Appendix chapter manually to the Table of Contents because Latex doesn't automatically include nonnumerated (...*) chapters/sections to the TOC
\addcontentsline{toc}{chapter}{Appendix}

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
\chaptermark{Appendix}

% End of the document
\end{document}

### 2019-12-27 Paper_EV/Paper_EV.tex
Template added, Simulink model updated (Ts changed from 0.01 to 1/500)

--- 2019-12-27 Other/FSD_templates/Latex_Template/Template.tex
@@
 %
-% pdflatex Template
-% makeindex Template.nlo -s nomencl.ist -o Template.nls
-% makeindex Template.acn -s Template.ist -t Template.alg -o Template.acr
-% makeindex Template.glo -s Template.ist -t Template.glg -o Template.gls
-% pdflatex Template
-% pdflatex Template
+% pdflatex Paper_EV
+% makeindex Paper_EV.nlo -s nomencl.ist -o Paper_EV.nls (Table of Symbols)
+% makeindex Paper_EV.acn -s Paper_EV.ist -t Paper_EV.alg -o Paper_EV.acr (Table of Acronyms)
+% makeindex Paper_EV.glo -s Paper_EV.ist -t Paper_EV.glg -o Paper_EV.gls
+% pdflatex Paper_EV
+% pdflatex Paper_EV
 %
@@
 % Foot (11 pt font size and 12 pt line spacing)
-\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Title\\First Name Last Name}
+\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implem. and Eval. of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}
 \fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage \thinspace / \lastpageref{LastPages}}
@@
 % Foot
-\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Title\\First Name Last Name}%
+\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implem. and Eval. of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}%
 \fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage}%
@@
 \section*{Statutory Declaration}
-I, , declare on oath towards the Institute of Flight System Dynamics of Technische Universität München, that I have prepared the present BA/SA/MA independently and with the aid of nothing but the resources listed in the bibliography.
+I, Evghenii Volodscoi, declare on oath towards the Institute of Flight System Dynamics of Technische Universität München, that I have prepared the present Semester Thesis independently and with the aid of nothing but the resources listed in the bibliography.
 \\
@@
 
-The Introduction shall give a short overview over the chapters. Here, this section is used to explain the formatting of thesis papers at FSD.
+\section{Motivation} \label{sec:motivation}
 
-\section{General} \label{sec:general}
+\section{Contribution of the Thesis} \label{sec:contribution_ofthe_thesis}
 
-This template works best, when using “English” as Language in Word, since otherwise some references to styles might not be processed correctly. 
-First of all, enter your name and the title of the thesis in the word ‘file’ tab (see Figure \ref{fig:word}).
-By doing this, all occurrences of the name and tile in this document will be replaced accordingly when refreshing the document.
+\section{Structure of the Thesis} \label{sec:structure_ofthe_thesis}
 
-\begin{figure}[H]
-  \centering 
-  \includegraphics[width=1 \linewidth]{figs/fig_word.pdf}
-  % Figure description is left aligned)
-  \captionsetup{justification=raggedright, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-  \caption[Titel und Autor als Dokumenteigenschaften]{Titel und Autor als Dokumenteigenschaften}
-  \label{fig:word}
-\end{figure}
+\chapter{Theoretical Background} \label{cha:theoretical_background}
 
-Enter the German title of the thesis on the first page, and choose the appropriate type from the drop-down menu.
-Matriculation number and supervisor have to be filled in, and the date when the thesis is handed in can be chosen via an interactive element.
+\section{Nonlinear Dynamic Inversion} \label{sec:ndi}
 
-In the text of the Statutory Declaration, the type of work and hand-in date have to be filled in.
-
-On the following page, a German and an English Abstract have to be included, followed by a table of contents for all headings Furthermore, tables for figures and tables have to be included, and the explanation of abbreviations and the nomenclature have to be included in the form of tables.
-
-The text of all chapter is to be written in justified alignment, with a font size of 11 and in ‘Arial’.
-The font color is black, and the line spacing is to be set to 1.15 (the “Normal” Style in this template).
-Names (file names, name of bus objects etc.) are to be written in italics (“Emphasis” Style in this template).
-
-Headings are numerated with Arabic characters and are again to be written in Arial. The font sizes are as follows (Microsoft standard with black font and written in Arial):
-\begin{description}[labelindent=1cm, topsep=0pt, noitemsep]
-	%\setlength{\itemsep}{-10pt}
-	\item First level = Chapters: 14, bold (Style “Heading 1”)
-	\item Second level: 13, bold (Style “Heading 2”)
-	\item Third level: 11, bold (Style “Heading 3”)
-	\item Fourth level: 11, bold, italic (Style “Heading 4”)
-	\item Fifth level: 11, non-bold, non-italic (Style “Heading 5”)
-\end{description}
-Every chapter (style ``Heading 1'') automatically starts on a new page.
-Abstracts, Contents and Lists, the first chapter and the bibliography have to start on an uneven page ($\rightarrow$ ``section break (odd page)'')
-
-References to sections, figures, tables and equations are to be done as cross references. Examples for references can be found in section \textbf{Fehler! Verweisquelle konnte nicht gefunden werden..}
-
-The bibliography is to be included according to the IEEE style, and references to sources are preferably to be included in square brackets \cite{Handbook}, \cite{Cooper}.
-The respective bibliography item has to describe the source clearly without ambiguity and citations from sources have to be marked with quotation marks.
-
-Headers and footers are different for even and uneven pages.
-The header contains the FSD and TUM logo, the current heading number and heading text for the first level.
-The footer contains the topic, name of the author and page number.
-
-The page numbers of the chapters (introduction until conclusion) are numerated in Arabic characters.
-The rest are numerated with Latin characters, where the enumeration starts anew from 1 with the Bibliography.
-
-\section{Figures, tables and equations} \label{sec:figs_tabs_eqs}
-
-Figures, tables and equations are to be centered in a separate line.
-The file format for figures should be *.emf (enhanced windows metafile) and captions for figures and tables are to be inserted below and centered.
-The font of the caption is Arial (bold) and the font size is 9.
-Equations are centered with the aid of invisible tables: The middle column contains the equation, the right column the equation number.
-The font of the equation number is Arial (bold) and the font-size is 9.
-In every caption, the chapter number is to be included, and with the beginning of every new chapter, the enumeration starts again at 1.
-Due to the complexity of this layout element, the best way to create new equations is by copying and pasting an existing equation.
-The equation then first is displayed to be the same as the one copied from.
-This is updated when performing printing or print preview, or by selecting the equation number and pressing the F9-key.
-
-\begin{figure}[H]
-  \centering 
-  \includegraphics[width=1 \linewidth]{figs/fig_sample_1.pdf}
-  % Figure description is left aligned
-  \captionsetup{justification=raggedright, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-  \caption[Sample figure 1]{Sample figure 1}
-  \label{fig:sample_1}
-\end{figure}
-
-Here, it is referenced to Figure \ref{fig:sample_1} (cross-reference, Reference Type: Figure, Insert reference to: only label and number)
-
-% Add table ([...ex] adds some extra vertical spacing after corresponding row)
-\begin{table}[H]
-  \centering
-  \begin{tabular}{c c} 
-    Column 1 & Column 2  \\ [0.5ex] 
-    Content & Content \\ 
-    Content & Content \\
-    Content & Content \\
-    Content & Content \\ [1ex] 
-  \end{tabular}
-  \captionsetup{font=bf, belowskip=-0.5cm}
-  \caption[Sample table 1]{Sample table 1}
-  \label{table:tab_1}
-\end{table}
-
-This is a reference to Table \ref{table:tab_1}. (Cross-reference, Reference Type: Figure, Insert reference to: only label and number)
-
-% Insert equation
-\begin{equation}
-	R_m = 10 + \Big(\frac{1}{-8.3^{n-1}}\Big) \displaystyle\prod_{i=1}^{n} (R_i-10)
-	\label{eq:eq_1}
-\end{equation}
-
-Reference to equation \ref{eq:eq_1}. (Cross-reference, Reference Type: Equation, Insert reference to: entire caption) 
-The following section 2 contains further example text, figures, tables and equations. 
-In section 3 some concluding remarks can be found.
-Here, we use the acronym \acrfull{ADF}.
-The second acronym is \acrfull{ADI}.
-After the first usage of the 1st acronym, only the short version is used: \acrshort{ADF}.
-
-\chapter{Section 2} \label{sec:section_2}
+\section{Incremental Nonlinear Dynamic Inversion} \label{sec:indi}
 
@@
 \thispagestyle{fancy}
-\chaptermark{Section 2}
+\chaptermark{Theoretical Background}
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-
-\section{Subsection 2.1} \label{sec:subsection_21}
-
-\subsection{Subsection 2.1.1} \label{sec:subsection_211}
-
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-
-\begin{figure}[H]
-  \centering 
-  \includegraphics[width=1 \linewidth]{figs/fig_sample_1.pdf}
-  % Figure description is left aligned
-  \captionsetup{justification=raggedright, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-  \caption[Sample figure 2]{Sample figure 2}
-  \label{fig:sample_2}
-\end{figure}
-
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-
-% Add table ([...ex] adds some extra vertical spacing after corresponding row)
-\begin{table}[H]
-  \centering
-  % Spacing added between columns
-  \begin{tabular}{c c@{\hskip 1.5in} c} 
-    & Column 1 & Column 2  \\ [0.5ex] 
-    Line 1 & Content & Content \\ 
-    Line 2 & Content & Content \\
-    Line 3 & Content & Content \\ [1ex] 
-  \end{tabular}
-  \captionsetup{font=bf, belowskip=-0.5cm}
-  \caption[Sample table 2]{Sample table 2}
-  \label{table:tab_2}
-
-\end{table}
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-
-\subsection{Subsection 2.1.2} \label{sec:subsection_212}
-
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-
-% Add table ([...ex] adds some extra vertical spacing after corresponding row)
-\begin{table}[H]
-  \centering
-  % Spacing added between columns
-  \begin{tabular}{c c@{\hskip 1in} c} 
-    & Column 1 & Column 2  \\ [0.5ex] 
-    Line 1 & Content & Content \\ 
-    Line 2 & Content & Content \\
-    Line 3 & Content & Content \\
-    Line 4 & Content & Content \\ [1ex] 
-  \end{tabular}
-  \captionsetup{font=bf, belowskip=-0.5cm}
-  \caption[Sample table 3]{Sample table 3}
-  \label{table:tab_3}
-\end{table}
-
-Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-
-% Insert equation
-\begin{equation}
-	R_m = 10 + \Big(\frac{1}{-8.3^{n-1}}\Big) \displaystyle\prod_{i=1}^{n} (R_i-10)
-	\label{eq:eq_2}
-\end{equation}
-
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-
-% Insert equation
-\begin{equation}
-	R_m = 10 + \Big(\frac{1}{-8.3^{n-1}}\Big) \displaystyle\prod_{i=1}^{n} (R_i-10)
-	\label{eq:eq_3}
-\end{equation}
-
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-
-\section{Subsection 2.2} \label{sec:subsection_22}
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-
-\chapter{Conclusions and perspective} \label{sec:conclusions}
-
-In this chapter, concluding remarks should be mentioned and an outlook to future work shall be given.
+\chapter{Implementation} \label{cha:implementation}
 
@@
 \thispagestyle{fancy}
-\chaptermark{Conclusions and Perspective}
+\chaptermark{Implementation}
+
+\section{Research Quadrotor} \label{sec:research_quadrotor}
+
+\section{Simulink Model} \label{sec:simulink_model}
+
+\subsection{Purpose} \label{subsec:purpose}
+
+\subsection{Structure} \label{subsec:Structure}
+
+\subsection{Simulation Results} \label{subsec:simulation_results}
+
+\section{Implementation on Hardware} \label{sec:implementation_on_hardware}
+
+\subsection{Testing with contact Forces and Moments} \label{subsec:testing_with_fandm}
+
+\chapter{Results} \label{cha:results}
+
+% Manually add Chapter names to the header (per default not included by Latex)
+\thispagestyle{fancy}
+\chaptermark{Results}
+
+\chapter{Discussion} \label{cha:discussion}
+
+% Manually add Chapter names to the header (per default not included by Latex)
+\thispagestyle{fancy}
+\chaptermark{Discussion}
 
@@
 \thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
+\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
 \chaptermark{Appendix}

### 2019-12-27 Simulink/Crazyflie_Simulation/inner_pd_cs.m

@@ -1,0 +1,44 @@
+function inner_pd_cs(k_omega_in, k_eta_in)
+
+    clc;
+    Ts = 0.01;                                      % Sample time
+    T = 1/15;                                       % Actuator time constant
+
+    % Actuator dynamic koefficients
+    C1 = Ts/(Ts+2*T);
+    C2 = (Ts-2*T)/(Ts+2*T);
+
+    % Generate different colors for plotting
+    colors = jet(size(k_omega_in, 2)*size(k_eta_in, 2));
+    clr = 1:(size(k_omega_in, 2)*size(k_eta_in, 2)); 
+    i  = 0;
+
+    % Iterative computation of poles
+    for k_om=k_omega_in
+        for k_et=k_eta_in
+            i = i+1;
+
+            % Define transfer function eta_ref -> eta (Control Systems Toolbox)
+            z = tf('z', Ts);
+            K_omega = k_om; 
+            K_eta = k_et; 
+            TF_etaref_eta = ( (Ts^2*K_eta*K_omega*C1)*z^3 + ...  
+                              (Ts^2*K_eta*K_omega*C1)*z^2 ) / ...
+                            ( (Ts^2*K_eta*K_omega*C1 + Ts*K_omega*C1 + 1)*z^3 + ... 
+                              (C2-2)*z^2 + (-Ts*K_omega*C1 - 2*C2 + 1)*z + C2 );
+
+            % Compute poles of TF_etaref_eta
+            display(['K_omega=', num2str(K_omega), ', K_eta=', num2str(K_eta)])
+            p = pole(TF_etaref_eta)
+
+            % Plot poles
+            name = ['KOmega= ', num2str(K_omega), ', KEta= ', num2str(K_eta)];
+            pzmap(TF_etaref_eta); hold on; axis equal;
+
+            % Plot settings
+            grid on; 
+
+        end
+    end
+
+end

### 2019-12-27 Simulink/Crazyflie_Simulation/outer_pd_cs.m

@@ -1,0 +1,55 @@
+function outer_pd_cs(k_dxi_in, k_xi_in, k_omega_fix, k_eta_fix)
+
+    clc;
+    K_omega = k_omega_fix;
+    K_eta = k_eta_fix;
+
+    Ts = 0.01;                                      % Sample time
+    T = 1/15;                                       % Actuator time constant
+
+    % Actuator dynamic koefficients
+    C1 = Ts/(Ts+2*T);
+    C2 = (Ts-2*T)/(Ts+2*T);
+
+    % Generate different colors for plotting
+    colors = jet(size(k_dxi_in, 2)*size(k_xi_in, 2));
+    clr = 1:(size(k_dxi_in, 2)*size(k_xi_in, 2)); 
+    i  = 0;
+
+    % Iterative computation of poles
+    for k_dxi=k_dxi_in
+        for k_xi=k_xi_in
+            i = i+1;
+
+            % Define transfer function xi_ref -> xi (Control Systems Toolbox)
+            z = tf('z', Ts);
+            K_d_xi = k_dxi;
+            K_xi = k_xi;
+
+            TF_etaref_eta = ( (Ts^2*K_eta*K_omega*C1)*z^3 + ...  
+                         (Ts^2*K_eta*K_omega*C1)*z^2 ) / ...
+                       ( (Ts^2*K_eta*K_omega*C1 + Ts*K_omega*C1 + 1)*z^3 + ... 
+                         (C2-2)*z^2 + (-Ts*K_omega*C1 - 2*C2 + 1)*z + C2 );
+
+            TF_dxierr_dxi = K_d_xi * TF_etaref_eta * Ts*z/(z-1);     % Open loop
+            TF_dxiref_dxi = TF_dxierr_dxi / (1 + TF_dxierr_dxi);     % Closed loop
+
+            TF_xierr_xi = K_xi * TF_dxiref_dxi * Ts*z/(z-1);         % Open loop
+            TF_xiref_xi = TF_xierr_xi / (1 + TF_xierr_xi);           % Closed
+
+            % Compute poles of TF_xiref_xi
+            display(['K_dxi=', num2str(k_dxi), ', K_xi=', num2str(k_xi)])
+            p = pole(TF_xiref_xi)
+
+            % Plot poles
+            name = ['KDxi= ', num2str(k_dxi), ', KXi= ', num2str(k_xi)];
+            pzmap(TF_xiref_xi); hold on;
+
+            % Plot settings
[…]

### 2019-12-27 Simulink/Crazyflie_Simulation/set_params.m

@@ -64,7 +64,7 @@ M2 =  [  0       0      0       0
 % Filter parameters and coefficients
 omega_n = 50;       % in [rad/s]
 zeta = 0.55;        
-Ts = 0.01;          % sample time in [s]
+Ts = 1/500;          % sample time in [s]
 
 N_0 = omega_n^2;
 N_1 = 2*omega_n^2;
@@ -75,7 +75,7 @@ D_1 = -8/(Ts^2) + 2*omega_n^2;
 D_2 = 4/(Ts^2) - 4*zeta*omega_n/Ts + omega_n^2; 
 
 % Outer INDI
-T_init = m_CF*0,1;      % T(t=0)!=0, prevents landing in singularity
+T_init = m_CF*0.1;      % T(t=0)!=0, prevents landing in singularity
 
 % PD gains (inner loop) 
 K_omega = 10; 

### 2020-01-07 Other/FSD_templates/Latex_Template_backup/Template/Template.tex
pd_outer_cs adjusted + some changes in the folder structure

--- 2019-12-27 Other/FSD_templates/Latex_Template/Template.tex
@@
 %
-% Compile Template in following order:
+% TODOs:
+% - Write instructions (what and where to fill in)
 %
-% pdflatex Template
-% makeindex Template.nlo -s nomencl.ist -o Template.nls
-% makeindex Template.acn -s Template.ist -t Template.alg -o Template.acr
-% makeindex Template.glo -s Template.ist -t Template.glg -o Template.gls
-% pdflatex Template
-% pdflatex Template
-%
-%
+% - References 
+% - Style of the List of Symbols
+
 %#################################################################################
-%#################################################################################
-%#################################################################################
-
 % Preamble
@@
 % This block prints only the chapter number and the chapter name, not the word "Chapter"
-%\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\ \thechapter. \ #1}}{}}
+\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\ \thechapter. \ #1}}{}}
 % Clear current page style 
@@
 
-% TODO
 % Package for using acronyms 
-%\usepackage[printonlyused]{acronym}
-%\renewcommand\acsfont{\textnormal}	% Set non-bold font of the acronym units
+\usepackage[printonlyused]{acronym}
+\renewcommand\acsfont{\textnormal}	% Set non-bold font of the acronym units
 
@@
 
-% Package for edditing TOC, LOF and LOT
+% Package for setting space between units in TOC, LOF...
 \usepackage[titles]{tocloft}
@@
 
-% Package for acronyms
-\usepackage[acronym, automake, nopostdot, nogroupskip]{glossaries}
-\setlength{\LTleft}{-0.15cm}			% left justified
-\renewcommand*{\arraystretch}{1.4}		% vertical distance between entries, default is 1
-% List
-\newacronym{ADF}{ADF}{Automatic Direction Finder}
-\newacronym{ADI}{ADI}{Automatic Direction Indicator}
-% Make gls
-\renewcommand*\entryname{Acronym}
-\makeglossaries
+% Package for edditing TOC, LOF and LOT
+\usepackage{tocloft}
 
-% Package for setting up the list of symbols
-%https://tex.stackexchange.com/questions/112884/how-to-achieve-nomenclature-entries-like-symbol-description-dimension-and-uni
-\usepackage{nomencl,etoolbox,ragged2e,siunitx}
-%
-\newcommand{\DimensUnits}[2]{\makebox[1em]{#1}\makebox[4em]{#2\hfill}\ignorespaces}
-\newcommand{\insertnomheaders}{\item[\bfseries Symbol]\DimensUnits{}{\textbf{Unit}}\textbf{Description}}
-%
-\renewcommand\nomgroup[1]{%
-  \item[\large\bfseries
-  \ifstrequal{#1}{A}{Acronyms}{%
-  \ifstrequal{#1}{B}{Latin Letters}{%
-  \ifstrequal{#1}{G}{Greek Letters}{%
-  \ifstrequal{#1}{S}{Indices}{% 
-  \ifstrequal{#1}{U}{Subscripts}{%   
-  \ifstrequal{#1}{X}{Other Symbols}{}}}}}}]
-  \insertnomheaders
-  }
-%
-\renewcommand*{\nompreamble}{\markboth{\nomname}{\nomname}}
-% parbox - Description
-\newcommand{\nomdescr}[1]{\parbox[t]{10cm}{\RaggedRight #1}}
-\newcommand{\nomwithdim}[5]{\nomenclature[#1]{#2}{\DimensUnits{}{#5}\nomdescr{#3}}}
-%
-\makenomenclature
-
-%#################################################################################%#################################################################################%#################################################################################
-
+%#################################################################################
 \begin{document}
@@
 \thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
 \chaptermark{Statutory Declaration}
@@
 \thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
 \chaptermark{Abstract}
@@
 \thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
 \chaptermark{Table of Contents}
@@
 \thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
 \chaptermark{List of Figures}
@@
 \thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
 \chaptermark{List of Tables}
@@
 
-% Print table of acronyms
-\printglossary[type=\acronymtype, title={Table of Acronyms}, nonumberlist, style=longheader]
+% Add Table of Acronyms 
+\chapter*{Table of Acronyms} \label{sec:acronyms}
+\textbf{Acronym}\hspace{3.3cm}\textbf{Description}
+\vspace*{-2mm}	% vertical space 
+\begin{acronym}[ADF\hspace{4cm}]\itemsep=0pt 	% in [] supposed to be the largest word
+	\acro{ADF}{Automatic Direction Finder}
+	\acro{ADI}{Automatic Direction Indicator}
+\end{acronym}
 
@@
 \thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
 \chaptermark{Table of Acronyms}
@@
 %Insert empty page after table of acronyms
-\newpage\null\thispagestyle{empty}
+\newpage\null\thispagestyle{empty}\newpage
 
 % Add Table of Symbols
-%\chapter*{Table of Symbols} \label{sec:symbols}
-\mbox{}
-\nomwithdim{B}{\( F \)}{Force}{L}{$N$}
-\nomwithdim{B}{\( g \)}{Gravitational acceleration}{}{$m/s^2$}
-\nomwithdim{G}{\( \alpha \)}{Angle of attack}{}{$rad$}
-\nomwithdim{G}{\( \zeta \)}{Damping of a linear second order system}{}{--}
-\nomwithdim{S}{\( m \)}{Variable related to pitch moment}{}{}
-\nomwithdim{S}{\( W \)}{Wind}{}{}
-\renewcommand{\nomname}{Table of Symbols}
-\printnomenclature[6em]
+\chapter*{Table of Symbols} \label{sec:symbols}
 
@@
 \thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
-\chaptermark{Table of Symbols}
+\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
+\chaptermark{List of Symbols}
 
-%Insert empty page after table of symbols
+%Insert empty page after table of acronyms
 \newpage\null\thispagestyle{empty}\newpage
@@
 \pagestyle{fancy} 
-\renewcommand{\chaptermark}[1]{\markboth{\ \thechapter \ #1}{}}
+\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\ \thechapter. \ #1}}{}}
 
@@
 
-The bibliography is to be included according to the IEEE style, and references to sources are preferably to be included in square brackets \cite{Handbook}, \cite{Cooper}.
+The bibliography is to be included according to the IEEE style, and references to sources are preferably to be included in square brackets \cite{Alberi2017}.
 The respective bibliography item has to describe the source clearly without ambiguity and citations from sources have to be marked with quotation marks.
@@
 In section 3 some concluding remarks can be found.
-Here, we use the acronym \acrfull{ADF}.
-The second acronym is \acrfull{ADI}.
-After the first usage of the 1st acronym, only the short version is used: \acrshort{ADF}.
+Here, we use the acronym \ac{ADF}.
+The second acronym is \ac{ADI}.
+After the first usage of the 1st acronym, only the short version is displayed: \ac{ADF}.
 
@@
 % Add references
-\renewcommand\bibname{References}		% Rename Bibliography to References
-\bibliographystyle{plain}
-\bibliography{Literature}
-
-% Manually add Chapter names to the header (per default not included by Latex)
-\thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
-\chaptermark{References}
+%\renewcommand\bibname{References}		% Rename Bibliography to References
+%\bibliographystyle{plain}
 

### 2020-01-07 Paper_EV/Paper_EV.tex
pd_outer_cs adjusted + some changes in the folder structure

@@
 %
+% TODO:
+% - Title page: Dr. -> Dr. ir.
 %
@@
 
+\section{General Equations of Motion} \label{sec:eqs_motion}
+General: \\
+- Linear Momentum\\
+- Angular Momentum\\
+- Attitude differential equations\\
+- Position differential equations\\
+- External forces and moments
+
+with some of the used assumptions
+
 \section{Nonlinear Dynamic Inversion} \label{sec:ndi}
 
+- Theory from Sieberling paper.
+
 \section{Incremental Nonlinear Dynamic Inversion} \label{sec:indi}
+
+- Here only the general principle is provided, next subsections show the full derivation of the two controller loops.
+
+\subsection{INDI inner loop} \label{subsec: indi_inner}
+
+- Derivation of the inner INDI loop (detailed equations).
+
+\subsection{INDI outer loop} \label{subsec: indi_outer}
+
+- Derivation of the outer INDI loop (detailed equations).
 
@@
 
+- Some facts about Crazyflie hardware (foto, uC frequency, weight, length)
+
 \section{Simulink Model} \label{sec:simulink_model}
@@
 
+- Estimation of relevant components (Matrices...)\\
+- Testing of the PD-gains\\
+- Testing the filter
+
 \subsection{Structure} \label{subsec:Structure}
+- Parameters\\
+- Actuator dynamics\\
+- Filter\\
+- Images of the Simulink model
 
@@
 \section{Implementation on Hardware} \label{sec:implementation_on_hardware}
+
+\subsection{Structure of the Code} \label{subsec:structure_ofthe_code}
 

### 2020-01-07 Simulink/Crazyflie_Simulation/outer_pd_cs.m

@@ -32,12 +32,15 @@ function outer_pd_cs(k_dxi_in, k_xi_in, k_omega_fix, k_eta_fix)
                          (C2-2)*z^2 + (-Ts*K_omega*C1 - 2*C2 + 1)*z + C2 );
 
             TF_dxierr_dxi = K_d_xi * TF_etaref_eta * Ts*z/(z-1);     % Open loop
-            TF_dxiref_dxi = TF_dxierr_dxi / (1 + TF_dxierr_dxi);     % Closed loop
-
+            %TF_dxiref_dxi = TF_dxierr_dxi / (1 + TF_dxierr_dxi)     % Closed loop computed wrong (see "Using FEEDBACK to Close Feedback Loops" documentation)
+            TF_dxiref_dxi = feedback(TF_dxierr_dxi, 1);              % Closed loop
+            
             TF_xierr_xi = K_xi * TF_dxiref_dxi * Ts*z/(z-1);         % Open loop
-            TF_xiref_xi = TF_xierr_xi / (1 + TF_xierr_xi);           % Closed
-
+            %TF_xiref_xi = TF_xierr_xi / (1 + TF_xierr_xi);          % Closed loop computed wrong (see "Using FEEDBACK to Close Feedback Loops" documentation)
+            TF_xiref_xi = feedback(TF_xierr_xi, 1);                  % Closed loop
+                
             % Compute poles of TF_xiref_xi
+            display(['K_omega=' num2str(K_omega), ' K_eta=' num2str(K_eta)])
             display(['K_dxi=', num2str(k_dxi), ', K_xi=', num2str(k_xi)])
             p = pole(TF_xiref_xi)
 

### 2020-01-07 temp/controller_indi.c

@@ -1,0 +1,363 @@
+/*
+ *
+ * Copyright (c) 2019 Ewoud Smeur and Andre Luis Ogando Paraense
+ *
+ * This program is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, in version 3.
+ *
+ * This program is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with this program. If not, see <http://www.gnu.org/licenses/>.
+ *
+ * This control algorithm is the Incremental Nonlinear Dynamic Inversion (INDI)
+ * controller.
+ *
+ * This is an implementation of the publication in the
+ * journal of Control Guidance and Dynamics: Adaptive Incremental Nonlinear
+ * Dynamic Inversion for Attitude Control of Micro Aerial Vehicles
+ * http://arc.aiaa.org/doi/pdf/10.2514/1.G001490
+ */
+
+#include "controller_indi.h"
+
+static float thrust_threshold = 300.0f;
+static float bound_control_input = 32000.0f;
+
+static attitude_t attitudeDesired;
+static attitude_t rateDesired;
+static vector_t positionDesired;		//ev_tag 
+static vector_t velocityDesired;		//ev_tag 
+static float actuatorThrust;
+static float roll_kp = 6.0f;
+static float pitch_kp = 6.0f;
+static float yaw_kp = 6.0f;
+
+static float r_roll;
+static float r_pitch;
+static float r_yaw;
+static float accelz;
+
+static struct IndiVariables indi = {
+		.g1 = {STABILIZATION_INDI_G1_P, STABILIZATION_INDI_G1_Q, STABILIZATION_INDI_G1_R},
+		.g2 = STABILIZATION_INDI_G2_R,
+		.reference_acceleration = {
+				STABILIZATION_INDI_REF_ERR_P,
+				STABILIZATION_INDI_REF_ERR_Q,
+				STABILIZATION_INDI_REF_ERR_R,
+				STABILIZATION_INDI_REF_RATE_P,
[…]

### 2020-01-08 Paper_EV/Paper_EV.tex
Paper_EV: NDI chapter added

@@
 \usepackage{pageslts}
+
+% Package for bold symbols and letters
+\usepackage{bm}
+
+% Package for equations
+\usepackage{amsmath}
 
@@
 % List
-\newacronym{ADF}{ADF}{Automatic Direction Finder}
-\newacronym{ADI}{ADI}{Automatic Direction Indicator}
+\newacronym{NDI}{NDI}{Nonlinear Dynamic Inversion}
+\newacronym{INDI}{INDI}{Incremental Nonlinear Dynamic Inversion}
 % Make gls
@@
 
-- Theory from Sieberling paper.
+In this subsection, the \acrfull{NDI} method is explained.
+\acrshort{NDI} is based on feedback linearization and is also called \textit{Input-Output Linearization}.
+This method is often involved in tracking control tasks, where objective is to track some desired trajectory.
+(cite-tag Slotine) To show it in practice, consider following nonlinear system
+\begin{subequations}
+	\begin{align}
+		&\bm{\dot{x}} = \bm{f(x)} + \bm{G(x)}\bm{u} \\
+		&\bm{y} = \bm{h(x)}
+		\label{eq:nonlin_sys}
+	\end{align}
+\end{subequations}
+where $\bm{x}$ is the $n\times1$ state vector, $\bm{u}$ the $m\times1$ input vector, $\bm{y}$ the $m\times1$ system output vector, $\bm{f(x)}$ and $\bm{h(x)}$ nonlinear vector fields and $\bm{G}$ an $m\times n$ matrix.
+Note that the system presented in Equation (\ref{eq:nonlin_sys}) is affine in the input, which is not allways the case.
+To deal with this problem the system can be transformed into nonlinear normal (canonical) form through the state transformation.
+
+The idea behind the input-output linearization method is to find a direct relationship between the desired system output and the control input and then invert it.
+To generate this relationship the output $\bm{y}$ is differentiated until the input $\bm{u}$ appears
+\begin{equation}
+	\begin{split}
+		\dot{\bm{y}} &=  \frac{\partial\bm{y}}{\partial t} = \frac{\partial\bm{h(x)}}{\partial t} \frac{\partial\bm{x}}{\partial t} = \frac{\partial\bm{h(x)}}{\partial t} \dot{\bm{x}} = \nabla\bm{h(x)} [\bm{f(x)} + \bm{G(x)}\bm{u}] \\
+		&= \nabla\bm{h(x)} \bm{f(x)} + \nabla\bm{h(x)} \bm{G(x)}\bm{u}] = L_{\bm{f}} \bm{h(x)} + L_{\bm{G}} \bm{h(x) u} 
+		\label{eq:dy}
+	\end{split}
+\end{equation}
+In Equation (\ref{eq:dy}) $L_{\bm{f}} \bm{h(x)}$ is called Lie derivative of $\bm{h(x)}$ with respect to $\bm{f(x)}$.
+The Lie derivative is defined as $L_{\bm{f}} \bm{h(x)} = \nabla\bm{h(x)} \bm{f(x)}$ with $\nabla$ being the Nabla operator.
+Thus, it represents a directional derivative of $\bm{h(x)}$ along the direction of the vector field $\bm{f(x)}$.
+If the term $L_{\bm{G}} \bm{h(x) u}$ is not zero, the relationship between input and output is
+\begin{equation}
+	\begin{split}
+		\dot{\bm{y}} = L_{\bm{f}} \bm{h(x)} + L_{\bm{G}} \bm{h(x) u} 
+		\label{eq:dy_u_rel}
+	\end{split}
+\end{equation}
+
+Now Equation (\ref{eq:dy_u_rel}) can be used to formulate the control law by solving it for $\bm{u}$ and substituting $\dot{\bm{y}}$ with $\bm{\nu}$
+\begin{equation}
+	\begin{split}
+		\bm{u} = L_{\bm{G}}\bm{h(x)}^{-1} (\bm{\nu} - L_{\bm{f}}\bm{h(x)})
+		\label{eq:u_control_law}
+	\end{split}
+\end{equation}
+The variable $\bm{\nu}$ is called an \textit{equivalent input}. It represents the desired output of the system.
+
+In the example provided above the input-output relationsip was found after the first differentiation of the output.
+If this is not the case and the term $L_{\bm{G}}\bm{h(x)}$ is zero, output $\bm{y}$ has to be differentiated until the Lie derivative with respect to $\bm{G}$ is nonzero
+\begin{equation}
+	\begin{split}
+		\frac{\partial^i\bm{y}}{\partial t} = \frac{\partial^i\bm{h(x)}}{\partial t} = L_{\bm{f}}^i \bm{h(x)} + L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x) u}
+		\label{eq:dy_i}
+	\end{split}
+\end{equation}
+with $i$ being the \textit{relative degree} of the system. Using Equation (\ref{eq:dy_i}) to formulate the control law, leads to the following expression for $\bm{u}$
+\begin{equation}
+	\begin{split}
+		\bm{u} = L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x)}^{-1} (\bm{\nu} - L_{\bm{f}}^i\bm{h(x)}) 
+		\label{eq:u_control_law_i}
+	\end{split}
+\end{equation}
+Equation (\ref{eq:u_control_law_i}) applied to Equation (\ref{eq:dy_i}) yields the simple linear relation
+\begin{equation}
+	\begin{split}
+		\bm{y}^i = \bm{\nu}
+		\label{eq:u_control_law_i}
+	\end{split}
+\end{equation}
+Despite wide usage (especially in the past of the flight control design) of the \acrshort{NDI} method and its numerrous extensions (cite-tag Horn), it also has drawbacks.
+The major one is that the control law derived with \acrshort{NDI} is dependend on the dynamics model and its uncertainties.
+As shown in the previous chapter (cite-tag prev-chapter), the equations of motion of an aircraft usually have a complicated nonlinear character.
+Thus, creating a perfectly aqurate model of the aircraft is not an easy task.
+To overcome this obstacle an extension of the \acrshort{NDI} method called \acrshort{INDI} can be incorporated.
 

### 2020-01-10 Paper_EV/Paper_EV.tex
/Paper_EV: INDI general subsection added

--- 2020-01-07 Paper_EV/Paper_EV.tex
@@
 {\normalfont\chapfnt\bfseries}{\thechapter}{1em}{\chapfnt} 	% set font size
-\titlespacing{\chapter}{0cm}{-1.2cm}{0cm}					% set spacing
+\titlespacing{\chapter}{0cm}{-7mm}{0cm}					% set spacing
 
@@
 {\normalfont\chapfnt\bfseries}{\thechapter}{1em}{\chapfnt} 	% set font size
-\titlespacing*{\chapter}{0cm}{-1.2cm}{0cm}					% set spacing
+\titlespacing*{\chapter}{0cm}{-7mm}{0cm}					% set spacing
 
@@
 
+% Manually add Chapter names to the header (per default not included by Latex)
+\thispagestyle{fancy}
+\chaptermark{Theoretical Background}
+
 \section{General Equations of Motion} \label{sec:eqs_motion}
@@
 
-- Theory from Sieberling paper.
+In this subsection, the \acrfull{NDI} method is explained.
+The \acrshort{NDI} approach is based on feedback linearization and is also called \textit{Input-Output Linearization}.
+Often, such type of controllers is involved in tracking control tasks, where objective is to track some desired trajectory \cite{Slotine}.
+To derive it, consider the following nonlinear system
+\begin{subequations}
+	\begin{align}
+		&\bm{\dot{x}} = \bm{f(x)} + \bm{G(x)}\bm{u} \label{eq:nonlin_sys1} \\
+		&\bm{y} = \bm{h(x)} \label{eq:nonlin_sys2}
+	\end{align}
+	\label{eq:nonlin_sys}
+\end{subequations}
+where $\bm{x}$ is the $n\times1$ state vector, $\bm{u}$ the $m\times1$ input vector, $\bm{y}$ the $m\times1$ system vector, $\bm{f(x)}$ and $\bm{h(x)}$ nonlinear vector fields and $\bm{G}$ an $m\times n$ input matrix.
+Note that the system presented in Equations (\ref{eq:nonlin_sys}) is affine in the input, which is not allways fulfilled.
+Using a state transformation $\bm{z = \phi(x)}$, the affine system from Equation \ref{eq:nonlin_sys1} can be transformed into normal (canonical) representation.
+
+The core idea behind the input-output linearization method is to find a direct relationship between the desired system output and the control input.
+After the relationship is found it is inverted to generate the control law.
+To derive this relationship the output $\bm{y}$ is differentiated until the input $\bm{u}$ appears
+\begin{equation}
+	\begin{split}
+		\dot{\bm{y}} &=  \frac{\partial\bm{y}}{\partial t} = \frac{\partial\bm{h(x)}}{\partial t} \frac{\partial\bm{x}}{\partial t} = \frac{\partial\bm{h(x)}}{\partial t} \dot{\bm{x}} = \nabla\bm{h(x)} [\bm{f(x)} + \bm{G(x)}\bm{u}] \\
+		&= \nabla\bm{h(x)} \bm{f(x)} + \nabla\bm{h(x)} \bm{G(x)}\bm{u}] = L_{\bm{f}} \bm{h(x)} + L_{\bm{G}} \bm{h(x) u} 
+		\label{eq:dy}
+	\end{split}
+\end{equation}
+
+In Equation (\ref{eq:dy}) $L_{\bm{f}} \bm{h(x)}$ is called Lie derivative of $\bm{h(x)}$ with respect to $\bm{f(x)}$.
+The Lie derivative is defined as $L_{\bm{f}} \bm{h(x)} = \nabla\bm{h(x)} \bm{f(x)}$ with $\nabla$ being the Nabla operator.
+Thus, it represents a directional derivative of $\bm{h(x)}$ along the direction of the vector field $\bm{f(x)}$.
+If the term $L_{\bm{G}} \bm{h(x)}$ is nonzero, the relationship between input and output is
+\begin{equation}
+	\begin{split}
+		\dot{\bm{y}} = L_{\bm{f}} \bm{h(x)} + L_{\bm{G}} \bm{h(x) u} 
+		\label{eq:dy_u_rel}
+	\end{split}
+\end{equation}
+
+Now Equation (\ref{eq:dy_u_rel}) can be used to formulate the control law by solving it for $\bm{u}$ and substituting $\dot{\bm{y}}$ with $\bm{\nu}$
+\begin{equation}
+	\begin{split}
+		\bm{u} = L_{\bm{G}}\bm{h(x)}^{-1} (\bm{\nu} - L_{\bm{f}}\bm{h(x)})
+		\label{eq:u_control_law}
+	\end{split}
+\end{equation}
+The variable $\bm{\nu}$ is called an \textit{equivalent input} and represents the desired output of the system.
+
+In the example provided above the input-output relationsip was found after the first differentiation of the output $\bm{y}$.
+But if after the first differentiation the term $L_{\bm{G}}\bm{h(x)}$ is zero, output $\bm{y}$ has to be differentiated until the Lie derivative with respect to $\bm{G}$ is nonzero.
+The $i$-th derivative of the output is then
+\begin{equation}
+	\begin{split}
+		\frac{\partial^i\bm{y}}{\partial t} = \frac{\partial^i\bm{h(x)}}{\partial t} = L_{\bm{f}}^i \bm{h(x)} + L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x) u}
+		\label{eq:dy_i}
+	\end{split}
+\end{equation}
+with $i$ being the \textit{relative degree} of the system. Using Equation (\ref{eq:dy_i}) to formulate the control law, leads to the following expression for the control input $\bm{u}$
+\begin{equation}
+	\begin{split}
+		\bm{u} = L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x)}^{-1} (\bm{\nu} - L_{\bm{f}}^i\bm{h(x)}) 
+		\label{eq:u_control_law_i}
+	\end{split}
+\end{equation}
+Thus, Equation (\ref{eq:u_control_law_i}) applied to Equation (\ref{eq:dy_i}) yields the simple linear relation
+\begin{equation}
+	\begin{split}
+		\bm{y}^i = \bm{\nu}
+		\label{eq:u_control_law_i}
+	\end{split}
+\end{equation}
+Despite wide usage (especially in the past of the flight control) of the \acrshort{NDI} method and its numerrous extensions (cite-tag Horn), it also has drawbacks.
+
+The \acrshort{NDI} method was widely adopted for civil and military aircrafts and has numerous of extensions \cite{Horn}.
+Nevertheless, it has some drawbacks.
+The major one is that the control law derived using the \acrshort{NDI} approach is dependent on the full system dynamics model \cite{Sieberling}.
+As shown in the previous chapter (cite-tag prev-chapter), the equations of motion of an aircraft usually have a complicated nonlinear character.
+Thus, describing complex physical phenomena often leads to the inconsistency between the real aircraft and its mathematical representation used in the model.
+As some of those inconsistencies are inevitable there is a need to build a control law which performance is less dependent on the uncertainties of the model.
+This method is called \acrfull{INDI} and will be discussed in the next subsection.
 
@@
 
-- Here only the general principle is provided, next subsections show the full derivation of the two controller loops.
+The \acrshort{INDI} is an incremental form of the \acrshort{NDI} for which the lack of the accurate system dynamics model does not critically affect the performance of the control algorithm \cite{Silva}.
+The incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
+\begin{equation}
+	\begin{split}
+		\bm{\dot{x}} &= \bm{f(x_0)} + \bm{G(x_0)}\bm{u_0} \\
+		&+ \frac{\partial}{\partial \bm{x}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{x-x_0}) \\
+		&+ \frac{\partial}{\partial \bm{u}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{u-u_0}) 
+		\label{eq:nonlin_sys_taylor}
+	\end{split}
+\end{equation}
+The first term on the right side of the Equation \ref{eq:nonlin_sys_taylor} is $\bm{\dot{x}_0}$. Also, evaluating the differentiation of the third term leads to 
+\begin{equation}
+	\begin{split}
+		\bm{\dot{x}} &= \bm{\dot{x}_0} \\ 
+		&+ \frac{\partial}{\partial \bm{x}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{x-x_0}) \\
+		&+ \bm{G(x_0)} (\bm{u-u_0}) 
+		\label{eq:nonlin_sys_taylor2}
+	\end{split}
+\end{equation}
+The second term of the Equation \ref{eq:nonlin_sys_taylor2} contains partial derivative with respect to the state vector.
+Considering very small time increments of the controller loop and applying the \textit{principle of time scale separation} the second term vanishes.
+This is a valid assumption if the dynamics of the actuators is fast compared with the dynamics of the system.
+Thus, the Equation \ref{eq:nonlin_sys_taylor2} is further simplified to
+\begin{equation}
+	\begin{split}
+		\bm{\dot{x}} = \bm{\dot{x}_0} + \bm{G(x_0)} (\bm{u-u_0}) 
+		\label{eq:nonlin_sys_indi}
+	\end{split}
+\end{equation}
+Solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\dot{\bm{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law can be obtained
+\begin{equation}
+	\begin{split}
+		\bm{u} = \bm{u_0} + \bm{G(x_0)^{-1}} (\bm{\nu} - \bm{\dot{x}_0})
+		\label{eq:u_control_law_indi}
+	\end{split}
+\end{equation}
+where $\bm{\dot{x}_0}$ is a measurable value from the previous step, $\bm{u_0}$ the control input from the previous step, $\bm{\nu}$ the reference value and $\bm{G(x_0)}$ the control effectiveness matrix.
+With $\bm{\Delta u=u-u_0}$ the control law from Equation \ref{eq:u_control_law_indi} represents an incremental version of the Equation \ref{eq:u_control_law}.
+This control law results in computing the increment $\bm{\Delta u}$ of the control input and adding it to the previous value $\bm{u_0}$, instead if computing complete control input command $\bm{u}$.
+As it is less dependent on the model of the system dynamics, it increases the robustness of the system \cite{Sieberling}.
+
+\subsection{General INDI} \label{subsec: indi_general}
 
@@
 - Derivation of the outer INDI loop (detailed equations).
-
-% Manually add Chapter names to the header (per default not included by Latex)
-\thispagestyle{fancy}
-\chaptermark{Theoretical Background}
 
@@
 \renewcommand\bibname{References}		% Rename Bibliography to References
-\bibliographystyle{plain}
-\bibliography{Literature}
+\bibliographystyle{unsrt}
+\bibliography{Lit/Literature}
 

### 2020-01-10 crazyflie-firmware/src/modules/interface/controller.h

@@ -33,6 +33,7 @@ typedef enum {
   ControllerTypePID,
   ControllerTypeMellinger,
   ControllerTypeINDI,
+  ControllerTypeSTEP,
   ControllerType_COUNT,
 } ControllerType;
 

### 2020-01-10 crazyflie-firmware/src/modules/interface/controller_step.h

@@ -7,7 +7,7 @@
  *
  * Crazyflie control firmware
  *
- * Copyright (C) 2012-2019 BitCraze AB
+ * Copyright (C) 2011-2016 Bitcraze AB
  *
  * This program is free software: you can redistribute it and/or modify
  * it under the terms of the GNU General Public License as published by
@@ -21,16 +21,27 @@
  * You should have received a copy of the GNU General Public License
  * along with this program. If not, see <http://www.gnu.org/licenses/>.
  *
- * mem.h - Memory sub system
+ * controller_indi.h - INDI Controller Interface
  */
+#ifndef __CONTROLLER_STEP_H__
+#define __CONTROLLER_STEP_H__
 
-#ifndef __MEM_H__
-#define __MEM_H__
+#include "stabilizer_types.h"
+#include "filter.h"
+#include "math3d.h"
+#include "log.h"
+#include "param.h"
+#include "position_controller.h"
+#include "attitude_controller.h"
+#include "controller_indi.h"
 
-#include <stdbool.h>
+#define ATTITUDE_UPDATE_DT    (float)(1.0f/ATTITUDE_RATE)
 
-/* Public functions */
-void memInit(void);
-bool memTest(void);
+void controllerSTEPInit(void);
+bool controllerSTEPTest(void);
+void controllerSTEP(control_t *control, setpoint_t *setpoint,
+                                         const sensorData_t *sensors,
+                                         const state_t *state,
+                                         const uint32_t tick);
 
-#endif /* __MEM_H__ */
+#endif //__CONTROLLER_STEP_H__

### 2020-01-10 crazyflie-firmware/src/modules/src/controller.c

@@ -6,6 +6,7 @@
 #include "controller_pid.h"
 #include "controller_mellinger.h"
 #include "controller_indi.h"
+#include "controller_step.h"
 
 #define DEFAULT_CONTROLLER ControllerTypePID
 static ControllerType currentController = ControllerTypeAny;
@@ -24,6 +25,7 @@ static ControllerFcns controllerFunctions[] = {
   {.init = controllerPidInit, .test = controllerPidTest, .update = controllerPid, .name = "PID"},
   {.init = controllerMellingerInit, .test = controllerMellingerTest, .update = controllerMellinger, .name = "Mellinger"},
   {.init = controllerINDIInit, .test = controllerINDITest, .update = controllerINDI, .name = "INDI"},
+  {.init = controllerSTEPInit, .test = controllerSTEPTest, .update = controllerSTEP, .name = "STEP"},
 };
 
 

### 2020-01-10 crazyflie-firmware/src/modules/src/stabilizer.c

@@ -184,7 +184,7 @@ void stabilizerInit(StateEstimatorType estimator)
 
   sensorsInit();
   stateEstimatorInit(estimator);
-  controllerInit(ControllerTypeAny);
+  controllerInit(ControllerTypeSTEP);
   powerDistributionInit();
   sitAwInit();
   estimatorType = getStateEstimator();

### 2020-01-11 Paper_EV/Paper_EV.tex
Paper_EV/ General Dynamic EOM chapter added

@@
 
-% Package for equations
+% Package for equations and math. symbols
 \usepackage{amsmath}
+\usepackage{amssymb}
 
@@
 % List
+\newacronym{INDI}{INDI}{Incremental Nonlinear Dynamic Inversion}
+\newacronym{NED}{NED}{North East Down}
 \newacronym{NDI}{NDI}{Nonlinear Dynamic Inversion}
-\newacronym{INDI}{INDI}{Incremental Nonlinear Dynamic Inversion}
 % Make gls
@@
 
+...
+
 % Manually add Chapter names to the header (per default not included by Latex)
@@
 
-\section{General Equations of Motion} \label{sec:eqs_motion}
-General: \\
-- Linear Momentum\\
-- Angular Momentum\\
-- Attitude differential equations\\
-- Position differential equations\\
-- External forces and moments
+\section{Dynamic Equations of Motion of an Aircraft} \label{sec:eqs_motion}
 
-with some of the used assumptions
+In this section general equations of motion of an aircraft are presented.
+
+For the derivation of the equation of motion the aircraft system will be assumed to be a rigid body.
+Such a rigid body system can be described uniquely by 12 states.
+Note that by taking in account additional effects, such propulsion system dynamics, multi-body dynamics etc., the number of required state variables will increase.
+
+Additionally to the rigid body assumption, it is also assumed that the earth is flat and non-rotating and the reference point of the force vector corresponds to the center of gravity of the body.
+Thus, the linear momentum equation is written as
+\begin{equation}
+	\begin{split}
+		\sum (\bm{F}^G)_B = m \cdot \Big[ (\bm{\dot{v}}^G)_{B} + (\bm{\omega}^{OB})\times(\bm{v}^R)_{B} \Big]
+		\label{eq:lin_momentum}
+	\end{split}
+\end{equation}
+where $\sum(\bm{F}^G)_B \in \mathbb{R}^{3 \times 1}$ is the sum of the external forces acting on the system and applied to the center of gravity $G$, $m$ the mass of the body, $(\bm{\dot{v}}^G)_{B} \in \mathbb{R}^{3 \times 1}$ the linear acceleration of the point $G$, $(\bm{\omega}^{OB}) \in \mathbb{R}^{3 \times 1}$ the angular velocity of the body-fixed frame ($B$) with respect to the \acrfull{NED} ($O$) coordinate frame.
+Subscript $B$ denotes that all variables are specified in the body-fixed coordinate frame.
+
+The rotational motion of a body is described with the angular momentum.
+To derive it, additionally to the assumptions made above it is also considered that the mass and the mass distribution are quasistationary, meaning $\frac{d}{dt}m=0$ and $\frac{d}{dt}(I)_B=0$ respectively?.
+$(I)_B$ is the inertia tensor of the body defined in the body-fixed frame.
+Thus, the angular momentum is
+\begin{equation}
+	\begin{split}
+		\sum (\bm{M}^G)_B = (\bm{I}^G)_B \cdot (\bm{\dot{\omega}}^{OB}) + (\bm{\omega}^{OB}) \times \Big[(\bm{I}^G)_B \cdot (\bm{\omega}^{OB})\Big]
+		\label{eq:ang_momentum}
+	\end{split}
+\end{equation}
+where $\sum (\bm{M}^G)_B \in \mathbb{R}^{3 \times 1}$ is the sum of the external moments acting on the system around the center of gravity $G$,
+
+The remaining two equations, that are necessary to fully describe the rigid body are the attitude differential equation and the position differential equation.
+The attitude differential equation describes the relationship between angular rates $p, q, r$ and derivatives of the Euler angles $\dot{\Phi}, \dot{\Theta}, \dot{\Psi}$ leading to
+\begin{equation}
+	\begin{bmatrix}
+		\dot{\Phi}\\
+		\dot{\Theta}\\
+		\dot{\Psi}
+	\end{bmatrix} =
+	\begin{bmatrix}
+    	1 & \sin\Phi\tan\Theta & \cos\Phi\tan\Theta \\
+    	0 & \cos\Phi & -\sin\Phi \\
+    	0 & \frac{\sin\Phi}{\cos\Theta} & \frac{\cos\Phi}{\cos\Theta}
+    \end{bmatrix}_B
+    \begin{bmatrix}
+		p\\
+		q\\
+		r
+	\end{bmatrix}_B
+	\label{eq:attitude_diff_eq}
+\end{equation}
+
+There are different options to represent the position differential equation.
+Here, for completeness only, it is written as a simple relationship between the change of the position coordinates in the local \acrshort{NED} frame and the velocity coordinates of the same frame
+\begin{equation}
+	\begin{bmatrix}
+		\dot{x}\\
+		\dot{y}\\
+		\dot{z}
+	\end{bmatrix}_O =
+	\begin{bmatrix}
+		\dot{V_N}\\
+		\dot{V_E}\\
+		\dot{V_D}
+	\end{bmatrix}_O
+	\label{eq:position_diff_eq}
+\end{equation}
+
+The above presented Equations (\ref{eq:lin_momentum})-(\ref{eq:position_diff_eq}) can be used to represent a motion of a general aircraft.
+$\sum(\bm{F}^G)_B$ and $\sum (\bm{M}^G)_B$ are sums of the external forces and moments acting on the aircraft.
+These could be the aerodynamic forces and moments caused by the air flow, propulsion forces and moments, forces caused by the gravitation etc..
+The detailed modelling of external forces and moments is presented in chapter (...Simulink).
 
@@
 \end{subequations}
-where $\bm{x}$ is the $n\times1$ state vector, $\bm{u}$ the $m\times1$ input vector, $\bm{y}$ the $m\times1$ system vector, $\bm{f(x)}$ and $\bm{h(x)}$ nonlinear vector fields and $\bm{G}$ an $m\times n$ input matrix.
+where $\bm{x} \in \mathbb{R}^{n \times 1}$ is the state vector, $\bm{u} \in \mathbb{R}^{m \times 1}$ the input vector, $\bm{y} \in \mathbb{R}^{m \times 1}$ the system vector, $\bm{f(x)} \in \mathbb{R}^{n \times 1}$ and $\bm{h(x) \in \mathbb{R}^{m \times 1}}$ nonlinear vector fields and $\bm{G} \in \mathbb{R}^{m \times n}$ an input matrix.
 Note that the system presented in Equations (\ref{eq:nonlin_sys}) is affine in the input, which is not allways fulfilled.
@@
 As some of those inconsistencies are inevitable there is a need to build a control law which performance is less dependent on the uncertainties of the model.
-This method is called \acrfull{INDI} and will be discussed in the next subsection.
+This method is called \acrfull{INDI} and will be discussed in the next section.
 
@@
 The \acrshort{INDI} is an incremental form of the \acrshort{NDI} for which the lack of the accurate system dynamics model does not critically affect the performance of the control algorithm \cite{Silva}.
+At first the general form of the \acrshort{INDI} is presented in \ref{subsec:indi_general}, then the inner and outer control loops for the Crazyflie quadrotor are derived in \ref{subsec: indi_inner} and \ref{subsec: indi_outer}.
+
+\subsection{General INDI} \label{subsec:indi_general}
+
 The incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
@@
 
-\subsection{General INDI} \label{subsec: indi_general}
+\subsection{Inner INDI loop for Quadrotor} \label{subsec: indi_inner}
 
-\subsection{INDI inner loop} \label{subsec: indi_inner}
+- Derivation of the inner INDI loop (what we want to control, detailed equations).
 
-- Derivation of the inner INDI loop (detailed equations).
+\subsection{Outer INDI loop for Quadrotor} \label{subsec: indi_outer}
 
-\subsection{INDI outer loop} \label{subsec: indi_outer}
-
-- Derivation of the outer INDI loop (detailed equations).
+- Derivation of the outer INDI loop (what we want to control, detailed equations).
 
@@
 
-\section{Simulink Model} \label{sec:simulink_model}
+\section{Implementation in Simulink (Simulink Model)} \label{sec:simulink_model}
 
@@
 \subsection{Structure} \label{subsec:Structure}
+- Force frame from B to O for an easy representation\\
+- Show each equation of forces with explaining the made assumptions\\
 - Parameters\\
@@
 
-\section{Implementation on Hardware} \label{sec:implementation_on_hardware}
+\section{Implementation on the Hardware} \label{sec:implementation_on_hardware}
 

### 2020-01-11 Paper_EV/Paper_EV.tex
/Paper_EV: refactoring of the actual state of the Chapter 2

@@
 % - Title page: Dr. -> Dr. ir.
+% - Acronyms, right order of full and short appearences
+% - Create List of Symbols
 %
@@
 % List
+\newacronym{EOM}{EOM}{Equations of Motion}
 \newacronym{INDI}{INDI}{Incremental Nonlinear Dynamic Inversion}
@@
 
-...
+The aim of this chapter is to provide the theoretical background which serves as a basis for some of the methods which are presented and applied in the course of this thesis.
+At the beginning, in section \ref{sec:eqs_motion} general \acrfull{EOM} of an aircraft are presented.
+These are later used to derive the control algorithm and build the Matlab/Simulink model of the Crazyflie quadrotor.
+Sections \ref{sec:ndi} and \ref{sec:indi} describe the \acrfull{NDI} and \acrfull{INDI} methods in general.
+Later in this chapter (subsections \ref{subsec: indi_inner} and \ref{subsec: indi_outer}) these methods are used to derive the inner and the outer loop of the \acrshort{INDI} flight controller for the Crazyflie quadrotor.
 
@@
 
-In this section general equations of motion of an aircraft are presented.
+The dynamic equations which describe the general motion of an aircraft are usually coupled first order implicit nonlinear differential equations.
+However, in many cases it is sufficient to use their simplified versions (Source needed!).
+This section presents simplified general \acrshort{EOM} and describes the assumptions which were considered to derive them.
 
@@
 Such a rigid body system can be described uniquely by 12 states.
-Note that by taking in account additional effects, such propulsion system dynamics, multi-body dynamics etc., the number of required state variables will increase.
+Note that by taking in account additional effects, such as propulsion system dynamics, multi-body dynamics etc., the number of required state variables will increase.
 
-Additionally to the rigid body assumption, it is also assumed that the earth is flat and non-rotating and the reference point of the force vector corresponds to the center of gravity of the body.
+Additionally to the rigid body assumption, it is also assumed that the earth is flat and non-rotating and the reference point of the sum of all external forces acting on the body corresponds to the center of gravity of the body.
 Thus, the linear momentum equation is written as
@@
 
-The rotational motion of a body is described with the angular momentum.
+The rotational motion of a body is described with the angular momentum equation.
 To derive it, additionally to the assumptions made above it is also considered that the mass and the mass distribution are quasistationary, meaning $\frac{d}{dt}m=0$ and $\frac{d}{dt}(I)_B=0$ respectively?.
@@
 \end{equation}
-where $\sum (\bm{M}^G)_B \in \mathbb{R}^{3 \times 1}$ is the sum of the external moments acting on the system around the center of gravity $G$,
+where $\sum (\bm{M}^G)_B \in \mathbb{R}^{3 \times 1}$ is the sum of the external moments acting on the system around the center of gravity $G$.
 
-The remaining two equations, that are necessary to fully describe the rigid body are the attitude differential equation and the position differential equation.
+The remaining two equations, that are necessary to fully describe the motion of a rigid body in space are the attitude differential equation and the position differential equation.
 The attitude differential equation describes the relationship between angular rates $p, q, r$ and derivatives of the Euler angles $\dot{\Phi}, \dot{\Theta}, \dot{\Psi}$ leading to
@@
 \end{equation}
+where the angular rates are related to the derivatives of the Euler angles through the \textit{strapdown matrix}.
 
@@
 
-The above presented Equations (\ref{eq:lin_momentum})-(\ref{eq:position_diff_eq}) can be used to represent a motion of a general aircraft.
-$\sum(\bm{F}^G)_B$ and $\sum (\bm{M}^G)_B$ are sums of the external forces and moments acting on the aircraft.
-These could be the aerodynamic forces and moments caused by the air flow, propulsion forces and moments, forces caused by the gravitation etc..
+The Equations (\ref{eq:lin_momentum})-(\ref{eq:position_diff_eq}) presented above can be used to represent a motion of a general aircraft.
+Note that terms $\sum(\bm{F}^G)_B$ and $\sum (\bm{M}^G)_B$ contain all external forces and moments acting on the rigid body.
+Considering an aircraft system these could be the aerodynamic forces and moments caused by the air flow, propulsion forces and moments, forces caused by the gravitation etc..
 The detailed modelling of external forces and moments is presented in chapter (...Simulink).
@@
 \end{subequations}
-where $\bm{x} \in \mathbb{R}^{n \times 1}$ is the state vector, $\bm{u} \in \mathbb{R}^{m \times 1}$ the input vector, $\bm{y} \in \mathbb{R}^{m \times 1}$ the system vector, $\bm{f(x)} \in \mathbb{R}^{n \times 1}$ and $\bm{h(x) \in \mathbb{R}^{m \times 1}}$ nonlinear vector fields and $\bm{G} \in \mathbb{R}^{m \times n}$ an input matrix.
+\hspace{-5pt}where $\bm{x} \in \mathbb{R}^{n \times 1}$ is the state vector, $\bm{u} \in \mathbb{R}^{m \times 1}$ the input vector, $\bm{y} \in \mathbb{R}^{m \times 1}$ the output vector, $\bm{f(x)} \in \mathbb{R}^{n \times 1}$ and $\bm{h(x) \in \mathbb{R}^{m \times 1}}$ nonlinear vector fields and $\bm{G} \in \mathbb{R}^{m \times n}$ an input matrix.
 Note that the system presented in Equations (\ref{eq:nonlin_sys}) is affine in the input, which is not allways fulfilled.
-Using a state transformation $\bm{z = \phi(x)}$, the affine system from Equation \ref{eq:nonlin_sys1} can be transformed into normal (canonical) representation.
+Using a state transformation $\bm{z = \phi(x)}$, the affine system from Equation \ref{eq:nonlin_sys1} can be transformed into a \textit{normal} (\textit{canonical}) representation.
 
@@
 \end{equation}
-with $i$ being the \textit{relative degree} of the system. Using Equation (\ref{eq:dy_i}) to formulate the control law, leads to the following expression for the control input $\bm{u}$
+with $i$ being the \textit{relative degree} of the system. Using Equation (\ref{eq:dy_i}) to formulate the control law leads to the following expression for the control input $\bm{u}$
 \begin{equation}
@@
 		\bm{y}^i = \bm{\nu}
-		\label{eq:u_control_law_i}
+		\label{eq:lin_relation}
 	\end{split}
 \end{equation}
-Despite wide usage (especially in the past of the flight control) of the \acrshort{NDI} method and its numerrous extensions (cite-tag Horn), it also has drawbacks.
-
 The \acrshort{NDI} method was widely adopted for civil and military aircrafts and has numerous of extensions \cite{Horn}.
@@
 The major one is that the control law derived using the \acrshort{NDI} approach is dependent on the full system dynamics model \cite{Sieberling}.
-As shown in the previous chapter (cite-tag prev-chapter), the equations of motion of an aircraft usually have a complicated nonlinear character.
+The equations of motion of an aircraft usually have a complicated nonlinear character.
 Thus, describing complex physical phenomena often leads to the inconsistency between the real aircraft and its mathematical representation used in the model.
 As some of those inconsistencies are inevitable there is a need to build a control law which performance is less dependent on the uncertainties of the model.
-This method is called \acrfull{INDI} and will be discussed in the next section.
+A method called \acrfull{INDI} can be used to achieve this, it is discussed in the next section.
 
@@
 \end{equation}
-Solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\dot{\bm{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law can be obtained
+Solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\dot{\bm{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law is obtained
 \begin{equation}
@@
 With $\bm{\Delta u=u-u_0}$ the control law from Equation \ref{eq:u_control_law_indi} represents an incremental version of the Equation \ref{eq:u_control_law}.
-This control law results in computing the increment $\bm{\Delta u}$ of the control input and adding it to the previous value $\bm{u_0}$, instead if computing complete control input command $\bm{u}$.
-As it is less dependent on the model of the system dynamics, it increases the robustness of the system \cite{Sieberling}.
+Instead of computing the complete control input command $\bm{u}$, this control law results in computing the increment of the control input $\bm{\Delta u}$ and adding it to the previous value $\bm{u_0}$.
+As it is less dependent on the model of the system dynamics, it is able to increase the robustness of the system \cite{Sieberling}.
 

### 2020-01-20 Paper_EV/Paper_EV.tex
Time constant (/actuator_dynamics) and G1,G2 parameters (/param_est added) estimated

@@
 	\begin{align}
-		&\bm{\dot{x}} = \bm{f(x)} + \bm{G(x)}\bm{u} \label{eq:nonlin_sys1} \\
-		&\bm{y} = \bm{h(x)} \label{eq:nonlin_sys2}
+		&\bm{\dot{x}} = \bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u} \label{eq:nonlin_sys1} \\
+		&\bm{y} = \bm{h}(\bm{x}) \label{eq:nonlin_sys2}
 	\end{align}
@@
 \end{subequations}
-\hspace{-5pt}where $\bm{x} \in \mathbb{R}^{n \times 1}$ is the state vector, $\bm{u} \in \mathbb{R}^{m \times 1}$ the input vector, $\bm{y} \in \mathbb{R}^{m \times 1}$ the output vector, $\bm{f(x)} \in \mathbb{R}^{n \times 1}$ and $\bm{h(x) \in \mathbb{R}^{m \times 1}}$ nonlinear vector fields and $\bm{G} \in \mathbb{R}^{m \times n}$ an input matrix.
+\hspace{-5pt}where $\bm{x} \in \mathbb{R}^{n \times 1}$ is the state vector, $\bm{u} \in \mathbb{R}^{m \times 1}$ the input vector, $\bm{y} \in \mathbb{R}^{m \times 1}$ the output vector, $\bm{f}(\bm{x}) \in \mathbb{R}^{n \times 1}$ and $\bm{h}(\bm{x}) \in \mathbb{R}^{m \times 1}$ nonlinear vector fields and $\bm{G} \in \mathbb{R}^{m \times n}$ an input matrix.
 Note that the system presented in Equations (\ref{eq:nonlin_sys}) is affine in the input, which is not allways fulfilled.
-Using a state transformation $\bm{z = \phi(x)}$, the affine system from Equation \ref{eq:nonlin_sys1} can be transformed into a \textit{normal} (\textit{canonical}) representation.
+Using a state transformation $\bm{z} = \bm{\phi}(\bm{x})$, the affine system from Equation \ref{eq:nonlin_sys1} can be transformed into a \textit{normal} (\textit{canonical}) representation.
 
@@
 	\begin{split}
-		\dot{\bm{y}} &=  \frac{\partial\bm{y}}{\partial t} = \frac{\partial\bm{h(x)}}{\partial t} \frac{\partial\bm{x}}{\partial t} = \frac{\partial\bm{h(x)}}{\partial t} \dot{\bm{x}} = \nabla\bm{h(x)} [\bm{f(x)} + \bm{G(x)}\bm{u}] \\
-		&= \nabla\bm{h(x)} \bm{f(x)} + \nabla\bm{h(x)} \bm{G(x)}\bm{u}] = L_{\bm{f}} \bm{h(x)} + L_{\bm{G}} \bm{h(x) u} 
+		\bm{\dot{y}} &=  \frac{\partial\bm{y}}{\partial t} = \frac{\partial\bm{h}(\bm{x})}{\partial t} \frac{\partial\bm{x}}{\partial t} = \frac{\partial\bm{h}(\bm{x})}{\partial t} \dot{\bm{x}} = \nabla\bm{h}(\bm{x}) [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \\
+		&= \nabla\bm{h}(\bm{x}) \bm{f}(\bm{x}) + \nabla\bm{h}(\bm{x}) \bm{G}(\bm{x})\bm{u}] = L_{\bm{f}} \bm{h}(\bm{x}) + L_{\bm{G}} \bm{h}(\bm{x}) \bm{u} 
 		\label{eq:dy}
@@
 
-In Equation (\ref{eq:dy}) $L_{\bm{f}} \bm{h(x)}$ is called Lie derivative of $\bm{h(x)}$ with respect to $\bm{f(x)}$.
-The Lie derivative is defined as $L_{\bm{f}} \bm{h(x)} = \nabla\bm{h(x)} \bm{f(x)}$ with $\nabla$ being the Nabla operator.
-Thus, it represents a directional derivative of $\bm{h(x)}$ along the direction of the vector field $\bm{f(x)}$.
-If the term $L_{\bm{G}} \bm{h(x)}$ is nonzero, the relationship between input and output is
+In Equation (\ref{eq:dy}) $L_{\bm{f}} \bm{h}(\bm{x})$ is called Lie derivative of $\bm{h}(\bm{x})$ with respect to $\bm{f}(\bm{x})$.
+The Lie derivative is defined as $L_{\bm{f}} \bm{h}(\bm{x}) = \nabla\bm{h}(\bm{x}) \bm{f}(\bm{x})$ with $\nabla$ being the Nabla operator.
+Thus, it represents a directional derivative of $\bm{h}(\bm{x})$ along the direction of the vector field $\bm{f}(\bm{x})$.
+If the term $L_{\bm{G}} \bm{h}(\bm{x})$ is nonzero, the relationship between input and output is
 \begin{equation}
 	\begin{split}
-		\dot{\bm{y}} = L_{\bm{f}} \bm{h(x)} + L_{\bm{G}} \bm{h(x) u} 
+		\bm{\dot{y}} = L_{\bm{f}} \bm{h}(\bm{x}) + L_{\bm{G}} \bm{h}(\bm{x}) \bm{u} 
 		\label{eq:dy_u_rel}
@@
 
-Now Equation (\ref{eq:dy_u_rel}) can be used to formulate the control law by solving it for $\bm{u}$ and substituting $\dot{\bm{y}}$ with $\bm{\nu}$
+Now Equation (\ref{eq:dy_u_rel}) can be used to formulate the control law by solving it for $\bm{u}$ and substituting $\bm{\dot{y}}$ with $\bm{\nu}$
 \begin{equation}
 	\begin{split}
-		\bm{u} = L_{\bm{G}}\bm{h(x)}^{-1} (\bm{\nu} - L_{\bm{f}}\bm{h(x)})
+		\bm{u} = L_{\bm{G}}\bm{h}(\bm{x})^{-1} (\bm{\nu} - L_{\bm{f}}\bm{h}(\bm{x}))
 		\label{eq:u_control_law}
@@
 In the example provided above the input-output relationsip was found after the first differentiation of the output $\bm{y}$.
-But if after the first differentiation the term $L_{\bm{G}}\bm{h(x)}$ is zero, output $\bm{y}$ has to be differentiated until the Lie derivative with respect to $\bm{G}$ is nonzero.
+But if after the first differentiation the term $L_{\bm{G}}\bm{h}(\bm{x})$ is zero, output $\bm{y}$ has to be differentiated until the Lie derivative with respect to $\bm{G}$ is nonzero.
 The $i$-th derivative of the output is then
@@
 	\begin{split}
-		\frac{\partial^i\bm{y}}{\partial t} = \frac{\partial^i\bm{h(x)}}{\partial t} = L_{\bm{f}}^i \bm{h(x)} + L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x) u}
+		\frac{\partial^i\bm{y}}{\partial t} = \frac{\partial^i\bm{h}(\bm{x})}{\partial t} = L_{\bm{f}}^i \bm{h}(\bm{x}) + L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h}(\bm{x}) \bm{u}
 		\label{eq:dy_i}
@@
 	\begin{split}
-		\bm{u} = L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h(x)}^{-1} (\bm{\nu} - L_{\bm{f}}^i\bm{h(x)}) 
+		\bm{u} = L_{\bm{G}} L_{\bm{f}}^{i-1} \bm{h}(\bm{x})^{-1} (\bm{\nu} - L_{\bm{f}}^i\bm{h}(\bm{x})) 
 		\label{eq:u_control_law_i}
@@
 	\begin{split}
-		\bm{\dot{x}} &= \bm{f(x_0)} + \bm{G(x_0)}\bm{u_0} \\
-		&+ \frac{\partial}{\partial \bm{x}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{x-x_0}) \\
-		&+ \frac{\partial}{\partial \bm{u}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{u-u_0}) 
+		\bm{\dot{x}} &= \bm{f}(\bm{x}_0) + \bm{G}(\bm{x}_0)\bm{u}_0 \\
+		&+ \frac{\partial}{\partial \bm{x}} [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \bigg|_{\bm{x}=\bm{x}_0,\bm{u}=\bm{u}_0} (\bm{x}-\bm{x}_0) \\
+		&+ \frac{\partial}{\partial \bm{u}} [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \bigg|_{\bm{x}=\bm{x}_0,\bm{u}=\bm{u}_0} (\bm{u}-\bm{u}_0) 
 		\label{eq:nonlin_sys_taylor}
@@
 	\begin{split}
-		\bm{\dot{x}} &= \bm{\dot{x}_0} \\ 
-		&+ \frac{\partial}{\partial \bm{x}} [\bm{f(x)} + \bm{G(x)}\bm{u}] \bigg|_{\bm{x=x_0,u=u_0}} (\bm{x-x_0}) \\
-		&+ \bm{G(x_0)} (\bm{u-u_0}) 
+		\bm{\dot{x}} &= \bm{\dot{x}}_0 \\ 
+		&+ \frac{\partial}{\partial \bm{x}} [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \bigg|_{\bm{x}=\bm{x}_0,\bm{u}=\bm{u}_0} (\bm{x}-\bm{x}_0) \\
+		&+ \bm{G}(\bm{x}_0) (\bm{u}-\bm{u}_0) 
 		\label{eq:nonlin_sys_taylor2}
@@
 	\begin{split}
-		\bm{\dot{x}} = \bm{\dot{x}_0} + \bm{G(x_0)} (\bm{u-u_0}) 
+		\bm{\dot{x}} = \bm{\dot{x}}_0 + \bm{G}(\bm{x}_0) (\bm{u}-\bm{u}_0) 
 		\label{eq:nonlin_sys_indi}
@@
 \end{equation}
-Solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\dot{\bm{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law is obtained
+Solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\bm{\dot{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law is obtained
 \begin{equation}
 	\begin{split}
-		\bm{u} = \bm{u_0} + \bm{G(x_0)^{-1}} (\bm{\nu} - \bm{\dot{x}_0})
+		\bm{u} = \bm{u}_0 + \bm{G}(\bm{x}_0)^{-1} (\bm{\nu} - \bm{\dot{x}}_0)
 		\label{eq:u_control_law_indi}
@@
 \end{equation}
-where $\bm{\dot{x}_0}$ is a measurable value from the previous step, $\bm{u_0}$ the control input from the previous step, $\bm{\nu}$ the reference value and $\bm{G(x_0)}$ the control effectiveness matrix.
-With $\bm{\Delta u=u-u_0}$ the control law from Equation \ref{eq:u_control_law_indi} represents an incremental version of the Equation \ref{eq:u_control_law}.
-Instead of computing the complete control input command $\bm{u}$, this control law results in computing the increment of the control input $\bm{\Delta u}$ and adding it to the previous value $\bm{u_0}$.
+where $\bm{\dot{x}}_0$ is a measurable value from the previous step, $\bm{u_0}$ the control input from the previous step, $\bm{\nu}$ the reference value and $\bm{G}(\bm{x}_0)$ the control effectiveness matrix.
+With $\bm{\Delta u}=\bm{u}-\bm{u}_0$ the control law from Equation \ref{eq:u_control_law_indi} represents an incremental version of the Equation \ref{eq:u_control_law}.
+Instead of computing the complete control input command $\bm{u}$, this control law results in computing the increment of the control input $\bm{\Delta u}$ and adding it to the previous value $\bm{u}_0$.
 As it is less dependent on the model of the system dynamics, it is able to increase the robustness of the system \cite{Sieberling}.
@@
 
-- Derivation of the inner INDI loop (what we want to control, detailed equations).
+In this subsection, using theory from \ref{subsec:indi_general} the inner loop \acrshort{INDI} controller is derived to control angular acceleration of the Crazyflie quadrotor.
+Equation \ref{eq:ang_momentum} from section \ref{sec:eqs_motion} serves as a basis for this derivation.
+This equation is also augmented with a thrust $T$ of all four rotors.
+As only the body-fixed frame is used for this derivation the subscripts $B$ are not used in this subsection.
+Also all external forces and moments apply to the center of gravity of the quadrotor, thus the upperscripts $G$ are also omitted.
+Solving equation \ref{eq:ang_momentum} for the angular acceleration $\dot{\bm{\omega}}$ results in
+\begin{equation}
+	\begin{bmatrix}
+		\dot{\bm{\omega}}\\
+		T
+	\end{bmatrix} = 
+	\underbrace{
+	\begin{bmatrix}
+		-\bm{I}^{-1} \big(\bm{\omega} \times \bm{I} \bm{\omega} \big)\\
+		0
+	\end{bmatrix}}_\text{$\bm{F}(\bm{\omega})$} +
+	\underbrace{	
+	\begin{bmatrix}
+		\bm{I}^{-1} \big( \bm{M}_G + \bm{M}_{A} +  \bm{M}_{P} \big)\\
+		T
+	\end{bmatrix}}_\text{$\bm{G}(\bm{\omega}, \bm{\Omega}, \bm{\dot{\Omega}})$}
+	\label{eq:main_eom_indi_inner}
+\end{equation}
+where $\bm{\omega}$ and $\dot{\bm{\omega}}$ are angular velocity and acceleration of the body-fixed frame ($B$) with respect to the \acrshort{NED} ($O$) coordinate frame, $\bm{M}_G$ the gravitational moment, $\bm{M}_A$ the aerodynamic moment and $\bm{M}_P$ propulsion moment.
+It is assumed that the gravitational force is applied to the center of gravity of the quadrotor and does not cause any moment around it.
+Due to the absence of the aerodynamic moment this term is omitted.
+It can also be seen as disturbance.
+The remaining propulsion moment is written as $\bm{M}_P=\bm{M}_C-\bm{M}_{gyro}$ where $\bm{M}_C$ is the control moment generated by the rotors and $\bm{M}_{gyro}$ the moment containing the gyroscopic effect of the rotors.
+This two moments can be explicitly written as
+\begin{equation}
+	\bm{M}_C = 	
+	\begin{bmatrix}
+		-bk_F & bk_F & bk_F & -bk_F \\
+		lk_F & lk_F & -lk_F & -lk_F \\
+		k_M & -k_M & k_M & -k_M 
+	\end{bmatrix} \bm{\Omega}
+	\label{eq:m_c}
+\end{equation}
+\begin{equation}
+	\begin{split}
+	\bm{M}_{gyro} = 
+	\begin{bmatrix}
+		0 & 0 & 0 & 0 \\
+		0 & 0 & 0 & 0 \\
+		I_{rzz} & -I_{rzz} & I_{rzz} & -I_{rzz}
+	\end{bmatrix} \bm{\dot{\Omega}}	+
+	\begin{bmatrix}
+		\bm{\omega}_y & 0 & 0 \\
+		0 & \bm{\omega}_x & 0 \\
+		0 & 0 & 0 
+	\end{bmatrix}	
+	\begin{bmatrix}
+		I_{rzz} & -I_{rzz} & I_{rzz} & -I_{rzz} \\
+		-I_{rzz} & I_{rzz} & -I_{rzz} & I_{rzz} \\
+		0 & 0 & 0 & 0 
+	\end{bmatrix} \bm{\omega}
+	\label{eq:m_gyro}
+	\end{split}
+\end{equation}
+where $I_{rzz}$ is the element of the inertia matrix $I_{r}$ of the rotor, $l$ and $b$ lever arms as denoted in the Figure (...), $k_F$ and $k_M$ force and moment constants of the rotors.
+
+As already explained in the previous section to derive the incremental control law the Taylor series expansion is perfromed on the Equation \ref{eq:main_eom_indi_inner}
+\begin{equation}
+	\begin{split}
+		\begin{bmatrix}
+			\bm{\dot{\omega}}\\
+			T
+		\end{bmatrix} &= \bm{F}(\bm{\omega}_0) + \bm{G}(\bm{\omega}_0, \bm{\Omega}_0, \bm{\dot{\Omega}}_0) \\
+		&+ \frac{\partial}{\partial \bm{\omega}} \big[\bm{F}(\bm{\omega}) + \bm{G}(\bm{\omega}_0, \bm{\Omega}_0, \bm{\dot{\Omega}}_0) \big] \bigg| _{\bm{\omega}=\bm{\omega}_0} (\bm{\omega}-\bm{\omega}_0) \\
+		&+ \frac{\partial}{\partial \bm{\Omega}} \big[\bm{G}(\bm{\omega}_0, \bm{\Omega}, \bm{\dot{\Omega}}_0) \big] \bigg| _{\bm{\Omega}=\bm{\Omega}_0} (\bm{\Omega}-\bm{\Omega}_0) \\
+		&+ \frac{\partial}{\partial \bm{\dot{\Omega}}} \big[\bm{G}(\bm{\omega}_0, \bm{\Omega}_0, \bm{\dot{\Omega}}) \big] \bigg| _{\bm{\dot{\Omega}}=\bm{\dot{\Omega}}_0} (\bm{\dot{\Omega}}-\bm{\dot{\Omega}}_0)
+		\label{eq:main_eom_indi_inner_taylor}
+	\end{split}
+\end{equation}
+The first term of this equation is the angular acceleration based on the current angular rates $\bm{\Omega}_0$ and inputs $\bm{\omega}_0$ and can be denoted as $\bm{\dot{\omega}}_0$.
+
+\begin{equation}
+	\begin{bmatrix}
+		\bm{\dot{\omega}}\\
+		T
+	\end{bmatrix} = 
+	\begin{bmatrix}
+		\bm{\dot{\omega}}_0\\
+		T_0
+	\end{bmatrix} + \bm{G}_1(\bm{\Omega} - \bm{\Omega}_0) + T_S \bm{G}_2(\bm{\dot{\Omega}} - \bm{\dot{\Omega}}_0)
+	\label{eq:TODO}
+\end{equation}
+
+\begin{equation}
+	\bm{G}_1 = 
+	\begin{bmatrix}
+		\bm{I}^{-1}\begin{bmatrix}
+			-bk_F & bk_F & bk_F & -bk_F \\
+			lk_F & lk_F & -lk_F & -lk_F \\
+			k_M & -k_M & k_M & -k_M 
+		\end{bmatrix} + 	
+		\begin{bmatrix}
+			\bm{\omega}_y & 0 & 0 \\
+			0 & \bm{\omega}_x & 0 \\
+			0 & 0 & 0 
+		\end{bmatrix}	
+		\begin{bmatrix}
+			I_{rzz} & -I_{rzz} & I_{rzz} & -I_{rzz} \\
+			-I_{rzz} & I_{rzz} & -I_{rzz} & I_{rzz} \\
+			0 & 0 & 0 & 0 
+		\end{bmatrix}\\
+			k_F \bm{1}_{1\times4}
+	\end{bmatrix}
+	\begin{bmatrix}
+		\Omega_1\\
+		\Omega_2\\
+		\Omega_3\\
+		\Omega_4
+	\end{bmatrix}
+	\label{eq:TODO}
+\end{equation}
+
+\begin{equation}
+	\bm{G}_2 = 
+	\begin{bmatrix}
+		\bm{I}^{-1} T_S^{-1}\begin{bmatrix}
+			0 & 0 & 0 & 0 \\
+			0 & 0 & 0 & 0 \\
+			I_{rzz} & -I_{rzz} & I_{rzz} & -I_{rzz}
+		\end{bmatrix} \\
+		\bm{0}_{1\times4}
+	\end{bmatrix}
+	\begin{bmatrix}
+		\dot{\Omega}_1\\
+		\dot{\Omega}_2\\
+		\dot{\Omega}_3\\
+		\dot{\Omega}_4
+	\end{bmatrix}
+	\label{eq:TODO}
+\end{equation}
+
+\begin{equation}
+	\begin{bmatrix}
+		\bm{\dot{\omega}}\\
+		T
+	\end{bmatrix} = 
+	\begin{bmatrix}
+		\bm{\dot{\omega}}_f\\
+		T_f
+	\end{bmatrix} + (\bm{G}_1+\bm{G}_2)(\bm{\Omega} - \bm{\Omega}_f) - \bm{G}_2z^{-1}(\bm{\Omega} - \bm{\Omega}_f)
+	\label{eq:TODO}
+\end{equation}
+
+\begin{equation}
+	\begin{split}
+		\bm{\dot{\Omega}}_c = \bm{\dot{\Omega}} = \bm{\dot{\Omega}}_f + (\bm{G}_1+\bm{G}_2)^{-1} \Bigg(
+		\begin{bmatrix}
+			\bm{\nu} - \bm{\dot{\Omega}}_f\\
+			\tilde{T}
+		\end{bmatrix} + \bm{G}_2z^{-1}(\bm{\Omega} - \bm{\Omega}_f) \Bigg)
+		\label{eq:TODO}	
+	\end{split}
+\end{equation}
+
+Note: \\
+- Name equations\\
+- Ts explain\\
+- remove brackets AND indices from bm\\
+- describe Attitude control with PD\\
+- derivation is based on the work of Smeur\\
+- Derivation of the inner INDI loop (what we want to control, detailed equations). \\
 
@@
 \section{Implementation on the Hardware} \label{sec:implementation_on_hardware}
+
+\subsection{Parameter Estimation} \label{subsec:parameter_estimation}
+
+- Actuator Dynamics (Estimation of the time constant) \\
+- Estimation of the control effectiveness parameters G1, G2
 
@@
 \end{document}
+
+%\begin{equation}
+%	\begin{bmatrix}
+%		\dot{\bm{\omega}}\\
+%		T
+%	\end{bmatrix} = \bm{F}(\bm{\omega}) + \bm{G}(\bm{\omega}, \bm{\Omega}, \bm{\dot{\Omega}})
+%	\label{eq:TODO}
+%\end{equation}

### 2020-01-20 code/actuator_dynamics/main.m

@@ -1,0 +1,149 @@
+clc 
+clear 
+close all
+
+%% Parameter 
+
+plot_full = 0;
+plot_4th = 0;
+plot_est = 0;
+
+T_sample = 0.005;                           % time between two samples in [s]
+
+
+%% Read data
+
+filename = 'experiment_thrust_changes.log';
+%filename = 'experiment_roll_changes.log';
+
+log = read_log(filename);                   % log in Hz for two blades
+
+% Choose interested area of the signal
+if (strcmp(filename,'experiment_roll_changes.log'))
+    log = log(1300:2400)/2;                 % log in Hz for one blade
+else
+    log = log(670:1550)/2;
+end
+
+% Filtering, smoothing
+log_sm = smooth(log, 20);
+
+% Plot
+if (plot_full)
+    figure;
+    plot(log)
+    hold on;
+    plot(log_sm)
+    grid on;
+    xlim([0 inf])
+    xlabel('Samples [-]')
+    ylabel('frequency [Hz]')
+end
+
+
+%% Step
+
+step = zeros(1, size(log, 1));
+
+% Generate step functions (manually)
+if (strcmp(filename,'experiment_roll_changes.log'))
+    step(1:40) = 100;
+    step(41:221) = 289; 
+    step(222:433) = 280;
+    step(434:620) = 301;
+    step(621:826) = 270;
+    step(827:1015) = 310;
+else
+    step(1:12) = 33;
+    step(13:207) = 288; 
+    step(208:405) = 314;
+    step(406:606) = 268;
+    step(607:803) = 341;
+end
+if (plot_full) 
+    plot(step); 
+end
+
+%% Extract 4th pt1
+
+if (strcmp(filename,'experiment_roll_changes.log'))
+    log_4th = log(829:970);
+    step_4th = step(829:970)';    
+else    
+    log_4th = log(606:760);
+    step_4th = step(606:760)';
+end
+t = (0:T_sample:(size(log_4th,1)-1)*T_sample)';
+
+if (plot_4th)
+    figure;
+    plot(t, log_4th); hold on; grid on; 
+    plot(t, step_4th)
+    xlabel('Samples [-]')
+    ylabel('frequency [Hz]')
+    xlim([0 inf])
+end
+
+
+%% 1. Option: tfest()
+% Using Matlab function for transfer function estimation
+
+data = iddata(log_4th, step_4th, T_sample);
+
+% Estimate 
+G = tfest(data, 1, 0);
+
+
+%% 2. Option: Least Squares Fit
+
[…]

### 2020-01-20 code/param_est/import_logdata.m

@@ -1,0 +1,36 @@
+%% Import data from text file
+% Script for importing data from the following text file:
+%
+%    filename: /home/evgheniivolodscoi/LRZ Sync+Share/TUM/Master_AS_RCI/Semester_3/Semesterarbeit/code/param_est/csv_data/data_1901.csv
+%
+% Auto-generated by MATLAB on 20-Jan-2020 01:14:14
+
+%% Setup the Import Options
+opts = delimitedTextImportOptions("NumVariables", 9);
+
+% Specify range and delimiter
+opts.DataLines = [2, Inf];
+opts.Delimiter = ",";
+
+% Specify column names and types
+opts.VariableNames = ["tick", "controllerr_roll", "controllerr_pitch", "controllerr_yaw", "controllercmd_thrust", "controllercmd_roll", "controllercmd_pitch", "controllercmd_yaw", "controlleraccelz"];
+opts.VariableTypes = ["double", "double", "double", "double", "double", "double", "double", "double", "double"];
+opts.ExtraColumnsRule = "ignore";
+opts.EmptyLineRule = "read";
+
+% Import the data
+tbl = readtable("csv_data/data_1901.csv", opts);
+
+%% Convert to output type
+tick = tbl.tick;
+gyro_roll = tbl.controllerr_roll;
+gyro_pitch = tbl.controllerr_pitch;
+gyro_yaw = tbl.controllerr_yaw;
+cmd_thrust = tbl.controllercmd_thrust;
+cmd_roll = tbl.controllercmd_roll;
+cmd_pitch = tbl.controllercmd_pitch;
+cmd_yaw = tbl.controllercmd_yaw;
+accelz = tbl.controlleraccelz;
+
+%% Clear temporary variables
+clear opts tbl

### 2020-01-20 temp/backup/actuator_dynamics/read_log.m

@@ -1,13 +1,9 @@
-function B = read_log(filename)
-
 %% Experiment comments:
 % Experiment 1: thrust: 36000, 42000, 30000, 48000, 0 
 % Experiment 2: thrust: 36000 roll: 5000, -5000, 10000, -10000, 0 (byte
 % misalignment, throw first byte away!)
 
-
-%%
-
+filename = 'experiment_roll_changes.log';
 fileID = fopen(filename);
 A = fread(fileID);
 
@@ -22,11 +18,7 @@ fclose(fileID);
 B = zeros(floor(length(A)/2),1);
 
 for n=1:2:length(A)
-    if (n==length(A)) 
-        break; 
-    else
-        B((n+1)/2) = swapbytes(typecast(uint8(A(n:(n+1))), 'uint16'));
-    end
+    B((n+1)/2) = swapbytes(typecast(uint8(A(n:(n+1))), 'uint16'));
 end
 
 % unit of B: Hz (two blades!)

### 2020-01-31 Paper_EV/Paper_EV.tex
Update backup data

@@
 
-- Some facts about Crazyflie hardware (foto, uC frequency, weight, length)
+- Some facts about Crazyflie hardware (foto, uC frequency, weight, length (foto of lever arms), onboard sensors, additional sensors/HW (optoflow, sd-card))
 
@@
 
-- Estimation of relevant components (Matrices...)\\
-- Testing of the PD-gains\\
-- Testing the filter
+- Estimation of the relevant for the HW implementation components (which terms make a huge impact on the controller performance: G1, G1 etc)\\
+- Estimate where value explosion can occur\\
+- Testing the behaviour of the filter\\
+- Testing of the PD-gains
 
 \subsection{Structure} \label{subsec:Structure}
-- Force frame from B to O for an easy representation\\
-- Show each equation of forces with explaining the made assumptions\\
-- Parameters\\
-- Actuator dynamics\\
-- Filter\\
+- Describe some assumptions: eg newton second law frame transformation from B to O for an easy representation\\
+- Present each equation of forces with explaining made assumptions\\
+- Parameter choice ($k_F$, $k_M$, ...)\\
+- Describe the actuator dynamics modelling\\
+- Describe the filter transfer function\\
 - Images of the Simulink model
@@
 \subsection{Simulation Results} \label{subsec:simulation_results}
+
+- Plot differences with or without some terms (G1, G2\_yaw) \\
 
@@
 
-- Actuator Dynamics (Estimation of the time constant) \\
-- Estimation of the control effectiveness parameters G1, G2
+- Actuator Dynamics (Estimation of the time constant), plot response with estimated constant\\
+- Estimation of the control effectiveness parameters G1, G2 for inner INDI (describe performed flight to log data), plot the curve with contribution of G1, G2 to the fitting\\
+- PD gain tuning for inner INDI (using pd\_inner\_cs(), show plots with different D-gains (e.g 25, 10 and 3) to see different damping behaviour), Before explaining gain tuning present all relevant transfer functions of the closed and open loops\\
+- Outer loop (show new diagram of the controller)
 
@@
 
-\subsection{Testing with contact Forces and Moments} \label{subsec:testing_with_fandm}
+\subsection{Testing with contact Forces and Moments?} \label{subsec:testing_with_fandm}
 
@@
 \chaptermark{Results}
+
+- To make the controller work a minimal knowledge of the system dynymics is need.
+Nevertherless G1, G2 still have to estimated accuratly because this 2 parameters do have inpact on the controller performance.
 

### 2020-01-31 code/Simulink/Crazyflie_Simulation/inner_pd_cs.m

@@ -27,13 +27,17 @@ function inner_pd_cs(k_omega_in, k_eta_in)
                             ( (Ts^2*K_eta*K_omega*C1 + Ts*K_omega*C1 + 1)*z^3 + ... 
                               (C2-2)*z^2 + (-Ts*K_omega*C1 - 2*C2 + 1)*z + C2 );
 
+            figure(1);
+            step(TF_etaref_eta); hold on; grid on;
+                   
             % Compute poles of TF_etaref_eta
             display(['K_omega=', num2str(K_omega), ', K_eta=', num2str(K_eta)])
             p = pole(TF_etaref_eta)
 
+            %figure(2);
             % Plot poles
             name = ['KOmega= ', num2str(K_omega), ', KEta= ', num2str(K_eta)];
-            pzmap(TF_etaref_eta); hold on; axis equal;
+            %pzmap(TF_etaref_eta); hold on; axis equal;
 
             % Plot settings
             grid on; 

### 2020-01-31 code/actuator_dynamics/actuator_dynamics.m

@@ -1,0 +1,149 @@
+clc 
+clear 
+close all
+
+%% Parameter 
+
+plot_full = 1;
+plot_4th = 0;
+plot_est = 1;
+
+T_sample = 0.005;                           % time between two samples in [s]
+
+
+%% Read data
+
+filename = 'experiment_thrust_changes.log';
+%filename = 'experiment_roll_changes.log';
+
+log = read_log(filename);                   % log in Hz for two blades
+
+% Choose interested area of the signal
+if (strcmp(filename,'experiment_roll_changes.log'))
+    log = log(1300:2400)/2;                 % log in Hz for one blade
+else
+    log = log(670:1550)/2;
+end
+
+% Filtering, smoothing
+log_sm = smooth(log, 20);
+
+% Plot
+if (plot_full)
+    figure;
+    plot(log)
+    hold on;
+    plot(log_sm)
+    grid on;
+    xlim([0 inf])
+    xlabel('Samples [-]')
+    ylabel('frequency [Hz]')
+end
+
+
+%% Step
+
+step = zeros(1, size(log, 1));
+
+% Generate step functions (manually)
+if (strcmp(filename,'experiment_roll_changes.log'))
+    step(1:40) = 100;
+    step(41:221) = 289; 
+    step(222:433) = 280;
+    step(434:620) = 301;
+    step(621:826) = 270;
+    step(827:1015) = 310;
+else
+    step(1:12) = 33;
+    step(13:207) = 288; 
+    step(208:405) = 314;
+    step(406:606) = 268;
+    step(607:803) = 341;
+end
+if (plot_full) 
+    plot(step); 
+end
+
+%% Extract 4th pt1
+
+if (strcmp(filename,'experiment_roll_changes.log'))
+    log_4th = log(829:970);
+    step_4th = step(829:970)';    
+else    
+    log_4th = log(606:760);
+    step_4th = step(606:760)';
+end
+t = (0:T_sample:(size(log_4th,1)-1)*T_sample)';
+
+if (plot_4th)
+    figure;
+    plot(t, log_4th); hold on; grid on; 
+    plot(t, step_4th)
+    xlabel('Samples [-]')
+    ylabel('frequency [Hz]')
+    xlim([0 inf])
+end
+
+
+%% 1. Option: tfest()
+% Using Matlab function for transfer function estimation
+
+data = iddata(log_4th, step_4th, T_sample);
+
+% Estimate 
+G = tfest(data, 1, 0);
+
+
+%% 2. Option: Least Squares Fit
+
[…]

### 2020-01-31 code/param_est/control_effectiveness_estimation.m

@@ -54,7 +54,7 @@ accelz = dataArray{1, 9}(1:N); %accel body z
 %% Filter signals
 
 % The filter needed to get rid of the noise on the gyro
-[b, a] = butter(4,4/(512/2));
+[b, a] = butter(4,4/(500/2));
 first_order_dynamics_constant = 0.0319;
 
 % Filter the stabilization command with the actuator dynamics to get an
@@ -98,10 +98,11 @@ disp('G2_yaw is scaled by 1000, this is intended')
 % plot(cmd_filtd(:,3)*G_pitch)
 % title('\Delta angular acceleration pitch')
 % 
-% figure;
-% plot(angular_accel_filtd(:,3)); hold on
-% plot([cmd_filtd(:,4) cmd_filtdd(:,4)]*G_yaw)
-% title('\Delta angular acceleration yaw')
+figure;
+plot(angular_accel_filtd(:,3)); hold on
+plot([cmd_filtd(:,4) cmd_filtdd(:,4)]*G_yaw)
+plot([cmd_filtd(:,4) 0*cmd_filtdd(:,4)]*G_yaw)
+title('\Delta angular acceleration yaw')
 % 
 % figure;
 % plot(accelzd_filt); hold on

### 2020-01-31 code/param_est/import_logdata.m

@@ -1,3 +1,7 @@
+function [tick, gyro_roll, gyro_pitch, gyro_yaw, ...
+         cmd_thrust, cmd_roll, cmd_pitch, cmd_yaw,...
+         accelz] = import_logdata(filename)
+
 %% Import data from text file
 % Script for importing data from the following text file:
 %
@@ -19,7 +23,7 @@ opts.ExtraColumnsRule = "ignore";
 opts.EmptyLineRule = "read";
 
 % Import the data
-tbl = readtable("csv_data/data_1901.csv", opts);
+tbl = readtable(filename, opts);
 
 %% Convert to output type
 tick = tbl.tick;
@@ -34,3 +38,5 @@ accelz = tbl.controlleraccelz;
 
 %% Clear temporary variables
 clear opts tbl
+
+end

### 2020-01-31 code/param_est/thrust_est.m

@@ -1,0 +1,12 @@
+clc
+clear 
+close all
+
+%% 
+
+filename = "csv_data/data_3001_1.csv";
+
+%% Import data
+
+[tick, gyro_roll, gyro_pitch, gyro_yaw, cmd_thrust, cmd_roll,... 
+ cmd_pitch, cmd_yaw, accelz] = import_logdata(filename);

### 2020-01-31 crazyflie-firmware/src/modules/src/controller_indi.c

@@ -30,10 +30,26 @@ static float bound_control_input = 32000.0f;
 
 static attitude_t attitudeDesired;
 static attitude_t rateDesired;
+
+// ev_tag
+static struct Vectr positionRef; 
+static struct Vectr velocityRef;
+float K_xi_x = 0.7;
+float K_xi_y = 0.7;
+float K_xi_z = 0.7;
+float K_dxi_x = 0.8;
+float K_dxi_y = 0.8;
+float K_dxi_z = 0.8;
+static float pos_set_x, pos_set_y, pos_set_z; 
+static float vel_set_x, vel_set_y, vel_set_z;
+static float posS_x, posS_y, posS_z;
+static float velS_x, velS_y, velS_z;
+// ev_tag
+
 static float actuatorThrust;
-static float roll_kp = 6.0f;
-static float pitch_kp = 6.0f;
-static float yaw_kp = 6.0f;
+static float roll_kp = 3.0f;
+static float pitch_kp = 3.0f;
+static float yaw_kp = 3.0f;
 
 static float r_roll;
 static float r_pitch;
@@ -73,6 +89,9 @@ void indi_init_filters(void)
 	for (int8_t i = 0; i < 3; i++) {
 		init_butterworth_2_low_pass(&indi.u[i], tau_axis[i], sample_time, 0.0f);
 		init_butterworth_2_low_pass(&indi.rate[i], tau_axis[i], sample_time, 0.0f);
+		init_butterworth_2_low_pass(&indi.ddxi[i], tau_axis[i], sample_time, 0.0f);
+		init_butterworth_2_low_pass(&indi.ang[i], tau_axis[i], sample_time, 0.0f);
+		init_butterworth_2_low_pass(&indi.thr[i], tau_axis[i], sample_time, 0.0f);
 	}
 }
 
@@ -89,6 +108,26 @@ static inline void filter_pqr(Butterworth2LowPass *filter, struct FloatRates *ne
 	update_butterworth_2_low_pass(&filter[2], new_values->r);
 }
 
+// ev_tag
+static inline void filter_ddxi(Butterworth2LowPass *filter, struct Vectr *old_values, struct Vectr *new_values)
+{
+	new_values->x = update_butterworth_2_low_pass(&filter[0], old_values->x);
+	new_values->y = update_butterworth_2_low_pass(&filter[1], old_values->y);
[…]

### 2020-01-31 temp/motion_commander_demo.py

@@ -1,0 +1,100 @@
+# -*- coding: utf-8 -*-
+#
+#     ||          ____  _ __
+#  +------+      / __ )(_) /_______________ _____  ___
+#  | 0xBC |     / __  / / __/ ___/ ___/ __ `/_  / / _ \
+#  +------+    / /_/ / / /_/ /__/ /  / /_/ / / /_/  __/
+#   ||  ||    /_____/_/\__/\___/_/   \__,_/ /___/\___/
+#
+#  Copyright (C) 2017 Bitcraze AB
+#
+#  Crazyflie Nano Quadcopter Client
+#
+#  This program is free software; you can redistribute it and/or
+#  modify it under the terms of the GNU General Public License
+#  as published by the Free Software Foundation; either version 2
+#  of the License, or (at your option) any later version.
+#
+#  This program is distributed in the hope that it will be useful,
+#  but WITHOUT ANY WARRANTY; without even the implied warranty of
+#  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+#  GNU General Public License for more details.
+#  You should have received a copy of the GNU General Public License
+#  along with this program; if not, write to the Free Software
+#  Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston,
+#  MA  02110-1301, USA.
+"""
+This script shows the basic use of the MotionCommander class.
+
+Simple example that connects to the crazyflie at `URI` and runs a
+sequence. This script requires some kind of location system, it has been
+tested with (and designed for) the flow deck.
+
+The MotionCommander uses velocity setpoints.
+
+Change the URI variable to your Crazyflie configuration.
+"""
+import logging
+import time
+
+import cflib.crtp
+from cflib.crazyflie import Crazyflie
+from cflib.crazyflie.syncCrazyflie import SyncCrazyflie
+from cflib.positioning.motion_commander import MotionCommander
+
+URI = 'radio://0/80/2M'
+
+# Only output errors from the logging framework
+logging.basicConfig(level=logging.ERROR)
+
+
+if __name__ == '__main__':
+    # Initialize the low-level drivers (don't list the debug drivers)
+    cflib.crtp.init_drivers(enable_debug_driver=False)
+
+    with SyncCrazyflie(URI, cf=Crazyflie(rw_cache='./cache')) as scf:
+        # We take off when the commander is created
+        with MotionCommander(scf) as mc:
+            time.sleep(1)
+
[…]

### 2020-02-19 Paper_EV/Paper_EV.tex
Just backup

@@
 - Actuator Dynamics (Estimation of the time constant), plot response with estimated constant\\
+- Thrust dynamics estimation\\
 - Estimation of the control effectiveness parameters G1, G2 for inner INDI (describe performed flight to log data), plot the curve with contribution of G1, G2 to the fitting\\

### 2020-02-19 code/cf_sdlogger/main.py

@@ -3,8 +3,8 @@ import csv
 from matplotlib import pyplot as plt
 
 # Decode binary log file
-log = cff.decode('log_data/log_3001_1')
-csv_file = 'csv_data/data_3001_1.csv'
+log = cff.decode('log_data/log_thrust_est_4')
+csv_file = 'csv_data/log_thrust_est_4.csv'
 
 # Begin writing to csv
 with open(csv_file, mode='w') as file:

### 2020-02-19 crazyflie-firmware/src/modules/src/controller_indi.c

@@ -30,20 +30,28 @@ static float bound_control_input = 32000.0f;
 
 static attitude_t attitudeDesired;
 static attitude_t rateDesired;
+static float attYawError; 
 
 // ev_tag
 static struct Vectr positionRef; 
 static struct Vectr velocityRef;
-float K_xi_x = 0.7;
-float K_xi_y = 0.7;
-float K_xi_z = 0.7;
-float K_dxi_x = 0.8;
-float K_dxi_y = 0.8;
-float K_dxi_z = 0.8;
+
+float K_xi_x = 0.7f;
+float K_xi_y = 0.7f;
+float K_xi_z = 0.7f;
+float K_dxi_x = 5.0f;
+float K_dxi_y = 5.0f;
+float K_dxi_z = 5.0f;
+float K_thr = 0.00024730f;
+
 static float pos_set_x, pos_set_y, pos_set_z; 
 static float vel_set_x, vel_set_y, vel_set_z;
 static float posS_x, posS_y, posS_z;
 static float velS_x, velS_y, velS_z;
+static float gyr_p, gyr_q, gyr_r;
+
+// TODO: DELETE
+static float arm = 0;
 // ev_tag
 
 static float actuatorThrust;
@@ -128,6 +136,21 @@ static inline void filter_thrust(Butterworth2LowPass *filter, float *old_thrust,
 	*new_thrust = update_butterworth_2_low_pass(&filter[0], *old_thrust);
 }
 
+
+// Computes transformation matrix from body frame (index B) into NED frame (index O)
+void m_ob(struct Angles att, float matrix[3][3]) {
+
+	matrix[0][0] = cosf(att.theta)*cosf(att.psi);
+	matrix[0][1] = sinf(att.phi)*sinf(att.theta)*cosf(att.psi) - cosf(att.phi)*sinf(att.psi); 
+	matrix[0][2] = cosf(att.phi)*sinf(att.theta)*cosf(att.psi) + sinf(att.phi)*sinf(att.psi);
+	matrix[1][0] = cosf(att.theta)*sinf(att.psi);
+	matrix[1][1] = sinf(att.phi)*sinf(att.theta)*sinf(att.psi) + cosf(att.phi)*cosf(att.psi);
+	matrix[1][2] = cosf(att.phi)*sinf(att.theta)*sinf(att.psi) - sinf(att.phi)*cosf(att.psi);
+	matrix[2][0] = -sinf(att.theta);
[…]

### 2020-02-19 temp/trofo_matrix_OB_test/mob.c

@@ -1,0 +1,50 @@
+
+#include <stdio.h>
+#include <math.h>
+
+
+struct Angles {
+  float phi; 
+  float theta;
+  float psi;
+};
+
+void m_ob(struct Angles att, float matrix[3][3]) {
+
+	// Compute transformation matrix from body frame (index B) into NED frame (index O)
+	matrix[0][0] = cosf(att.theta)*cosf(att.psi);
+	matrix[0][1] = sinf(att.phi)*sinf(att.theta)*cosf(att.psi) - cosf(att.phi)*sinf(att.psi); 
+	matrix[0][2] = cosf(att.phi)*sinf(att.theta)*cosf(att.psi) + sinf(att.phi)*sinf(att.psi);
+	matrix[1][0] = cosf(att.theta)*sinf(att.psi);
+	matrix[1][1] = sinf(att.phi)*sinf(att.theta)*sinf(att.psi) + cosf(att.phi)*cosf(att.psi);
+	matrix[1][2] = cosf(att.phi)*sinf(att.theta)*sinf(att.psi) - sinf(att.phi)*cosf(att.psi);
+	matrix[2][0] = -sinf(att.theta);
+	matrix[2][1] = sinf(att.phi)*cosf(att.theta);
+	matrix[2][2] = cosf(att.phi)*cosf(att.theta);
+}
+
+int main () {
+
+	struct Angles att = {
+		.phi = 0.9,
+		.theta = 0.8,
+		.psi = 0.2
+	};
+
+	
+
+	float matrix[3][3] = {0, 0, 0, 0, 0, 0, 0, 0, 0};
+
+
+	m_ob(att, matrix);
+
+	int r, c; 
+	for(r=0; r<3; r++) {
+		for(c=0; c<3; c++) {
+			printf("M_OB%d%d: %.5f\n", r+1, c+1, matrix[r][c]);
+		}
+	}
+	
+
+	return 0;
+}

### 2020-03-04 Paper_EV/Paper_EV.tex
Chapter 2: Theoretical Background finished, light improvements necessary

@@
 The dynamic equations which describe the general motion of an aircraft are usually coupled first order implicit nonlinear differential equations.
-However, in many cases it is sufficient to use their simplified versions (Source needed!).
+However, in many cases it is sufficient to use their simplified versions (TODO:Source needed!).
 This section presents simplified general \acrshort{EOM} and describes the assumptions which were considered to derive them.
 
-For the derivation of the equation of motion the aircraft system will be assumed to be a rigid body.
+For the derivation of the equations of motion the aircraft system will be assumed to be a rigid body.
 Such a rigid body system can be described uniquely by 12 states.
@@
 The rotational motion of a body is described with the angular momentum equation.
-To derive it, additionally to the assumptions made above it is also considered that the mass and the mass distribution are quasistationary, meaning $\frac{d}{dt}m=0$ and $\frac{d}{dt}(I)_B=0$ respectively?.
-$(I)_B$ is the inertia tensor of the body defined in the body-fixed frame.
+To derive it, additionally to the assumptions made above it is also considered that the mass and the mass distribution are quasistationary, meaning $\frac{d}{dt}m=0$ and $\frac{d}{dt}(\bm{I})_B=0$ with $(\bm{I})_B$ being the inertia tensor of the body defined in the body-fixed frame.
 Thus, the angular momentum is
@@
 
-The Equations (\ref{eq:lin_momentum})-(\ref{eq:position_diff_eq}) presented above can be used to represent a motion of a general aircraft.
+The Equations (\ref{eq:lin_momentum})-(\ref{eq:position_diff_eq}) presented above can be used to represent a motion of a general aircraft in a three-dimensional space.
 Note that terms $\sum(\bm{F}^G)_B$ and $\sum (\bm{M}^G)_B$ contain all external forces and moments acting on the rigid body.
-Considering an aircraft system these could be the aerodynamic forces and moments caused by the air flow, propulsion forces and moments, forces caused by the gravitation etc..
-The detailed modelling of external forces and moments is presented in chapter (...Simulink).
+Considering a general aircraft system, these could be the aerodynamic forces and moments caused by the air flow, propulsion forces and moments, forces caused by the gravitation etc..
+The detailed modelling of external forces and moments is presented in chapter \ref{sec:simulink_model}.
 
@@
 		\bm{\dot{y}} &=  \frac{\partial\bm{y}}{\partial t} = \frac{\partial\bm{h}(\bm{x})}{\partial t} \frac{\partial\bm{x}}{\partial t} = \frac{\partial\bm{h}(\bm{x})}{\partial t} \dot{\bm{x}} = \nabla\bm{h}(\bm{x}) [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \\
-		&= \nabla\bm{h}(\bm{x}) \bm{f}(\bm{x}) + \nabla\bm{h}(\bm{x}) \bm{G}(\bm{x})\bm{u}] = L_{\bm{f}} \bm{h}(\bm{x}) + L_{\bm{G}} \bm{h}(\bm{x}) \bm{u} 
+		&= \nabla\bm{h}(\bm{x}) \bm{f}(\bm{x}) + \nabla\bm{h}(\bm{x}) \bm{G}(\bm{x})\bm{u} = L_{\bm{f}} \bm{h}(\bm{x}) + L_{\bm{G}} \bm{h}(\bm{x}) \bm{u} 
 		\label{eq:dy}
@@
 Considering very small time increments of the controller loop and applying the \textit{principle of time scale separation} the second term vanishes.
-This is a valid assumption if the dynamics of the actuators is fast compared with the dynamics of the system.
+This is a valid assumption if the dynamics of the actuators is fast compared with the dynamics of the system \cite{Silva}.
 Thus, the Equation \ref{eq:nonlin_sys_taylor2} is further simplified to
@@
 \end{equation}
-Solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\bm{\dot{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law is obtained
+By solving Equation \ref{eq:nonlin_sys_indi} for $\bm{u}$ and substituting $\bm{\dot{y}}$ with $\bm{\nu}$, the \acrshort{INDI} control law is obtained
 \begin{equation}
@@
 In this subsection, using theory from \ref{subsec:indi_general} the inner loop \acrshort{INDI} controller is derived to control angular acceleration of the Crazyflie quadrotor.
+The derivation of the inner loop, as well as the outer loop controllers is based on the \acrshort{INDI} controller architecture introduced by Smeur \cite{Smeur1}, \cite{Smeur2}.
 Equation \ref{eq:ang_momentum} from section \ref{sec:eqs_motion} serves as a basis for this derivation.
-This equation is also augmented with a thrust $T$ of all four rotors.
-As only the body-fixed frame is used for this derivation the subscripts $B$ are not used in this subsection.
-Also all external forces and moments apply to the center of gravity of the quadrotor, thus the upperscripts $G$ are also omitted.
-Solving equation \ref{eq:ang_momentum} for the angular acceleration $\dot{\bm{\omega}}$ results in
+The desired variable to be controlled by the inner loop \acrshort{INDI} is the angular acceleration of the quadrotor in the body-fixed coordinate frame.
+As in the case of a real quadrotor control problem the value of the thrust can be seen as an output of the dynamic system, it makes sense to incorporate thrust as a control variable into the control law as well.
+Thus, the angular momentum Equation \ref{eq:ang_momentum} is augmented with the total thrust $T$ of all four rotors \cite{Smeur2}.
+As only the body-fixed frame is used in the following control law derivation, the subscripts $B$ are not used in this subsection.
+Also all external forces and moments apply to the center of gravity of the quadrotor, thus the superscripts $G$ are also omitted.
+Solving Equation \ref{eq:ang_momentum} for the angular acceleration results in
 \begin{equation}
@@
 \end{equation}
-where $\bm{\omega}$ and $\dot{\bm{\omega}}$ are angular velocity and acceleration of the body-fixed frame ($B$) with respect to the \acrshort{NED} ($O$) coordinate frame, $\bm{M}_G$ the gravitational moment, $\bm{M}_A$ the aerodynamic moment and $\bm{M}_P$ propulsion moment.
+where $\bm{\omega}$ and $\dot{\bm{\omega}}$ are angular velocity and acceleration of the body-fixed frame ($B$) with respect to the \acrshort{NED} ($O$) coordinate frame, $\bm{M}_G$ the gravitational moment, $\bm{M}_A$ the aerodynamic moment and $\bm{M}_P$ the propulsion moment.
+The vector $\bm{\Omega}$ contains angular velocities of all four rotors and serves as an input variable of the system.
 It is assumed that the gravitational force is applied to the center of gravity of the quadrotor and does not cause any moment around it.
-Due to the absence of the aerodynamic moment this term is omitted.
-It can also be seen as disturbance.
+Due to the absence of the aerodynamic moment this term is also omitted and can be seen as a disturbance \cite{Smeur1}.
 The remaining propulsion moment is written as $\bm{M}_P=\bm{M}_C-\bm{M}_{gyro}$ where $\bm{M}_C$ is the control moment generated by the rotors and $\bm{M}_{gyro}$ the moment containing the gyroscopic effect of the rotors.
@@
 \end{equation}
-where $I_{rzz}$ is the element of the inertia matrix $I_{r}$ of the rotor, $l$ and $b$ lever arms as denoted in the Figure (...), $k_F$ and $k_M$ force and moment constants of the rotors.
+where $I_{rzz}$ is the element of the inertia matrix $I_{r}$ of the rotor, $l$ and $b$ lever arms as denoted in the Figure (TODO:Figure), $k_F$ and $k_M$ force and moment constants of the rotors.
 
@@
 \end{equation}
-The first term of this equation is the angular acceleration based on the current angular rates $\bm{\Omega}_0$ and inputs $\bm{\omega}_0$ and can be denoted as $\bm{\dot{\omega}}_0$.
-
+By applying differentiation and rewriting some of the terms, following equation is obtained
 \begin{equation}
@@
 	\end{bmatrix} + \bm{G}_1(\bm{\Omega} - \bm{\Omega}_0) + T_S \bm{G}_2(\bm{\dot{\Omega}} - \bm{\dot{\Omega}}_0)
-	\label{eq:TODO}
+	\label{eq:main_eom_indi_inner_lin}
 \end{equation}
-
+The first term of the Equation \ref{eq:main_eom_indi_inner_lin} is the angular acceleration based on the current angular rates $\bm{\omega}_0$ and inputs $\bm{\Omega}_0$ and can be denoted as $\bm{\dot{\omega}}_0$.
+$T_0$ is the current thrust value.
+The last term on the right side of the Equation \ref{eq:main_eom_indi_inner_lin} is scaled with the sample time $T_s$ which is introduced only to simplify further mathematical transformations.
+The expressions of the control moment $\bm{M}_C$ and the gyroscopic moment of the rotors $\bm{M}_{gyro}$ have been summarized to control effectiveness matrices $\bm{G}_1$ and $\bm{G}_2$
 \begin{equation}
@@
 			k_M & -k_M & k_M & -k_M 
-		\end{bmatrix} + 	
+		\end{bmatrix} - 	
 		\begin{bmatrix}
@@
 		\end{bmatrix}\\
-			k_F \bm{1}_{1\times4}
+			k_F \cdot \bm{1}_{1\times4}
 	\end{bmatrix}
-	\begin{bmatrix}
-		\Omega_1\\
-		\Omega_2\\
-		\Omega_3\\
-		\Omega_4
-	\end{bmatrix}
-	\label{eq:TODO}
+	\label{eq:G1}
 \end{equation}
-
 \begin{equation}
@@
 	\begin{bmatrix}
-		\bm{I}^{-1} T_S^{-1}\begin{bmatrix}
+		-\bm{I}^{-1} T_S^{-1}\begin{bmatrix}
 			0 & 0 & 0 & 0 \\
@@
 	\end{bmatrix}
-	\begin{bmatrix}
-		\dot{\Omega}_1\\
-		\dot{\Omega}_2\\
-		\dot{\Omega}_3\\
-		\dot{\Omega}_4
-	\end{bmatrix}
-	\label{eq:TODO}
+	\label{eq:G2}
 \end{equation}
+with the terms $\bm{1}_{1\times4}$ and $\bm{0}_{1\times4}$ being $1\times4$ vectors of ones and zeros, respectively.
 
+To prepare the linearized dynamic Equation \ref{eq:main_eom_indi_inner_lin} for discrete implementation on a computing system, the discrete approximation ($z$ domain) of the derivative is used: $\bm{\dot{\Omega}} = (\bm{\Omega} - \bm{\Omega}z^{-1})T_S^{-1}$.
+Furthermore, angular acceleration $\bm{\dot{\omega}}_0$ which is obtained from the differentiated gyroscope measurements is usually noisy.
+It has been shown, that using a second order filtering can help to reduce measurement nose.
+At the same time such a filter introduces time delay, which has to be considered in the derivation, as it is important to have a unique delay for all variables which are used in the Taylor expansion \cite{Smeur1}.
+Thus, the same second order filter is applied to all variables with a subscript $0$.
+By applying filtering (subscript $f$) and finite differences method to the Equation \ref{eq:main_eom_indi_inner_lin}, its discrete version results in
 \begin{equation}
@@
 	\end{bmatrix} + (\bm{G}_1+\bm{G}_2)(\bm{\Omega} - \bm{\Omega}_f) - \bm{G}_2z^{-1}(\bm{\Omega} - \bm{\Omega}_f)
-	\label{eq:TODO}
+	\label{eq:main_eom_indi_inner_lin_final}
 \end{equation}
-
+By solving Equation \ref{eq:main_eom_indi_inner_lin_final} for $\bm{\dot{\Omega}}$ and substituting $\bm{\dot{\omega}}$ with the equivalent input $\bm{\nu}_{ang}$, the control law of the inner loop is obtained
 \begin{equation}
@@
 		\begin{bmatrix}
-			\bm{\nu} - \bm{\dot{\Omega}}_f\\
+			\bm{\nu}_{ang} - \bm{\dot{\omega}}_f\\
 			\tilde{T}
 		\end{bmatrix} + \bm{G}_2z^{-1}(\bm{\Omega} - \bm{\Omega}_f) \Bigg)
-		\label{eq:TODO}	
+		\label{eq:indi_inner_control_law}	
 	\end{split}
 \end{equation}
-
-Note: \\
-- Name equations\\
-- Ts explain\\
-- remove brackets AND indices from bm\\
-- describe Attitude control with PD\\
-- derivation is based on the work of Smeur\\
-- Derivation of the inner INDI loop (what we want to control, detailed equations). \\
+where $\bm{\dot{\Omega}}$ is a vector of commanded rotational rates for every rotor and $\tilde{T} = T - T_f$ being the thrust increment which is provided by the outer loop \acrshort{INDI}.
+The block diagram of the inner loop \acrshort{INDI} controller is presented in Figure (TODO:Figure).
+In the figure the derived controller which controls the angular acceleration is augmented with two simple controllers which control the angular velocity $\bm{\omega}$ and the attitude $\bm{\eta}$ of the quadrotor.
+Each controller consists of a single gain.
+Thus, the reference values of the \acrshort{INDI} part of the inner loop are provided by these two controllers.
 
@@
 
-- Derivation of the outer INDI loop (what we want to control, detailed equations).
+In this subsection the derivation of the outer loop \acrshort{INDI} controller is introduced.
+The outer loop \acrshort{INDI} controls translational acceleration of the quadrotor.
+Linear momentum Equation \ref{eq:lin_momentum} serves as a basis for this derivation.
+For the simplicity of the further transformations the derivation is performed in the \acrshort{NED} frame (subscript $O$).
+Thus, the Equation \ref{eq:lin_momentum} becomes
+\begin{equation}
+	\begin{split}
+		\sum (\bm{F}^G)_O = m \cdot (\bm{\dot{v}}^G)_{O}
+		\label{eq:lin_momentum_indi_outer}
+	\end{split}
+\end{equation}
+As it is assumed that all forces apply to the center of gravity of the quadrotor, the superscript $G$ is omitted in the future.
+Thus, solving Equation \ref{eq:lin_momentum_indi_outer} for $\bm{\dot{v}}$ and assuming that the sum of all forces acting on the quadrotor consists only of gravitational, propulsive and aerodynamic forces, following equation is obtained
+\begin{equation}
+	\begin{split}
+		\bm{\dot{v}} = m^{-1} ((\bm{F}_G)_O + (\bm{F}_P)_O+ (\bm{F}_A)_O)
+		\label{eq:lin_momentum_indi_outer_simple}
+	\end{split}
+\end{equation}
+The aerodynamic force $(\bm{F}_A)_O$ is modelled as an unknown function of velocity $\bm{v}$ and wind vector $\bm{\chi}$.
+For the gravitational force $(\bm{F}_G)_O$ the simplest one-dimensional gravity model is assumed.
+\begin{equation}
+	\begin{split}
+		(\bm{F}_A)_O = \bm{f}(\bm{v}, \bm{\chi})
+		\label{eq:Fa}
+	\end{split}
+\end{equation}
+\begin{equation}
+	\begin{split}
+		(\bm{F}_G)_O = m 
+		\begin{bmatrix}
+			0\\
+			0\\
+			g
+		\end{bmatrix}_O
+		\label{eq:Fg}
+	\end{split}
+\end{equation}
+The propulsive force $(\bm{F}_P)_O$ (produced by the rotors) has only one nonzero component if defined in the body-fixed frame.
+To transform it to the \acrshort{NED} frame the rotation matrix $\bm{M}_{OB}$ is used.
+This results in
+\begin{equation}
+	\begin{split}
+		(\bm{F}_P)_O = \bm{M}_{OB}
+		\begin{bmatrix}
+			0\\
+			0\\
+			-T
+		\end{bmatrix}_B = 
+		\begin{bmatrix}
+			* & * & c\Psi s\Theta c\Phi + s\Psi s\Phi\\
+			* & * & s\Psi s\Theta c\Phi + c\Psi s\Phi\\
+			* & * & c\Theta c\Phi
+		\end{bmatrix}
+		\begin{bmatrix}
+			0\\
+			0\\
+			-T
+		\end{bmatrix}_B = 
+		\begin{bmatrix}
+			(c\Psi s\Theta c\Phi + s\Psi s\Phi)(-T) \\
+			(s\Psi s\Theta c\Phi + c\Psi s\Phi)(-T) \\
+			(c\Theta c\Phi)(-T)
+		\end{bmatrix}_O
+		\label{eq:Fp}
+	\end{split}
+\end{equation}
+To obtain the incremental form of the linear momentum equation, the same strategy as in the case of the inner loop derivation is applied: the Equation \ref{eq:lin_momentum_indi_outer_simple} is linearized using Taylor series expansion
+\begin{equation}
+	\begin{split}
+		\bm{\dot{v}} &= m^{-1} [\bm{F}_G + \bm{F}_P(\Phi_0, \Theta_0, \Psi_0, T_0)+ \bm{F}_A(\bm{v}_0, \bm{\chi}_0)]  \\		
+		&+ \frac{\partial}{\partial \bm{v}} \big[ \bm{F}_A(\bm{v}, \bm{\chi}_0) \big] \bigg| _{\bm{v}=\bm{v}_0} (\bm{v}-\bm{v}_0) \\
+		&+ \frac{\partial}{\partial \bm{\chi}} \big[ \bm{F}_A(\bm{v}_0, \bm{\chi}) \big] \bigg| _{\bm{\chi}=\bm{\chi}_0} (\bm{\chi}-\bm{\chi}_0) \\
+		&+ \frac{\partial}{\partial \Phi} \big[ \bm{F}_P(\Phi, \Theta_0, \Psi_0, T_0) \big] \bigg| _{\Phi=\Phi_0} (\Phi-\Phi_0) \\
+		&+ \frac{\partial}{\partial \Theta} \big[ \bm{F}_P(\Phi_0, \Theta, \Psi_0, T_0) \big] \bigg| _{\Theta=\Theta_0} (\Theta-\Theta_0) \\
+		&+ \frac{\partial}{\partial \Psi} \big[ \bm{F}_P(\Phi_0, \Theta_0, \Psi, T_0) \big] \bigg| _{\Psi=\Psi_0} (\Psi-\Psi_0) \\
+		&+ \frac{\partial}{\partial T} \big[ \bm{F}_P(\Phi_0, \Theta_0, \Psi_0, T) \big] \bigg| _{T=T_0} (T-T_0) \\
+		\label{eq:main_eom_indi_outer_taylor}
+	\end{split}
+\end{equation}
+The first term on the right side of the Equation \ref{eq:main_eom_indi_outer_taylor} is the acceleration at previous time step $\bm{\dot{v}}_0$.
+It can be obtained from the onboard accelerometer and then tranformed to the \acrshort{NED} frame.
+The next two terms on the right are assumed to be zero since it is very complicated to develop an accurate model of the aerodynamic force as the nature of the wind influence can vary and remains unknown.
+It is also assumed that the change of the yaw angle $\Psi$ is small and can be neglected as well.
+By applying considered assumptions Equation \ref{eq:main_eom_indi_outer_taylor} is written as
+\begin{equation}
+	\begin{split}
+		\bm{\dot{v}} = \bm{\dot{v}}_0 +  m^{-1} \bm{G}(\Phi_0, \Theta_0, \Psi_0, T_0) (\bm{u} - \bm{u}_0)
+		\label{eq:lin_momentum_indi_outer_lin}
+	\end{split}
+\end{equation}
+where
+\begin{equation}
+	\begin{split}
+		\bm{G}(\Phi_0, \Theta_0, \Psi_0, T_0) = 
+		\underbrace{
+		\begin{bmatrix}
+			(-c\Psi_0 s\Theta_0 s\Phi_0 + s\Psi_0 c\Phi_0)T_0  &%
+			c\Psi_0 c\Theta_0 c\Phi_0 T_0 &%
+			c\Psi_0 s\Theta_0 c\Phi_0 + s\Psi_0 s\Phi_0 \\			
+			(-s\Psi_0 s\Theta_0 s\Phi_0 - c\Psi_0 c\Phi_0)T_0 &%
+			s\Psi_0 c\Theta_0 c\Phi_0 T_0 &% 
+			s\Psi_0 s\Theta_0 c\Phi_0 - c\Psi_0 s\Phi_0\\
+			-c\Theta_0 s\Phi_0T_0 &%
+			-s\Theta_0 c\Phi_0T_0 &%
+			c\Theta_0 c\Phi_0
+		\end{bmatrix}}_\text{$\bm{G}(\Phi_0, \Theta_0, \Psi_0, T_0)$}
+		\label{eq:G}
+	\end{split}
+\end{equation}
+and
+\begin{equation}
+	\begin{split}
+		\bm{u} = 
+		\begin{bmatrix}
+			\Phi\\
+			\Theta\\
+			T
+		\end{bmatrix}
+		\label{eq:u_outer}
+	\end{split}
+\end{equation}
+$\bm{G}(\Phi_0, \Theta_0, \Psi_0, T_0)$ is the control effectiveness matrix which is computed based on the attitude and thrust values from the previous step.
+$\bm{u}$ is a vector of control variables which are passed to the inner loop.
+
+The linear acceleration $\bm{\dot{v}}_0$ which is obtained from accelerometer measurements is usually noisy.
+Applying the same filter as in the case of the inner loop derivation, the Equation \ref{eq:lin_momentum_indi_outer_lin} is given by
+\begin{equation}
+	\begin{split}
+		\bm{\dot{v}} = \bm{\dot{v}}_f +  m^{-1} \bm{G}(\Phi_0, \Theta_0, \Psi_0, T_0) (\bm{u} - \bm{u}_f)
+		\label{eq:lin_momentum_indi_outer_lin_final}
+	\end{split}
+\end{equation}
+Solving Equation \ref{eq:lin_momentum_indi_outer_lin_final} for $\bm{u}$ and substituting $\bm{\dot{v}}$ with the equivalent control variable $\bm{\nu}_{lin}$, the control law of the outer loop is obtained
+\begin{equation}
+	\begin{split}
+		\bm{u_c} = \bm{u} = \bm{u}_f +  m \bm{G}^{-1}(\Phi_0, \Theta_0, \Psi_0, T_0) (\bm{\nu}_{lin} - \bm{\dot{v}}_f)
+		\label{eq:indi_outer_control_law}
+	\end{split}
+\end{equation}
+Figure (TODO:show Figure) shows the block diagram of the outer loop \acrshort{INDI}.
+Using the same approach as with the inner loop, the outer loop which controls linear acceleration is augmented with two closed loops consisting of two gains.
+These gains represent two controllers which control linear velocity and position.
+
+TODOs: \\
+- 2.1   Source (Probably Holzapfel script) \\
+- 2.3.2 Figure with Crazyflie lever arms and motor numbers \\
+- 2.3.2 Figure with block diagram of the inner loop controller
+- 2.3.3 Figure with block diagram of the outer loop controller
 
@@
 Nevertherless G1, G2 still have to estimated accuratly because this 2 parameters do have inpact on the controller performance.
+\\
+- Plain step responses of the outer loop \\
+- Step responses with disturbance of the outer loop
 

### 2020-03-04 crazyflie-firmware/src/modules/src/controller_indi.c

@@ -242,9 +242,9 @@ void controllerINDI(control_t *control, setpoint_t *setpoint,
 		velocityRef.y = vel_set_y;
 		velocityRef.z = vel_set_z;
 		*/
-		pos_set_z = setpoint->attitude.pitch;
-		pos_set_y = setpoint->attitude.roll;
-		pos_set_x = setpoint->thrust/60000.0f;
+		//pos_set_x = setpoint->attitude.pitch;
+		//pos_set_y = setpoint->attitude.roll;
+		//pos_set_z = -setpoint->thrust/60000.0f;
 
 		// State position, velocity
 		posS_x = state->position.x;
@@ -257,7 +257,7 @@ void controllerINDI(control_t *control, setpoint_t *setpoint,
 		gyr_q = sensors->gyro.y;
 		gyr_r = sensors->gyro.z; 
 
-		// Position controller (K_xi?)
+		// Position controller
 		positionRef.x = posS_x;//pos_set_x;
 		positionRef.y = posS_y;//pos_set_y;
 		positionRef.z = pos_set_z;
@@ -265,7 +265,7 @@ void controllerINDI(control_t *control, setpoint_t *setpoint,
 		velocityRef.y = K_xi_x*(positionRef.y - posS_y);
 		velocityRef.z = K_xi_x*(positionRef.z - posS_z);
 
-		// Velocity controller (K_dxi?)
+		// Velocity controller
 		indi.linear_accel_ref.x = K_dxi_x*(velocityRef.x - velS_x);
 		indi.linear_accel_ref.y = K_dxi_x*(velocityRef.y - velS_y);
 		indi.linear_accel_ref.z = K_dxi_z*(velocityRef.z - velS_z); 
@@ -583,10 +583,11 @@ LOG_GROUP_STOP(ctrlINDI)
 
 // INDI outer loop
 PARAM_GROUP_START(INDI_Outer)
-/*
+
 PARAM_ADD(PARAM_FLOAT, pos_set_x, &pos_set_x)
 PARAM_ADD(PARAM_FLOAT, pos_set_y, &pos_set_y)
 PARAM_ADD(PARAM_FLOAT, pos_set_z, &pos_set_z)
+/*
 PARAM_ADD(PARAM_FLOAT, vel_set_x, &vel_set_x)
 PARAM_ADD(PARAM_FLOAT, vel_set_y, &vel_set_y)
 PARAM_ADD(PARAM_FLOAT, vel_set_z, &vel_set_z)

### 2020-03-07 Paper_EV/Paper_EV.tex
Backup update 07.03

@@
 
+% For inserting images, figures
+\usepackage{tikz}
+
+% For citation of URLs
+\usepackage{url}
+
+% Define subsection depth
+\setcounter{secnumdepth}{3}
+
 % Set line spacing to 1.15pt
@@
 \newacronym{EOM}{EOM}{Equations of Motion}
+\newacronym{IMU}{IMU}{Inertial Measurement Unit}
 \newacronym{INDI}{INDI}{Incremental Nonlinear Dynamic Inversion}
+\newacronym{MCU}{MCU}{Microcontroller}
 \newacronym{NED}{NED}{North East Down}
 \newacronym{NDI}{NDI}{Nonlinear Dynamic Inversion}
+\newacronym{ToF}{ToF}{Time-of-Flight}
 % Make gls
@@
 
+- 3. Implementation in Simulink for testing (both loops)\\
+- 3. Implementation on HW (outer loop)
+
 \section{Structure of the Thesis} \label{sec:structure_ofthe_thesis}
@@
 The dynamic equations which describe the general motion of an aircraft are usually coupled first order implicit nonlinear differential equations.
-However, in many cases it is sufficient to use their simplified versions (TODO:Source needed!).
+However, considering a quadrotor control problem a lot of plausible assumptions (e.g.
+neglecting the Coriolis and centrifugal acceleration due to the earth rotation) can be made to obtain more simplified versions of those equations.
 This section presents simplified general \acrshort{EOM} and describes the assumptions which were considered to derive them.
@@
 As some of those inconsistencies are inevitable there is a need to build a control law which performance is less dependent on the uncertainties of the model.
-A method called \acrfull{INDI} can be used to achieve this, it is discussed in the next section.
+A method called \acrfull{INDI} can be used to achieve this, it is discussed in the next subsection.
 
@@
 \end{equation}
-where $I_{rzz}$ is the element of the inertia matrix $I_{r}$ of the rotor, $l$ and $b$ lever arms as denoted in the Figure (TODO:Figure), $k_F$ and $k_M$ force and moment constants of the rotors.
-
-As already explained in the previous section to derive the incremental control law the Taylor series expansion is perfromed on the Equation \ref{eq:main_eom_indi_inner}
+where $I_{rzz}$ is the element of the inertia matrix $I_{r}$ of the rotor, $l$ and $b$ lever arms as denoted in the Figure \ref{fig:frames_leverarms}, $k_F$ and $k_M$ force and moment constants of the rotors.
+
+\begin{figure}[H]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=1\textwidth]{figs/frames.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Crazyflie 2.1 nano-quadrotor with indicated lever arms of the motors]{Image of the Crazyflie 2.1 quadrotor adopted from \cite{bitcraze} with indicated lever arms of the motors.}
+	\label{fig:frames_leverarms}
+\end{figure}
+
+As already explained in the previous subsection to derive the incremental control law the Taylor series expansion is perfromed on the Equation \ref{eq:main_eom_indi_inner}
 \begin{equation}
@@
 TODOs: \\
-- 2.1   Source (Probably Holzapfel script) \\
+- INDI inner loop (order)\\
 - 2.3.2 Figure with Crazyflie lever arms and motor numbers \\
-- 2.3.2 Figure with block diagram of the inner loop controller
+- 2.3.2 Figure with block diagram of the inner loop controller\\
 - 2.3.3 Figure with block diagram of the outer loop controller
@@
 \chapter{Implementation} \label{cha:implementation}
+
+This chapter describes different aspects of the practical realization of the control architecture introduced in the previous chapter.
+Section \ref{sec:research_quadrotor} gives an overview about the quadrotor system on which the \acrshort{INDI} outer loop controller was implemented and tested.
+In section \ref{sec:simulink_model} the simulation model of the Crazyflie quadrotor with implemented \acrshort{INDI} inner and outer loops is presented.
+Finally, in section \ref{sec:implementation_on_hardware} the process of the controller implementation on the hardware system is described.
+Here, additionally to the complete outer loop implementation, it is described how the already existing inner loop was modified to achieve a better performance.
 
@@
 
-- Some facts about Crazyflie hardware (foto, uC frequency, weight, length (foto of lever arms), onboard sensors, additional sensors/HW (optoflow, sd-card))
-
-\section{Implementation in Simulink (Simulink Model)} \label{sec:simulink_model}
-
-\subsection{Purpose} \label{subsec:purpose}
-
-- Estimation of the relevant for the HW implementation components (which terms make a huge impact on the controller performance: G1, G1 etc)\\
-- Estimate where value explosion can occur\\
-- Testing the behaviour of the filter\\
-- Testing of the PD-gains
-
-\subsection{Structure} \label{subsec:Structure}
-- Describe some assumptions: eg newton second law frame transformation from B to O for an easy representation\\
-- Present each equation of forces with explaining made assumptions\\
-- Parameter choice ($k_F$, $k_M$, ...)\\
-- Describe the actuator dynamics modelling\\
-- Describe the filter transfer function\\
-- Images of the Simulink model
-
-\subsection{Simulation Results} \label{subsec:simulation_results}
-
+The Crazyflie 2.1 quadrotor developed by Swedish company Bitcraze belongs to the nano-quadrotor class (see Figure \ref{fig:crazyflie_drone}).
+Its total weight ranges from 27g to 42g, which makes possible to extend the default hardware with a pair of additional extension decks of various functionality.
+As it is an open source project, the main firmware, development tools and other software packages are freely available.
+This is one of the reasons why this small quadrotor gained a lot of popularity in different academia fields, being used for tasks reaching from the classical control theory all the way down to the obstacle avoidance problems.
+
+The Crazyflie's main application \acrfull{MCU} is STM32F405.
+It runs the firmware with frequency of 1000 Hz and communicates with a large number of peripheral devices such as Bluetooth and long range radio, power management system \acrshort{MCU}, \acrfull{IMU} etc..
+The \acrfull{IMU} consists of the 3-axis accelerometer, the 3-axis gyroscope and the high precision pressure sensor.
+
+The quadrotor used in this project was extended with a flow deck sensor.
+The flow deck itself is equipped with two sensors: the optical flow sensor which measures the visual motion and the \acrfull{ToF} sensor which measures the range to the next object along the body-fixed z-axis of the quadcopter.
+By employing these sensors, the flow deck can provide estimates of the current position and linear velocity.
+
+\begin{figure}[H]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=0.4\textwidth]{figs/crazyflie_drone.jpg}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Crazyflie 2.1 nano-quadrotor]{Crazyflie 2.1 nano-quadrotor \cite{bitcraze}}
+	\label{fig:crazyflie_drone}
+\end{figure}
+
+\section{Simulink Model} \label{sec:simulink_model}
+
+Before implementing the outer loop of the \acrshort{INDI} controller derived in \ref{subsec: indi_outer} on the real Crazyflie quadrotor it was decided firstly to build a simulation model using Matlab/Simulink software.
+Such a simulation has a number of advantages compared to the direct implementation on the hardware.
+The main one is, it allows one to conveniently test different model components (e.g.
+filtering algorithms, actuator dynamic models etc.) on their dedicated functions, facilitating the debugging process.
+It also can ease the process of parameter tuning of the controller.
+
+In the framework of this thesis the Simulink model was also applied to better understand the controller structure and its characteristics.
+Based on the simulation it was determined which of the control effectiveness terms have a greater influence on the system response and which ones can be neglected.
+Additionally the simulation model provided a good overview of potential computational problems and mistakes which could lead to drastically growing values and unstable behaviour of the system.
+To solve some of them, saturation blocks have been used  in different places.
+
+\subsection{Quadrotor Dynamics} \label{subsec:quadrotor_dynamics}
+
+The core of the Crazyflie simulation is the model of the quadrotor dynamics.
+It is based on dynamic equations of motion presented in Chapter \ref{sec:eqs_motion}.
+Similarly to the section \ref{subsec: indi_outer}, it was assumed that the sum of the forces in the linear momentum equation is composed of three components, namely gravitational, propulsive and aerodynamic.
+The gravity and the propulsive force have not been changed, so the Equations \ref{eq:Fg} and \ref{eq:Fp} were also adopted for the simulation model.
+The thrust value $T$ was modelled as a linear function of rotational rates of propellers
+\begin{equation}
+	\begin{split}
+		T = - k_F (\Omega_1 + \Omega_2 + \Omega_3 + \Omega_4)
+		\label{eq:thrust}
+	\end{split}
+\end{equation}
+where $k_F$ is the force constant of the rotors.
+In subsection \ref{subsec:parameter_estimation} it is shown how to estimate the thrust coefficient directly from the flight data.
+However, for the simulation model $k_F$ was computed based on the assumption that the influence of the force constant of the rotors $k_F$ (considering the lever arm) is greater than the influence of the moment constant of the rotors $k_M$, and that the thrust to weight ratio expression $\frac{T}{W} \approx 2$.
+
+To account for aerodynamic effects such as drag the aerodynamic force was approximated with following expression 
+\begin{equation}
+	\begin{split}
+		(\bm{F}_A)_B =  
+		\begin{bmatrix}
+			-k_x (u_K)_B\\
+			-k_y (v_K)_B\\
+			-k_z (w_K)_B
+		\end{bmatrix}_B
+		\label{eq:Fa_simulink}
+	\end{split}
+\end{equation}
+where $(u_K)_B$, $(v_K)_B$ and $(w_K)_B$ are kinematic velocities of the quadrotor along the axes $x_K$, $y_K$ and $z_K$ respectively, given in the body-fixed coordinate frame.
+$k_x$, $k_y$ and $k_z$ are experimentally estimated drag coefficients adopted from \cite{foerster}.
+
+The angular momentum equation used in the simulation model has the same form as defined in Equation \ref{eq:ang_momentum}.
+The numerical values of the inertia tensor $(\bm{I}^G)_B$ were estimated using pendulum method in \cite{foerster}.
+The total external moment acting on the Crazyflie consists only of the propulsive moment $\bm{M}_P$ as it is defined in \ref{subsec: indi_inner}.
+It consist of the control moment generated by the rotors $\bm{M}_C$  and moment containing the gyroscopic effect of the rotors $\bm{M}_{gyro}$ (see Equations \ref{eq:m_c} and \ref{eq:m_gyro}).
+The moment constant of the rotor was computed to fulfil the requirements on $k_F$ and $k_M$ which were described above.
+To obtain the numerical estimate of the propeller inertia matrix $I_{rzz}$, the propeller was approximated with a bar element.
+This has been shown to be a valid assumption since the influence of the propeller inertia (due to its negligible weight) is very small.
+
+TODOs:\\
+- 3.2.1 reference to the table with all used constants in the appendix
+
+\subsection{Actuator Dynamics} \label{subsec:actuator_dynamics}
+
+The inner loop \acrshort{INDI} controller relies on the measurement of the rotor angular rates.
+If the actuator feedback is not available, it is possible to use its model instead.
+The model of the actuator dynamics was assumed to be a first order lag filter with following transfer function in continuous Laplace domain
+\begin{equation}
+	\begin{split}
+		A(s) = \frac{k}{1+Ts}
+		\label{eq:act_dynamics_c}
+	\end{split}
+\end{equation}
+where $k$ is the gain and $T$ the time constant.
+Section \ref{sec:implementation_on_hardware} shortly describes the process of using flight data to estimate the time constant $T$.
+In the Simulink model it was assumed that the actuator feedback is available, hovewer for the implementation on hardware it is necessary to have a discrete version of the transfer function in Equation \ref{eq:act_dynamics_c}.
+Transforming the transfer function in Equation \ref{eq:act_dynamics_c} from continuous domain into discrete by applying \textit{Zero-Order Hold method} results in
+\begin{equation}
+	\begin{split}
+		A(z) = \frac{k\alpha}{z+(\alpha-1)}
+		\label{eq:act_dynamics_d}
+	\end{split}
+\end{equation}
+with $\alpha = 1-e^{\frac{-T_S}{T}}$ and sample time $T_S$.
+
+\subsection{Filtering} \label{subsec:filtering}
+
+- Continuous TF \\
+- Discrete TF \\
+- All filter have the same parameter \\
+- Block diagram of the filter
+
+\subsection{Simulation Results and Analysis} \label{subsec:simulation_results}
+
+- Inner loop subsubsection (Tell that it is descrete implementation and then analysis) \\
+- Outer loop subsubsection (- // -) \\
+- Appendix: simulink model images, table with all constants \\
 - Plot differences with or without some terms (G1, G2\_yaw) \\
+- Responces for different step inputs
+- pz-Plot
+
+TODOs:\\
+- 3.2.2 'Actuator Dynamics' Fig4 from Adaptive... Smeur paper
 
@@
 \subsection{Structure of the Code} \label{subsec:structure_ofthe_code}
+
+- Moore-Penrose instead of the inverse
 

### 2020-03-07 code/Simulink/Crazyflie_Simulation_paper/inner_pd_cs.m

@@ -1,0 +1,50 @@
+function inner_pd_cs(k_omega_in, k_eta_in)
+
+    clc;
+    Ts = 1/500;                                       % Sample time
+    T = 0.0617;                                       % Actuator time constant
+
+    % Actuator dynamic koefficients
+    C1 = Ts/(Ts+2*T);
+    C2 = (Ts-2*T)/(Ts+2*T);
+
+    % Generate different colors for plotting
+    colors = jet(size(k_omega_in, 2)*size(k_eta_in, 2));
+    clr = 1:(size(k_omega_in, 2)*size(k_eta_in, 2)); 
+    i  = 0;
+
+    % Iterative computation of poles
+    for k_om=k_omega_in
+        for k_et=k_eta_in
+            i = i+1;
+
+            % Define transfer function eta_ref -> eta (Control Systems Toolbox)
+            z = tf('z', Ts);
+            K_omega = k_om; 
+            K_eta = k_et; 
+            TF_etaref_eta = ( (Ts^2*K_eta*K_omega*C1)*z^3 + ...  
+                              (Ts^2*K_eta*K_omega*C1)*z^2 ) / ...
+                            ( (Ts^2*K_eta*K_omega*C1 + Ts*K_omega*C1 + 1)*z^3 + ... 
+                              (C2-2)*z^2 + (-Ts*K_omega*C1 - 2*C2 + 1)*z + C2 );
+
+            figure(1);
+            step(TF_etaref_eta); hold on; grid on;
+            figure(2);
+            bode(TF_etaref_eta);
+                   
+            % Compute poles of TF_etaref_eta
+            display(['K_omega=', num2str(K_omega), ', K_eta=', num2str(K_eta)])
+            p = pole(TF_etaref_eta)
+
+            %figure(2);
+            % Plot poles
+            name = ['KOmega= ', num2str(K_omega), ', KEta= ', num2str(K_eta)];
+            %pzmap(TF_etaref_eta); hold on; axis equal;
+
+            % Plot settings
+            grid on; 
+
+        end
+    end
+
+end

### 2020-03-07 code/Simulink/Crazyflie_Simulation_paper/outer_pd_cs.m

@@ -1,0 +1,58 @@
+function outer_pd_cs(k_dxi_in, k_xi_in, k_omega_fix, k_eta_fix)
+
+    clc;
+    K_omega = k_omega_fix;
+    K_eta = k_eta_fix;
+
+    Ts = 0.01;                                      % Sample time
+    T = 1/15;                                       % Actuator time constant
+
+    % Actuator dynamic koefficients
+    C1 = Ts/(Ts+2*T);
+    C2 = (Ts-2*T)/(Ts+2*T);
+
+    % Generate different colors for plotting
+    colors = jet(size(k_dxi_in, 2)*size(k_xi_in, 2));
+    clr = 1:(size(k_dxi_in, 2)*size(k_xi_in, 2)); 
+    i  = 0;
+
+    % Iterative computation of poles
+    for k_dxi=k_dxi_in
+        for k_xi=k_xi_in
+            i = i+1;
+
+            % Define transfer function xi_ref -> xi (Control Systems Toolbox)
+            z = tf('z', Ts);
+            K_d_xi = k_dxi;
+            K_xi = k_xi;
+
+            TF_etaref_eta = ( (Ts^2*K_eta*K_omega*C1)*z^3 + ...  
+                         (Ts^2*K_eta*K_omega*C1)*z^2 ) / ...
+                       ( (Ts^2*K_eta*K_omega*C1 + Ts*K_omega*C1 + 1)*z^3 + ... 
+                         (C2-2)*z^2 + (-Ts*K_omega*C1 - 2*C2 + 1)*z + C2 );
+
+            TF_dxierr_dxi = K_d_xi * TF_etaref_eta * Ts*z/(z-1);     % Open loop
+            %TF_dxiref_dxi = TF_dxierr_dxi / (1 + TF_dxierr_dxi)     % Closed loop computed wrong (see "Using FEEDBACK to Close Feedback Loops" documentation)
+            TF_dxiref_dxi = feedback(TF_dxierr_dxi, 1);              % Closed loop
+            
+            TF_xierr_xi = K_xi * TF_dxiref_dxi * Ts*z/(z-1);         % Open loop
+            %TF_xiref_xi = TF_xierr_xi / (1 + TF_xierr_xi);          % Closed loop computed wrong (see "Using FEEDBACK to Close Feedback Loops" documentation)
+            TF_xiref_xi = feedback(TF_xierr_xi, 1);                  % Closed loop
+                
+            % Compute poles of TF_xiref_xi
[…]

### 2020-03-07 code/Simulink/Crazyflie_Simulation_paper/set_params.m

@@ -1,0 +1,88 @@
+clc 
+clear 
+close all
+
+%%
+% Force and Moment Notation:
+% 'FX_Y' or 'MX_Y' with: 
+% - X: Force nature (e.g gravitational (G), aerodynamical (A), propulsive (P) etc)
+% - Y Coordinate frame (e.g Body-Fixed (B), NED (O) etc)
+% 
+% Notation of other values: (TODO)
+% - omegaR_X: vector of rotor angular velocities
+% - ...
+
+
+%% Dynamics
+
+% Crazyflie
+g = 9.81;           % gravitational acceleration in [m/s^2]
+m_CF = 0.028;       % mass of the Crazyflie quadrotor in [kg]
+l = 0.033;          % lever arm to the rotor in x-direction [m]
+b = 0.033;          % lever arm to the rotor in y-direction [m]
+I_rzz = 9.3e-9;     % Component of moment of inertia of the rotor [kg*m^2]
+
+
+I_CF_1 = [16.823890  -1.224320  -0.716891    % Moment of inertia of the 
+          -1.224320   16.885278  2.083147    % Crazyflie quadrotor in [kg*m^2]
+          -0.716891   2.083147   29.808912] * 10e-6;       
+% I_CF_1 = [16.823890     0          0       % Moment of inertia of the 
+%              0      16.885278      0       % Crazyflie quadrotor in [kg*m^2]
+%              0          0       29.808912] * 10e-6; 
+
+I_CF_1_inv = inv(I_CF_1);                 % Inverted I_CF_1
+
+% Propulsive force
+k_f = 1.6e-4;       % motor constant for F_P and M_P[N/(rad/s)]
+k_m = 1e-6;         % motor constant for M_P [N*m/(rad/s)]
+
+% Aerodynanic force
+kx = 10.25e-4;      % drag constant in x-direction [kg/s]
+ky = 10.25e-4;      % drag constant in y-direction [kg/s]
+kz = 7.553e-4;      % drag constant in z-direction [kg/s]
+
+% Actuator dynamics 
+T = 0.0617;                        % Actuator time constant [s]
+omegaR_init = [1; 1; 1; 1]*200;    % Initial rotor angular velocity [rad/s]
+
[…]

### 2020-03-07 crazyflie-firmware/src/modules/src/controller_indi.c

@@ -24,6 +24,7 @@
  */
 
 #include "controller_indi.h"
+#include "estimator.h"
 
 static float thrust_threshold = 300.0f;
 static float bound_control_input = 32000.0f;
@@ -36,9 +37,9 @@ static float attYawError;
 static struct Vectr positionRef; 
 static struct Vectr velocityRef;
 
-float K_xi_x = 5.0f;
-float K_xi_y = 5.0f;
-float K_xi_z = 5.0f;
+float K_xi_x = 1.0f;
+float K_xi_y = 1.0f;
+float K_xi_z = 1.0f;
 float K_dxi_x = 5.0f;
 float K_dxi_y = 5.0f;
 float K_dxi_z = 5.0f;
@@ -242,9 +243,10 @@ void controllerINDI(control_t *control, setpoint_t *setpoint,
 		velocityRef.y = vel_set_y;
 		velocityRef.z = vel_set_z;
 		*/
-		//pos_set_x = setpoint->attitude.pitch;
+		//pos_set_x = -setpoint->attitude.pitch;
 		//pos_set_y = setpoint->attitude.roll;
 		//pos_set_z = -setpoint->thrust/60000.0f;
+
 
 		// State position, velocity
 		posS_x = state->position.x;
@@ -258,16 +260,16 @@ void controllerINDI(control_t *control, setpoint_t *setpoint,
 		gyr_r = sensors->gyro.z; 
 
 		// Position controller
-		positionRef.x = posS_x;//pos_set_x;
-		positionRef.y = posS_y;//pos_set_y;
+		positionRef.x = pos_set_x;
+		positionRef.y = pos_set_y;
 		positionRef.z = pos_set_z;
 		velocityRef.x = K_xi_x*(positionRef.x - posS_x);
-		velocityRef.y = K_xi_x*(positionRef.y - posS_y);
-		velocityRef.z = K_xi_x*(positionRef.z - posS_z);
+		velocityRef.y = K_xi_y*(positionRef.y - posS_y);
+		velocityRef.z = K_xi_z*(positionRef.z - posS_z);
 
 		// Velocity controller
 		indi.linear_accel_ref.x = K_dxi_x*(velocityRef.x - velS_x);
[…]

### 2020-03-07 Paper_EV/Paper_EV.tex
Folder refactoring

@@
 	\begin{split}
-		A(s) = \frac{k}{1+Ts}
+		A(s) = \frac{k}{1+T_S}
 		\label{eq:act_dynamics_c}
@@
 with $\alpha = 1-e^{\frac{-T_S}{T}}$ and sample time $T_S$.
+The default frequency of the Crazyflie controller update is 500 Hz.
+Thus, sampling time $T_S$ was set to the reciprocal value of the default frequency.
 
@@
 
-- Continuous TF \\
-- Discrete TF \\
-- All filter have the same parameter \\
-- Block diagram of the filter
+As it was shown in Chapter \ref{cha:theoretical_background} (TODO also see Figures ...
+and ...), the inner and outer loops employ several second order filters.
+The main task of two of them is to reduce  noise in the measurements of the angular and linear acceleration.
+Other filters are applied to remaining feedback quantities.
+Using the same parameters for every filter, this technique accounts for the time delay which is introduced by the filters and ensures that all quantities that were fed back are from the same point in time.
+The gneral transfer function of a second order filter in continuous domain is defined by the following formula
+\begin{equation}
+	\begin{split}
+		F(s) = \frac{\omega_n^2}{s^2+2\zeta\omega_ns+\omega_n^2}
+		\label{eq:filter_c}
+	\end{split}
+\end{equation}
+with a relative damping coefficient $\zeta$ and an eigenfrequency $\omega_n$.
+To implement transfer function from Equation \ref{eq:filter_c} on a digital computer it must be transformed to the discrete domain.
+To perform this transformation \textit{bilinear transformation} (also called \textit{Tustin-Transformation}) was used.
+Using bilinear transformation, the mapping relation between $s$ and $z$ results in
+\begin{equation}
+	\begin{split}
+		s \ \widehat{=} \ \frac{2}{T_S} \frac{1-z^{-1}}{1+z^{-1}}
+		\label{eq:filter_c}
+	\end{split}
+\end{equation}
+Thus, the discrete version of the Equation \ref{eq:filter_c} is 
+\begin{equation}
+	\begin{split}
+		F(z) = \frac{n_0 + n_1z^{-1} + n_2z^{-2}}{d_0 + d_1z^{-1} + d_2z^{-2}}
+		\label{eq:filter_d}
+	\end{split}
+\end{equation}
+where 
+\begin{subequations}
+	\begin{align}
+		n_0 &= \omega_n^2 \\
+		n_1 &= 2\omega_n^2 \\
+		n_2 &= \omega_n^2 \\
+		d_0 &= \bigg[(\frac{2}{T_S})^2 + \frac{4\zeta \omega_n}{T_S} + \omega_n^2\bigg] \\
+		d_1 &= \bigg[\frac{8}{T_S^2} + 2\omega_n^2\bigg] \\
+		d_2 &= \bigg[(\frac{2}{T_S})^2 - \frac{4\zeta \omega_n}{T_S} + \omega_n^2\bigg]
+	\end{align}
+	\label{eq:filter_parameters}
+\end{subequations}
 
@@
 - 3.2.2 'Actuator Dynamics' Fig4 from Adaptive... Smeur paper
-
+- 3.2.3 'Filtering' Reference figures of the inner and outer block diagrams
+- 3.2.3 'Filtering' Block diagram of the filter 
 \section{Implementation on the Hardware} \label{sec:implementation_on_hardware}

### 2020-03-07 code/Simulink/Crazyflie_Simulation_paper/inner_pd_cs.m

@@ -1,50 +1,0 @@
-function inner_pd_cs(k_omega_in, k_eta_in)
-
-    clc;
-    Ts = 1/500;                                       % Sample time
-    T = 0.0617;                                       % Actuator time constant
-
-    % Actuator dynamic koefficients
-    C1 = Ts/(Ts+2*T);
-    C2 = (Ts-2*T)/(Ts+2*T);
-
-    % Generate different colors for plotting
-    colors = jet(size(k_omega_in, 2)*size(k_eta_in, 2));
-    clr = 1:(size(k_omega_in, 2)*size(k_eta_in, 2)); 
-    i  = 0;
-
-    % Iterative computation of poles
-    for k_om=k_omega_in
-        for k_et=k_eta_in
-            i = i+1;
-
-            % Define transfer function eta_ref -> eta (Control Systems Toolbox)
-            z = tf('z', Ts);
-            K_omega = k_om; 
-            K_eta = k_et; 
-            TF_etaref_eta = ( (Ts^2*K_eta*K_omega*C1)*z^3 + ...  
-                              (Ts^2*K_eta*K_omega*C1)*z^2 ) / ...
-                            ( (Ts^2*K_eta*K_omega*C1 + Ts*K_omega*C1 + 1)*z^3 + ... 
-                              (C2-2)*z^2 + (-Ts*K_omega*C1 - 2*C2 + 1)*z + C2 );
-
-            figure(1);
-            step(TF_etaref_eta); hold on; grid on;
-            figure(2);
-            bode(TF_etaref_eta);
-                   
-            % Compute poles of TF_etaref_eta
-            display(['K_omega=', num2str(K_omega), ', K_eta=', num2str(K_eta)])
-            p = pole(TF_etaref_eta)
-
-            %figure(2);
-            % Plot poles
-            name = ['KOmega= ', num2str(K_omega), ', KEta= ', num2str(K_eta)];
-            %pzmap(TF_etaref_eta); hold on; axis equal;
-
-            % Plot settings
-            grid on; 
-
-        end
-    end
-
-end

### 2020-03-07 code/Simulink/Crazyflie_Simulation_paper/outer_pd.m

@@ -1,67 +1,0 @@
-function outer_pd(k_dxi_in, k_xi_in, k_omega_fix, k_eta_fix)
-
-    clc;
-    K_omega = k_omega_fix;
-    K_eta = k_eta_fix;
-
-    Ts = 0.01;                                      % Sample time
-    T = 1/15;                                       % Actuator time constant
-
-    % Actuator dynamic koefficients
-    C1 = Ts/(Ts+2*T);
-    C2 = (Ts-2*T)/(Ts+2*T);
-
-    % Generate different colors for plotting
-    colors = jet(size(k_dxi_in, 2)*size(k_xi_in, 2));
-    clr = 1:(size(k_dxi_in, 2)*size(k_xi_in, 2)); 
-    i  = 0;
-
-    % Iterative computation of poles
-    for k_dxi=k_dxi_in
-        for k_xi=k_xi_in
-            i = i+1;
-
-            % Define transfer function xi_ref -> xi (symbolic)
-            syms z K_d_xi K_xi
-            TF_etaref_eta = ( (Ts^2*K_eta*K_omega*C1)*z^3 + ...  
-                         (Ts^2*K_eta*K_omega*C1)*z^2 ) / ...
-                       ( (Ts^2*K_eta*K_omega*C1 + Ts*K_omega*C1 + 1)*z^3 + ... 
-                         (C2-2)*z^2 + (-Ts*K_omega*C1 - 2*C2 + 1)*z + C2 );
-
-            TF_dxierr_dxi = K_d_xi * TF_etaref_eta * Ts*z/(z-1);     % Open loop
-            TF_dxiref_dxi = TF_dxierr_dxi / (1 + TF_dxierr_dxi);     % Closed loop
-
-            TF_xierr_xi = K_xi * TF_dxiref_dxi * Ts*z/(z-1);         % Open loop
-            TF_xiref_xi = TF_xierr_xi / (1 + TF_xierr_xi);           % Closed
-
-            % Extract numerator and denumerator from TF_xiref_xi
-            [Num, Denum] = numden(TF_xiref_xi);
-
-            % Substitute some values for K_dxi and K_xi in Denum
-            Denum = subs(Denum, {K_d_xi, K_xi}, {k_dxi, k_xi});
-
-            % Compute poles of TF_xiref_xi
-            display(['K_dxi=', num2str(k_dxi), ', K_xi=', num2str(k_xi)])
-            p = vpasolve(Denum, z)
-
[…]

### 2020-03-07 code/Simulink/Crazyflie_Simulation_paper/set_params.m

@@ -1,88 +1,0 @@
-clc 
-clear 
-close all
-
-%%
-% Force and Moment Notation:
-% 'FX_Y' or 'MX_Y' with: 
-% - X: Force nature (e.g gravitational (G), aerodynamical (A), propulsive (P) etc)
-% - Y Coordinate frame (e.g Body-Fixed (B), NED (O) etc)
-% 
-% Notation of other values: (TODO)
-% - omegaR_X: vector of rotor angular velocities
-% - ...
-
-
-%% Dynamics
-
-% Crazyflie
-g = 9.81;           % gravitational acceleration in [m/s^2]
-m_CF = 0.028;       % mass of the Crazyflie quadrotor in [kg]
-l = 0.033;          % lever arm to the rotor in x-direction [m]
-b = 0.033;          % lever arm to the rotor in y-direction [m]
-I_rzz = 9.3e-9;     % Component of moment of inertia of the rotor [kg*m^2]
-
-
-I_CF_1 = [16.823890  -1.224320  -0.716891    % Moment of inertia of the 
-          -1.224320   16.885278  2.083147    % Crazyflie quadrotor in [kg*m^2]
-          -0.716891   2.083147   29.808912] * 10e-6;       
-% I_CF_1 = [16.823890     0          0       % Moment of inertia of the 
-%              0      16.885278      0       % Crazyflie quadrotor in [kg*m^2]
-%              0          0       29.808912] * 10e-6; 
-
-I_CF_1_inv = inv(I_CF_1);                 % Inverted I_CF_1
-
-% Propulsive force
-k_f = 1.6e-4;       % motor constant for F_P and M_P[N/(rad/s)]
-k_m = 1e-6;         % motor constant for M_P [N*m/(rad/s)]
-
-% Aerodynanic force
-kx = 10.25e-4;      % drag constant in x-direction [kg/s]
-ky = 10.25e-4;      % drag constant in y-direction [kg/s]
-kz = 7.553e-4;      % drag constant in z-direction [kg/s]
-
-% Actuator dynamics 
-T = 0.0617;                        % Actuator time constant [s]
-omegaR_init = [1; 1; 1; 1]*200;    % Initial rotor angular velocity [rad/s]
-
[…]

### 2020-03-07 code/Simulink/Crazyflie_Simulation_paper/test.m

@@ -1,54 +1,0 @@
-clc
-clear
-close all
-
-%% Set some variables 
-T = 1/15;                       % Actuator dynamics time constant [s]
-Ts = 0.01;                      % Sampling time [s]
-
-%% Filter test
-
-%Check if manually transformed H(s) corresponds to the one computed with
-%matlab
-
-% s = tf('s');
-% z = tf('z', Ts);
-% 
-% H = omega_n^2/(s^2 + 2*zeta*omega_n*s + omega_n^2);
-% Hz = tf( (N_0/D_0*z^2 + N_1/D_0*z + N_2/D_0)/((z^2 + D_1/D_0*z + D_2/D_0)));
-% Hzm = c2d(H, Ts, 'tustin')
-% 
-% step(H, Hz, Hzm)
-% legend('H', 'Hz', 'Hzm')
-
-
-%% Transfer functions for inner gains 
-
-% s = tf('s');                    % Laplace variable
-% z = tf('z', Ts);                % z variable
-% 
-% A = 1/(T*s+1);                  % Actuator dynamic in s domain              
-% Az = c2d(A, Ts, 'tustin');      % Transformation from s to z domain
-% 
-% K_omega = 10;
-% K_eta = 4;
-%     
-% TF_omega_ol = K_omega * Az * Ts*z/(z-1);          % Open loop tf
-% TF_omega_cl = feedback(TF_omega_ol, 1);           % Closed loop tf
-% 
-% TF_eta_ol = K_eta * TF_omega_cl * Ts*z/(z-1);     % Open loop tf
-% TF_eta_cl = feedback(TF_eta_ol, 1)               % Closed loop tf
-
-
-%% Transfer functions for outer gains 
-
-% K_d_xi = 1.5;
-% K_xi = 0.7;
-% 
-% TF_dxi_ol = K_d_xi * TF_eta_cl * Ts*z/(z-1);     % Open loop tf
-% TF_dxi_cl = feedback(TF_dxi_ol, 1);              % Closed loop tf
-% 
-% TF_xi_ol = K_xi * TF_dxi_cl * Ts*z/(z-1);        % Open loop tf
-% TF_xi_cl = feedback(TF_xi_ol, 1);                % Closed loop tf
-
-

### 2020-03-13 Paper_EV/Paper_EV.tex
Backup 13_03_2020

@@
 The dynamic equations which describe the general motion of an aircraft are usually coupled first order implicit nonlinear differential equations.
-However, considering a quadrotor control problem a lot of plausible assumptions (e.g.
+However, considering a quadrotor control problem, a lot of plausible assumptions (e.g.
 neglecting the Coriolis and centrifugal acceleration due to the earth rotation) can be made to obtain more simplified versions of those equations.
@@
 
-\subsection{Inner INDI loop for Quadrotor} \label{subsec: indi_inner}
+\subsection{Inner loop INDI for Quadrotor} \label{subsec: indi_inner}
 
@@
 where $I_{rzz}$ is the element of the inertia matrix $I_{r}$ of the rotor, $l$ and $b$ lever arms as denoted in the Figure \ref{fig:frames_leverarms}, $k_F$ and $k_M$ force and moment constants of the rotors.
-
 \begin{figure}[H]
@@
 		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
-		\includegraphics[width=1\textwidth]{figs/frames.pdf}};
+		\includegraphics[width=0.8\textwidth]{figs/frames.pdf}};
 	\end{tikzpicture}
@@
 \end{figure}
-
 As already explained in the previous subsection to derive the incremental control law the Taylor series expansion is perfromed on the Equation \ref{eq:main_eom_indi_inner}
@@
 		T_0
-	\end{bmatrix} + \bm{G}_1(\bm{\Omega} - \bm{\Omega}_0) + T_S \bm{G}_2(\bm{\dot{\Omega}} - \bm{\dot{\Omega}}_0)
+	\end{bmatrix} + \bm{G}_1(\bm{\Omega} - \bm{\Omega}_0) + T_s \bm{G}_2(\bm{\dot{\Omega}} - \bm{\dot{\Omega}}_0)
 	\label{eq:main_eom_indi_inner_lin}
@@
 		\end{bmatrix} - 	
-		\begin{bmatrix}
+		\bm{I}^{-1}\begin{bmatrix}
 			\bm{\omega}_y & 0 & 0 \\
@@
 	\begin{bmatrix}
-		-\bm{I}^{-1} T_S^{-1}\begin{bmatrix}
+		-\bm{I}^{-1} T_s^{-1}\begin{bmatrix}
 			0 & 0 & 0 & 0 \\
@@
 
-To prepare the linearized dynamic Equation \ref{eq:main_eom_indi_inner_lin} for discrete implementation on a computing system, the discrete approximation ($z$ domain) of the derivative is used: $\bm{\dot{\Omega}} = (\bm{\Omega} - \bm{\Omega}z^{-1})T_S^{-1}$.
+To prepare the linearized dynamic Equation \ref{eq:main_eom_indi_inner_lin} for discrete implementation on a computing system, the discrete approximation ($z$ domain) of the derivative is used: $\bm{\dot{\Omega}} = (\bm{\Omega} - \bm{\Omega}z^{-1})T_s^{-1}$.
 Furthermore, angular acceleration $\bm{\dot{\omega}}_0$ which is obtained from the differentiated gyroscope measurements is usually noisy.
@@
 where $\bm{\dot{\Omega}}$ is a vector of commanded rotational rates for every rotor and $\tilde{T} = T - T_f$ being the thrust increment which is provided by the outer loop \acrshort{INDI}.
-The block diagram of the inner loop \acrshort{INDI} controller is presented in Figure (TODO:Figure).
-In the figure the derived controller which controls the angular acceleration is augmented with two simple controllers which control the angular velocity $\bm{\omega}$ and the attitude $\bm{\eta}$ of the quadrotor.
-Each controller consists of a single gain.
+The block diagram of the inner loop \acrshort{INDI} controller is presented in Figure \ref{fig:indi_inner_croped}.
+\begin{figure}[H]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=1\textwidth]{figs/indi_inner_croped.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Block diagram of the inner loop \acrshort{INDI} controller]{Block diagram of the inner loop \acrshort{INDI} controller.
+$A(z)$ is the actuator dynamics (see \ref{subsec:actuator_dynamics}) and $F(z)$ is the second-order filter (see \ref{subsec:filtering}).}
+	\label{fig:indi_inner_croped}
+\end{figure}
+The inner \acrshort{INDI} controller which controls the angular acceleration is then augmented with two simple controllers which control the angular velocity $\bm{\omega}$ and the attitude $\bm{\eta}$ of the quadrotor (see Figure \ref{fig:pid_inner_croped}).
+Each of them consists of a single gain.
 Thus, the reference values of the \acrshort{INDI} part of the inner loop are provided by these two controllers.
-
-\subsection{Outer INDI loop for Quadrotor} \label{subsec: indi_outer}
+\begin{figure}[H]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=0.7\textwidth]{figs/pid_inner_croped.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Attitude controller as an augmentation of the inner loop \acrshort{INDI} controller]{Attitude controller as an augmentation of the inner loop \acrshort{INDI} controller.}
+	\label{fig:pid_inner_croped}
+\end{figure}
+
+\subsection{Outer loop INDI for Quadrotor} \label{subsec: indi_outer}
 
@@
 \end{equation}
-Figure (TODO:show Figure) shows the block diagram of the outer loop \acrshort{INDI}.
-Using the same approach as with the inner loop, the outer loop which controls linear acceleration is augmented with two closed loops consisting of two gains.
+Figure \ref{fig:indi_outer_croped} shows the block diagram of the outer loop \acrshort{INDI}. 
+\begin{figure}[H]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=1\textwidth]{figs/indi_outer_croped.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Block diagram of the outer loop \acrshort{INDI} controller.]{Block diagram of the outer loop \acrshort{INDI} controller.}
+	\label{fig:indi_outer_croped}
+\end{figure}
+Using the same approach as with the inner loop, the outer loop which controls linear acceleration is augmented with two closed loops consisting of two gains (see Figure \ref{fig:pid_outer_croped}).
 These gains represent two controllers which control linear velocity and position.
-
-TODOs: \\
-- INDI inner loop (order)\\
-- 2.3.2 Figure with Crazyflie lever arms and motor numbers \\
-- 2.3.2 Figure with block diagram of the inner loop controller\\
-- 2.3.3 Figure with block diagram of the outer loop controller
+\begin{figure}[H]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=0.8\textwidth]{figs/pid_outer_croped.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Position controller as an augmentation of the outer loop \acrshort{INDI} controller]{Position controller as an augmentation of the outer loop \acrshort{INDI} controller.}
+	\label{fig:pid_outer_croped}
+\end{figure}
 
@@
 The flow deck itself is equipped with two sensors: the optical flow sensor which measures the visual motion and the \acrfull{ToF} sensor which measures the range to the next object along the body-fixed z-axis of the quadcopter.
-By employing these sensors, the flow deck can provide estimates of the current position and linear velocity.
+By employing these sensors, the flow deck can provide estimates of the current position and linear velocity of the aircraft.
 
@@
 	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-	\caption[Crazyflie 2.1 nano-quadrotor]{Crazyflie 2.1 nano-quadrotor \cite{bitcraze}}
+	\caption[Crazyflie 2.1 nano-quadrotor]{Crazyflie 2.1 nano-quadrotor \cite{bitcraze}.}
 	\label{fig:crazyflie_drone}
@@
 Based on the simulation it was determined which of the control effectiveness terms have a greater influence on the system response and which ones can be neglected.
-Additionally the simulation model provided a good overview of potential computational problems and mistakes which could lead to drastically growing values and unstable behaviour of the system.
+Additionally, the simulation model provided a good overview of potential computational problems and mistakes which could lead to drastically growing values and unstable behaviour of the system.
 To solve some of them, saturation blocks have been used  in different places.
@@
 Similarly to the section \ref{subsec: indi_outer}, it was assumed that the sum of the forces in the linear momentum equation is composed of three components, namely gravitational, propulsive and aerodynamic.
-The gravity and the propulsive force have not been changed, so the Equations \ref{eq:Fg} and \ref{eq:Fp} were also adopted for the simulation model.
-The thrust value $T$ was modelled as a linear function of rotational rates of propellers
+The expressions of the gravity and propulsive forces have not been changed, so the Equations \ref{eq:Fg} and \ref{eq:Fp} were adopted for the simulation model.
+The thrust value $T$ was modelled as a linear function of rotational rates of the propellers
 \begin{equation}
@@
 In subsection \ref{subsec:parameter_estimation} it is shown how to estimate the thrust coefficient directly from the flight data.
-However, for the simulation model $k_F$ was computed based on the assumption that the influence of the force constant of the rotors $k_F$ (considering the lever arm) is greater than the influence of the moment constant of the rotors $k_M$, and that the thrust to weight ratio expression $\frac{T}{W} \approx 2$.
+However, for the simulation model $k_F$ was approximated based on the assumption that the influence of the force constant of the rotors $k_F$ (considering the lever arm) is greater than the influence of the moment constant of the rotors $k_M$, and that the \textit{thrust to weight ratio} expression is $\frac{T}{W} \approx 2$.
 
@@
 The numerical values of the inertia tensor $(\bm{I}^G)_B$ were estimated using pendulum method in \cite{foerster}.
-The total external moment acting on the Crazyflie consists only of the propulsive moment $\bm{M}_P$ as it is defined in \ref{subsec: indi_inner}.
+The total external moment acting on the Crazyflie contains only the propulsive moment $\bm{M}_P$ as it is defined in \ref{subsec: indi_inner}.
 It consist of the control moment generated by the rotors $\bm{M}_C$  and moment containing the gyroscopic effect of the rotors $\bm{M}_{gyro}$ (see Equations \ref{eq:m_c} and \ref{eq:m_gyro}).
-The moment constant of the rotor was computed to fulfil the requirements on $k_F$ and $k_M$ which were described above.
+The moment constant of the rotor was computed to fulfil the requirements on $k_F$ and $k_M$ which are described above.
 To obtain the numerical estimate of the propeller inertia matrix $I_{rzz}$, the propeller was approximated with a bar element.
-This has been shown to be a valid assumption since the influence of the propeller inertia (due to its negligible weight) is very small.
-
-TODOs:\\
-- 3.2.1 reference to the table with all used constants in the appendix
+This has been shown (see \ref{subsec:simulation_results}) to be a valid assumption since the influence of the propeller inertia (due to its negligible weight) is very small.
 
@@
 If the actuator feedback is not available, it is possible to use its model instead.
-The model of the actuator dynamics was assumed to be a first order lag filter with following transfer function in continuous Laplace domain
-\begin{equation}
-	\begin{split}
-		A(s) = \frac{k}{1+T_S}
+The model of the actuator dynamics was assumed to be a first order lag filter with the following transfer function defined in a continuous Laplace domain
+\begin{equation}
+	\begin{split}
+		A(s) = \frac{k}{1+Ts}
 		\label{eq:act_dynamics_c}
@@
 In the Simulink model it was assumed that the actuator feedback is available, hovewer for the implementation on hardware it is necessary to have a discrete version of the transfer function in Equation \ref{eq:act_dynamics_c}.
-Transforming the transfer function in Equation \ref{eq:act_dynamics_c} from continuous domain into discrete by applying \textit{Zero-Order Hold method} results in
+Transforming it from continuous domain into discrete by applying \textit{Zero-Order Hold method} results in
 \begin{equation}
@@
 with $\alpha = 1-e^{\frac{-T_S}{T}}$ and sample time $T_S$.
-The default frequency of the Crazyflie controller update is 500 Hz.
+The default frequency with which the Crazyflie controller updates its state is 500 Hz.
 Thus, sampling time $T_S$ was set to the reciprocal value of the default frequency.
@@
 
-As it was shown in Chapter \ref{cha:theoretical_background} (TODO also see Figures ...
-and ...), the inner and outer loops employ several second order filters.
+As it was shown in Chapter \ref{cha:theoretical_background} (see Figures \ref{fig:indi_inner_croped} and \ref{fig:indi_outer_croped}), the inner and outer loops employ several second order filters.
 The main task of two of them is to reduce  noise in the measurements of the angular and linear acceleration.
@@
 Using the same parameters for every filter, this technique accounts for the time delay which is introduced by the filters and ensures that all quantities that were fed back are from the same point in time.
-The gneral transfer function of a second order filter in continuous domain is defined by the following formula
+The general transfer function of a second order filter in continuous domain is defined by the following formula
 \begin{equation}
@@
 \end{equation}
-with a relative damping coefficient $\zeta$ and an eigenfrequency $\omega_n$.
+with the relative damping coefficient $\zeta$ and the eigenfrequency $\omega_n$.
 To implement transfer function from Equation \ref{eq:filter_c} on a digital computer it must be transformed to the discrete domain.
@@
 	\begin{split}
-		s \ \widehat{=} \ \frac{2}{T_S} \frac{1-z^{-1}}{1+z^{-1}}
+		s \ \widehat{=} \ \frac{2}{T_s} \frac{1-z^{-1}}{1+z^{-1}}
 		\label{eq:filter_c}
@@
 
-\subsection{Simulation Results and Analysis} \label{subsec:simulation_results}
-
-- Inner loop subsubsection (Tell that it is descrete implementation and then analysis) \\
-- Outer loop subsubsection (- // -) \\
-- Appendix: simulink model images, table with all constants \\
-- Plot differences with or without some terms (G1, G2\_yaw) \\
-- Responces for different step inputs
-- pz-Plot
-
-TODOs:\\
-- 3.2.2 'Actuator Dynamics' Fig4 from Adaptive... Smeur paper
-- 3.2.3 'Filtering' Reference figures of the inner and outer block diagrams
-- 3.2.3 'Filtering' Block diagram of the filter 
+\subsection{Simulation Results} \label{subsec:simulation_results}
+
+This subsection shortly presents simulation results of the closed loop \acrshort{INDI} controller (consisting of the inner and outer loops).
+Both control loops were implemented (as depicted in Figures \ref{fig:indi_inner_croped} and \ref{fig:indi_outer_croped}) in discrete domain, the model of the Cryzyflie dynamics was implemented in continuous domain.
+This is usually done, because a real physical system such as a quadrotor operates in continuous time, however a control algorithm representing a cyber component always runs on a digital system with a discrete sampling rate.
+
+The input of the overall system is a position vector.
+Thus, the closed loop model was tested by applying a sequence of position steps of different intervals.
+Figure \ref{fig:sim_outer_all} shows three plots containing responses of the outer loop controllers for the $x$-component of the position, linear velocity and linear acceleration states.
+% of the position $x$, the linear velocity $\dot{x}$ and the linear acceleration $\ddot{x}$.
+It should be noted that the gains of the position and velocity controllers can be tunsimulation_resultsed, to achieve a faster response, however that is beyond the scope of this project as the main focus was the control.
+
+\begin{figure}[h]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=1\textwidth]{figs/sim_outer_all.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Response of the outer loop model to a step input.]{Response of the outer loop model to a step input. Blue lines represent reference values, red lines denote measured values.}
+	\label{fig:sim_outer_all}
+\end{figure}
+
+The input of the inner loop is the attitude, which is computed and provided by the outer loop.
+Figure \ref{fig:sim_inner_all} shows the response of inner loop (for the same position step sequence as above) which controls the attitude, the angular velocity and the angular acceleration of the quadrotor.
+
+\begin{figure}[h]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=1\textwidth]{figs/sim_inner_all.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Response of the inner loop model to the input provided by the outer loop]{Response of the inner loop model to the input provided by the outer loop.
+Blue lines represent reference values, red lines denote measured values.}
+	\label{fig:sim_inner_all}
+\end{figure}
+
+As mentioned in the beginning of this chapter, a simulation can be used to determine terms of the model which have a greater influence on the overall controller performance.
+Matrix $G_2$ of the control effectiveness term in Equation \ref{eq:indi_inner_control_law} contains only the term of the inertia tensor of the propeller $I_{rzz}$.
+Since $I_{rzz}$ is small, it was expected that $G_2$ will not have a big impact on the model response.
+Figure \ref{fig:g2_comparison} confirms this expectation, by plotting the step response of the Crazyflie model with and without considering  the gyroscopic effects of the quadrotor propellers.
+It can be seen that both responses are almost similar.
+In the next section, (see \ref{subsec:parameter_estimation_inner}) through the estimation of the control effectiveness terms using the flight data, this observation will be practically confirmed.
+In practice, considering only important terms, can reduce the implementation effort of a particular control algorithm.
+
+\begin{figure}[h]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=0.7\textwidth]{figs/g2.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Responses of the closed loop with and without gyroscopic effects.]{Responses of the closed loop using dynamics model with and without considering the gyroscopic effects of the propellers.}
+	\label{fig:g2_comparison}
+\end{figure}
+
 \section{Implementation on the Hardware} \label{sec:implementation_on_hardware}
 
-\subsection{Parameter Estimation} \label{subsec:parameter_estimation}
+This section describes some important aspects of the controller implementation on the Crazyflie hardware.
+As it was mentioned at the beginning of this chapter, the inner loop \acrshort{INDI} controller was already implemented on the provided hardware.
+Thus, this section is mainly dedicated to the implementation of the outer loop.
+
+\subsection{Parameter Estimation of the Inner Loop} \label{subsec:parameter_estimation_inner}
+
+To ensure proper functioning of the inner loop, some of the implementation errors were corrected.
+Additionally, the control effectiveness parameters $\bm{G_1}$ and $\bm{G_2}$ were reestimated with a new flight data.
+
+To estimate model parameters of a quadrotor two strategies can be applied: estimation through measurements and estimation with flight data.
+Using the first strategy it is usually difficult to achieve accurate results \cite{Smeur2}.
+By contrast, pursuing the second approach can reduce the amount of effort and also lead to plausible results.
+To collect the flight data, the only requirement is that the quadrotor has a functioning controller (e.g.
+PID controller) to perform flights.
+After the first estimates of the control effectiveness parameters are obtained, further flight can be performed with the \acrshort{INDI} controller.
+
+Equation \ref{eq:main_eom_indi_inner_lin_final} serves as a basis for the  parameter estimation.
+Since the existing implementation of the inner loop does not include the increment term of the thrust, Equation  \ref{eq:main_eom_indi_inner_lin_final} reduces to
+\begin{equation}
+	\bm{\Delta\dot{\omega}} = 
+	\begin{bmatrix}
+		\bm{G}_1 & \bm{G}_2
+	\end{bmatrix} 
+	\begin{bmatrix}
+		\bm{\Delta\Omega}\\
+		\bm{\Delta\dot{\Omega}}
+	\end{bmatrix} 	
+	\label{eq:inner_indi_estimation}
+\end{equation}
+where $\bm{\Delta\dot{\omega}} = \bm{\dot{\omega}} - \bm{\dot{\omega}}_f$ and $\bm{\Delta\dot{\Omega}} = \bm{\dot{\Omega}} - \bm{\dot{\Omega}}_f$.
+Note that the terms $\bm{\Delta\Omega}$ and $\bm{\Delta\dot{\Omega}}$ have to be passed through the actuator dynamics $A(s)$.
+Furthermore, the Equation \ref{eq:inner_indi_estimation} is differentiated to amplify high frequencies of the signal for a better parameter estimation performance.
+Differentiation works like a high-pass filter, passing through only fast changing portion of the signal (e.g.
+fast and sharp maneuvers).
+It also eliminates bias of the signal.
+Considering these changes, Equation \ref{eq:inner_indi_estimation} results in
+\begin{equation}
+	\bm{\Delta\ddot{\omega}} = 
+	\begin{bmatrix}
+		\bm{G}_1 & \bm{G}_2
+	\end{bmatrix} 
+	\begin{bmatrix}
+		\bm{\Delta\dot{\Omega}}\\
+		\bm{\Delta\ddot{\Omega}}
+	\end{bmatrix} 	
+	\label{eq:inner_indi_estimation_diff}
+\end{equation}
+When the log data is available, the \textit{least squares} approach can be applied to find solution of the Equation \ref{eq:inner_indi_estimation_diff}.
+
+To confirm the observation that $\bm{G_2}$ term has a very small influence on the overall control effectiveness, made in \ref{subsec:simulation_results}, contribution of both terms ($\bm{G_1}$ and $\bm{G_2}$) were compared.
+Figure \ref{fig:g2_comparison} shows the contribution of the estimated $\bm{G_1}$ and $\bm{G_2}$ terms to the yaw component of the differentiated angular acceleration.
+Clearly, the contribution of $\Delta\ddot{\Omega}_z \cdot \bm{G_2}$ is noticeably smaller than the one of $\Delta\dot{\Omega}_z \cdot \bm{G_1}$.
+
+\begin{figure}[h]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=1\textwidth]{figs/g_contribution.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Contribution of control effectiveness terms to the angular acceleration]{Contribution of the estimated $\bm{G_1}$ and $\bm{G_2}$ terms to the yaw component of the angular acceleration.}
+	\label{fig:g2_comparison}
+\end{figure}
+
+\subsection{Estimation of the Actuator Dynamics Time Constant} \label{subsec:time_const_estimation}
+
+The \acrshort{INDI} controller derived in Chapter \ref{cha:theoretical_background} controls Crazyflie by adding increments to the current angular rates of the rotors.
+Unfortunately, the hardware of the quadrotor does not support the measurement of the propeller rates.
+Thus, to be able to feedback the propeller rates they are passed through the actuator dynamics model $A'(s)$ (see \ref{subsec:actuator_dynamics}).
+The feedback of the propeller rates is then obtained as shown in Figure \ref{fig:actuator}.
+
+\begin{figure}[h]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=0.7\textwidth]{figs/actuator_croped.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Estimation of the actuator state in case of the missing actuator feedback]{Estimation of the actuator state in case of the missing actuator feedback}
+	\label{fig:actuator}
+\end{figure}
+
+If the transfer function of the actuator $A'(s)$ is assumed to be of the first order, the only unknown parameter is the time constant $T$ (since it is assumed that the commanded propeller rates are not amplified by the actuator, the gain $k$ is simply $1$).
+To estimate the time constant $T$, propeller rates were measured for different step inputs.
+Finally, the general form of the first order lag element was fitted to the measured data.
+
+The transfer function of the first order lag element (Equation \ref{eq:act_dynamics_c}) in time domain has the following form 
+\begin{equation}
+	a(t) = 	k (1 - e^{\frac{-t}{T}})
+	\label{eq:act_dynamics_time}
+\end{equation}
+The fitting is then done by minimizing the squared error between measured $a_{measured}(t)$ and predicted $a(t)$ data. For multiple data points $n$ the objective function $E(T)$ is defined as 
+\begin{equation}
+	E(T) = \sum_{i=1}^{n} (a(T) - a_{measured}(T))^2
+	\label{eq:obj_function}
+\end{equation}
+$T$ is then computed such that Equation \ref{eq:obj_function} is minimal.
+Note that in Equation \ref{eq:obj_function} $a(T)$ is a function of the time constant $T$, since it is an optimization parameter.
+Figure \ref{fig:actuator_dynamics_est} shows the obtained result of the optimization.
+Here, the red curve was fitted to the measured data (blue line).
+In the figure the signal contains $n=155$ samples recorded with a frequency of 200 Hz.
+The estimated value for the time constant is $T = 0.061658 \ s$.
+
+\begin{figure}[h]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=0.8\textwidth]{figs/actuator_dynamics_est.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[]{}
+	\label{fig:actuator_dynamics_est}
+\end{figure}
+
+A simpler alternative to estimate the time constant would be reading off the time point at which the response reaches $63.2 \%$ of its final value.
+Using this approach, the value of the time constant is approximately $0.0675 \ s$, which is very close to the value estimated through solving the optimization problem.
+
+\subsection{Estimation of the Thrust Mappint} \label{subsec:thrust_mapping}
+
+The thrust increments provided by the outer loop \acrshort{INDI} are values in  Newton.
+Later, in the inner loop \acrshort{INDI} commanded thrust values are computed by adding thrust increments to the current thrust values and passed to the motor mixing algorithm.
+Depending on the commanded roll, pitch and yaw values, the motor mixing algorithm computes values for each rotor and sends these commands to the motor.
+Unfortunately, the values which are sent to the motor are not in the same units as thrust.
+These are defined in a specific range (e.g unsigned integer value of 32 bits has a valid number range between 0 and 65535).
+Mapping a thrust value in physical units to a motor command value is called \textit{thrust mapping}.
 
 - Actuator Dynamics (Estimation of the time constant), plot response with estimated constant\\
-- Thrust dynamics estimation\\
+- Thrust dynamics estimation (control allocation)\\
 - Estimation of the control effectiveness parameters G1, G2 for inner INDI (describe performed flight to log data), plot the curve with contribution of G1, G2 to the fitting\\
@@
 
-\subsection{Testing with contact Forces and Moments?} \label{subsec:testing_with_fandm}
-
 \chapter{Results} \label{cha:results}
@@
 
-- To make the controller work a minimal knowledge of the system dynymics is need.
+%- To make the controller work a minimal knowledge of the system dynymics is need.
 Nevertherless G1, G2 still have to estimated accuratly because this 2 parameters do have inpact on the controller performance.
 \\
-- Plain step responses of the outer loop \\
-- Step responses with disturbance of the outer loop
+%- Plain step responses of the outer loop \\
+%- Step responses with disturbance of the outer loop
 
@@
 %\end{equation}
+
+%\begin{subequations}
+%	\begin{align}
+%		n_0 &= \omega_n^2 \\
+%		n_1 &= 2\omega_n^2 \\
+%		n_2 &= \omega_n^2 \\
+%		d_0 &= \bigg[(\frac{2}{T_S})^2 + \frac{4\zeta \omega_n}{T_S} + \omega_n^2\bigg] \\
+%		d_1 &= \bigg[\frac{8}{T_S^2} + 2\omega_n^2\bigg] \\
+%		d_2 &= \bigg[(\frac{2}{T_S})^2 - \frac{4\zeta \omega_n}{T_S} + \omega_n^2\bigg]
+%	\end{align}
+%	\label{eq:filter_parameters}
+%\end{subequations}

### 2020-03-13 code/Simulink/Crazyflie_Simulation_paper/plot_responses_paper.m

@@ -1,0 +1,177 @@
+clc 
+close all
+
+%% Import
+
+% Outer loop
+xi_ref = out.xi_ref;
+xi = out.xi;
+
+dxi_ref = out.dxi_ref;
+dxi = out.dxi;
+
+ddxi_ref = out.ddxi_ref;
+ddxi = out.ddxi;
+
+
+% Inner loop
+eta_ref = out.eta_ref;
+eta = out.eta;
+
+omega_ref = out.omega_ref;
+omega = out.omega;
+
+domega_ref = out.domega_ref;
+domega = out.domega;
+
+t = out.tout;
+
+
+%% Plot response - outer loop - xi
+
+% Plotting
+fig_outer = figure('Name', 'Outer loop response xi');
+for i = 1:3
+    subplot(3, 1, i)
+    plot(t, xi_ref(i, :), 'LineWidth', 1);
+    hold on; grid on;
+    plot(t, xi(i, :), 'LineWidth', 1);
+    xlim([0 inf]);
+    if(i==1)
+        xlabel('Time $$[s]$$', 'Interpreter', 'latex');   
+        ylabel('$$x \ [m]$$', 'Interpreter', 'latex');
+    elseif (i==2)
+        xlabel('Time $$[s]$$', 'Interpreter', 'latex');   
+        ylabel('$$y \ [m]$$', 'Interpreter', 'latex');
+    else
+        xlabel('Time $$[s]$$', 'Interpreter', 'latex');   
+        ylabel('$$z \ [m]$$', 'Interpreter', 'latex');
+    end
+    legend('reference', 'state')
+end
+
+% Saving
+set(fig_outer, 'Units', 'points');
+pos = get(fig_outer, 'Position');                        % gives x left, y bottom, width, height
+width = pos(3);
+height = pos(4);
+set(fig_outer, 'PaperUnits', 'points');
+set(fig_outer, 'PaperPosition', [0 0 width height]);     % Position plot at left hand corner with width 5 and height 5.
+set(fig_outer, 'PaperSize', [width height]);             % Set the paper to have width 5 and height 5.
+saveas(fig_outer, 'plots/sim_outer', 'pdf');                       % Save figure
+
+
+%% Plot response - outer loop xi, dxi, ddxi
+
+fig_outer_all = figure('Name', 'Outer loop response xi, dxi, ddxi');
+
+% Plotting xi
+subplot(3, 1, 1)
[…]

### 2020-03-13 code/Simulink/Crazyflie_Simulation_paper/set_params_paper.m

@@ -1,0 +1,95 @@
+clc 
+clear 
+close all
+
+%%
+% Force and Moment Notation:
+% 'FX_Y' or 'MX_Y' with: 
+% - X: Force nature (e.g gravitational (G), aerodynamical (A), propulsive (P) etc)
+% - Y Coordinate frame (e.g Body-Fixed (B), NED (O) etc)
+% 
+% Notation of other values: (TODO)
+% - omegaR_X: vector of rotor angular velocities
+% - ...
+
+
+%% Dynamics
+
+% Crazyflie
+g = 9.81;           % gravitational acceleration in [m/s^2]
+m_CF = 0.028;       % mass of the Crazyflie quadrotor in [kg]
+l = 0.033;          % lever arm to the rotor in x-direction [m]
+b = 0.033;          % lever arm to the rotor in y-direction [m]
+I_rzz = 9.3e-9;     % Component of moment of inertia of the rotor [kg*m^2]
+
+
+I_CF_1 = [16.823890  -1.224320  -0.716891    % Moment of inertia of the 
+          -1.224320   16.885278  2.083147    % Crazyflie quadrotor in [kg*m^2]
+          -0.716891   2.083147   29.808912] * 10e-6;       
+% I_CF_1 = [16.823890     0          0       % Moment of inertia of the 
+%              0      16.885278      0       % Crazyflie quadrotor in [kg*m^2]
+%              0          0       29.808912] * 10e-6; 
+
+I_CF_1_inv = inv(I_CF_1);                 % Inverted I_CF_1
+
+% Propulsive force
+k_f = 1.6e-4;       % motor constant for F_P and M_P[N/(rad/s)]
+k_m = 1e-6;         % motor constant for M_P [N*m/(rad/s)]
+
+% Aerodynanic force
+kx = 10.25e-4;      % drag constant in x-direction [kg/s]
+ky = 10.25e-4;      % drag constant in y-direction [kg/s]
+kz = 7.553e-4;      % drag constant in z-direction [kg/s]
+
+% Actuator dynamics 
+T = 0.061658;                      % Actuator time constant [s]
+omegaR_init = [1; 1; 1; 1]*200;    % Initial rotor angular velocity [rad/s]
+
[…]

### 2020-03-13 code/actuator_dynamics/actuator_dynamics.m

@@ -5,7 +5,7 @@ close all
 %% Parameter 
 
 plot_full = 1;
-plot_4th = 0;
+plot_4th = 1;
 plot_est = 1;
 
 T_sample = 0.005;                           % time between two samples in [s]
@@ -30,7 +30,7 @@ log_sm = smooth(log, 20);
 
 % Plot
 if (plot_full)
-    figure;
+    figure('Name', 'plot_full');
     plot(log)
     hold on;
     plot(log_sm)
@@ -62,6 +62,7 @@ else
 end
 if (plot_full) 
     plot(step); 
+    legend('log', 'log smooth', 'step', 'Location', 'best')
 end
 
 %% Extract 4th pt1
@@ -76,10 +77,10 @@ end
 t = (0:T_sample:(size(log_4th,1)-1)*T_sample)';
 
 if (plot_4th)
-    figure;
+    figure('Name', 'ploth_4th');
     plot(t, log_4th); hold on; grid on; 
     plot(t, step_4th)
-    xlabel('Samples [-]')
+    xlabel('Time [s]')
     ylabel('frequency [Hz]')
     xlim([0 inf])
 end
@@ -102,8 +103,8 @@ tdata = (0:T_sample:(size(ydata,1)-1)*T_sample)';
 T = optimvar('T', 1);                   % Create optimization variable
 K = optimvar('K', 1);
 
-fun = @(T,K) K*(1-exp(-tdata/T));             % Create function to optimize
-response = fcn2optimexpr(fun, T, K);
+fun = @(T,K) K*(1-exp(-tdata/T));       % Create function to optimize
+response = fcn2optimexpr(fun, T, K);    % Convert function to optim expession
 obj = sum((response - ydata).^2);       % Define error function
 
 % Create optimization problem
@@ -123,13 +124,14 @@ responsedata = evaluate(response, sol);
 
 % Plot data
 if (plot_est)
-    figure; 
-    plot(tdata, ydata); grid on; hold on; 
+    fig_est = figure('Name', 'plot_est'); 
+    plot(tdata, ydata+log_4th(1)); grid on; hold on; 
     xlim([0 inf]); 
-    plot(tdata, responsedata);
-    xlabel('Samples [-]');
-    ylabel('frequency (scaled) [Hz]');
-    legend('original', 'estimated');
+    plot(tdata, responsedata+log_4th(1));
+    ylim([responsedata(1)+log_4th(1) 350])
[…]

### 2020-03-13 code/param_est/param_est.m

@@ -16,6 +16,7 @@ filename = "csv_data/data_1901.csv";
 [tick, gyro_roll, gyro_pitch, gyro_yaw, cmd_thrust, cmd_roll,... 
  cmd_pitch, cmd_yaw, accelz] = import_logdata(filename);
 
+time = (tick - tick(1)) / 1000;
 
 %% Actuator dynamics
 cmd_roll_a = filter([alpha], [1, -(1-alpha)], cmd_roll);
@@ -67,17 +68,53 @@ display(['T = ' num2str(T) 's; Fs = ' num2str(Fs) 'Hz; alpha = ' num2str(alpha)]
 display(['G1_roll = ' num2str(G_roll) '; G1_pitch = ' num2str(G_pitch) ...
          '; G1_yaw = ' num2str(G_yaw(1)) '; G2_yaw = ' num2str(G_yaw(2))])
 
-% Plot contributions of G matrices
-figure('Name','G1_yaw contribution');
-plot(ang_accel_yaw_d); hold on
-plot([cmd_yaw_fd 0*cmd_yaw_fdd]*G_yaw)
-xlim([0 inf]); grid on;
-legend('ang\_accel\_yaw\_d', 'cmd*G1')
+% % Plot contributions of G matrices
+% figure('Name','G1_yaw contribution');
+% plot(ang_accel_yaw_d); hold on
+% plot([cmd_yaw_fd 0*cmd_yaw_fdd]*G_yaw)
+% xlim([0 inf]); grid on;
+% legend('ang\_accel\_yaw\_d', 'cmd*G1')
+% 
+% figure('Name','G2_yaw contribution');
+% plot(ang_accel_yaw_d); hold on
+% plot([0*cmd_yaw_fd cmd_yaw_fdd]*G_yaw)
+% xlim([0 inf]); grid on;
+% legend('ang\_accel\_yaw\_d', 'cmdd*G2')
 
-figure('Name','G2_yaw contribution');
-plot(ang_accel_yaw_d); hold on
-plot([0*cmd_yaw_fd cmd_yaw_fdd]*G_yaw)
-xlim([0 inf]); grid on;
-legend('ang\_accel\_yaw\_d', 'cmdd*G2')
+
+%% Plots for the papaer
+
+min = 1500;
+max = 6000;%size(time, 1);
+
+fig_c = figure('Name','G_yaw contribution');
+
+%subplot(2, 1, 1)
+plot(ang_accel_yaw_d(min:max)); hold on; grid on;
[…]

### 2020-03-27 Paper_EV/Paper_EV.tex
Backup update 27.03.2020

@@
 
+% For writing angle symbol °
+\usepackage{siunitx}
+
 % Define subsection depth
 \setcounter{secnumdepth}{3}
+
+% For SI units
+\usepackage{siunitx}
 
@@
 \fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implem. and Eval. of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}
-\fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage \thinspace / \lastpageref{LastPages}}
+\fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage \thinspace / \lastpageref{pagesLTS.arabic}}
 % Line settings
@@
 \newacronym{INDI}{INDI}{Incremental Nonlinear Dynamic Inversion}
+\newacronym{MAV}{MAV}{Micro Air Vehicle}
 \newacronym{MCU}{MCU}{Microcontroller}
@@
 \begin{itshape}
-Deutsche Kurzfassung der Arbeit.
+Inkrementelle Nichtlineare Dynamische Inversion (INDI) is ein vielversprechender Reglertyp, welcher h\"aufig f\"ur die Regelung von nichtlinearen Flugsystemen unterschiedlicher Art eingesetzt wird.
+Ein Vorteil der INDI ist, dass dieser Reglertyp kein detalliertes Modell der geregelten Strecke ben\"otigt.
+Au\ss{}erdem, wirkt INDI sehr effektiv gegen St\"orungen.
+Diese Semesterarbeit befasst sich mit der Auslegung eines INDI-Reglers f\"ur die Lage- und Positionsregelung eines Nano-Quadrotors.
+Die Arbeit beginnt mit der Herleitung des Regelalgorithmus.
+Der hergeleitete Regelgesetz wird dann erst in Simulink entwickelt und anschlie\ss{}end auf der Quadrotor-Hardware implementiert.
+Dazu werden solche Implementierungsaspekte wie Ermittlung der Eingangsparameter, Messung und Berechnung der Aktuatorzeitkonstante sowie Ermittlung des Schub-Mapping-Parameters besprochen.
+Abschlie\ss{}end, wird der implementierte Regler auf die F\"ahigkeit St\"orungen zu bek\"ampfen getestet.
 \end{itshape}
@@
 \begin{itshape}
-English abstract of the thesis.
+Incremental Nonlinear Dynamic Inversion (INDI) is a promising control technique, widely used for control of different types of aircraft systems.
+Besides providing high-performance nonlinear control, this controller type does not require a detailed model of the controlled aircraft and is effective against disturbances.
+This semester thesis describes the development of an INDI controller to control the attitude and the position of a nano-quadrotor.
+It begins with the derivation of the control algorithm.
+The controller is then firstly developed in the Simulink environment and afterwards implemented on the quadrotor hardware.
+Subsequently, the implementation aspects of the INDI controller such as estimation of the control effectiveness, measurement of the actuator time constant and estimation of the thrust mapping parameter are discussed.
+Finally, the implemented controller is tested on the ability to cope with disturbances.
 \end{itshape}
@@
 \mbox{}
-\nomwithdim{B}{\( F \)}{Force}{L}{$N$}
+\nomwithdim{B}{\( \bm{F} \)}{Force}{L}{$N$}
 \nomwithdim{B}{\( g \)}{Gravitational acceleration}{}{$m/s^2$}
@@
 
+The popularity of Micro Air Vehicles (MAVs) in research and industry has grown over the past years.
+The large interest in \acrshort{MAV}s can be expalined with their potential of performing a wide range of civilian and military tasks, reaching from the investigation of hazardous regions up to the agriculture mapping \cite{Ward}.
+One of the most popular representatives of \acrshort{MAV}s are quadrotors, belonging to the rotary-wing \acrshort{MAV}s.
+Their dynamic behaviour is usually of a nonlinear character.
+Thus, to control such an aircraft, robust control strategies have to be applied.
+One such strategy is called \acrfull{INDI}, which is the incremental form of the nonlinearity cancelling technique \acrfull{NDI}.
+The \acrshort{INDI} technique makes it possible to control an aircraft without fully modelling its dynamics.
+Instead, \acrshort{INDI} uses a primitive aircraft model, which eases the development and implementation of the control algorithm.
+In addition, \acrshort{INDI} has good properties of coping with unmodelled gust and disturbances.
+
 \section{Contribution of the Thesis} \label{sec:contribution_ofthe_thesis}
 
-- 3. Implementation in Simulink for testing (both loops)\\
-- 3. Implementation on HW (outer loop)
+The main goal of this thesis was to implement an \acrshort{INDI} controller to control the linear acceleration of a nano-quadrotor.
+Furthermore, to have the ability to control the quadrotors position, the \acrshort{INDI} loop had to be augmented with a velocity as well as a position controller.
+For the role of the research quadrotor, a small quadrotor named Crazyflie 2.1 was employed.
+Besides the derivation of the control algorithm itself, this thesis covers the process of estimation of the control effectiveness terms, as well as the estimation of other parameters such as actuator dynamics time constant and thrust mapping parameter, which are necessary for proper functioning of the controller.
+Additionally to the hardware implementation of the control algorithm, this work describes the development of the controller as well as the quadrotor model in Simulink.
+Finally, it discusses the capability of the successfully implemented \acrshort{INDI} controller to cope with disturbances.
+
+%- Implementation in Simulink for testing (both loops)\\
+%- Implementation on HW (outer loop)  \\
 
 \section{Structure of the Thesis} \label{sec:structure_ofthe_thesis}
+
+This semester thesis is organized into five chapters.
+The introductory chapter is followed by the second chapter, containing the theoretical background.
+Here, after introducing dynamic equations of motion of an aircraft (\ref{sec:eqs_motion}), \acrshort{NDI} (\ref{sec:ndi}) and \acrshort{INDI} (\ref{sec:indi}) control algorithms are discussed.
+The \acrshort{INDI} technique is then used to derive the attitude (\ref{subsec: indi_inner}) and position (\ref{subsec: indi_outer}) controllers for the Crazyflie quadrotor.
+Chapter three focuses on the implementation aspects of the \acrshort{INDI} algorithm derived in the previous chapter.
+It starts with a short description of the quadrotor hardware (\ref{sec:research_quadrotor}).
+In the second part (\ref{sec:simulink_model}) of the third chapter, simplified model of the Crazyflie quadrotor as well as the attitude and position controllers are developed in the Simulink environment.
+The third section (\ref{sec:implementation_on_hardware}) of the same chapter covers aspects that are relevant for the hardware implementation of the \acrshort{INDI} control algorithm, such as the estimation of the control effectiveness terms and thrust mapping parameter.
+After controller was implemented, it was tested and validated.
+The test results are summarized in the fourth chapter.
+The final chapter contains a short conclusion of the performed work.
 
@@
 \end{equation}
-where $\sum(\bm{F}^G)_B \in \mathbb{R}^{3 \times 1}$ is the sum of the external forces acting on the system and applied to the center of gravity $G$, $m$ the mass of the body, $(\bm{\dot{v}}^G)_{B} \in \mathbb{R}^{3 \times 1}$ the linear acceleration of the point $G$, $(\bm{\omega}^{OB}) \in \mathbb{R}^{3 \times 1}$ the angular velocity of the body-fixed frame ($B$) with respect to the \acrfull{NED} ($O$) coordinate frame.
+where $\sum(\bm{F}^G)_B \in \mathbb{R}^{3 \times 1}$ is the sum of the external forces acting on the system and applied to the center of gravity $G$, $m$ the mass of the body, $(\bm{\dot{v}}^G)_{B} \in \mathbb{R}^{3 \times 1}$ the linear acceleration of the point $G$, $(\bm{v}^R)_{B} \in \mathbb{R}^{3 \times 1}$ the velocity of any reference point $R$, $(\bm{\omega}^{OB}) \in \mathbb{R}^{3 \times 1}$ the angular velocity of the body-fixed frame ($B$) with respect to the \acrfull{NED} ($O$) coordinate frame.
 Subscript $B$ denotes that all variables are specified in the body-fixed coordinate frame.
@@
 	\begin{bmatrix}
-		\dot{V_N}\\
-		\dot{V_E}\\
-		\dot{V_D}
+		V_N\\
+		V_E\\
+		V_D
 	\end{bmatrix}_O
@@
 The \acrshort{NDI} approach is based on feedback linearization and is also called \textit{Input-Output Linearization}.
-Often, such type of controllers is involved in tracking control tasks, where objective is to track some desired trajectory \cite{Slotine}.
+Often, such type of controllers is involved in tracking control tasks, where the objective is to track some desired trajectory \cite{Slotine}.
 To derive it, consider the following nonlinear system
@@
 	\begin{split}
-		\bm{\dot{y}} &=  \frac{\partial\bm{y}}{\partial t} = \frac{\partial\bm{h}(\bm{x})}{\partial t} \frac{\partial\bm{x}}{\partial t} = \frac{\partial\bm{h}(\bm{x})}{\partial t} \dot{\bm{x}} = \nabla\bm{h}(\bm{x}) [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \\
+		\bm{\dot{y}} &=  \frac{\partial\bm{y}}{\partial t} = \frac{\partial\bm{h}(\bm{x})}{\partial x} \frac{\partial\bm{x}}{\partial t} = \frac{\partial\bm{h}(\bm{x})}{\partial x} \dot{\bm{x}} = \nabla\bm{h}(\bm{x}) [\bm{f}(\bm{x}) + \bm{G}(\bm{x})\bm{u}] \\
 		&= \nabla\bm{h}(\bm{x}) \bm{f}(\bm{x}) + \nabla\bm{h}(\bm{x}) \bm{G}(\bm{x})\bm{u} = L_{\bm{f}} \bm{h}(\bm{x}) + L_{\bm{G}} \bm{h}(\bm{x}) \bm{u} 
@@
 	\begin{split}
-		\bm{u} = L_{\bm{G}}\bm{h}(\bm{x})^{-1} (\bm{\nu} - L_{\bm{f}}\bm{h}(\bm{x}))
+		\bm{u} = (L_{\bm{G}}\bm{h}(\bm{x}))^{-1} (\bm{\nu} - L_{\bm{f}}\bm{h}(\bm{x}))
 		\label{eq:u_control_law}
@@
 \end{equation}
-The variable $\bm{\nu}$ is called an \textit{equivalent input} and represents the desired output of the system.
+The variable $\bm{\nu}$ is called an \textit{virtual control input} and represents the desired output of the system.
 
@@
 
-The \acrshort{INDI} is an incremental form of the \acrshort{NDI} for which the lack of the accurate system dynamics model does not critically affect the performance of the control algorithm \cite{Silva}.
+\acrshort{INDI} is an incremental form of \acrshort{NDI} for which the lack of the accurate system dynamics model does not critically affect the performance of the control algorithm \cite{Silva}.
 At first the general form of the \acrshort{INDI} is presented in \ref{subsec:indi_general}, then the inner and outer control loops for the Crazyflie quadrotor are derived in \ref{subsec: indi_inner} and \ref{subsec: indi_outer}.
@@
 
-The incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
+Assuming that the output variable corresponds to the state varible ($y=x$), the incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
 \begin{equation}
@@
 Considering very small time increments of the controller loop and applying the \textit{principle of time scale separation} the second term vanishes.
-This is a valid assumption if the dynamics of the actuators is fast compared with the dynamics of the system \cite{Silva}.
-Thus, the Equation \ref{eq:nonlin_sys_taylor2} is further simplified to
+This is a valid assumption if the dynamics of the actuators are fast compared with the dynamics of the system \cite{Silva}.
+Thus, Equation \ref{eq:nonlin_sys_taylor2} is further simplified to
 \begin{equation}
@@
 where $\bm{\dot{x}}_0$ is a measurable value from the previous step, $\bm{u_0}$ the control input from the previous step, $\bm{\nu}$ the reference value and $\bm{G}(\bm{x}_0)$ the control effectiveness matrix.
-With $\bm{\Delta u}=\bm{u}-\bm{u}_0$ the control law from Equation \ref{eq:u_control_law_indi} represents an incremental version of the Equation \ref{eq:u_control_law}.
+With $\bm{\Delta u}=\bm{u}-\bm{u}_0$ the control law from Equation \ref{eq:u_control_law_indi} represents an incremental version of Equation \ref{eq:u_control_law}.
 Instead of computing the complete control input command $\bm{u}$, this control law results in computing the increment of the control input $\bm{\Delta u}$ and adding it to the previous value $\bm{u}_0$.
@@
 
-\subsection{Inner loop INDI for Quadrotor} \label{subsec: indi_inner}
+\subsection{Inner loop INDI for a Quadrotor} \label{subsec: indi_inner}
 
 In this subsection, using theory from \ref{subsec:indi_general} the inner loop \acrshort{INDI} controller is derived to control angular acceleration of the Crazyflie quadrotor.
-The derivation of the inner loop, as well as the outer loop controllers is based on the \acrshort{INDI} controller architecture introduced by Smeur \cite{Smeur1}, \cite{Smeur2}.
+The derivation of the inner loop, as well as the outer loop controllers is based on the \acrshort{INDI} controller architecture introduced by Smeur et al.
+\cite{Smeur1}, \cite{Smeur2}.
 Equation \ref{eq:ang_momentum} from section \ref{sec:eqs_motion} serves as a basis for this derivation.
@@
 As only the body-fixed frame is used in the following control law derivation, the subscripts $B$ are not used in this subsection.
-Also all external forces and moments apply to the center of gravity of the quadrotor, thus the superscripts $G$ are also omitted.
+Furthermore, all external forces and moments apply to the center of gravity of the quadrotor, thus the superscripts $G$ are omitted.
 Solving Equation \ref{eq:ang_momentum} for the angular acceleration results in
@@
 		0 & 0 & 0 & 0 
-	\end{bmatrix} \bm{\omega}
+	\end{bmatrix} \bm{\Omega}
 	\label{eq:m_gyro}
@@
 \end{figure}
-As already explained in the previous subsection to derive the incremental control law the Taylor series expansion is perfromed on the Equation \ref{eq:main_eom_indi_inner}
+As already explained in the previous subsection, to derive the incremental control law the Taylor series expansion is perfromed on Equation \ref{eq:main_eom_indi_inner}
 \begin{equation}
@@
 \end{equation}
-By applying differentiation and rewriting some of the terms, following equation is obtained
+By applying differentiation and rewriting some of the terms, the following equation is obtained:
 \begin{equation}
@@
 \begin{equation}
-	\bm{G}_1 = 
+	\bm{G}_1 (\bm{\omega}) =
 	\begin{bmatrix}
@@
 		\bm{I}^{-1}\begin{bmatrix}
-			\bm{\omega}_y & 0 & 0 \\
-			0 & \bm{\omega}_x & 0 \\
+			\omega_y & 0 & 0 \\
+			0 & \omega_x & 0 \\
 			0 & 0 & 0 
@@
 Furthermore, angular acceleration $\bm{\dot{\omega}}_0$ which is obtained from the differentiated gyroscope measurements is usually noisy.
-It has been shown, that using a second order filtering can help to reduce measurement nose.
+Using a second order filtering can help to reduce measurement nose.
 At the same time such a filter introduces time delay, which has to be considered in the derivation, as it is important to have a unique delay for all variables which are used in the Taylor expansion \cite{Smeur1}.
-Thus, the same second order filter is applied to all variables with a subscript $0$.
+Thus, the same second order filter $H(z)$ is applied to all variables with a subscript $0$.
 By applying filtering (subscript $f$) and finite differences method to the Equation \ref{eq:main_eom_indi_inner_lin}, its discrete version results in
@@
 \end{equation}
-By solving Equation \ref{eq:main_eom_indi_inner_lin_final} for $\bm{\dot{\Omega}}$ and substituting $\bm{\dot{\omega}}$ with the equivalent input $\bm{\nu}_{ang}$, the control law of the inner loop is obtained
-\begin{equation}
-	\begin{split}
-		\bm{\dot{\Omega}}_c = \bm{\dot{\Omega}} = \bm{\dot{\Omega}}_f + (\bm{G}_1+\bm{G}_2)^{-1} \Bigg(
-		\begin{bmatrix}
-			\bm{\nu}_{ang} - \bm{\dot{\omega}}_f\\
+By solving Equation \ref{eq:main_eom_indi_inner_lin_final} for $\bm{\dot{\Omega}}$ and substituting $\bm{\dot{\omega}}$ with the virtual control input $\bm{\nu}_{\bm{\dot{\omega}}}$, the control law of the inner loop is obtained
+\begin{equation}
+	\begin{split}
+		\bm{\Omega}_c = \bm{\Omega}_f + (\bm{G}_1+\bm{G}_2)^{-1} \Bigg(
+		\begin{bmatrix}
+			\bm{\nu}_{\bm{\dot{\omega}}} - \bm{\dot{\omega}}_f\\
 			\tilde{T}
@@
 \end{equation}
-where $\bm{\dot{\Omega}}$ is a vector of commanded rotational rates for every rotor and $\tilde{T} = T - T_f$ being the thrust increment which is provided by the outer loop \acrshort{INDI}.
+where $\bm{\Omega}$ is a vector of commanded rotational rates for every rotor and  $\tilde{T} = T - T_f$ and $\tilde{\bm{\Omega}} = \bm{\Omega}_c - \bm{\Omega}_f$ being thrust and propeller rates increments respectively, provided by the inner loop \acrshort{INDI}.
 The block diagram of the inner loop \acrshort{INDI} controller is presented in Figure \ref{fig:indi_inner_croped}.
@@
 	\caption[Block diagram of the inner loop \acrshort{INDI} controller]{Block diagram of the inner loop \acrshort{INDI} controller.
-$A(z)$ is the actuator dynamics (see \ref{subsec:actuator_dynamics}) and $F(z)$ is the second-order filter (see \ref{subsec:filtering}).}
+$A(z)$ is the actuator dynamics (see \ref{subsec:actuator_dynamics}) and $H(z)$ is the second-order filter (see \ref{subsec:filtering}).}
 	\label{fig:indi_inner_croped}
@@
 
-\subsection{Outer loop INDI for Quadrotor} \label{subsec: indi_outer}
+\subsection{Outer loop INDI for a Quadrotor} \label{subsec: indi_outer}
 
@@
 As it is assumed that all forces apply to the center of gravity of the quadrotor, the superscript $G$ is omitted in the future.
-Thus, solving Equation \ref{eq:lin_momentum_indi_outer} for $\bm{\dot{v}}$ and assuming that the sum of all forces acting on the quadrotor consists only of gravitational, propulsive and aerodynamic forces, following equation is obtained
+Thus, solving Equation \ref{eq:lin_momentum_indi_outer} for $\bm{\dot{v}}$ and assuming that the sum of all forces acting on the quadrotor consists only of gravitational, propulsive and aerodynamic forces, the following equation is obtained
 \begin{equation}
@@
 The propulsive force $(\bm{F}_P)_O$ (produced by the rotors) has only one nonzero component if defined in the body-fixed frame.
-To transform it to the \acrshort{NED} frame the rotation matrix $\bm{M}_{OB}$ is used.
-This results in
-\begin{equation}
-	\begin{split}
-		(\bm{F}_P)_O = \bm{M}_{OB}
+To transform it from the body-fixed to the \acrshort{NED} frame the rotation matrix $\bm{M}_{OB}$ is used.
+Here, the transformation from the $B$-frame to the $O$-frame is defined by the following rotation sequence: $\Phi$, $\Theta$, $\Psi$.
+Depending on the  rotation sequence, a different orientation coordinate causes gimbal lock.
+The introduced rotation sequence is suitable for horizontally oriented aircrafts as the gimbal lock is caused for $\Theta = \pm\ang{90}$.
+This results in the following expression for the propulsive force
+\begin{equation}
+	\begin{split}
+		(\bm{F}_P)_O &= \bm{M}_{OB}
 		\begin{bmatrix}
@@
 			-T
-		\end{bmatrix}_B = 
-		\begin{bmatrix}
-			* & * & c\Psi s\Theta c\Phi + s\Psi s\Phi\\
-			* & * & s\Psi s\Theta c\Phi + c\Psi s\Phi\\
-			* & * & c\Theta c\Phi
+		\end{bmatrix}_B \\ 
+		&= 
+		\begin{bmatrix}
+			c\Theta c\Psi & c\Psi s\Theta s\Phi - s\Psi c\Phi & c\Psi s\Theta c\Phi + s\Psi s\Phi\\
+			c\Theta s\Psi & s\Psi s\Theta s\Phi + c\Psi c\Phi & s\Psi s\Theta c\Phi - c\Psi s\Phi\\
+			-s\Theta & c\Theta s\Phi & c\Theta c\Phi
 		\end{bmatrix}
@@
 			-T
-		\end{bmatrix}_B = 
+		\end{bmatrix}_B \\
+		&= 
 		\begin{bmatrix}
 			(c\Psi s\Theta c\Phi + s\Psi s\Phi)(-T) \\
-			(s\Psi s\Theta c\Phi + c\Psi s\Phi)(-T) \\
+			(s\Psi s\Theta c\Phi - c\Psi s\Phi)(-T) \\
 			(c\Theta c\Phi)(-T)
@@
 \end{equation}
-To obtain the incremental form of the linear momentum equation, the same strategy as in the case of the inner loop derivation is applied: the Equation \ref{eq:lin_momentum_indi_outer_simple} is linearized using Taylor series expansion
+where $cx$ and $sx$ denote $\cos(x)$ and $\sin(x)$ respectively.
+
+To obtain the incremental form of the linear momentum equation, the same strategy as in the case of the inner loop derivation is applied: the Equation \ref{eq:lin_momentum_indi_outer_simple} is linearized using Taylor series expansion and neglecting higher order terms
 \begin{equation}
@@
 \end{equation}
-The first term on the right side of the Equation \ref{eq:main_eom_indi_outer_taylor} is the acceleration at previous time step $\bm{\dot{v}}_0$.
+The first term on the right side of the Equation \ref{eq:main_eom_indi_outer_taylor} is the acceleration at the previous time step $\bm{\dot{v}}_0$.
 It can be obtained from the onboard accelerometer and then tranformed to the \acrshort{NED} frame.
-The next two terms on the right are assumed to be zero since it is very complicated to develop an accurate model of the aerodynamic force as the nature of the wind influence can vary and remains unknown.
-It is also assumed that the change of the yaw angle $\Psi$ is small and can be neglected as well.
+The next two terms represent partial derivatives of the aerodynamic forces.
+Due to the absence of an accurate model of the aerodynamic effects, these terms are omitted and considered as disturbances.
+It is assumed that the change of the yaw angle $\Psi$ is small and can be neglected as well.
 By applying considered assumptions Equation \ref{eq:main_eom_indi_outer_taylor} is written as
@@
 		\bm{G}(\Phi_0, \Theta_0, \Psi_0, T_0) = 
-		\underbrace{
 		\begin{bmatrix}
@@
 			c\Theta_0 c\Phi_0
-		\end{bmatrix}}_\text{$\bm{G}(\Phi_0, \Theta_0, \Psi_0, T_0)$}
+		\end{bmatrix}
 		\label{eq:G}
@@
 The linear acceleration $\bm{\dot{v}}_0$ which is obtained from accelerometer measurements is usually noisy.
-Applying the same filter as in the case of the inner loop derivation, the Equation \ref{eq:lin_momentum_indi_outer_lin} is given by
+Applying the same filter $H(z)$ as in the case of the inner loop derivation, the Equation \ref{eq:lin_momentum_indi_outer_lin} is given by:
 \begin{equation}
@@
 \end{equation}
-Solving Equation \ref{eq:lin_momentum_indi_outer_lin_final} for $\bm{u}$ and substituting $\bm{\dot{v}}$ with the equivalent control variable $\bm{\nu}_{lin}$, the control law of the outer loop is obtained
-\begin{equation}
-	\begin{split}
-		\bm{u_c} = \bm{u} = \bm{u}_f +  m \bm{G}^{-1}(\Phi_0, \Theta_0, \Psi_0, T_0) (\bm{\nu}_{lin} - \bm{\dot{v}}_f)
+Solving Equation \ref{eq:lin_momentum_indi_outer_lin_final} for $\bm{u}$ and substituting $\bm{\dot{v}}$ with the virtual control variable $\bm{\nu}_{\bm{\dot{v}}}$, the control law of the outer loop is obtained
+\begin{equation}
+	\begin{split}
+		\bm{u_c} = \bm{u}_f +  m \bm{G}^{-1}(\Phi_0, \Theta_0, \Psi_0, T_0) (\bm{\nu}_{\bm{\dot{v}}} - \bm{\dot{v}}_f)
 		\label{eq:indi_outer_control_law}
@@
 Figure \ref{fig:indi_outer_croped} shows the block diagram of the outer loop \acrshort{INDI}.
+In Figure \ref{fig:indi_outer_croped} $\tilde{\Phi}$ and $\tilde{\Theta}$ are increments of the roll and pitch angles which are added to the current roll and pitch angle values and then passed to the inner loop as reference values.
+The increments are defined as
+\begin{subequations}
+	\begin{align}
+		\tilde{\Phi} &= \Phi_c - \Phi_f \label{eq:roll_increment} \\
+		\tilde{\Theta} &= \Theta_c - \Theta_f \label{eq:pitch_increment}
+	\end{align}
+	\label{eq:rool_pitch_increments}
+\end{subequations}
+
 \begin{figure}[H]
@@
 \end{figure}
-Using the same approach as with the inner loop, the outer loop which controls linear acceleration is augmented with two closed loops consisting of two gains (see Figure \ref{fig:pid_outer_croped}).
-These gains represent two controllers which control linear velocity and position.
+Using the same approach as with the inner loop, the outer loop which controls linear acceleration is augmented with two gains (see Figure \ref{fig:pid_outer_croped}).
+These gains represent two controllers which control linear velocity and position $\xi$.
 \begin{figure}[H]
@@
 
-The Crazyflie 2.1 quadrotor developed by Swedish company Bitcraze belongs to the nano-quadrotor class (see Figure \ref{fig:crazyflie_drone}).
-Its total weight ranges from 27g to 42g, which makes possible to extend the default hardware with a pair of additional extension decks of various functionality.
+With its arm length of approx.
+$4~\si{\mm}$, the Crazyflie 2.1 quadrotor developed by Swedish company Bitcraze belongs to the \acrfull{MAV} class (see Figure \ref{fig:crazyflie_drone}) \cite{petricca}.
+Its total weight is approx.
+$27~\si{g}$  with a capability to increase it up to $42~\si{g}$, which makes it possible to extend the default hardware with a pair of additional extension decks of various functionality.
 As it is an open source project, the main firmware, development tools and other software packages are freely available.
-This is one of the reasons why this small quadrotor gained a lot of popularity in different academia fields, being used for tasks reaching from the classical control theory all the way down to the obstacle avoidance problems.
+This is one of the reasons why this small quadrotor gained a lot of popularity in different academia fields, being used for tasks reaching from the classical control theory all the way down to the obstacle avoidance problems \cite{bitcraze-research}.
 
 The Crazyflie's main application \acrfull{MCU} is STM32F405.
-It runs the firmware with frequency of 1000 Hz and communicates with a large number of peripheral devices such as Bluetooth and long range radio, power management system \acrshort{MCU}, \acrfull{IMU} etc..
+It runs the firmware with frequency of $1000~\si{\Hz}$ and communicates with a large number of peripheral devices such as Bluetooth and long range radio, power management system \acrshort{MCU}, \acrfull{IMU} etc..
 The \acrfull{IMU} consists of the 3-axis accelerometer, the 3-axis gyroscope and the high precision pressure sensor.
@@
 The quadrotor used in this project was extended with a flow deck sensor.
-The flow deck itself is equipped with two sensors: the optical flow sensor which measures the visual motion and the \acrfull{ToF} sensor which measures the range to the next object along the body-fixed z-axis of the quadcopter.
+The flow deck itself is equipped with two sensors: the optical flow sensor which measures the visual motion and the \acrfull{ToF} laser-ranging sensor which measures the range to the next object along the body-fixed z-axis of the quadcopter.
 By employing these sensors, the flow deck can provide estimates of the current position and linear velocity of the aircraft.
@@
 		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
-		\includegraphics[width=0.4\textwidth]{figs/crazyflie_drone.jpg}};
+		\includegraphics[width=0.37\textwidth]{figs/crazyflie_drone.jpg}};
 	\end{tikzpicture}
@@
 It is based on dynamic equations of motion presented in Chapter \ref{sec:eqs_motion}.
-Similarly to the section \ref{subsec: indi_outer}, it was assumed that the sum of the forces in the linear momentum equation is composed of three components, namely gravitational, propulsive and aerodynamic.
+Similarly to section \ref{subsec: indi_outer}, it was assumed that the sum of the forces in the linear momentum equation is composed of three components, namely gravitational, propulsive and aerodynamic.
 The expressions of the gravity and propulsive forces have not been changed, so the Equations \ref{eq:Fg} and \ref{eq:Fp} were adopted for the simulation model.
@@
 where $k_F$ is the force constant of the rotors.
-In subsection \ref{subsec:parameter_estimation} it is shown how to estimate the thrust coefficient directly from the flight data.
-However, for the simulation model $k_F$ was approximated based on the assumption that the influence of the force constant of the rotors $k_F$ (considering the lever arm) is greater than the influence of the moment constant of the rotors $k_M$, and that the \textit{thrust to weight ratio} expression is $\frac{T}{W} \approx 2$.
-
-To account for aerodynamic effects such as drag the aerodynamic force was approximated with following expression 
+In subsection \ref{subsec:thrust_mapping} it is shown how to estimate the thrust coefficient directly from the flight data.
+However, for the simulation model $k_F$ was approximated based on the assumption that the influence of the force constant of the rotors $k_F$ (considering the lever arm) on the total moment is greater than the one of the moment constant of the rotors $k_M$, and that the \textit{thrust to weight ratio} expression is $\frac{T}{W} \approx 2$ (as the real Crazyflie quadrotor is able to hover at half throttle).
+
+To account for aerodynamic effects such as drag the aerodynamic force was approximated with the following expression 
 \begin{equation}
@@
 			-k_z (w_K)_B
-		\end{bmatrix}_B
+		\end{bmatrix}
 		\label{eq:Fa_simulink}
@@
 \end{equation}
-where $(u_K)_B$, $(v_K)_B$ and $(w_K)_B$ are kinematic velocities of the quadrotor along the axes $x_K$, $y_K$ and $z_K$ respectively, given in the body-fixed coordinate frame.
+where $(u_K)_B$, $(v_K)_B$ and $(w_K)_B$ are kinematic velocities of the quadrotor along the axes $x_B$, $y_B$ and $z_B$ respectively, given in the body-fixed coordinate frame.
 $k_x$, $k_y$ and $k_z$ are experimentally estimated drag coefficients adopted from \cite{foerster}.
@@
 The angular momentum equation used in the simulation model has the same form as defined in Equation \ref{eq:ang_momentum}.
-The numerical values of the inertia tensor $(\bm{I}^G)_B$ were estimated using pendulum method in \cite{foerster}.
+The numerical values of the inertia tensor $(\bm{I}^G)_B$ were estimated using the pendulum method in \cite{foerster}.
 The total external moment acting on the Crazyflie contains only the propulsive moment $\bm{M}_P$ as it is defined in \ref{subsec: indi_inner}.
@@
 with $\alpha = 1-e^{\frac{-T_S}{T}}$ and sample time $T_S$.
-The default frequency with which the Crazyflie controller updates its state is 500 Hz.
+The default frequency with which the Crazyflie controller updates its state is $500~\si{\Hz}$.
 Thus, sampling time $T_S$ was set to the reciprocal value of the default frequency.
@@
 To perform this transformation \textit{bilinear transformation} (also called \textit{Tustin-Transformation}) was used.
-Using bilinear transformation, the mapping relation between $s$ and $z$ results in
-\begin{equation}
-	\begin{split}
-		s \ \widehat{=} \ \frac{2}{T_s} \frac{1-z^{-1}}{1+z^{-1}}
+Using the bilinear transformation (with frequency warping technique), the mapping relation between $s$ and $z$ results in
+\begin{equation}
+	\begin{split}
+		s \ \widehat{=} \ \frac{\omega_n}{\tan(\omega_n\frac{T_S}{2})} \frac{1-z^{-1}}{1+z^{-1}}
 		\label{eq:filter_c}
@@
 \end{equation}
-Thus, the discrete version of the Equation \ref{eq:filter_c} is 
+Thus, the discrete version of the Equation \ref{eq:filter_c} is:
 \begin{equation}
@@
 	\begin{align}
-		n_0 &= \omega_n^2 \\
-		n_1 &= 2\omega_n^2 \\
-		n_2 &= \omega_n^2 \\
-		d_0 &= \bigg[(\frac{2}{T_S})^2 + \frac{4\zeta \omega_n}{T_S} + \omega_n^2\bigg] \\
-		d_1 &= \bigg[\frac{8}{T_S^2} + 2\omega_n^2\bigg] \\
-		d_2 &= \bigg[(\frac{2}{T_S})^2 - \frac{4\zeta \omega_n}{T_S} + \omega_n^2\bigg]
+		n_0 &= 1 \\
+		n_1 &= 2\\
+		n_2 &= 1 \\
+		d_0 &= \frac{1}{\tan^2(\omega_n\frac{T_S}{2})} + \frac{2\zeta}{\tan(\omega_n\frac{T_S}{2})} + 1 \\
+		d_1 &= -\frac{2}{\tan^2(\omega_n\frac{T_S}{2})} + \frac{4\zeta}{\tan(\omega_n\frac{T_S}{2})} \\
+		d_2 &= \frac{1}{\tan^2(\omega_n\frac{T_S}{2})} - \frac{2\zeta}{\tan(\omega_n\frac{T_S}{2})} + 1
 	\end{align}
@@
 
-\begin{figure}[h]
+The input of the inner loop is the attitude, which is computed and provided by the outer loop.
+Figure \ref{fig:sim_inner_all} shows the response of inner loop (for the same position step sequence as above) which controls the attitude, the angular velocity and the angular acceleration of the quadrotor.
+
+As mentioned in the beginning of this chapter, a simulation can be used to determine terms of the model which have a greater influence on the overall controller performance.
+Matrix $G_2$ of the control effectiveness term in Equation \ref{eq:indi_inner_control_law} contains only the term of the inertia tensor of the propeller $I_{rzz}$.
+Since $I_{rzz}$ is small, it was expected that $G_2$ will not have a big impact on the model response.
+Figure \ref{fig:g2_comp} confirms this expectation, by plotting the step response of the Crazyflie model with and without considering  the gyroscopic effects of the quadrotor propellers.
+\begin{figure}[H]
 	\centering 
@@
 		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
-		\includegraphics[width=1\textwidth]{figs/sim_outer_all.pdf}};
+		\includegraphics[width=0.85\textwidth]{figs/sim_outer_all.pdf}};
 	\end{tikzpicture}
@@
 	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-	\caption[Response of the outer loop model to a step input.]{Response of the outer loop model to a step input. Blue lines represent reference values, red lines denote measured values.}
+	\caption[Response of the outer loop simulation model to a step input.]{Response of the outer loop simulation model to a step input.
+Blue lines represent reference values, red lines denote measured values.}
 	\label{fig:sim_outer_all}
 \end{figure}
-
-The input of the inner loop is the attitude, which is computed and provided by the outer loop.
-Figure \ref{fig:sim_inner_all} shows the response of inner loop (for the same position step sequence as above) which controls the attitude, the angular velocity and the angular acceleration of the quadrotor.
-
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering 
@@
 		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
-		\includegraphics[width=1\textwidth]{figs/sim_inner_all.pdf}};
+		\includegraphics[width=0.85\textwidth]{figs/sim_inner_all.pdf}};
 	\end{tikzpicture}
@@
 	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-	\caption[Response of the inner loop model to the input provided by the outer loop]{Response of the inner loop model to the input provided by the outer loop.
+	\caption[Response of the inner loop simulation model to the input provided by the outer loop]{Response of the inner loop simulation model to the input provided by the outer loop.
 Blue lines represent reference values, red lines denote measured values.}
 	\label{fig:sim_inner_all}
-\end{figure}
-
-As mentioned in the beginning of this chapter, a simulation can be used to determine terms of the model which have a greater influence on the overall controller performance.
-Matrix $G_2$ of the control effectiveness term in Equation \ref{eq:indi_inner_control_law} contains only the term of the inertia tensor of the propeller $I_{rzz}$.
-Since $I_{rzz}$ is small, it was expected that $G_2$ will not have a big impact on the model response.
-Figure \ref{fig:g2_comparison} confirms this expectation, by plotting the step response of the Crazyflie model with and without considering  the gyroscopic effects of the quadrotor propellers.
-It can be seen that both responses are almost similar.
+\end{figure}It can be seen that both responses are almost the same.
 In the next section, (see \ref{subsec:parameter_estimation_inner}) through the estimation of the control effectiveness terms using the flight data, this observation will be practically confirmed.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering 
@@
 	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-	\caption[Responses of the closed loop with and without gyroscopic effects.]{Responses of the closed loop using dynamics model with and without considering the gyroscopic effects of the propellers.}
-	\label{fig:g2_comparison}
+	\caption[Responses of the closed loop system with and without gyroscopic effects.]{Responses of the closed loop system using simulation of the Crazyflie's dynamics with and without considering the gyroscopic effects of the propellers.}
+	\label{fig:g2_comp}
 \end{figure}
@@
 
-To ensure proper functioning of the inner loop, some of the implementation errors were corrected.
+To ensure proper functioning of the inner loop, some of the errors in the already existing implementation 1were corrected.
 Additionally, the control effectiveness parameters $\bm{G_1}$ and $\bm{G_2}$ were reestimated with a new flight data.
-
-To estimate model parameters of a quadrotor two strategies can be applied: estimation through measurements and estimation with flight data.
-Using the first strategy it is usually difficult to achieve accurate results \cite{Smeur2}.
-By contrast, pursuing the second approach can reduce the amount of effort and also lead to plausible results.
-To collect the flight data, the only requirement is that the quadrotor has a functioning controller (e.g.
+For the matrix $\bm{G_1}$ it was assumed that it does not change over the operational domain and can be considered as static.
+
+To estimate model parameters of a quadrotor two strategies can be applied: estimation through measurements of each parameter that is part of the control effectiveness terms and estimation with flight data.
+Using the first strategy, requires additional measuring equipment to achieve accurate results.
+By contrast, having access only to \acrshort{IMU} data and pursuing the second approach, can reduce the amount of effort and also lead to plausible results \cite{hamel}.
+To collect the flight data (gyroscope measurements $\bm{\omega}$ and actuator inputs $\bm{\Omega}$), the only requirement is that the quadrotor has a functioning controller (e.g.
 PID controller) to perform flights.
@@
 \begin{equation}
-	\bm{\Delta\dot{\omega}} = 
+	\bm{\dot{\omega}}_f = 
 	\begin{bmatrix}
@@
 	\begin{bmatrix}
-		\bm{\Delta\Omega}\\
-		\bm{\Delta\dot{\Omega}}
+		\bm{\Omega}_{f,a}\\
+		\bm{\dot{\Omega}}_{f,a}
 	\end{bmatrix} 	
@@
 \end{equation}
-where $\bm{\Delta\dot{\omega}} = \bm{\dot{\omega}} - \bm{\dot{\omega}}_f$ and $\bm{\Delta\dot{\Omega}} = \bm{\dot{\Omega}} - \bm{\dot{\Omega}}_f$.
-Note that the terms $\bm{\Delta\Omega}$ and $\bm{\Delta\dot{\Omega}}$ have to be passed through the actuator dynamics $A(s)$.
+Note that the terms $\bm{\Omega}_{f,a}$ and $\bm{\dot{\Omega}}_{f,a}$ are passed through the actuator dynamics $A(s)$ (subscript ``a'').
 Furthermore, the Equation \ref{eq:inner_indi_estimation} is differentiated to amplify high frequencies of the signal for a better parameter estimation performance.
@@
 \begin{equation}
-	\bm{\Delta\ddot{\omega}} = 
+	\bm{\ddot{\omega}}_f = 
 	\begin{bmatrix}
@@
 	\begin{bmatrix}
-		\bm{\Delta\dot{\Omega}}\\
-		\bm{\Delta\ddot{\Omega}}
+		\bm{\dot{\Omega}}_{f,a}\\
+		\bm{\ddot{\Omega}}_{f,a}
 	\end{bmatrix} 	
@@
 		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
-		\includegraphics[width=1\textwidth]{figs/g_contribution.pdf}};
+		\includegraphics[width=0.83\textwidth]{figs/g_contribution.pdf}};
 	\end{tikzpicture}
@@
 	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-	\caption[Contribution of control effectiveness terms to the angular acceleration]{Contribution of the estimated $\bm{G_1}$ and $\bm{G_2}$ terms to the yaw component of the angular acceleration.}
+	\caption[Contribution of control effectiveness terms to the angular acceleration]{Contribution of the estimated $\bm{G_1}$ and $\bm{G_2}$ terms to the yaw component of the angular acceleration.
+$\omega_z$ and $\Omega_z$ are obtained from the flight data.}
 	\label{fig:g2_comparison}
@@
 
-The \acrshort{INDI} controller derived in Chapter \ref{cha:theoretical_background} controls Crazyflie by adding increments to the current angular rates of the rotors.
+The \acrshort{INDI} controller derived in Chapter \ref{cha:theoretical_background} controls the Crazyflie quadrotor by adding increments of the propeller rates to the current propeller rates.
 Unfortunately, the hardware of the quadrotor does not support the measurement of the propeller rates.
-Thus, to be able to feedback the propeller rates they are passed through the actuator dynamics model $A'(s)$ (see \ref{subsec:actuator_dynamics}).
+Thus, to be able to feedback the propeller rates they are passed through the actuator dynamics model.
 The feedback of the propeller rates is then obtained as shown in Figure \ref{fig:actuator}.
-
-\begin{figure}[h]
+Here, $A(z)$ is the real and unknown actuator dynamics and $A'(z)$ is the model of the actuator dynamics approximated with a first order lag element (as shown in \ref{subsec:actuator_dynamics}).
+
+\begin{figure}[H]
 	\centering 
@@
 	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-	\caption[Estimation of the actuator state in case of the missing actuator feedback]{Estimation of the actuator state in case of the missing actuator feedback}
+	\caption[Estimation of the actuator state in case of the missing actuator feedback]{Estimation of the actuator state in case of the missing actuator feedback.}
 	\label{fig:actuator}
@@
 
-If the transfer function of the actuator $A'(s)$ is assumed to be of the first order, the only unknown parameter is the time constant $T$ (since it is assumed that the commanded propeller rates are not amplified by the actuator, the gain $k$ is simply $1$).
+If the transfer function of the actuator $A'(z)$ is assumed to be of the first order, the only unknown parameter is the time constant $T$ (since it is assumed that the commanded propeller rates are not amplified by the actuator, the gain $k$ is simply $1$).
 To estimate the time constant $T$, propeller rates were measured for different step inputs.
@@
 Here, the red curve was fitted to the measured data (blue line).
-In the figure the signal contains $n=155$ samples recorded with a frequency of 200 Hz.
+In the figure the signal contains $n=155$ samples recorded with a frequency of $200~\si{\Hz}$.
 The estimated value for the time constant is $T = 0.061658 \ s$.
+
+A simpler alternative to estimate the time constant would be reading off the time point at which the response reaches $63.2 \%$ of its final value.
+Using this approach, the value of the time constant is approximately $0.0675~\si{\second}$, which is very close to the value estimated through solving the optimization problem.
 
@@
 		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
-		\includegraphics[width=0.8\textwidth]{figs/actuator_dynamics_est.pdf}};
+		\includegraphics[width=0.8\textwidth]{figs/actuator_dynamic_est.pdf}};
 	\end{tikzpicture}
@@
 	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-	\caption[]{}
+	\caption[Fitting first order lag element to propeller rates measurement]{Blue line represents propeller rates obtained from a measurement.
+Red line is then fitted to the measured propeller rates to minimize squared error between corresponding red and blue data points.
+}
 	\label{fig:actuator_dynamics_est}
@@
 
-A simpler alternative to estimate the time constant would be reading off the time point at which the response reaches $63.2 \%$ of its final value.
-Using this approach, the value of the time constant is approximately $0.0675 \ s$, which is very close to the value estimated through solving the optimization problem.
-
 \subsection{Estimation of the Thrust Mappint} \label{subsec:thrust_mapping}
@@
 The thrust increments provided by the outer loop \acrshort{INDI} are values in  Newton.
-Later, in the inner loop \acrshort{INDI} commanded thrust values are computed by adding thrust increments to the current thrust values and passed to the motor mixing algorithm.
-Depending on the commanded roll, pitch and yaw values, the motor mixing algorithm computes values for each rotor and sends these commands to the motor.
-Unfortunately, the values which are sent to the motor are not in the same units as thrust.
-These are defined in a specific range (e.g unsigned integer value of 32 bits has a valid number range between 0 and 65535).
-Mapping a thrust value in physical units to a motor command value is called \textit{thrust mapping}.
-
-- Actuator Dynamics (Estimation of the time constant), plot response with estimated constant\\
-- Thrust dynamics estimation (control allocation)\\
-- Estimation of the control effectiveness parameters G1, G2 for inner INDI (describe performed flight to log data), plot the curve with contribution of G1, G2 to the fitting\\
-- PD gain tuning for inner INDI (using pd\_inner\_cs(), show plots with different D-gains (e.g 25, 10 and 3) to see different damping behaviour), Before explaining gain tuning present all relevant transfer functions of the closed and open loops\\
-- Outer loop (show new diagram of the controller)
-
-\subsection{Structure of the Code} \label{subsec:structure_ofthe_code}
-
-- Moore-Penrose instead of the inverse
+Later, in the inner loop \acrshort{INDI}, commanded thrust values are computed by adding thrust increments to the current thrust values, the result is then passed to the motor mixing algorithm.
+Depending on the commanded roll, pitch and yaw values, the motor mixing algorithm computes values for each rotor and sends these commands to each motor.
+Unfortunately, the values which are sent to the motors are not in the same units as the thrust.
+These values are defined in a specific range (e.g Crazyflie's motors accept integer numbers from $0$ to $60000$).
+Mapping a thrust value in physical units to a motor command value is called \textit{thrust mapping} \cite{faessler}.
+
+It was assumed that the relation between the physical thrust value $T$ and the thrust value represented in motor units $T_{cmd}$ is linear. Thus, this relation can be defined as
+\begin{equation}
+	T = T_{cmd} K_{cmd}
+	\label{eq:thrust_mapping}
+\end{equation}
+with $K_{cmd}$ being the \textit{thrust mapping parameter}.
+This parameter can be estimated similarly to the control effectiveness parameters from the previous section, by using the flight data of a vertical flight.
+
+Third component of the Equation \ref{eq:indi_outer_control_law} serves as a basis for the estimation of the mapping parameter $K_{cmd}$.
+If a vertical flight is assumed, the angle states $\Phi$ and $\Theta$ have to be zero, which leads to the vanishing of the terms with $x$- and $y$-component of the linear acceleration $\bm{\dot{v}}$.
+Furthermore, instead of the thrust $T_0$ in the $G$ matrix, specific thrust $\frac{T_0}{m}$ is used.
+This transformation will simplify the expression for the thrust increment $\tilde{T}$, by eliminating the mass $m$ from it.
+With the above assumptions Equation \ref{eq:indi_outer_control_law}  simplifies to
+\begin{equation}
+	\tilde{T} = \dot{v}_{err,z}
+	\label{eq:t_tilde_est}
+\end{equation}
+where $\dot{v}_{err,z}$ is the $z$-component of the linear acceleration error $\dot{v}_{err}$.
+
+Replacing thrust with a thrust increment in Equation \ref{eq:thrust_mapping} and inserting it into Equation \ref{eq:t_tilde_est}, results in
+\begin{equation}
+	\tilde{T}_{cmd} = \dot{v}_{err,z} K_{cmd}^{-1}
+	\label{eq:t_tilde_est_cmd}
+\end{equation}
+
+By making use of the finite difference approximation, Equation \ref{eq:t_tilde_est_cmd} can be rewritten as
+\begin{equation}
+	\dot{T}_{cmd} = \ddot{v}_{z} K_{cmd}^{-1}
+	\label{eq:t_tilde_est_cmd_diff}
+\end{equation}
+where $T_{cmd}$ is the commanded thrust, and $\dot{v}_{z}$ the linear acceleration along the $z$-axis.
+Both values can be obtained from the flight data.
+Similarly to subsection \ref{subsec:parameter_estimation_inner}, differentiating will amplify high-frequency portion of the signal and contribute to the elimination of the bias.
+Note that to obtain realistic course of the commanded thrust values, just before the differentiation, these values have to be passed through the actuator dynamics model $A'(s)$.
+Equation \ref{eq:t_tilde_est_cmd_diff} has then the following form
+\begin{equation}
+	\dot{T}_{cmd, a} = \ddot{v}_{z} K_{cmd}^{-1}
+	\label{eq:t_tilde_est_cmd_diff_actuator}
+\end{equation}
+where $T_{cmd, a}$ is the thrust value filtered with the actuator dynamics model. The least squares approach is then be applied to obtain $K_{cmd}$.
+
+Figure \ref{fig:thrust_mapping} shows the results of the thrust mapping parameter estimation.
+The first subplot contains the courses of the quantities from Equation \ref{eq:t_tilde_est_cmd_diff_actuator}.
+The second subplot shows that the course of the mapped commanded thrust $T_{cmd, a} \cdot K_{cmd}$ matches the course of the linear acceleration $\dot{v}_{z}$ for the estimated parameter $K_{cmd}$.
+
+\begin{figure}[h]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=1\textwidth]{figs/thrust_mapping.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Estimation of the thrust mapping parameter]{First subplot shows the matching between the derivative of the linear acceleration $\ddot{v}_{z}$ and the mapped derivative of the commanded thrust $\dot{T}_{cmd, a}$.
+Second subplot shows the matching between the linear acceleration $\dot{v}_{z}$ and the mapped commanded thrust $\dot{T}_{cmd, a}$.
+Mapping was achieved through the estimation of the mapping parameter $K_{cmd}$.
+$T_{cmd, a}$ and $\dot{v}_{z}$ are values obtained from the flight data.}
+	\label{fig:thrust_mapping}
+\end{figure}
+
+%- Actuator Dynamics (Estimation of the time constant), plot response with estimated constant\\
+%- Thrust dynamics estimation (control allocation)\\
+%- Estimation of the control effectiveness parameters G1, G2 for inner INDI (describe performed flight to log data), plot the curve with contribution of G1, G2 to the fitting\\
+%- PD gain tuning for inner INDI (using pd\_inner\_cs(), show plots with different D-gains (e.g 25, 10 and 3) to see different damping behaviour), Before explaining gain tuning present all relevant transfer functions of the closed and open loops\\
+%- Outer loop (show new diagram of the controller)
+
+\subsection{Implementation of the Outer Loop on the Crazyflie's Hardware} \label{subsec:outer_hardware_implementation}
+
+This subsection provides several worth notes regarding the implementation of the outer loop on the real quadrotor.
+As the already existing implementation of the inner loop on the quadrotor was not including thrust increments as control inputs, the interface between the outer and the inner loops had to be adjusted.
+Thus, at the place, where thrust increments $\tilde{T}$ are passed to the inner loop, a complete thrust value $T_c$ (``c'' stands for ``commanded'') has to be provided.
+
+To obtain $T_c$, current thrust value $T_0$ is filtered with a second order filter $F(z)$ ($\omega_n=8~\si{\radian/\second}$, $\zeta=0.707$) and passed through the model of the actuator dynamics $A'(z)$.
+The result is then added to the thrust increment $\tilde{T}$, provided by the outer loop \acrshort{INDI}.
+This computation is graphically shown in Figure \ref{fig:outer_loop_hw}.
+The part of the outer loop which is different from the one used in the Simulink model (see Figure \ref{fig:indi_outer_croped}) is presented in blue color.
+
+\begin{figure}[h]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=1\textwidth]{figs/indi_outer_mod_croped.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Block diagram of the outer loop with adjustments]{Block diagram of the outer loop from \ref{subsec: indi_outer} with adjustments (blue) to account for the inner loop implementation with no thrust increment as input.}
+	\label{fig:outer_loop_hw}
+\end{figure}
+
+An additional aspect of the hardware implementation, which is worth to mention is the computation of the inverse of the $\bm{G}(\Phi_0, \Theta_0, \Psi_0, T_0)$ matrix.
+As the $\bm{G}(\Phi_0, \Theta_0, \Psi_0, T_0)$ is a square matrix, its inverse can be computed with a regular formula for the inverse of a $3 \times 3$ matrix.
+However, to account to possible numerical errors and vanishing of matrix terms with very small values, the inverse was implemented as a pseudoinverse (\textit{Moore-Penrose Inverse}).
 
 \chapter{Results} \label{cha:results}
+
+This chapter describes the performance of the implemented outer loop.
+In section \ref{sec:disturbance_rejection} the disturbance rejection is experimentally analysed.
+Section \ref{sec:pos_controller_response} presents the general response of the position controller for different step inputs.
 
@@
 
+\section{Disturbance Rejection} \label{sec:disturbance_rejection}
+
+This section describes the experiment performed to show the disturbance rejection ability of the \acrshort{INDI} controller implemented in the framework of this thesis.
+In \cite{Smeur1} was shown, that the transfer function of the inner loop \acrshort{INDI} can be simplified to the actuator dynamics $A(s)$.
+In this section, using this information and additional assumptions, the transfer function of the outer loop \acrshort{INDI} is derived and experimentally validated to analytically confirm the obtained results of the experiment.
+
+In the experiment, by disturbing the quadrotor flight with an additional weight, the linear acceleration  $\dot{v}_{z}$ along the vertical axis was examined.
+The decision to investigate the vertical motion is based on the fact that it will ease the derivation of the outer loop transfer behaviour.
+Figure \ref{fig:experiment_block_diag} shows the block diagram of the combined \acrshort{INDI}.
+
+\begin{figure}[H]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=1\textwidth]{figs/experiment_croped.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Block diagram of the combined \acrshort{INDI}]{Block diagram of the combined \acrshort{INDI}.}
+	\label{fig:experiment_block_diag}
+\end{figure}
+
+Here, $\bm{G}_{inner}$ and $\bm{G}_{outer}$ represent the quadrotor dynamics terms of the inner and outer loop respectively.
+If no roll and pitch motion ($\Phi=0$, $\Theta=0$) is assumed, the outer loop dynamics is simply $\bm{G}_{outer} = 1$.
+The term $d$ represents disturbance (here due to an additional weight $m_r g$).
+Thus, the disturbance is $d=\frac{m_r g}{m_{cf}}$.
+By introducing additional mass $m_r$ to the quadrotor system, the estimated terms of $\bm{G}_{inner}$ change and slightly deviate from those derived in \ref{subsec:parameter_estimation_inner}.
+Thus, to account for this change, the gain $K = \frac{m_{cf}}{m_{cf} + m_r}$ is introduced, where $m_{cf}$ is the mass of the Crazyflie quadrotor without additional mass.
+
+According to the block diagram in Figure \ref{fig:experiment_block_diag} the vertical acceleration $\dot{v}_{z}$ is then given by:
+
+\begin{equation}
+	\begin{split}
+	\dot{v}_{z} &= \frac{1-z^{-1}A(z)H(z)}{1+(K-z^{-1})A(z)H(z)}d + \frac{KA(z)}{1+(K-z^{-1})A(z)H(z)} \dot{v}_{z,ref} \\
+	&= P^{-1}[1-z^{-1}A(z)H(z)]d + P^{-1}KA(z)\dot{v}_{z,ref}
+	\label{eq:experiment_tf}
+	\end{split}
+\end{equation}
+
+The goal of the experiment was to show that the vertical acceleration of the Crazyflie $\dot{v}_{z,measured}$, measured by the accelerometer during the test flight, corresponds to the analytically computed term $\dot{v}_{z}$ from Equation \ref{eq:experiment_tf}, given the disturbance $d$ and the reference acceleration $\dot{v}_{z,ref}$.
+Ten experiments were performed, in which the quadrotor was disturbed during its flight with the additional mass $m_r=5\si{\g}$, applied to the center of gravity.
+Figure \ref{fig:experiment_plot} shows the result of this experiment for one of the performed repetitions.
+
+\begin{figure}[H]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=0.9\textwidth]{figs/disturbance_rej.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Response of the vertical acceleration of the outer loop \acrshort{INDI}]{Response of the vertical acceleration of the outer loop \acrshort{INDI} in an experimental flight with disturbance}
+	\label{fig:experiment_plot}
+\end{figure}
+
+In the figure above two cases can be distinguished: the moment in which the additional weight is applied and the moment when the weight is removed.
+The moment when the disturbance $d$ occurs is characterized by the large difference (yellow spike in positive direction) between the measured acceleration and the reference acceleration.
+Similarly, the moment when the weight is removed is characterized by the large spike in the negative direction.
+In both cases, after approx.
+half a second the measured acceleration $\dot{v}_{z,measured}$ tracks the expected acceleration $\dot{v}_{z}$.
+This result confirms that assumptions applied to derive the block diagram of the outer loop in Figure \ref{fig:experiment_block_diag} are plausible.
+It also shows that due to the presence of the disturbance, the expected acceleration $\dot{v}_{z}$ slightly deviates from the reference acceleration $\dot{v}_{z,ref}$ (as was analytically derived in Equation \ref{eq:experiment_tf}).
+From this experiment the ability of the \acrshort{INDI} controller to react to sudden disturbances becomes apparent.
+
+\section{Position Controller Response} \label{sec:pos_controller_response}
+
+As on the top level the control of the Crazyflie quadrotor (with the implemented outer loop) works by providing the reference position to the position controller, this section briefly shows the response of the position controller for different step inputs.
+The position and velocity controllers which augment the outer loop \acrshort{INDI} consist solely of proportional gains, which were manually tuned to achieve stable responses.
+
+Figure \ref{fig:results_responses} contains two subplots with responses of the position and velocity controllers respectively.
+In the first subplot the response to position steps in $x$-direction of different length is depicted.
+Second subplot shows the corresponding response of the velocity controller.
+
+\begin{figure}[H]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=0.9\textwidth]{figs/results_responses.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Responses of the position and velocity controllers obtained from a test flight]{Responses of the position controller (first subplot) and the velocity controller (second subplot) obtained from a test flight.}
+	\label{fig:results_responses}
+\end{figure}
+
 %- To make the controller work a minimal knowledge of the system dynymics is need.
@@
 \\
-%- Plain step responses of the outer loop \\
-%- Step responses with disturbance of the outer loop
 
 \chapter{Discussion} \label{cha:discussion}
+
+In this semester thesis, the \acrfull{INDI} control algorithm was discussed on the example of the Crazyflie quadrotor.
+In the first part, a simplified model of the Crazyflie quadrotor was developed in the Simulink environment.
+Both, the inner loop (attitude controller) and the outer loop (position controller) were then derived and subsequently simulated on this simplified model.
+In the second part, the outer loop was implemented on the Crazyflie hardware.
+To implement the algorithm, different parameters such as: actuator dynamics time constant, control effectiveness terms, etc.
+were estimated using the flight data from test flights.
+Finally, the implemented outer loop was successfully tested on the ability to cope with disturbances.
+
+The \acrshort{INDI} approach has shown itself to be straightforward in the implementation, since the most parameters (e.g.
+control effectiveness, thrust mapping) can be estimated from the flight data using the onboard sensors and do not require complex methods based on experimental measurements.
+
+Another advantage of \acrshort{INDI}, is the ability to reject disturbances.
+Unmodelled dynamics and disturbances are measured with the angular (inner loop) and linear (outer loop) acceleration.
+This means, that in comparison to the \acrfull{NDI} method, there is no need in complex modelling for \acrshort{INDI}.
+
+These characteristics make \acrshort{INDI} a flexible and promissing control algorithm for Micro Air Vehicles (MAV).
 
@@
 \end{document}
-
-%\begin{equation}
-%	\begin{bmatrix}
-%		\dot{\bm{\omega}}\\
-%		T
-%	\end{bmatrix} = \bm{F}(\bm{\omega}) + \bm{G}(\bm{\omega}, \bm{\Omega}, \bm{\dot{\Omega}})
-%	\label{eq:TODO}
-%\end{equation}
-
-%\begin{subequations}
-%	\begin{align}
-%		n_0 &= \omega_n^2 \\
-%		n_1 &= 2\omega_n^2 \\
-%		n_2 &= \omega_n^2 \\
-%		d_0 &= \bigg[(\frac{2}{T_S})^2 + \frac{4\zeta \omega_n}{T_S} + \omega_n^2\bigg] \\
-%		d_1 &= \bigg[\frac{8}{T_S^2} + 2\omega_n^2\bigg] \\
-%		d_2 &= \bigg[(\frac{2}{T_S})^2 - \frac{4\zeta \omega_n}{T_S} + \omega_n^2\bigg]
-%	\end{align}
-%	\label{eq:filter_parameters}
-%\end{subequations}

### 2020-03-27 code/Simulink/Crazyflie_Simulation_paper/CHANGE_set_params_paper.m

@@ -1,0 +1,106 @@
+clc 
+clear 
+close all
+
+%%
+% Force and Moment Notation:
+% 'FX_Y' or 'MX_Y' with: 
+% - X: Force nature (e.g gravitational (G), aerodynamical (A), propulsive (P) etc)
+% - Y Coordinate frame (e.g Body-Fixed (B), NED (O) etc)
+
+
+%% Dynamics
+
+% Crazyflie
+g = 9.81;           % gravitational acceleration in [m/s^2]
+m_CF = 0.028;       % mass of the Crazyflie quadrotor in [kg]
+l = 0.033;          % lever arm to the rotor in x-direction [m]
+b = 0.033;          % lever arm to the rotor in y-direction [m]
+I_rzz = 9.3e-9;     % Component of moment of inertia of the rotor [kg*m^2]
+
+
+I_CF_1 = [16.823890  -1.224320  -0.716891    % Moment of inertia of the 
+          -1.224320   16.885278  2.083147    % Crazyflie quadrotor in [kg*m^2]
+          -0.716891   2.083147   29.808912] * 10e-6;       
+% I_CF_1 = [16.823890     0          0       % Moment of inertia of the 
+%              0      16.885278      0       % Crazyflie quadrotor in [kg*m^2]
+%              0          0       29.808912] * 10e-6; 
+
+I_CF_1_inv = inv(I_CF_1);                 % Inverted I_CF_1
+
+% Propulsive force
+k_f = 1.6e-4;       % motor constant for F_P and M_P[N/(rad/s)]
+k_m = 1e-6;         % motor constant for M_P [N*m/(rad/s)]
+% k_f = 1.25e-7;
+% k_m = 4.12e-9;
+% k_f = 4.53e-7;
+% k_m = 1.49e-9;
+
+
+% Aerodynanic force
+kx = 10.25e-4;      % drag constant in x-direction [kg/s]
+ky = 10.25e-4;      % drag constant in y-direction [kg/s]
+kz = 7.553e-4;      % drag constant in z-direction [kg/s]
+
+% Actuator dynamics 
+T = 0.061658;                      % Actuator time constant [s]
[…]

### 2020-03-27 code/Simulink/Crazyflie_Simulation_paper/plot_responses_paper.m

@@ -29,126 +29,126 @@ t = out.tout;
 
 %% Plot response - outer loop - xi
 
-% Plotting
-fig_outer = figure('Name', 'Outer loop response xi');
-for i = 1:3
-    subplot(3, 1, i)
-    plot(t, xi_ref(i, :), 'LineWidth', 1);
-    hold on; grid on;
-    plot(t, xi(i, :), 'LineWidth', 1);
-    xlim([0 inf]);
-    if(i==1)
-        xlabel('Time $$[s]$$', 'Interpreter', 'latex');   
-        ylabel('$$x \ [m]$$', 'Interpreter', 'latex');
-    elseif (i==2)
-        xlabel('Time $$[s]$$', 'Interpreter', 'latex');   
-        ylabel('$$y \ [m]$$', 'Interpreter', 'latex');
-    else
-        xlabel('Time $$[s]$$', 'Interpreter', 'latex');   
-        ylabel('$$z \ [m]$$', 'Interpreter', 'latex');
-    end
-    legend('reference', 'state')
-end
-
-% Saving
-set(fig_outer, 'Units', 'points');
-pos = get(fig_outer, 'Position');                        % gives x left, y bottom, width, height
-width = pos(3);
-height = pos(4);
-set(fig_outer, 'PaperUnits', 'points');
-set(fig_outer, 'PaperPosition', [0 0 width height]);     % Position plot at left hand corner with width 5 and height 5.
-set(fig_outer, 'PaperSize', [width height]);             % Set the paper to have width 5 and height 5.
-saveas(fig_outer, 'plots/sim_outer', 'pdf');                       % Save figure
+% % Plotting
+% fig_outer = figure('Name', 'Outer loop response xi');
+% for i = 1:3
+%     subplot(3, 1, i)
+%     plot(t, xi_ref(i, :), 'LineWidth', 1);
+%     hold on; grid on;
+%     plot(t, xi(i, :), 'LineWidth', 1);
+%     xlim([0 inf]);
+%     if(i==1)
+%         xlabel('Time $$[s]$$', 'Interpreter', 'latex');   
+%         ylabel('$$x \ [m]$$', 'Interpreter', 'latex');
+%     elseif (i==2)
+%         xlabel('Time $$[s]$$', 'Interpreter', 'latex');   
[…]

### 2020-03-27 code/actuator_dynamics/actuator_dynamics.m

@@ -130,7 +130,7 @@ if (plot_est)
     plot(tdata, responsedata+log_4th(1));
     ylim([responsedata(1)+log_4th(1) 350])
     xlabel('Time [s]');
-    ylabel('Frequency [Hz]');
+    ylabel('Rotation frequency [Hz]');
     legend('Measured', 'Fitted', 'Location', 'best');
 end
 

### 2020-03-27 code/experiments/disturbance_rejection/import_data.m

@@ -1,0 +1,48 @@
+function [timestamp, az_reference, az_computed, az_measured] = importfile(filename, dataLines)
+%IMPORTFILE Import data from a text file
+%  [TIMESTAMP, AZ_REFERENCE, AZ_COMPUTED, AZ_MEASURED] =
+%  IMPORTFILE(FILENAME) reads data from text file FILENAME for the
+%  default selection.  Returns the data as column vectors.
+%
+%  [TIMESTAMP, AZ_REFERENCE, AZ_COMPUTED, AZ_MEASURED] =
+%  IMPORTFILE(FILE, DATALINES) reads data for the specified row
+%  interval(s) of text file FILENAME. Specify DATALINES as a positive
+%  scalar integer or a N-by-2 array of positive scalar integers for
+%  dis-contiguous row intervals.
+%
+%  Example:
+%  [Timestamp, az_reference, az_computed, az_measured] = importfile("/home/evgheniivolodscoi/LRZ Sync+Share/TUM/Master_AS_RCI/Semester_3/Semesterarbeit/code/experiments/data/exp_1_acc.csv", [2, Inf]);
+%
+%  See also READTABLE.
+%
+% Auto-generated by MATLAB on 23-Mar-2020 22:36:42
+
+%% Input handling
+
+% If dataLines is not specified, define defaults
+if nargin < 2
+    dataLines = [2, Inf];
+end
+
+%% Setup the Import Options
+opts = delimitedTextImportOptions("NumVariables", 4);
+
+% Specify range and delimiter
+opts.DataLines = dataLines;
+opts.Delimiter = ",";
+
+% Specify column names and types
+opts.VariableNames = ["Timestamp", "az_reference", "az_computed", "az_measured"];
+opts.VariableTypes = ["double", "double", "double", "double"];
+opts.ExtraColumnsRule = "ignore";
+opts.EmptyLineRule = "read";
+
+% Import the data
+tbl = readtable(filename, opts);
+
+%% Convert to output type
+timestamp = tbl.Timestamp;
+az_reference = tbl.az_reference;
+az_computed = tbl.az_computed;
+az_measured = tbl.az_measured;
+end

### 2020-03-27 code/experiments/pos_vel_reponses/importfile.m

@@ -1,0 +1,48 @@
+function [timestamp, posRef_x, posS_x, velRef_x, velS_x] = importfile(filename, dataLines)
+%IMPORTFILE Import data from a text file
+%  [TIMESTAMP, POSREF_X, POSS_X, VELREF_X, VELS_X] =
+%  IMPORTFILE(FILENAME) reads data from text file FILENAME for the
+%  default selection.  Returns the data as column vectors.
+%
+%  [TIMESTAMP, POSREF_X, POSS_X, VELREF_X, VELS_X] = IMPORTFILE(FILE,
+%  DATALINES) reads data for the specified row interval(s) of text file
+%  FILENAME. Specify DATALINES as a positive scalar integer or a N-by-2
+%  array of positive scalar integers for dis-contiguous row intervals.
+%
+%  Example:
+%  [timestamp, posRef_x, posS_x, velRef_x, velS_x] = importfile("/home/evgheniivolodscoi/LRZ Sync+Share/TUM/Master_AS_RCI/Semester_3/Semesterarbeit/code/experiments/pos_vel_reponses/exp_1_pos_vel.csv", [2, Inf]);
+%
+%  See also READTABLE.
+%
+% Auto-generated by MATLAB on 25-Mar-2020 00:13:26
+
+%% Input handling
+
+% If dataLines is not specified, define defaults
+if nargin < 2
+    dataLines = [2, Inf];
+end
+
+%% Setup the Import Options
+opts = delimitedTextImportOptions("NumVariables", 5);
+
+% Specify range and delimiter
+opts.DataLines = dataLines;
+opts.Delimiter = ",";
+
+% Specify column names and types
+opts.VariableNames = ["timestamp", "posRef_x", "posS_x", "velRef_x", "velS_x"];
+opts.VariableTypes = ["double", "double", "double", "double", "double"];
+opts.ExtraColumnsRule = "ignore";
+opts.EmptyLineRule = "read";
+
+% Import the data
+tbl = readtable(filename, opts);
+
+%% Convert to output type
+timestamp = tbl.timestamp;
+posRef_x = tbl.posRef_x;
+posS_x = tbl.posS_x;
+velRef_x = tbl.velRef_x;
+velS_x = tbl.velS_x;
+end

### 2020-03-27 code/experiments/pos_vel_reponses/pos_vel_responses.m

@@ -1,0 +1,58 @@
+clc
+clear
+close all
+
+
+%% Import data 
+
+filename = 'exp_1_pos_vel.csv';
+[timestamp, posRef_x, posS_x, velRef_x, velS_x] = importfile(filename);
+
+
+%% Prepare data 
+
+xs = 1000;
+xe = 2550;
+
+% TODO delete
+velS_x = circshift(velS_x, -15);
+
+posRef_x = posRef_x(xs:xe);
+posS_x = posS_x(xs:xe);
+velRef_x = velRef_x(xs:xe);
+velS_x = velS_x(xs:xe);
+timestamp = timestamp(xs:xe)/1000;
+
+
+%% Plot data 
+
+fig = figure('Name', 'Pos/Vel Responses');
+
+subplot(2, 1, 1);
+plot(timestamp, posRef_x); hold on; grid on;
+plot(timestamp, posS_x);
+xlim([-inf inf])
+xlabel('Time $$[s]$$', 'Interpreter', 'latex')
+ylabel('$$[m]$$', 'Interpreter', 'latex')
+legend('$$x_{ref}$$', '$$x$$', 'Interpreter', 'latex', 'Location', 'southeast')
+
+subplot(2, 1, 2);
+plot(timestamp, velRef_x); hold on; grid on;
+plot(timestamp, velS_x);
+xlim([-inf inf])
+xlabel('Time $$[s]$$', 'Interpreter', 'latex')
+ylabel('$$[m/s^2]$$', 'Interpreter', 'latex')
+legend('$$v_{x,ref}$$', '$$v_x$$', 'Interpreter', 'latex', 'Location', 'southeast')
+
+% Saving plots
+set(fig, 'Units', 'points');
+pos = get(fig, 'Position');                        % gives x left, y bottom, width, height
+width = pos(3);
+height = pos(4);
+set(fig, 'PaperUnits', 'points');
+set(fig, 'PaperPosition', [0 0 width height]);     % Position plot at left hand corner with width 5 and height 5.
+set(fig, 'PaperSize', [width height]);             % Set the paper to have width 5 and height 5.
+saveas(fig, 'results_responses', 'pdf');                       % Save figure
+
+
+

### 2020-03-27 code/param_est/param_est.m

@@ -96,7 +96,7 @@ plot([cmd_yaw_fd(min:max) cmd_yaw_fdd(min:max)]*G_yaw)
 xlim([-inf inf]);
 xlabel('Samples $$[-]$$', 'Interpreter', 'latex');
 %ylabel('$$ \Delta\ddot{\omega}_z \ [rad/s^3]$$', 'Interpreter', 'latex');
-legend('$$ \Delta\ddot{\omega}_z $$', '$$ \Delta\dot{\Omega}_z \cdot G_1 $$', '$$ \Delta\dot{\Omega}_z \cdot G_1 +  \Delta\ddot{\Omega}_z \cdot G_2 $$', 'Interpreter', 'latex')
+legend('$$ \ddot{\omega}_z $$', '$$ \dot{\Omega}_z \cdot G_1 $$', '$$ \dot{\Omega}_z \cdot G_1 +  \ddot{\Omega}_z \cdot G_2 $$', 'Interpreter', 'latex')
 
 % subplot(2, 1, 2)
 % plot(ang_accel_yaw_d(min:max)); hold on; grid on;

### 2020-03-27 code/param_est/thrust_est.m

@@ -42,29 +42,47 @@ K_cmd = d_cmd_thrust_a \ d_accelz
 
 %% Plotting
 
-% Specific force
-figure('Name', 'Specifc force');
-plot(accelz); hold on; grid on;
-xlim([0 inf])
+% % Specific force
+% fig1 = figure('Name', 'Specifc force');
+% plot(accelz); hold on; grid on;
+% xlim([0 inf])
 
-% Thrust command 
-figure('Name', 'Thrust cmd');
-plot(cmd_thrust); grid on; hold on;
-plot(cmd_thrust_a)
-legend('original', 'actuator')
-xlim([0 inf])
+% % Thrust command 
+% fig2 = figure('Name', 'Thrust cmd');
+% plot(cmd_thrust); grid on; hold on;
+% plot(cmd_thrust_a)
+% legend('original', 'actuator')
+% xlim([0 inf])
 
 % Results derivatives
-figure('Name', 'Results derivatives')
+fig3 = figure('Name', 'Results derivatives')
+subplot(2, 1, 1)
 plot(d_accelz); hold on;
 plot(d_cmd_thrust_a * K_cmd);
 xlim([0 inf]); grid on;
-legend('d\_accelz', 'd\_cmd*Kcmd')
+xlabel('Samples $$[-]$$', 'Interpreter', 'latex')
+ylabel('$$[m/s^3]$$', 'Interpreter', 'latex')
+legend('$$\ddot{v}_{z}$$', '$$ \dot{T}_{cmd, a} \cdot K_{cmd} $$', 'Interpreter', 'latex', 'Location', 'southeast');
 
 % Results original value
-figure('Name', 'Results original values')
+%fig4 = figure('Name', 'Results original values')
+subplot(2, 1, 2)
 plot(accelz); hold on;
 plot(cmd_thrust_a * K_cmd);
 xlim([0 inf]); grid on;
-legend('accelz', 'cmd*Kcmd')
+xlabel('Samples $$[-]$$', 'Interpreter', 'latex')
+ylabel('$$[m/s^2]$$', 'Interpreter', 'latex')
+legend('$$\dot{v}_{z}$$', '$$ T_{cmd, a} \cdot K_{cmd} $$', 'Interpreter', 'latex', 'Location', 'southeast');
+
+
+%% Saving plots
+set(fig3, 'Units', 'points');
+pos = get(fig3, 'Position');                        % gives x left, y bottom, width, height
+width = pos(3);
+height = pos(4);
+set(fig3, 'PaperUnits', 'points');
[…]

### 2020-03-27 code/transfer_functions/test.m

@@ -4,19 +4,21 @@ close all
 
 %% Set some variables 
 T = 1/15;                       % Actuator dynamics time constant [s]
-Ts = 0.01;                      % Sampling time [s]
+Ts = 1/500;                      % Sampling time [s]
+omega_n = 50;
+zeta = 0.55;
 
 %% Filter test
 
 %Check if manually transformed H(s) corresponds to the one computed with
 %matlab
 
-% s = tf('s');
-% z = tf('z', Ts);
-% 
-% H = omega_n^2/(s^2 + 2*zeta*omega_n*s + omega_n^2);
-% Hz = tf( (N_0/D_0*z^2 + N_1/D_0*z + N_2/D_0)/((z^2 + D_1/D_0*z + D_2/D_0)));
-% Hzm = c2d(H, Ts, 'tustin')
+s = tf('s');
+z = tf('z', Ts);
+
+H = omega_n^2/(s^2 + 2*zeta*omega_n*s + omega_n^2);
+%Hz = tf( (N_0/D_0*z^2 + N_1/D_0*z + N_2/D_0)/((z^2 + D_1/D_0*z + D_2/D_0)));
+Hzm = c2d(H, Ts, 'tustin')
 % 
 % step(H, Hz, Hzm)
 % legend('H', 'Hz', 'Hzm')

### 2020-03-29 temp/Paper_EV/Paper_EV.tex
backup update 28_03

--- 2020-03-27 Paper_EV/Paper_EV.tex
@@
 
-% Add List of Tables
-\renewcommand{\cfttabfont}{Table }				% Add "Figure" to the LOF
-\renewcommand\cfttabaftersnum{:} 				% Put ":" after the figure num 
-\setlength{\cfttabindent}{0pt}					% Remove left indent
-\setlength\cftbeforetabskip{-0.2cm}				% Space between tables
-\addtocontents{lot}{\vspace*{10pt}}			    % Set distance between LOT title and list
-\listoftables{}
-
-% Manually add Chapter names to the header (per default not included by Latex)
-\thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
-\chaptermark{List of Tables}
-
-%Insert empty page after the list of tables 
-\newpage\null\thispagestyle{empty}\newpage
+%% Add List of Tables
+%\renewcommand{\cfttabfont}{Table }				% Add "Figure" to the LOF
+%\renewcommand\cfttabaftersnum{:} 				% Put ":" after the figure num 
+%\setlength{\cfttabindent}{0pt}					% Remove left indent
+%\setlength\cftbeforetabskip{-0.2cm}				% Space between tables
+%\addtocontents{lot}{\vspace*{10pt}}			    % Set distance between LOT %title and list
+%\listoftables{}
+
+%% Manually add Chapter names to the header (per default not included by Latex)
+%\thispagestyle{fancy_beginning}
+%\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+%\chaptermark{List of Tables}
+
+%%Insert empty page after the list of tables 
+%\newpage\null\thispagestyle{empty}\newpage
 
@@
 \mbox{}
-\nomwithdim{B}{\( \bm{F} \)}{Force}{L}{$N$}
-\nomwithdim{B}{\( g \)}{Gravitational acceleration}{}{$m/s^2$}
-\nomwithdim{G}{\( \alpha \)}{Angle of attack}{}{$rad$}
-\nomwithdim{G}{\( \zeta \)}{Damping of a linear second order system}{}{--}
-\nomwithdim{S}{\( m \)}{Variable related to pitch moment}{}{}
-\nomwithdim{S}{\( W \)}{Wind}{}{}
+\nomwithdim{B, 001}{\( A(s),~A(z) \)}{Transfer function of the actuator dynamics}{}{--}
+\nomwithdim{B, 002}{\( A'(s),~A'(z) \)}{Transfer function of the actuator dynamics model}{}{--}
+\nomwithdim{B, 002}{\( a(t) \)}{Function of the first order lag element in time domain}{}{--}
+\nomwithdim{B, 005}{\( b \)}{Lever arm of the rotors to the C.G. along the body $y$-axis}{}{$m$}
+\nomwithdim{B, 010}{\( d \)}{Disturbance}{}{$m/s^2$}
+\nomwithdim{B, 010}{\( d_0, d_1, d_2 \)}{Denominator coefficients of the discrete second order filter}{}{--}
+\nomwithdim{B, 015}{\( E(t) \)}{Objective function}{}{$m$}
+\nomwithdim{B, 020}{\( \bm{F} \)}{Force vector}{}{$N$}
+\nomwithdim{B, 020}{\( \bm{F}_A \)}{Aerodynamic force vector}{}{$N$}
+\nomwithdim{B, 020}{\( \bm{F}_G \)}{Gravitational force vector}{}{$N$}
+\nomwithdim{B, 020}{\( \bm{F}_P \)}{Propulsive force vector}{}{$N$}
+\nomwithdim{B, 021}{\( \bm{f}(\bm{x}) \)}{Nonlinear vector field}{}{--}
+\nomwithdim{B, 025}{\( \bm{G} \)}{Control effectiveness matrix of the outer loop}{}{--}
+\nomwithdim{B, 025}{\( \bm{G}_1 \)}{Control effectiveness matrix of the inner loop}{}{--}
+\nomwithdim{B, 025}{\( \bm{G}_2 \)}{Control effectiveness matrix of the inner loop}{}{--}
+\nomwithdim{B, 025}{\( \bm{G}_{inner} \)}{Dynamics matrix of the inner loop}{}{--}
+\nomwithdim{B, 025}{\( \bm{G}_{outer} \)}{Dynamics matrix of the outer loop}{}{--}
+\nomwithdim{B, 025}{\( \bm{G}(x) \)}{Input matrix}{}{--}
+\nomwithdim{B, 025}{\( g \)}{Gravitational acceleration}{}{$m/s^2$}
+\nomwithdim{B, 030}{\( H(s),~H(z) \)}{Transfer function of the second order filter}{}{--}
+\nomwithdim{B, 031}{\( \bm{h}(\bm{x}) \)}{Nonlinear vector field}{}{--}
+\nomwithdim{B, 035}{\( \bm{I} \)}{Inertia tensor of the quadrotor}{}{$Nm^2$}
+\nomwithdim{B, 036}{\( \bm{I_{rzz}} \)}{$zz$-element of the inertia tensor of the rotor}{}{$Nm^2$}
+\nomwithdim{B, 036}{\( i \)}{Relative degree of the dynamic system}{}{--}
+\nomwithdim{B, 040}{\( K \)}{Compensation gain}{}{--}
+\nomwithdim{B, 040}{\( K_{cmd} \)}{Thrust mapping parameter}{}{--}
+\nomwithdim{B, 041}{\( k \)}{Drag coefficient}{}{$kg/s$}
+\nomwithdim{B, 041}{\( k \)}{Gain of the actuator dynamics}{}{--}
+\nomwithdim{B, 041}{\( k_F \)}{Force constant of the rotors}{}{$\frac{N}{rad/s}$}
+\nomwithdim{B, 041}{\( k_M \)}{Moment constant of the rotors}{}{$\frac{Nm}{rad/s}$}
+\nomwithdim{B, 045}{\( L \)}{Lie derivative operator}{}{--}
+\nomwithdim{B, 045}{\( l \)}{Lever arm of the rotors to the C.G. along the body $y$-axis}{}{$m$}
+\nomwithdim{B, 050}{\( \bm{M} \)}{Moment vector}{}{$Nm$}
+\nomwithdim{B, 050}{\( \bm{M}_A \)}{Aerodynamic moment vector}{}{$Nm$}
+\nomwithdim{B, 050}{\( \bm{M}_c \)}{Control moment vector}{}{$Nm$}
+\nomwithdim{B, 050}{\( \bm{M}_G \)}{Gravitational moment vector}{}{$Nm$}
+\nomwithdim{B, 050}{\( \bm{M}_{gyro} \)}{Moment vector due to the gyroscopic effects of the rotor}{}{$Nm$}
+\nomwithdim{B, 050}{\( \bm{M}_{OB} \)}{Transformation matrix from the body-fixed into NED frame}{}{--}
+\nomwithdim{B, 050}{\( \bm{M}_P \)}{Propulsion moment vector}{}{$Nm$}
+\nomwithdim{B, 052}{\( m \)}{Mass of the quadrotor}{}{$kg$}
+\nomwithdim{B, 052}{\( m_{cf} \)}{Mass of the Crazyflie quadrotor}{}{$kg$}
+\nomwithdim{B, 053}{\( m_r \)}{Additional mass (disturbance)}{}{$kg$}
+\nomwithdim{B, 055}{\( n \)}{Number of samples}{}{$m$}
+\nomwithdim{B, 055}{\( n_0, n_1, n_2 \)}{Numerator coefficients of the discrete second order filter}{}{--}
+\nomwithdim{B, 060}{\( P \)}{Parameter}{}{--}
+\nomwithdim{B, 060}{\( p \)}{Roll rate}{}{$rad/s$}
+\nomwithdim{B, 065}{\( q \)}{Pitch rate}{}{$rad/s$}
+\nomwithdim{B, 070}{\( r \)}{Yaw rate}{}{$rad/s$}
+\nomwithdim{B, 075}{\( s \)}{Laplace variable}{}{--}
+\nomwithdim{B, 080}{\( T \)}{Thrust}{}{$N$}
+\nomwithdim{B, 080}{\( T \)}{Time constant of the actuator dynamics}{}{$s$}
+\nomwithdim{B, 080}{\( T_{cmd} \)}{Thrust in motor units}{}{--}
+\nomwithdim{B, 080}{\( T_s \)}{Sample time of the controller}{}{$s$}
+\nomwithdim{B, 081}{\( \tilde{T} \)}{Thrust increment}{}{$N$}
+\nomwithdim{B, 081}{\( t \)}{Time}{}{$s$}
+\nomwithdim{B, 085}{\( \bm{u} \)}{Input vector}{}{--}
+\nomwithdim{B, 085}{\( \bm{u}_c \)}{Control vector}{}{--}
+\nomwithdim{B, 085}{\( u \)}{$x$-component of the velocity vector}{}{$m/s$}
+\nomwithdim{B, 090}{\( V \)}{Component of the velocity vector}{}{$m/s$}
+\nomwithdim{B, 091}{\( v \)}{$y$-component of the velocity vector}{}{$m/s$}
+\nomwithdim{B, 091}{\( \bm{v} \)}{Velocity vector}{}{$m/s$}
+\nomwithdim{B, 095}{\( W \)}{Weight of the quadrotor}{}{$N$}
+\nomwithdim{B, 095}{\( w \)}{$z$-component of the velocity vector}{}{$m/s$}
+\nomwithdim{B, 100}{\( \bm{x} \)}{State vector}{}{--}
+\nomwithdim{B, 100}{\( x \)}{Position coordinate in $x$-direction}{}{$m$}
+\nomwithdim{B, 105}{\( \bm{y} \)}{Output vector}{}{--}
+\nomwithdim{B, 105}{\( y \)}{Position coordinate in $y$-direction}{}{$m$}
+\nomwithdim{B, 110}{\( \bm{z} \)}{Transformed state vector}{}{--}
+\nomwithdim{B, 110}{\( z \)}{z-Transformation variable}{}{--}
+\nomwithdim{B, 110}{\( z \)}{Position coordinate in $z$-direction}{}{$m$}
+
+\nomwithdim{G, 200}{\( \alpha \)}{Parameter of the discrete first order lag element}{}{$N$}
+\nomwithdim{G, 205}{\( \zeta \)}{Relative damping coefficient of the second order filter}{}{--}
+\nomwithdim{G, 206}{\( \bm{\eta} \)}{Attitude vector}{}{$rad$}
+\nomwithdim{G, 210}{\( \Theta \)}{Pitch angle}{}{$rad$}
+\nomwithdim{G, 210}{\( \tilde{\Theta} \)}{Pitch angle increment}{}{$rad$}
+\nomwithdim{G, 210}{\( \Theta_c \)}{Control pitch angle}{}{$rad$}
+\nomwithdim{G, 215}{\( \bm{\nu} \)}{Virtual control input vector}{}{--}
+\nomwithdim{G, 215}{\( \bm{\nu}_{\bm{\dot{v}}} \)}{Virtual control input vector of the outer loop}{}{$m/s^2$}
+\nomwithdim{G, 215}{\( \bm{\nu}_{\bm{\dot{\omega}}} \)}{Virtual control input vector of the inner loop}{}{$rad/s^2$}
+\nomwithdim{G, 219}{\( \bm{\xi} \)}{Position vector}{}{$m$}
+\nomwithdim{G, 220}{\( \Phi \)}{Roll/Bank angle}{}{$rad$}
+\nomwithdim{G, 220}{\( \tilde{\Phi} \)}{Roll angle increment}{}{$rad$}
+\nomwithdim{G, 220}{\( \Phi_c \)}{Control roll angle}{}{$rad$}
+\nomwithdim{G, 221}{\( \bm{\phi}(\bm{x}) \)}{State transformation function}{}{--}
+\nomwithdim{G, 225}{\( \bm{\chi} \)}{Wind vector}{}{$m/s$}
+\nomwithdim{G, 230}{\( \Psi \)}{Yaw/Bank angle}{}{$rad$}
+\nomwithdim{G, 235}{\( \bm{\Omega} \)}{Propeller rate vector of the four rotors}{}{$rad/s$}
+\nomwithdim{G, 235}{\( \bm{\Omega}_i \)}{Propeller rate of the i-th rotor}{}{$rad/s$}
+\nomwithdim{G, 235}{\( \tilde{\bm{\Omega}} \)}{Propeller rate increment}{}{$rad/s$}
+\nomwithdim{G, 235}{\( \bm{\Omega}_c \)}{Propeller rate control vector of the four rotors around}{}{$rad/s$}
+\nomwithdim{G, 236}{\( \bm{\omega} \)}{Angular velocity vector of the quadrotor}{}{$rad/s$}
+\nomwithdim{G, 236}{\( \omega_n \)}{Cutoff frequency of the second order filter}{}{$rad/s$}
+
+\nomwithdim{S}{\( 0 \)}{Initial point in time}{}{--}
+\nomwithdim{S}{\( a \)}{Passed through the actuator dynamics}{}{--}
+\nomwithdim{S}{\( B \)}{Body-fixed coordinate frame}{}{--}
+\nomwithdim{S}{\( D \)}{Down}{}{--}
+\nomwithdim{S}{\( E \)}{East}{}{--}
+\nomwithdim{S}{\( f \)}{Filtered}{}{--}
+\nomwithdim{S}{\( G \)}{Center of gravity}{}{--}
+\nomwithdim{S}{\( G \)}{Gravitational}{}{--}
+\nomwithdim{S}{\( K \)}{Kinematic coordinate frame}{}{--}
+\nomwithdim{S}{\( N \)}{North}{}{--}
+\nomwithdim{S}{\( O \)}{North-East-Down coordinate frame}{}{--}
+\nomwithdim{S}{\( R \)}{Reference point}{}{--}
+\nomwithdim{S}{\( x \)}{$x$-component of a variable}{}{--}
+\nomwithdim{S}{\( y \)}{$y$-component of a variable}{}{--}
+\nomwithdim{S}{\( z \)}{$z$-component of a variable}{}{--}
+
+\nomwithdim{X, 400}{\( L \)}{Lie derivative operator}{}{--}
+\nomwithdim{X, 401}{\( \nabla \)}{Nabla-Operator}{}{--}
+
 \renewcommand{\nomname}{Table of Symbols}
+
 \printnomenclature[6em]
@@
 % Manually add Chapter names to the header (per default not included by Latex) 
-\thispagestyle{fancy_beginning}
+\pagestyle{fancy_beginning}
 \renewcommand{\chaptermark}[1]{\markboth{#1}{}}
@@
 
-In this subsection, the \acrfull{NDI} method is explained.
+In this subsection, the \acrlong{NDI} method is explained.
 The \acrshort{NDI} approach is based on feedback linearization and is also called \textit{Input-Output Linearization}.
@@
 As some of those inconsistencies are inevitable there is a need to build a control law which performance is less dependent on the uncertainties of the model.
-A method called \acrfull{INDI} can be used to achieve this, it is discussed in the next subsection.
+A method called \acrlong{INDI} can be used to achieve this, it is discussed in the next subsection.
 
@@
 
-Assuming that the output variable corresponds to the state varible ($y=x$), the incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
+Assuming that the output variable corresponds to the state varible ($\bm{y}=\bm{x}$), the incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
 \begin{equation}
@@
 It runs the firmware with frequency of $1000~\si{\Hz}$ and communicates with a large number of peripheral devices such as Bluetooth and long range radio, power management system \acrshort{MCU}, \acrfull{IMU} etc..
-The \acrfull{IMU} consists of the 3-axis accelerometer, the 3-axis gyroscope and the high precision pressure sensor.
+The \acrlong{IMU} consists of the 3-axis accelerometer, the 3-axis gyroscope and the high precision pressure sensor.
 
@@
 The expressions of the gravity and propulsive forces have not been changed, so the Equations \ref{eq:Fg} and \ref{eq:Fp} were adopted for the simulation model.
-The thrust value $T$ was modelled as a linear function of rotational rates of the propellers
+To achieve a simple relationship between the thrust of a quadrotor and the propeller rates, thrust value $T$ was modelled as a linear function of propeller rates $\bm{\Omega}$
 \begin{equation}
@@
 \end{equation}
-with $\alpha = 1-e^{\frac{-T_S}{T}}$ and sample time $T_S$.
+with $\alpha = 1-e^{\frac{-T_s}{T}}$ and sample time $T_s$.
 The default frequency with which the Crazyflie controller updates its state is $500~\si{\Hz}$.
-Thus, sampling time $T_S$ was set to the reciprocal value of the default frequency.
+Thus, sampling time $T_s$ was set to the reciprocal value of the default frequency.
 
@@
 	\begin{split}
-		F(s) = \frac{\omega_n^2}{s^2+2\zeta\omega_ns+\omega_n^2}
+		H(s) = \frac{\omega_n^2}{s^2+2\zeta\omega_ns+\omega_n^2}
 		\label{eq:filter_c}
@@
 	\begin{split}
-		s \ \widehat{=} \ \frac{\omega_n}{\tan(\omega_n\frac{T_S}{2})} \frac{1-z^{-1}}{1+z^{-1}}
+		s \ \widehat{=} \ \frac{\omega_n}{\tan(\omega_n\frac{T_s}{2})} \frac{1-z^{-1}}{1+z^{-1}}
 		\label{eq:filter_c}
@@
 	\begin{split}
-		F(z) = \frac{n_0 + n_1z^{-1} + n_2z^{-2}}{d_0 + d_1z^{-1} + d_2z^{-2}}
+		H(z) = \frac{n_0 + n_1z^{-1} + n_2z^{-2}}{d_0 + d_1z^{-1} + d_2z^{-2}}
 		\label{eq:filter_d}
@@
 		n_2 &= 1 \\
-		d_0 &= \frac{1}{\tan^2(\omega_n\frac{T_S}{2})} + \frac{2\zeta}{\tan(\omega_n\frac{T_S}{2})} + 1 \\
-		d_1 &= -\frac{2}{\tan^2(\omega_n\frac{T_S}{2})} + \frac{4\zeta}{\tan(\omega_n\frac{T_S}{2})} \\
-		d_2 &= \frac{1}{\tan^2(\omega_n\frac{T_S}{2})} - \frac{2\zeta}{\tan(\omega_n\frac{T_S}{2})} + 1
+		d_0 &= \frac{1}{\tan^2(\omega_n\frac{T_s}{2})} + \frac{2\zeta}{\tan(\omega_n\frac{T_s}{2})} + 1 \\
+		d_1 &= -\frac{2}{\tan^2(\omega_n\frac{T_s}{2})} + \frac{4\zeta}{\tan(\omega_n\frac{T_s}{2})} \\
+		d_2 &= \frac{1}{\tan^2(\omega_n\frac{T_s}{2})} - \frac{2\zeta}{\tan(\omega_n\frac{T_s}{2})} + 1
 	\end{align}
@@
 As mentioned in the beginning of this chapter, a simulation can be used to determine terms of the model which have a greater influence on the overall controller performance.
-Matrix $G_2$ of the control effectiveness term in Equation \ref{eq:indi_inner_control_law} contains only the term of the inertia tensor of the propeller $I_{rzz}$.
-Since $I_{rzz}$ is small, it was expected that $G_2$ will not have a big impact on the model response.
+Matrix $\bm{G}_2$ of the control effectiveness term in Equation \ref{eq:indi_inner_control_law} contains only the term of the inertia tensor of the propeller $I_{rzz}$.
+Since $I_{rzz}$ is small, it was expected that $\bm{G}_2$ will not have a big impact on the model response.
 Figure \ref{fig:g2_comp} confirms this expectation, by plotting the step response of the Crazyflie model with and without considering  the gyroscopic effects of the quadrotor propellers.
@@
 \end{equation}
-where $T_{cmd, a}$ is the thrust value filtered with the actuator dynamics model. The least squares approach is then be applied to obtain $K_{cmd}$.
+–––where $T_{cmd, a}$ is the thrust value filtered with the actuator dynamics model. The least squares approach is then be applied to obtain $K_{cmd}$.
 
@@
 
-To obtain $T_c$, current thrust value $T_0$ is filtered with a second order filter $F(z)$ ($\omega_n=8~\si{\radian/\second}$, $\zeta=0.707$) and passed through the model of the actuator dynamics $A'(z)$.
+To obtain $T_c$, current thrust value $T_0$ is filtered with a second order filter $H(z)$ ($\omega_n=8~\si{\radian/\second}$, $\zeta=0.707$) and passed through the model of the actuator dynamics $A'(z)$.
 The result is then added to the thrust increment $\tilde{T}$, provided by the outer loop \acrshort{INDI}.
@@
 
-\chapter*{Appendix} \label{sec:appendix}
-% Add Appendix chapter manually to the Table of Contents because Latex doesn't automatically include nonnumerated (...*) chapters/sections to the TOC
-\addcontentsline{toc}{chapter}{Appendix}
-
-% Manually add Chapter names to the header (per default not included by Latex)
-\thispagestyle{fancy_beginning}
-\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
-\chaptermark{Appendix}
+%\chapter*{Appendix} \label{sec:appendix}
+%% Add Appendix chapter manually to the Table of Contents because Latex doesn't automatically include nonnumerated (...*) chapters/sections to the TOC
+%\addcontentsline{toc}{chapter}{Appendix}
+
+%% Manually add Chapter names to the header (per default not included by Latex)
+%\thispagestyle{fancy_beginning}
+%\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+%\chaptermark{Appendix}
 

### 2020-03-29 code/Simulink/Crazyflie_Simulation/set_params.m

@@ -6,46 +6,43 @@ close all
 % Force and Moment Notation:
 % 'FX_Y' or 'MX_Y' with: 
 % - X: Force nature (e.g gravitational (G), aerodynamical (A), propulsive (P) etc)
-% - Y Coordinate frame (e.g Body-Fixed (B), NED (O) etc)
-% 
-% Notation of other values: (TODO)
-% - omegaR_X: vector of rotor angular velocities
-% - ...
+% - Y: Coordinate frame (e.g Body-Fixed (B), NED (O) etc)
 
 
-%% Dynamics
+%% Dynamics of the Crazyflie Quadrotro
 
 % Crazyflie
 g = 9.81;           % gravitational acceleration in [m/s^2]
 m_CF = 0.028;       % mass of the Crazyflie quadrotor in [kg]
-l = 0.033;          % lever arm to the rotor in x-direction [m]
-b = 0.033;          % lever arm to the rotor in y-direction [m]
-I_rzz = 9.3e-9;     % Component of moment of inertia of the rotor [kg*m^2]
+l = 0.033;          % lever arm to the rotor in x-direction (body frame) [m]
+b = 0.033;          % lever arm to the rotor in y-direction (body frame) [m]
+I_rzz = 9.3e-9;     % component of moment of inertia of the rotor [kg*m^2]
 
 
-I_CF_1 = [16.823890  -1.224320  -0.716891    % Moment of inertia of the 
-          -1.224320   16.885278  2.083147    % Crazyflie quadrotor in [kg*m^2]
+I_CF_1 = [16.823890  -1.224320  -0.716891                 % Moment of inertia of the 
+          -1.224320   16.885278  2.083147                 % Crazyflie quadrotor in [kg*m^2]
           -0.716891   2.083147   29.808912] * 10e-6;       
-% I_CF_1 = [16.823890     0          0       % Moment of inertia of the 
-%              0      16.885278      0       % Crazyflie quadrotor in [kg*m^2]
+% I_CF_1 = [16.823890     0          0                    % Moment of inertia (symmetric configuration) of the 
+%              0      16.885278      0                    % Crazyflie quadrotor in [kg*m^2]
 %              0          0       29.808912] * 10e-6; 
 
[…]

### 2020-04-01 Paper_EV/Paper_EV.tex
Backup update 01_04

@@
 %
-% TODO:
-% - Title page: Dr. -> Dr. ir.
-% - Acronyms, right order of full and short appearences
-% - Create List of Symbols
 %
@@
 
-% Package for setting up the list of symbols
-%https://tex.stackexchange.com/questions/112884/how-to-achieve-nomenclature-entries-like-symbol-description-dimension-and-uni
-\usepackage{nomencl,etoolbox,ragged2e,siunitx}
-%
-\newcommand{\DimensUnits}[2]{\makebox[1em]{#1}\makebox[4em]{#2\hfill}\ignorespaces}
-\newcommand{\insertnomheaders}{\item[\bfseries Symbol]\DimensUnits{}{\textbf{Unit}}\textbf{Description}}
-%
-\renewcommand\nomgroup[1]{%
-  \item[\large\bfseries
-  \ifstrequal{#1}{A}{Acronyms}{%
-  \ifstrequal{#1}{B}{Latin Letters}{%
-  \ifstrequal{#1}{G}{Greek Letters}{%
-  \ifstrequal{#1}{S}{Indices}{% 
-  \ifstrequal{#1}{U}{Subscripts}{%   
-  \ifstrequal{#1}{X}{Other Symbols}{}}}}}}]
-  \insertnomheaders
-  }
-%
-\renewcommand*{\nompreamble}{\markboth{\nomname}{\nomname}}
-% parbox - Description
-\newcommand{\nomdescr}[1]{\parbox[t]{10cm}{\RaggedRight #1}}
-\newcommand{\nomwithdim}[5]{\nomenclature[#1]{#2}{\DimensUnits{}{#5}\nomdescr{#3}}}
-%
-\makenomenclature
-
 %#################################################################################%#################################################################################%#################################################################################
@@
 %Insert empty page after table of acronyms
-\newpage\null\thispagestyle{empty}
-
-% Add Table of Symbols
-%\chapter*{Table of Symbols} \label{sec:symbols}
-\mbox{}
-\nomwithdim{B}{\( \bm{F} \)}{Force}{L}{$N$}
-\nomwithdim{B}{\( g \)}{Gravitational acceleration}{}{$m/s^2$}
-\nomwithdim{G}{\( \alpha \)}{Angle of attack}{}{$rad$}
-\nomwithdim{G}{\( \zeta \)}{Damping of a linear second order system}{}{--}
-\nomwithdim{S}{\( m \)}{Variable related to pitch moment}{}{}
-\nomwithdim{S}{\( W \)}{Wind}{}{}
-\renewcommand{\nomname}{Table of Symbols}
-\printnomenclature[6em]
+\newpage\null\thispagestyle{empty}\newpage
 
 % Manually add Chapter names to the header (per default not included by Latex) 
-\thispagestyle{fancy_beginning}
+\protect\thispagestyle{fancy_beginning}
 \renewcommand{\chaptermark}[1]{\markboth{#1}{}}
@@
 
+\chapter*{Table of Symbols} \label{sec:table_of_symbols}
+
+\textbf{Latin Letters}
+% Add table ([...ex] adds some extra vertical spacing after corresponding row)
+\begin{table}[H]
+  %\centering
+  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
+    \textbf{Symbol} & \textbf{Unit} & \textbf{Description} \\ [1.2ex] 
+    $A(s),~A(z)$ & -- & Transfer function of the actuator dynamics \\ 
+    $A'(s),~A'(z)$ & -- & Transfer function of the actuator dynamics model \\
+    $a(t)$ & -- & Function of the first order lag element in time domain \\
+    $b$ & $m$ & Lever arm of the rotors to the C.G. along the body $y$-axis \\
+    $d$ & $m/s^2$ & Disturbance \\
+    $d_0, d_1, d_2$ & -- & Denominator coefficients of the discrete second order filter \\
+    $E(t)$ & -- & Objective function \\
+    $\bm{F}$ & $N$ & Force vector \\
+    $\bm{F}_A$ & $N$ & Aerodynamic force vector \\
+    $\bm{F}_G$ & $N$ & Gravitational force vector \\
+    $\bm{F}_P$ & $N$ & Propulsive force vector \\
+    $\bm{f}(\bm{x})$ & -- & Nonlinear vector field \\
+    $\bm{G}$ & -- & Control effectiveness matrix of the outer loop \\
+    $\bm{G}_1$ & -- & Control effectiveness matrix of the inner loop \\
+    $\bm{G}_2$ & -- & Control effectiveness matrix of the inner loop \\
+    $\bm{G}_{inner}$ & -- & Dynamics matrix of the inner loop \\
+    $\bm{G}_{outer}$ & -- & Dynamics matrix of the outer loop \\
+    $\bm{G}(x)$ & -- & Input matrix \\
+    $g$ & $m/s^2$ & Gravitational acceleration \\
+    $H(s),~H(z)$ & -- & Transfer function of the second order filter \\
+    $\bm{h}(\bm{x})$ & -- & Nonlinear vector field \\
+    $\bm{I}$ & $Nm^2$ & Inertia tensor of the quadrotor \\
+    $\bm{I_{rzz}}$ & $Nm^2$ & $zz$-element of the inertia tensor of the rotor \\
+    $i$ & -- & Relative degree of the dynamic system \\
+    $K$ & -- & Compensation gain \\
+    $K_{cmd}$ & -- & Thrust mapping parameter \\
+    $k$ & $kg/s$ & Drag coefficient \\ %[0.5ex]  
+  \end{tabular}
+  %\caption[Sample table 1]{Sample table 1}  
+  %\captionsetup{font=bf, belowskip=-0.5cm}
+  \label{table:tab_latin_1}
+\end{table}
+
+% Manually add Chapter names to the header (per default not included by Latex) 
+\protect\thispagestyle{fancy_beginning}
+\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+\chaptermark{Table of Symbols}
+
+% Add table ([...ex] adds some extra vertical spacing after corresponding row)
+\begin{table}[H]
+  %\centering
+  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
+    $k$ & -- & Gain of the actuator dynamics \\ 
+    $k_F$ & $\frac{N}{rad/s}$ & Force constant of the rotors \\
+    $k_M$ & $\frac{Nm}{rad/s}$ & Moment constant of the rotors \\
+    $L$ & -- & Lie derivative operator \\
+    $l$ & $m$ & Lever arm of the rotors to the C.G. along the body $y$-axis \\
+    $\bm{M}$ & $Nm$ & Moment vector \\
+    $\bm{M}_A$ & $Nm$ & Aerodynamic Moment vector \\
+    $\bm{M}_c$ & $Nm$ & Control moment vector \\
+    $\bm{M}_G$ & $Nm$ & Gravitational Moment vector \\
+    $\bm{M}_{gyro}$ & $Nm$ & Moment vector due to the gyroscopic effects of the rotor \\
+    $\bm{M}_{OB}$ & -- & Transformation matrix from the body-fixed into NED frame \\
+    $\bm{M}_P$ & $Nm$ & Propulsion moment vector \\
+    $m$ & $kg$ & Mass of the quadrotor \\
+    $m_{cf}$ & $kg$ & Mass of the Crazyflie quadrotor \\
+    $m_r$ & $kg$ & Additional mass (disturbance \\
+    $n$ & -- & Number of samples \\
+    $n_0, n_1, n_2$ & -- & Numerator coefficients of the discrete second order filter \\
+    $P$ & -- & Parameter \\
+    $p$ & $rad/s$ & Roll rate \\ 
+	$q$ & $rad/s$ & Pitch rate \\
+    $r$ & $rad/s$ & Yaw rate \\
+	$s$ & -- & Laplace variable \\
+    $T$ & $N$ & Thrust \\
+	$T$ & $s$ & Time constant of the actuator dynamics \\
+    $T_{cmd}$ & -- & Thrust in motor units \\
+	$T_s$ & $s$ & Sample time of the controller \\
+    $\tilde{T}$ & $N$ & Thrust increment\\
+	$t$ & $s$ & Time \\    
+    $u$ & -- & Input vector \\
+    $\bm{u}_c$ & -- & Control vector \\
+    $u$ & $m/s$ & $x$-component of the velocity vector \\ %[0.5ex]
+  \end{tabular}
+  %\caption[Sample table 1]{Sample table 1}  
+  \captionsetup{font=bf, belowskip=-0.5cm}
+  \label{table:tab_latin_2}
+\end{table}
+
+% Manually add Chapter names to the header (per default not included by Latex) 
+\protect\thispagestyle{fancy_beginning}
+\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+\chaptermark{Table of Symbols}
+
+% Add table ([...ex] adds some extra vertical spacing after corresponding row)
+\begin{table}[H]
+  %\centering
+  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
+    $V$ & $m/s$ & Component of the velocity vector \\ 
+    $v$ & $m/s$ & $y$-component of the velocity vector \\
+    $ \bm{v}$ & $m/s$ & Velocity vector \\
+    $W$ & $N$ & Weight of the quadrotor \\
+    $w$ & $m/s$ & $z$-component of the velocity vector \\
+    $\bm{x}$ & -- & State vector \\
+    $x$ & $m$ & Position coordinate in $x$-direction \\
+    $\bm{y}$ & -- & Output vector \\
+    $y$ & $m$ & Position coordinate in $y$-direction \\
+    $\bm{z} $ & -- & Transformed state vector \\
+    $z$ & -- & z-Transformation variable \\
+    $z$ & $m$ & Position coordinate in $z$-direction \\ %[0.5ex]  
+  \end{tabular}
+  %\caption[Sample table 1]{Sample table 1}  
+  \captionsetup{font=bf, belowskip=-0.5cm}
+  \label{table:tab_latin_3}
+\end{table}
+
+% Manually add Chapter names to the header (per default not included by Latex) 
+\protect\thispagestyle{fancy_beginning}
+\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+\chaptermark{Table of Symbols}
+
+\textbf{Greek Letters}
+% Add table ([...ex] adds some extra vertical spacing after corresponding row)
+\begin{table}[H]
+  %\centering
+  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
+    \textbf{Symbol} & \textbf{Unit} & \textbf{Description} \\ [1.2ex] 
+    $\alpha$ & -- & Parameter of the discrete first order lag element \\ 
+    $\zeta$ & -- & Relative damping coefficient of the second order filter \\
+    $\bm{\eta}$ & $rad$ & Attitude vector \\
+    $\Theta$ & $rad$ & Pitch angle \\
+    $\tilde{\Theta}$ & $rad$ & Pitch angle increment \\
+    $\Theta_c$ & $rad$ & Control pitch angle \\
+    $\bm{\nu}$ & -- & Virtual control input vector \\
+    $\bm{\nu}_{\bm{\dot{v}}}$ & $m/s^2$ & Virtual control input vector of the outer loop \\
+    $\bm{\nu}_{\bm{\dot{\omega}}}$ & $rad/s^2$ & Virtual control input vector of the inner loop \\
+    $\bm{\xi}$ & $m$ & Position vector \\
+    $\Phi$ & $rad$ & Roll/Bank angle \\
+    $\tilde{\Phi}$ & $rad$ & Roll angle increment \\
+    $\Phi_c$ & $rad$ & Control roll angle \\
+	$\bm{\phi}(\bm{x})$ & -- & State transformation function \\ %[0.5ex]  
+  \end{tabular}
+  %\caption[Sample table 1]{Sample table 1}  
+  \captionsetup{font=bf, belowskip=-0.5cm}
+  \label{table:tab_greek}
+\end{table}
+
+\textbf{Indices}
+% Add table ([...ex] adds some extra vertical spacing after corresponding row)
+\begin{table}[H]
+  %\centering
+  \begin{tabular}{p{2.5cm} p{10cm}} 
+    \textbf{Symbol} & \textbf{Description} \\ [1.2ex] 
+    $0$ & Initial point in time \\ 
+    $a$ & Passed through the actuator dynamics \\ 
+    $B$ & Body-fixed coordinate frame \\ 
+    $D$ & Down \\
+    $E$ & East \\ 
+    $f$ & Filtered \\ 
+    $G$ & Center of gravity \\ 
+    $G$ & Gravitational \\
+    $K$ & Kinematic coordinate frame \\
+    $N$ & North \\
+    $O$ & North-East-Down coordinate frame \\
+    $R$ & Reference point \\
+    $x$ & $x$-component of a variable \\
+	$y$ & $y$-component of a variable \\
+	$z$ & $z$-component of a variable \\ %[0.5ex]  
+  \end{tabular}
+  %\caption[Sample table 1]{Sample table 1}  
+  \captionsetup{font=bf, belowskip=-0.5cm}
+  \label{table:tab_indices}
+\end{table}
+
+\textbf{Other Symbols}
+% Add table ([...ex] adds some extra vertical spacing after corresponding row)
+\begin{table}[H]
+  %\centering
+  \begin{tabular}{p{2.5cm} p{10cm}} 
+    \textbf{Symbol} & \textbf{Description} \\ [1.2ex] 
+    $L$ & Lie derivative operator \\ 
+	$\nabla$ & Nabla-Operator \\ %[0.5ex]  
+  \end{tabular}
+  %\caption[Sample table 1]{Sample table 1}  
+  \captionsetup{font=bf, belowskip=-0.5cm}
+  \label{table:tab_other_symbols}
+\end{table}
+
+% Manually add Chapter names to the header (per default not included by Latex) 
+\protect\thispagestyle{fancy_beginning}
+\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
+\chaptermark{Table of Symbols}
+
 %Insert empty page after table of symbols
-\newpage\null\thispagestyle{empty}\newpage
+\newpage
 

### 2020-04-01 code/param_est/for_pull_request/param_estimation.m

@@ -9,7 +9,7 @@ Fs = 1/Ts;
 T = 0.0617;                      % Time constant T [s]
 alpha = 1 - exp(-Ts/T);   
 
-filename = "csv_data/data_1901.csv";
+filename = "data_1901.csv";
 
 %% Import data
 
@@ -29,39 +29,38 @@ cmd_thrust_a = filter([alpha], [1, -(1-alpha)], cmd_thrust);
 
 [b, a] = butter(4, 4/(Fs/2));       % compute filter coeffs
 
-% Filter gyro data to remove noise
+% Filtering gyro data to remove noise
 gyro_roll_f = filter(b, a, gyro_roll);
 gyro_pitch_f = filter(b, a, gyro_pitch);
 gyro_yaw_f = filter(b, a, gyro_yaw);
 
-% Filter cmd data to remove noise
+% Filtering cmd data to remove noise
 cmd_roll_f = filter(b, a, cmd_roll_a);
 cmd_pitch_f = filter(b, a, cmd_pitch_a);
 cmd_yaw_f = filter(b, a, cmd_yaw_a);
 
-% Differtiate angular velocities to get angular accelerations
+% Differtiating angular velocities to get angular accelerations
 ang_accel_roll = [0; diff(gyro_roll_f)]/Ts;
 ang_accel_pitch = [0; diff(gyro_pitch_f)]/Ts;
 ang_accel_yaw = [0; diff(gyro_yaw_f)]/Ts;
 
-% Differentiate 2nd time (for parameter estimation)
+% Differentiating 2nd time (for parameter estimation)
 ang_accel_roll_d = [0; diff(ang_accel_roll)]/Ts;
 ang_accel_pitch_d = [0; diff(ang_accel_pitch)]/Ts;
 ang_accel_yaw_d = [0; diff(ang_accel_yaw)]/Ts;
 
-% Differentiate cmd (for parameter estimation)
+% Differentiating cmd (for parameter estimation)
 cmd_roll_fd = [0; diff(cmd_roll_f)]/Ts;
 cmd_pitch_fd = [0; diff(cmd_pitch_f)]/Ts;
 cmd_yaw_fd = [0; diff(cmd_yaw_f)]/Ts;
 cmd_yaw_fdd = [0; diff(cmd_yaw_fd)]/Ts;
 
 
-%% Compute control effectiveness parameters
[…]

### 2020-04-01 crazyflie-firmware/src/modules/interface/controller_indi.h

@@ -33,7 +33,7 @@
 #include "param.h"
 #include "position_controller.h"
 #include "attitude_controller.h"
-#include "math.h"  //ev_tag
+#include "position_controller_indi.h"
 
 #define ATTITUDE_UPDATE_DT    (float)(1.0f/ATTITUDE_RATE)
 
@@ -48,22 +48,15 @@
 #define STABILIZATION_INDI_G1_Q 0.0052125f
 #define STABILIZATION_INDI_G1_R -0.001497f
 #define STABILIZATION_INDI_G2_R 0.000043475f
-#define STABILIZATION_INDI_REF_ERR_P 20.0f
-#define STABILIZATION_INDI_REF_ERR_Q 20.0f
-#define STABILIZATION_INDI_REF_ERR_R 20.0f
+#define STABILIZATION_INDI_REF_ERR_P 24.0f
+#define STABILIZATION_INDI_REF_ERR_Q 24.0f
+#define STABILIZATION_INDI_REF_ERR_R 24.0f
 #define STABILIZATION_INDI_REF_RATE_P 14.0f
 #define STABILIZATION_INDI_REF_RATE_Q 14.0f
 #define STABILIZATION_INDI_REF_RATE_R 14.0f
 #define STABILIZATION_INDI_ACT_DYN_P 0.03149f
 #define STABILIZATION_INDI_ACT_DYN_Q 0.03149f
 #define STABILIZATION_INDI_ACT_DYN_R 0.03149f
-
-// Crazyflie mass [kg]
-#define CF_MASS 0.028f
-
-// Thrust command
-#define MIN_THRUST  0
-#define MAX_THRUST  60000
 
 /**
  * @brief angular rates
@@ -83,19 +76,6 @@ struct ReferenceSystem {
   float rate_r;
 };
 
-// ev_tag
-struct Vectr {
-  float x; 
-  float y; 
-  float z;
-};
-// ev_tag
-struct Angles {
-  float phi; 
-  float theta;
-  float psi;
-};
-
 struct IndiVariables {
   float thrust;
   struct FloatRates angular_accel_ref;
@@ -106,9 +86,6 @@ struct IndiVariables {
 
   Butterworth2LowPass u[3];
   Butterworth2LowPass rate[3];
-  Butterworth2LowPass ddxi[3];
-  Butterworth2LowPass ang[3];
-  Butterworth2LowPass thr[3];
   struct FloatRates g1;
   float g2;
 
[…]

### 2020-04-04 Paper_EV/Paper_EV.tex
Backup update 04_04

@@
     $K_{cmd}$ & -- & Thrust mapping parameter \\
-    $k$ & $kg/s$ & Drag coefficient \\ %[0.5ex]  
+    $K_{\eta}$ & -- & Gain of the inner loop \\ %[0.5ex]  
   \end{tabular}
@@
   \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
+    $K_{\omega}$ & -- & Gain of the inner loop \\
+    $K_{\xi}$ & -- & Gain of the outer loop \\
+    $K_{\dot{v}}$ & -- & Gain of the outer loop \\
+    $k$ & $kg/s$ & Drag coefficient \\ 
     $k$ & -- & Gain of the actuator dynamics \\ 
@@
 	$T_s$ & $s$ & Sample time of the controller \\
-    $\tilde{T}$ & $N$ & Thrust increment\\
-	$t$ & $s$ & Time \\    
-    $u$ & -- & Input vector \\
-    $\bm{u}_c$ & -- & Control vector \\
-    $u$ & $m/s$ & $x$-component of the velocity vector \\ %[0.5ex]
+    $\tilde{T}$ & $N$ & Thrust increment \\ %[0.5ex]
   \end{tabular}
@@
   \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
+	$t$ & $s$ & Time \\    
+    $u$ & -- & Input vector \\
+    $\bm{u}_c$ & -- & Control vector \\
+    $u$ & $m/s$ & $x$-component of the velocity vector \\
     $V$ & $m/s$ & Component of the velocity vector \\ 
@@
     $z$ & -- & z-Transformation variable \\
-    $z$ & $m$ & Position coordinate in $z$-direction \\ %[0.5ex]  
+    $z$ & $m$ & Position coordinate in $z$-direction %[0.5ex]  
   \end{tabular}
@@
     $\bm{\xi}$ & $m$ & Position vector \\
-    $\Phi$ & $rad$ & Roll/Bank angle \\
-    $\tilde{\Phi}$ & $rad$ & Roll angle increment \\
-    $\Phi_c$ & $rad$ & Control roll angle \\
-	$\bm{\phi}(\bm{x})$ & -- & State transformation function \\ %[0.5ex]  
+    $\Phi$ & $rad$ & Roll/Bank angle \\ %[0.5ex]  
   \end{tabular}
@@
   \captionsetup{font=bf, belowskip=-0.5cm}
-  \label{table:tab_greek}
+  \label{table:tab_greek_1}
+\end{table}
+
+% Add table ([...ex] adds some extra vertical spacing after corresponding row)
+\begin{table}[H]
+  %\centering
+  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
+    $\tilde{\Phi}$ & $rad$ & Roll angle increment \\
+    $\Phi_c$ & $rad$ & Control roll angle \\
+	$\bm{\phi}(\bm{x})$ & -- & State transformation function %[0.5ex]  
+  \end{tabular}
+  %\caption[Sample table 1]{Sample table 1}  
+  \captionsetup{font=bf, belowskip=-0.5cm}
+  \label{table:tab_greek_2}
 \end{table}
@@
 	$y$ & $y$-component of a variable \\
-	$z$ & $z$-component of a variable \\ %[0.5ex]  
+	$z$ & $z$-component of a variable %[0.5ex]  
   \end{tabular}

### 2020-04-18 Paper_EV/Paper_EV.tex
Backup update 18_04_2020

@@
 %
+% TODO:
+% - Change date on the title page
+% - Change date on the statutory declaration page
 %
@@
 % Foot (11 pt font size and 12 pt line spacing)
-\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implem. and Eval. of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}
+\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implementation \& Evaluation of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}
 \fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage \thinspace / \lastpageref{pagesLTS.arabic}}
@@
 % Foot
-\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implem. and Eval. of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}%
+\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implementation \& Evaluation of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}%
 \fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage}%
@@
 \newacronym{INDI}{INDI}{Incremental Nonlinear Dynamic Inversion}
+\newacronym{IR}{IR}{Infrared}
 \newacronym{MAV}{MAV}{Micro Air Vehicle}
@@
 \\
-Garching,
+Garching, April 25, 2020
+\\
+\\
+\\
+\\
+Evghenii Volodscoi
 
@@
 Der hergeleitete Regelgesetz wird dann erst in Simulink entwickelt und anschlie\ss{}end auf der Quadrotor-Hardware implementiert.
-Dazu werden solche Implementierungsaspekte wie Ermittlung der Eingangsparameter, Messung und Berechnung der Aktuatorzeitkonstante sowie Ermittlung des Schub-Mapping-Parameters besprochen.
+Dazu werden solche Implementierungsaspekte wie Ermittlung der Eingangsmatrix, Messung und Berechnung der Aktuatorzeitkonstante sowie Ermittlung des Schub-Mapping-Parameters besprochen.
 Abschlie\ss{}end, wird der implementierte Regler auf die F\"ahigkeit St\"orungen zu bek\"ampfen getestet.
+Der finale Regler ist \"uber das offizielle Open-Source-Firmware des Crazyflie-Quadrotors verf\"ugbar.
 \end{itshape}
@@
 It begins with the derivation of the control algorithm.
-The controller is then firstly developed in the Simulink environment and afterwards implemented on the quadrotor hardware.
+The controller is then firstly developed in the Simulink environment and afterwards implemented on the embedded hardware of the quadrotor.
 Subsequently, the implementation aspects of the INDI controller such as estimation of the control effectiveness, measurement of the actuator time constant and estimation of the thrust mapping parameter are discussed.
-Finally, the implemented controller is tested on the ability to cope with disturbances.
+Finally, the implemented controller is tested on the ability to cope with disturbance.
+The final version of the implemented control algorithm is available via official open source firmware of the Crazyflie quadrotor.
 \end{itshape}
@@
 The popularity of Micro Air Vehicles (MAVs) in research and industry has grown over the past years.
-The large interest in \acrshort{MAV}s can be expalined with their potential of performing a wide range of civilian and military tasks, reaching from the investigation of hazardous regions up to the agriculture mapping \cite{Ward}.
+The large interest in \acrshort{MAV}s can be explained with their potential of performing a wide range of civilian and military tasks, reaching from the investigation of hazardous regions up to agriculture mapping \cite{Ward}.
 One of the most popular representatives of \acrshort{MAV}s are quadrotors, belonging to the rotary-wing \acrshort{MAV}s.
@@
 Finally, it discusses the capability of the successfully implemented \acrshort{INDI} controller to cope with disturbances.
+The hardware version of the control algorithm was then made available to general public via official open source firmware.
 
@@
 The third section (\ref{sec:implementation_on_hardware}) of the same chapter covers aspects that are relevant for the hardware implementation of the \acrshort{INDI} control algorithm, such as the estimation of the control effectiveness terms and thrust mapping parameter.
-After controller was implemented, it was tested and validated.
+After the controller was implemented, it was tested and validated.
 The test results are summarized in the fourth chapter.
@@
 At the beginning, in section \ref{sec:eqs_motion} general \acrfull{EOM} of an aircraft are presented.
-These are later used to derive the control algorithm and build the Matlab/Simulink model of the Crazyflie quadrotor.
+These are later used to derive the control algorithm and build the Simulink model of the Crazyflie quadrotor.
 Sections \ref{sec:ndi} and \ref{sec:indi} describe the \acrfull{NDI} and \acrfull{INDI} methods in general.
@@
 Considering a general aircraft system, these could be the aerodynamic forces and moments caused by the air flow, propulsion forces and moments, forces caused by the gravitation etc..
-The detailed modelling of external forces and moments is presented in chapter \ref{sec:simulink_model}.
+The detailed modelling of external forces and moments is presented in sections \ref{subsec: indi_inner}, \ref{subsec: indi_outer} and \ref{sec:simulink_model}.
 
@@
 \end{equation}
-The variable $\bm{\nu}$ is called an \textit{virtual control input} and represents the desired output of the system.
+The variable $\bm{\nu}$ is called a \textit{virtual control input} and represents the desired output of the system.
 
@@
 
-Assuming that the output variable corresponds to the state varible ($\bm{y}=\bm{x}$), the incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
+Assuming that the output variable corresponds to the state varible ($\bm{y}=\bm{h}(\bm{x})=\bm{x}$), the incremental form of the system can be obtained by taking a Taylor series expansion of the Equation \ref{eq:nonlin_sys1}
 \begin{equation}
@@
 It is assumed that the gravitational force is applied to the center of gravity of the quadrotor and does not cause any moment around it.
-Due to the absence of the aerodynamic moment this term is also omitted and can be seen as a disturbance \cite{Smeur1}.
+Due to the absence of the aerodynamic moment, this term is also omitted and can be seen as a disturbance \cite{Smeur1}.
 The remaining propulsion moment is written as $\bm{M}_P=\bm{M}_C-\bm{M}_{gyro}$ where $\bm{M}_C$ is the control moment generated by the rotors and $\bm{M}_{gyro}$ the moment containing the gyroscopic effect of the rotors.
@@
 \end{equation}
-where $I_{rzz}$ is the element of the inertia matrix $I_{r}$ of the rotor, $l$ and $b$ lever arms as denoted in the Figure \ref{fig:frames_leverarms}, $k_F$ and $k_M$ force and moment constants of the rotors.
+where $I_{rzz}$ is an element of the inertia matrix $I_{r}$ of the rotor, $l$ and $b$ lever arms as denoted in the Figure \ref{fig:frames_leverarms}, $k_F$ and $k_M$ force and moment constants of the rotors.
 \begin{figure}[H]
@@
 \end{equation}
-The first term of the Equation \ref{eq:main_eom_indi_inner_lin} is the angular acceleration based on the current angular rates $\bm{\omega}_0$ and inputs $\bm{\Omega}_0$ and can be denoted as $\bm{\dot{\omega}}_0$.
+The first term of the Equation \ref{eq:main_eom_indi_inner_lin} is the angular acceleration based on the current angular rates $\bm{\omega}_0$ and inputs $\bm{\Omega}_0$.
 $T_0$ is the current thrust value.
 The last term on the right side of the Equation \ref{eq:main_eom_indi_inner_lin} is scaled with the sample time $T_s$ which is introduced only to simplify further mathematical transformations.
-The expressions of the control moment $\bm{M}_C$ and the gyroscopic moment of the rotors $\bm{M}_{gyro}$ have been summarized to control effectiveness matrices $\bm{G}_1$ and $\bm{G}_2$
+The expressions of the control moment $\bm{M}_C$ and the gyroscopic moment of the rotors $\bm{M}_{gyro}$ have been summarized to control effectiveness matrices $\bm{G}_1$ and $\bm{G}_2$ which are defined as
 \begin{equation}
@@
 Thus, the same second order filter $H(z)$ is applied to all variables with a subscript $0$.
-By applying filtering (subscript $f$) and finite differences method to the Equation \ref{eq:main_eom_indi_inner_lin}, its discrete version results in
+By applying the filtering (subscript $f$) and the finite differences method to the Equation \ref{eq:main_eom_indi_inner_lin}, its discrete version results in
 \begin{equation}
@@
 \end{equation}
-By solving Equation \ref{eq:main_eom_indi_inner_lin_final} for $\bm{\dot{\Omega}}$ and substituting $\bm{\dot{\omega}}$ with the virtual control input $\bm{\nu}_{\bm{\dot{\omega}}}$, the control law of the inner loop is obtained
+By solving Equation \ref{eq:main_eom_indi_inner_lin_final} for $\bm{\Omega}$ and substituting $\bm{\dot{\omega}}$ with the virtual control input $\bm{\nu}_{\bm{\dot{\omega}}}$, the control law of the inner loop is obtained
 \begin{equation}
@@
 \end{equation}
-where $\bm{\Omega}$ is a vector of commanded rotational rates for every rotor and  $\tilde{T} = T - T_f$ and $\tilde{\bm{\Omega}} = \bm{\Omega}_c - \bm{\Omega}_f$ being thrust and propeller rates increments respectively, provided by the inner loop \acrshort{INDI}.
+where $\bm{\Omega}_c$ is a vector of commanded rotational rates for every rotor and  $\tilde{T} = T - T_f$ and $\tilde{\bm{\Omega}} = \bm{\Omega}_c - \bm{\Omega}_f$ being thrust and propeller rates increments respectively, provided by the inner loop \acrshort{INDI}.
 The block diagram of the inner loop \acrshort{INDI} controller is presented in Figure \ref{fig:indi_inner_croped}.
@@
 \end{equation}
-The aerodynamic force $(\bm{F}_A)_O$ is modelled as an unknown function of velocity $\bm{v}$ and wind vector $\bm{\chi}$.
+The aerodynamic force $(\bm{F}_A)_O$ is modelled as an unknown function of the velocity $\bm{v}$ and wind vector $\bm{\chi}$.
 For the gravitational force $(\bm{F}_G)_O$ the simplest one-dimensional gravity model is assumed.
@@
 		\bm{\dot{v}} &= m^{-1} [\bm{F}_G + \bm{F}_P(\Phi_0, \Theta_0, \Psi_0, T_0)+ \bm{F}_A(\bm{v}_0, \bm{\chi}_0)]  \\		
-		&+ \frac{\partial}{\partial \bm{v}} \big[ \bm{F}_A(\bm{v}, \bm{\chi}_0) \big] \bigg| _{\bm{v}=\bm{v}_0} (\bm{v}-\bm{v}_0) \\
-		&+ \frac{\partial}{\partial \bm{\chi}} \big[ \bm{F}_A(\bm{v}_0, \bm{\chi}) \big] \bigg| _{\bm{\chi}=\bm{\chi}_0} (\bm{\chi}-\bm{\chi}_0) \\
-		&+ \frac{\partial}{\partial \Phi} \big[ \bm{F}_P(\Phi, \Theta_0, \Psi_0, T_0) \big] \bigg| _{\Phi=\Phi_0} (\Phi-\Phi_0) \\
-		&+ \frac{\partial}{\partial \Theta} \big[ \bm{F}_P(\Phi_0, \Theta, \Psi_0, T_0) \big] \bigg| _{\Theta=\Theta_0} (\Theta-\Theta_0) \\
-		&+ \frac{\partial}{\partial \Psi} \big[ \bm{F}_P(\Phi_0, \Theta_0, \Psi, T_0) \big] \bigg| _{\Psi=\Psi_0} (\Psi-\Psi_0) \\
-		&+ \frac{\partial}{\partial T} \big[ \bm{F}_P(\Phi_0, \Theta_0, \Psi_0, T) \big] \bigg| _{T=T_0} (T-T_0) \\
+		&+ m^{-1} \frac{\partial}{\partial \bm{v}} \big[ \bm{F}_A(\bm{v}, \bm{\chi}_0) \big] \bigg| _{\bm{v}=\bm{v}_0} (\bm{v}-\bm{v}_0) \\
+		&+ m^{-1} \frac{\partial}{\partial \bm{\chi}} \big[ \bm{F}_A(\bm{v}_0, \bm{\chi}) \big] \bigg| _{\bm{\chi}=\bm{\chi}_0} (\bm{\chi}-\bm{\chi}_0) \\
+		&+ m^{-1} \frac{\partial}{\partial \Phi} \big[ \bm{F}_P(\Phi, \Theta_0, \Psi_0, T_0) \big] \bigg| _{\Phi=\Phi_0} (\Phi-\Phi_0) \\
+		&+ m^{-1} \frac{\partial}{\partial \Theta} \big[ \bm{F}_P(\Phi_0, \Theta, \Psi_0, T_0) \big] \bigg| _{\Theta=\Theta_0} (\Theta-\Theta_0) \\
+		&+ m^{-1} \frac{\partial}{\partial \Psi} \big[ \bm{F}_P(\Phi_0, \Theta_0, \Psi, T_0) \big] \bigg| _{\Psi=\Psi_0} (\Psi-\Psi_0) \\
+		&+ m^{-1} \frac{\partial}{\partial T} \big[ \bm{F}_P(\Phi_0, \Theta_0, \Psi_0, T) \big] \bigg| _{T=T_0} (T-T_0) \\
 		\label{eq:main_eom_indi_outer_taylor}
@@
 The linear acceleration $\bm{\dot{v}}_0$ which is obtained from accelerometer measurements is usually noisy.
-Applying the same filter $H(z)$ as in the case of the inner loop derivation, the Equation \ref{eq:lin_momentum_indi_outer_lin} is given by:
+By applying the same filter $H(z)$ as in the case of the inner loop derivation, the Equation \ref{eq:lin_momentum_indi_outer_lin} is given by:
 \begin{equation}
@@
 Using the same approach as with the inner loop, the outer loop which controls linear acceleration is augmented with two gains (see Figure \ref{fig:pid_outer_croped}).
-These gains represent two controllers which control linear velocity and position $\xi$.
+These gains represent two controllers which control linear velocity $\bm{v}$ and position $\xi$.
 \begin{figure}[H]
@@
 
+%Insert empty page after table of acronyms
+\newpage\null\thispagestyle{empty}\newpage
+
 \chapter{Implementation} \label{cha:implementation}
@@
 The quadrotor used in this project was extended with a flow deck sensor.
-The flow deck itself is equipped with two sensors: the optical flow sensor which measures the visual motion and the \acrfull{ToF} laser-ranging sensor which measures the range to the next object along the body-fixed z-axis of the quadcopter.
+The flow deck itself is equipped with two sensors: the optical flow sensor which measures the visual motion and the \acrfull{ToF} laser-ranging sensor which measures the range to the next object along the body-fixed z-axis of the quadrotor.
 By employing these sensors, the flow deck can provide estimates of the current position and linear velocity of the aircraft.
@@
 
-Before implementing the outer loop of the \acrshort{INDI} controller derived in \ref{subsec: indi_outer} on the real Crazyflie quadrotor it was decided firstly to build a simulation model using Matlab/Simulink software.
+Before implementing the outer loop of the \acrshort{INDI} controller derived in \ref{subsec: indi_outer} on the real Crazyflie quadrotor it was decided firstly to build a simulation model using the Matlab/Simulink software.
 Such a simulation has a number of advantages compared to the direct implementation on the hardware.
 The main one is, it allows one to conveniently test different model components (e.g.
-filtering algorithms, actuator dynamic models etc.) on their dedicated functions, facilitating the debugging process.
+filtering algorithms, actuator dynamics models etc.) on their dedicated functions, facilitating the debugging process.
 It also can ease the process of parameter tuning of the controller.
 
-In the framework of this thesis the Simulink model was also applied to better understand the controller structure and its characteristics.
+In the framework of this thesis the Simulink model was also used to better understand the controller structure and its characteristics.
 Based on the simulation it was determined which of the control effectiveness terms have a greater influence on the system response and which ones can be neglected.
@@
 The expressions of the gravity and propulsive forces have not been changed, so the Equations \ref{eq:Fg} and \ref{eq:Fp} were adopted for the simulation model.
-To achieve a simple relationship between the thrust of a quadrotor and the propeller rates, thrust value $T$ was modelled as a linear function of propeller rates $\bm{\Omega}$
+The thrust of the quadrotor was modelled as a linear function of propeller rates $\bm{\Omega}$.
+Instead of using quadratic relationship between the thrust and propeller rates (which can be often found in the literature), the choice fell on the linear relationship to avoid mixing of linear relations with quadratic ones.
+This would make the control allocation problem more difficult, since the term which contains the effect of the propeller inertia $\bm{G_2}$ is linear.
+Thus, the thrust $T$ is given as:
 \begin{equation}
@@
 Section \ref{sec:implementation_on_hardware} shortly describes the process of using flight data to estimate the time constant $T$.
-In the Simulink model it was assumed that the actuator feedback is available, hovewer for the implementation on hardware it is necessary to have a discrete version of the transfer function in Equation \ref{eq:act_dynamics_c}.
+In the Simulink model it was assumed that the actuator feedback is available, hovewer for the implementation on hardware it is necessary to have a discrete version of the transfer function in Equation \ref{eq:act_dynamics_c} (see subsection \ref{subsec:time_const_estimation} for details).
 Transforming it from continuous domain into discrete by applying \textit{Zero-Order Hold method} results in
@@
 Other filters are applied to remaining feedback quantities.
-Using the same parameters for every filter, this technique accounts for the time delay which is introduced by the filters and ensures that all quantities that were fed back are from the same point in time.
+By using the same parameters for every filter, this technique accounts for the time delay which is introduced by the filters and ensures that all quantities that were fed back are from the same point in time.
 The general transfer function of a second order filter in continuous domain is defined by the following formula
@@
 		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
-		\includegraphics[width=0.85\textwidth]{figs/sim_outer_all.pdf}};
+		\includegraphics[width=0.81\textwidth]{figs/sim_outer_all.pdf}};
 	\end{tikzpicture}
@@
 		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
-		\includegraphics[width=0.85\textwidth]{figs/sim_inner_all.pdf}};
+		\includegraphics[width=0.81\textwidth]{figs/sim_inner_all.pdf}};
 	\end{tikzpicture}
@@
 	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-	\caption[Responses of the closed loop system with and without gyroscopic effects.]{Responses of the closed loop system using simulation of the Crazyflie's dynamics with and without considering the gyroscopic effects of the propellers.}
+	\caption[Responses of the closed loop system with and without gyroscopic effects.]{Responses of the closed loop system using simulation of the Crazyflie dynamics with and without considering the gyroscopic effects of the propellers.}
 	\label{fig:g2_comp}
@@
 
-To ensure proper functioning of the inner loop, some of the errors in the already existing implementation 1were corrected.
+To ensure proper functioning of the inner loop, some of the mistakes in the already existing implementation were corrected.
 Additionally, the control effectiveness parameters $\bm{G_1}$ and $\bm{G_2}$ were reestimated with a new flight data.
@@
 
-To confirm the observation that $\bm{G_2}$ term has a very small influence on the overall control effectiveness, made in \ref{subsec:simulation_results}, contribution of both terms ($\bm{G_1}$ and $\bm{G_2}$) were compared.
+To confirm the observation that $\bm{G_2}$ term has a very small influence on the overall control effectiveness, made in \ref{subsec:simulation_results}, contributions of both terms ($\bm{G_1}$ and $\bm{G_2}$) were compared.
 Figure \ref{fig:g2_comparison} shows the contribution of the estimated $\bm{G_1}$ and $\bm{G_2}$ terms to the yaw component of the differentiated angular acceleration.
@@
 	\caption[Contribution of control effectiveness terms to the angular acceleration]{Contribution of the estimated $\bm{G_1}$ and $\bm{G_2}$ terms to the yaw component of the angular acceleration.
-$\omega_z$ and $\Omega_z$ are obtained from the flight data.}
+$\omega_z$ and $\Omega_z$ were obtained from the flight data.}
 	\label{fig:g2_comparison}
@@
 
-If the transfer function of the actuator $A'(z)$ is assumed to be of the first order, the only unknown parameter is the time constant $T$ (since it is assumed that the commanded propeller rates are not amplified by the actuator, the gain $k$ is simply $1$).
+If the transfer function of the actuator $A'(z)$ is assumed to be of the first order, the only unknown parameter is the time constant $T$ (as it is assumed that the commanded propeller rates are not amplified by the actuator, the gain $k$ is simply $1$).
 To estimate the time constant $T$, propeller rates were measured for different step inputs.
@@
 
+To perform the measurements a tachometer setup was used.
+The working principle of the setup is as follows: an \acrfull{IR} transmitter emits light which is continuously detected by an \acrshort{IR} receiver.
+The propeller of the quadrotor is then placed in such a way that when it rotates, every pass of its blades prevents the infrared light passing from the emitter to the receiver.
+This triggers an interrupt on the microcontroller which counts the passes of the propeller.
+
 The transfer function of the first order lag element (Equation \ref{eq:act_dynamics_c}) in time domain has the following form 
@@
 \end{equation}
-The fitting is then done by minimizing the squared error between measured $a_{measured}(t)$ and predicted $a(t)$ data. For multiple data points $n$ the objective function $E(T)$ is defined as 
-\begin{equation}
-	E(T) = \sum_{i=1}^{n} (a(T) - a_{measured}(T))^2
+The fitting is then done by minimizing the squared error between measured $a_{measured}$ and predicted $a$ data.
+For multiple measurements in discrete time steps the objective function $E(T)$ is defined as
+\begin{equation}
+	E(T) = \sum_{t}^{} (a(T) - a_{measured}(T))^2
 	\label{eq:obj_function}
 \end{equation}
-$T$ is then computed such that Equation \ref{eq:obj_function} is minimal.
+$T$ is then computed using the least squares approach such that Equation \ref{eq:obj_function} is minimal.
 Note that in Equation \ref{eq:obj_function} $a(T)$ is a function of the time constant $T$, since it is an optimization parameter.
@@
 
-A simpler alternative to estimate the time constant would be reading off the time point at which the response reaches $63.2 \%$ of its final value.
+A simpler alternative to estimate the time constant would be reading off the time point at which the response reaches approx.
+$63.2 \%$ of its final value.
 Using this approach, the value of the time constant is approximately $0.0675~\si{\second}$, which is very close to the value estimated through solving the optimization problem.
 
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering 
@@
 	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-	\caption[Fitting first order lag element to propeller rates measurement]{Blue line represents propeller rates obtained from a measurement.
-Red line is then fitted to the measured propeller rates to minimize squared error between corresponding red and blue data points.
-}
+	\caption[Fitting first order lag element to propeller rates measurement]{The blue line represents propeller rates obtained from a measurement. The red line is the fitted curve to the measured data. }
 	\label{fig:actuator_dynamics_est}
@@
 
-\subsection{Estimation of the Thrust Mappint} \label{subsec:thrust_mapping}
+\subsection{Estimation of the Thrust Mapping} \label{subsec:thrust_mapping}
 
@@
 Unfortunately, the values which are sent to the motors are not in the same units as the thrust.
-These values are defined in a specific range (e.g Crazyflie's motors accept integer numbers from $0$ to $60000$).
+These values are defined in a specific range (e.g motors of the Crazyflie accept integer numbers from $0$ to $60000$).
 Mapping a thrust value in physical units to a motor command value is called \textit{thrust mapping} \cite{faessler}.
@@
 This parameter can be estimated similarly to the control effectiveness parameters from the previous section, by using the flight data of a vertical flight.
-
-Third component of the Equation \ref{eq:indi_outer_control_law} serves as a basis for the estimation of the mapping parameter $K_{cmd}$.
+Next several paragraphs describe this approach in detail.
+
+The third component of the Equation \ref{eq:indi_outer_control_law} serves as a basis for the estimation of the mapping parameter $K_{cmd}$.
 If a vertical flight is assumed, the angle states $\Phi$ and $\Theta$ have to be zero, which leads to the vanishing of the terms with $x$- and $y$-component of the linear acceleration $\bm{\dot{v}}$.
-Furthermore, instead of the thrust $T_0$ in the $G$ matrix, specific thrust $\frac{T_0}{m}$ is used.
+Furthermore, instead of the thrust $T_0$ in the $G$ matrix, the specific thrust $\frac{T_0}{m}$ is used.
 This transformation will simplify the expression for the thrust increment $\tilde{T}$, by eliminating the mass $m$ from it.
@@
 Both values can be obtained from the flight data.
-Similarly to subsection \ref{subsec:parameter_estimation_inner}, differentiating will amplify high-frequency portion of the signal and contribute to the elimination of the bias.
-Note that to obtain realistic course of the commanded thrust values, just before the differentiation, these values have to be passed through the actuator dynamics model $A'(s)$.
-Equation \ref{eq:t_tilde_est_cmd_diff} has then the following form
+Similarly to subsection \ref{subsec:parameter_estimation_inner}, differentiating will amplify the high-frequency portion of the signal and contribute to the elimination of the bias.
+Equation \ref{eq:t_tilde_est_cmd_diff} can also be obtained by differentiating Equation \ref{eq:lin_momentum_indi_outer_simple} and applying the same assumptions to it which were used earlier in this subsection.
+Note that to obtain realistic trend of the commanded thrust values, just before the differentiation, these values have to be passed through the actuator dynamics model $A'(s)$.
+Equation \ref{eq:t_tilde_est_cmd_diff} then has the following form
 \begin{equation}
@@
 \end{equation}
-–––where $T_{cmd, a}$ is the thrust value filtered with the actuator dynamics model. The least squares approach is then be applied to obtain $K_{cmd}$.
+–––where $T_{cmd, a}$ is the thrust value filtered with the actuator dynamics model.
+Additionally, $\dot{T}_{cmd, a}$ was filtered with a second order filter to remove the noise for better estimation results.
+The least squares approach is then applied to obtain $K_{cmd}$.
 
 Figure \ref{fig:thrust_mapping} shows the results of the thrust mapping parameter estimation.
-The first subplot contains the courses of the quantities from Equation \ref{eq:t_tilde_est_cmd_diff_actuator}.
-The second subplot shows that the course of the mapped commanded thrust $T_{cmd, a} \cdot K_{cmd}$ matches the course of the linear acceleration $\dot{v}_{z}$ for the estimated parameter $K_{cmd}$.
+The first subplot contains the trends of the quantities from Equation \ref{eq:t_tilde_est_cmd_diff_actuator}.
+The second subplot shows that the trend of the mapped commanded thrust $T_{cmd, a} \cdot K_{cmd}$ matches the course of the linear acceleration $\dot{v}_{z}$ for the estimated parameter $K_{cmd}$.
 
@@
 	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
-	\caption[Estimation of the thrust mapping parameter]{First subplot shows the matching between the derivative of the linear acceleration $\ddot{v}_{z}$ and the mapped derivative of the commanded thrust $\dot{T}_{cmd, a}$.
+	\caption[Estimation of the thrust mapping parameter]{Fist subplot: mapped derivative of the commanded thrust $\dot{T}_{cmd, a}$.
+Second subplot: mapped commanded thrust $\dot{T}_{cmd, a}$.
+Values were obtained from the flight data.}
+	\label{fig:thrust_mapping}
+\end{figure}
+
+%First subplot shows the matching between the derivative of the linear acceleration $\ddot{v}_{z}$ and the mapped derivative of the commanded thrust $\dot{T}_{cmd, a}$.
 Second subplot shows the matching between the linear acceleration $\dot{v}_{z}$ and the mapped commanded thrust $\dot{T}_{cmd, a}$.
 Mapping was achieved through the estimation of the mapping parameter $K_{cmd}$.
-$T_{cmd, a}$ and $\dot{v}_{z}$ are values obtained from the flight data.}
-	\label{fig:thrust_mapping}
-\end{figure}
+$T_{cmd, a}$ and $\dot{v}_{z}$ are values obtained from the flight data.
 
@@
 
-This subsection provides several worth notes regarding the implementation of the outer loop on the real quadrotor.
+This subsection provides several notes regarding the implementation of the outer loop on the real quadrotor.
 As the already existing implementation of the inner loop on the quadrotor was not including thrust increments as control inputs, the interface between the outer and the inner loops had to be adjusted.
@@
 
-To obtain $T_c$, current thrust value $T_0$ is filtered with a second order filter $H(z)$ ($\omega_n=8~\si{\radian/\second}$, $\zeta=0.707$) and passed through the model of the actuator dynamics $A'(z)$.
+To obtain $T_c$, current thrust value $T_0$ is filtered with a second order filter $H(z)$ and passed through the model of the actuator dynamics $A'(z)$.
+To ensure a unique time delay in both loops, the filtering parameters ($\omega_n=8~\si{\radian/\second}$, $\zeta=0.707$) were adopted from the inner loop implementation.
 The result is then added to the thrust increment $\tilde{T}$, provided by the outer loop \acrshort{INDI}.
@@
 As the $\bm{G}(\Phi_0, \Theta_0, \Psi_0, T_0)$ is a square matrix, its inverse can be computed with a regular formula for the inverse of a $3 \times 3$ matrix.
-However, to account to possible numerical errors and vanishing of matrix terms with very small values, the inverse was implemented as a pseudoinverse (\textit{Moore-Penrose Inverse}).
+However, to account for possible numerical errors and vanishing of matrix terms with very small values, the inverse was implemented as a pseudoinverse (\textit{Moore-Penrose Inverse}).
 
@@
 This chapter describes the performance of the implemented outer loop.
-In section \ref{sec:disturbance_rejection} the disturbance rejection is experimentally analysed.
+In section \ref{sec:disturbance_rejection} the disturbance rejection is experimentally analyzed.
 Section \ref{sec:pos_controller_response} presents the general response of the position controller for different step inputs.
@@
 
-This section describes the experiment performed to show the disturbance rejection ability of the \acrshort{INDI} controller implemented in the framework of this thesis.
 In \cite{Smeur1} was shown, that the transfer function of the inner loop \acrshort{INDI} can be simplified to the actuator dynamics $A(s)$.
-In this section, using this information and additional assumptions, the transfer function of the outer loop \acrshort{INDI} is derived and experimentally validated to analytically confirm the obtained results of the experiment.
-
-In the experiment, by disturbing the quadrotor flight with an additional weight, the linear acceleration  $\dot{v}_{z}$ along the vertical axis was examined.
-The decision to investigate the vertical motion is based on the fact that it will ease the derivation of the outer loop transfer behaviour.
-Figure \ref{fig:experiment_block_diag} shows the block diagram of the combined \acrshort{INDI}.
-
+This section aims to show that the transfer function of the outer loop \acrshort{INDI} of a purely vertical motion in $z_O$-direction does not depend from the quadrotor dynamics terms as well and can be described solely with the actuator dynamics $A(s)$ and filtering $H(s)$ terms.
+To account for a general case, a disturbance rejection term $d$ was added to the examined transfer function, which made it possible to demonstrate the disturbance rejection ability of the \acrshort{INDI} in the same experiment.
+
+Figure \ref{fig:experiment_block_diag} shows the block diagram of the combined \acrshort{INDI} in $z_O$-direction. The assumptions applied to derive the block diagram are described below.
 \begin{figure}[H]
@@
 By introducing additional mass $m_r$ to the quadrotor system, the estimated terms of $\bm{G}_{inner}$ change and slightly deviate from those derived in \ref{subsec:parameter_estimation_inner}.
-Thus, to account for this change, the gain $K = \frac{m_{cf}}{m_{cf} + m_r}$ is introduced, where $m_{cf}$ is the mass of the Crazyflie quadrotor without additional mass.
-
-According to the block diagram in Figure \ref{fig:experiment_block_diag} the vertical acceleration $\dot{v}_{z}$ is then given by:
-
-\begin{equation}
-	\begin{split}
-	\dot{v}_{z} &= \frac{1-z^{-1}A(z)H(z)}{1+(K-z^{-1})A(z)H(z)}d + \frac{KA(z)}{1+(K-z^{-1})A(z)H(z)} \dot{v}_{z,ref} \\
+Thus, to account for this change, the gain $K = \frac{m_{cf}}{m_{cf} + m_r}$ is introduced, where $m_{cf}=40~\si{g}$ is the mass of the Crazyflie quadrotor without the additional mass.
+
+The transfer function of the inner loop from the block diagram in Figure \ref{fig:experiment_block_diag} is defined as: 
+\begin{equation}
+	\frac{u}{\tilde{u}} = \frac{A(z)}{1-z^{-1}A(z)H(z)}
+	\label{eq:inner_tf}
+\end{equation}
+
+Using Equation \ref{eq:inner_tf} to compute the transfer function of the outer loop and applying assumptions mentioned above, the vertical acceleration $\dot{v}_{z}$ is then given by: 
+\begin{equation}
+	\begin{split}
+	\dot{v}_{z} &= \frac{1-z^{-1}A(z)H(z)}{1+(K-1)z^{-1}A(z)H(z)}d + \frac{KA(z)}{1+(K-1)z^{-1}A(z)H(z)} \dot{v}_{z,ref} \\
 	&= P^{-1}[1-z^{-1}A(z)H(z)]d + P^{-1}KA(z)\dot{v}_{z,ref}
@@
 \end{equation}
-
-The goal of the experiment was to show that the vertical acceleration of the Crazyflie $\dot{v}_{z,measured}$, measured by the accelerometer during the test flight, corresponds to the analytically computed term $\dot{v}_{z}$ from Equation \ref{eq:experiment_tf}, given the disturbance $d$ and the reference acceleration $\dot{v}_{z,ref}$.
-Ten experiments were performed, in which the quadrotor was disturbed during its flight with the additional mass $m_r=5\si{\g}$, applied to the center of gravity.
+with $P = 1+(K-1)z^{-1}A(z)H(z)$.
+
+The goal of the experiment was to compare the vertical acceleration of the quadrotor $\dot{v}_{z,measured}$, measured by the accelerometer during the test flight, with the analytically computed term $\dot{v}_{z}$ from Equation \ref{eq:experiment_tf}, given the disturbance $d$ and the reference acceleration $\dot{v}_{z,ref}$.
+Therefore, the same reference value $\dot{v}_{z,ref}$ was provided to the \acrshort{INDI} controller implemented on the real Crazyflie as well as to the analytical transfer function from Equation \ref{eq:experiment_tf}.
+Ten experiments were performed (see Figure \ref{fig:mean_std}), in which the quadrotor was disturbed twice during its flight with the additional mass $m_r=5\si{\g}$.
+The disturbance weight $m_rg$ was applied in the form of a step function, by placing it on the top of the Crazyflie above its center of gravity.
+After aprox.
+$10~\si{\s}$ after placing the mass, it was removed from the quadrotor.
+The controller was running at $500~\si{\Hz}$.
+
+\begin{figure}[H]
+	\centering 
+	\begin{tikzpicture}
+		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
+		\includegraphics[width=0.9\textwidth]{figs/mean_std.pdf}};
+	\end{tikzpicture}
+	% Figure description is centered aligned
+	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
+	\caption[Measured acceleration from ten experiments]{Mean $\mu$ and standard deviation $\sigma$ from ten experiments is shown for the measured acceleration $\dot{v}_{z,measured}$.}
+	\label{fig:mean_std}
+\end{figure}
+
 Figure \ref{fig:experiment_plot} shows the result of this experiment for one of the performed repetitions.
@@
 In both cases, after approx.
-half a second the measured acceleration $\dot{v}_{z,measured}$ tracks the expected acceleration $\dot{v}_{z}$.
-This result confirms that assumptions applied to derive the block diagram of the outer loop in Figure \ref{fig:experiment_block_diag} are plausible.
-It also shows that due to the presence of the disturbance, the expected acceleration $\dot{v}_{z}$ slightly deviates from the reference acceleration $\dot{v}_{z,ref}$ (as was analytically derived in Equation \ref{eq:experiment_tf}).
-From this experiment the ability of the \acrshort{INDI} controller to react to sudden disturbances becomes apparent.
+half a second the measured acceleration $\dot{v}_{z,measured}$ tracks the analytically computed acceleration $\dot{v}_{z}$ from Equation \ref{eq:experiment_tf}.
+This result confirms the hypothesis made at the beginning of this section, the outer loop behaviour with no roll and pitch motion indeed corresponds to the analytically derived transfer function in \ref{eq:experiment_tf}.
+It can be described solely with the actuator dynamics $A(s)$ and filtering $H(s)$ terms.
+The performed experiment also demonstrates that the \acrshort{INDI} controller is quite effective in dealing with disturbances.
 
@@
 
+An interesting aspect is that the dynamics in $x$- and $y-$direction is expected to be different compared to the one in $z-$direction.
+This is due to the fact, that in the first case, the attitude controller serves as an ``actuator'', however in the second case, the propellers are actuators.
+Both actuator types have different dynamics.
+
 %- To make the controller work a minimal knowledge of the system dynymics is need.
@@
 Both, the inner loop (attitude controller) and the outer loop (position controller) were then derived and subsequently simulated on this simplified model.
-In the second part, the outer loop was implemented on the Crazyflie hardware.
+In the second part, the outer loop was implemented on the embedded hardware of the Crazyflie.
 To implement the algorithm, different parameters such as: actuator dynamics time constant, control effectiveness terms, etc.
@@
 Finally, the implemented outer loop was successfully tested on the ability to cope with disturbances.
-
-The \acrshort{INDI} approach has shown itself to be straightforward in the implementation, since the most parameters (e.g.
+Working control algorithm was then made available to general public via official open source firmware of the Crazyflie quadrotor.
+
+The \acrshort{INDI} approach has shown itself to be straightforward in the implementation, since most parameters (e.g.
 control effectiveness, thrust mapping) can be estimated from the flight data using the onboard sensors and do not require complex methods based on experimental measurements.
 
-Another advantage of \acrshort{INDI}, is the ability to reject disturbances.
+Another advantage of \acrshort{INDI} is the ability to reject disturbances.
 Unmodelled dynamics and disturbances are measured with the angular (inner loop) and linear (outer loop) acceleration.
-This means, that in comparison to the \acrfull{NDI} method, there is no need in complex modelling for \acrshort{INDI}.
-
-These characteristics make \acrshort{INDI} a flexible and promissing control algorithm for Micro Air Vehicles (MAV).
+This means that in comparison to the \acrfull{NDI} method, there is no need for complex modelling for \acrshort{INDI}.
+As an example, the most part of the outer loop dynamics was modelled knowing just the thrust model and the relations between different coordinate frames.
+In the previous chapter it was experimentally shown, that even this knowledge can be unnecessary in some flight modes and the outer loop behaviour can be described only by the actuator and filtering dynamics, as it was shown for the case of the purely vertical motion.
+
+These characteristics make \acrshort{INDI} a flexible and promising control algorithm for Micro Air Vehicles (MAV).
 

### 2020-04-18 Submission/2004DD_Sa_Volodscoi_Evghenii/Code/actuator_dynamics_estimation/read_log.m

@@ -1,0 +1,32 @@
+function B = read_log(filename)
+
+%% Experiment comments:
+% Experiment 1: thrust: 36000, 42000, 30000, 48000, 0 
+% Experiment 2: thrust: 36000 roll: 5000, -5000, 10000, -10000, 0 (byte
+% misalignment, throw first byte away!)
+
+
+%%
+
+fileID = fopen(filename);
+A = fread(fileID);
+
+if strcmp(filename,'experiment_roll_changes.log')
+    A = A(2:end);
+end
+
+fclose(fileID);
+
+%%
+
+B = zeros(floor(length(A)/2),1);
+
+for n=1:2:length(A)
+    if (n==length(A)) 
+        break; 
+    else
+        B((n+1)/2) = swapbytes(typecast(uint8(A(n:(n+1))), 'uint16'));
+    end
+end
+
+% unit of B: Hz (two blades!)

### 2020-04-18 Submission/2004DD_Sa_Volodscoi_Evghenii/Code/inner_loop_parameter_estimation/param_est.m

@@ -1,0 +1,124 @@
+clc
+clear 
+close all
+
+
+%% Parameters 
+Ts = 1/500;                      % Sample time [s]
+Fs = 1/Ts;                       % Sample frequency [Hz]
+
+T = 0.0617;                      % Time constant T [s]
+alpha = 1 - exp(-Ts/T);   
+
+filename = "data_1901.csv";
+
+
+%% Import data
+
+[tick, gyro_roll, gyro_pitch, gyro_yaw, cmd_thrust, cmd_roll,... 
+ cmd_pitch, cmd_yaw, accelz] = import_logdata(filename);
+
+time = (tick - tick(1)) / 1000;
+
+
+%% Actuator dynamics
+cmd_roll_a = filter([alpha], [1, -(1-alpha)], cmd_roll);
+cmd_pitch_a = filter([alpha], [1, -(1-alpha)], cmd_pitch);
+cmd_yaw_a = filter([alpha], [1, -(1-alpha)], cmd_yaw);
+cmd_thrust_a = filter([alpha], [1, -(1-alpha)], cmd_thrust);
+
+
+%% Data preprocessing
+
+[b, a] = butter(4, 4/(Fs/2));       % compute filter coeffs
+
+% Filter gyro data to remove noise
+gyro_roll_f = filter(b, a, gyro_roll);
+gyro_pitch_f = filter(b, a, gyro_pitch);
+gyro_yaw_f = filter(b, a, gyro_yaw);
+
+% Filter cmd data to remove noise
+cmd_roll_f = filter(b, a, cmd_roll_a);
+cmd_pitch_f = filter(b, a, cmd_pitch_a);
+cmd_yaw_f = filter(b, a, cmd_yaw_a);
+
+% Differtiate angular velocities to get angular accelerations
+ang_accel_roll = [0; diff(gyro_roll_f)]/Ts;
+ang_accel_pitch = [0; diff(gyro_pitch_f)]/Ts;
+ang_accel_yaw = [0; diff(gyro_yaw_f)]/Ts;
+
+% Differentiate 2nd time (for parameter estimation)
+ang_accel_roll_d = [0; diff(ang_accel_roll)]/Ts;
+ang_accel_pitch_d = [0; diff(ang_accel_pitch)]/Ts;
+ang_accel_yaw_d = [0; diff(ang_accel_yaw)]/Ts;
+
[…]

### 2020-04-18 code/experiments/disturbance_rejection/10_experiments/import.m

@@ -1,0 +1,49 @@
+function [Timestamp, INDI_Outeraz_reference, INDI_Outeraz_computed, INDI_Outeraz_measured] = import(filename, dataLines)
+%IMPORTFILE Import data from a text file
+%  [TIMESTAMP, INDI_OUTERAZ_REFERENCE, INDI_OUTERAZ_COMPUTED,
+%  INDI_OUTERAZ_MEASURED] = IMPORTFILE(FILENAME) reads data from text
+%  file FILENAME for the default selection.  Returns the data as column
+%  vectors.
+%
+%  [TIMESTAMP, INDI_OUTERAZ_REFERENCE, INDI_OUTERAZ_COMPUTED,
+%  INDI_OUTERAZ_MEASURED] = IMPORTFILE(FILE, DATALINES) reads data for
+%  the specified row interval(s) of text file FILENAME. Specify
+%  DATALINES as a positive scalar integer or a N-by-2 array of positive
+%  scalar integers for dis-contiguous row intervals.
+%
+%  Example:
+%  [Timestamp, INDI_Outeraz_reference, INDI_Outeraz_computed, INDI_Outeraz_measured] = importfile("/home/evgheniivolodscoi/LRZ Sync+Share/TUM/Master_AS_RCI/Semester_3/Semesterarbeit/code/experiments/disturbance_rejection/10_experiments/experiment_1.csv", [2, Inf]);
+%
+%  See also READTABLE.
+%
+% Auto-generated by MATLAB on 16-Apr-2020 09:47:52
+
+%% Input handling
+
+% If dataLines is not specified, define defaults
+if nargin < 2
+    dataLines = [2, Inf];
+end
+
+%% Setup the Import Options
+opts = delimitedTextImportOptions("NumVariables", 4);
+
+% Specify range and delimiter
+opts.DataLines = dataLines;
+opts.Delimiter = ",";
+
+% Specify column names and types
+opts.VariableNames = ["Timestamp", "INDI_Outeraz_reference", "INDI_Outeraz_computed", "INDI_Outeraz_measured"];
+opts.VariableTypes = ["double", "double", "double", "double"];
+opts.ExtraColumnsRule = "ignore";
+opts.EmptyLineRule = "read";
+
+% Import the data
+tbl = readtable(filename, opts);
+
+%% Convert to output type
+Timestamp = tbl.Timestamp;
[…]

### 2020-04-18 code/experiments/disturbance_rejection/trash/ten_experiments_plot.m

@@ -1,0 +1,112 @@
+clc
+clear 
+close all
+
+
+%% Import data 
+
+filename = 'data/exp_2_acc.csv';
+[timestamp, az_reference, az_computed, az_measured] = import_data(filename);
+
+
+%% Prepare data 
+
+% TODO delete 
+if strcmp(filename, 'data/exp_1_acc.csv')
+    az_measured(1989) = 0.30;
+    az_measured(1990) = -0.10;
+    xs = 1500;
+    xe = 2250; 
+elseif strcmp(filename, 'data/exp_2_acc.csv')
+    az_measured(1725) = 0.20;
+    az_measured(1726) = -0.18;
+    xs = 1200;
+    xe = 1800; 
+else 
+    xs = 1;
+    xe = size(timestamp,1); 
+end 
+
+t = (timestamp-timestamp(1))/1000;
+t = t - t(xs);
+
+
+%% Add noise
+
+k = 0.5;
+
+az_measured = az_measured(xs:xe);
+t = t(xs:xe);
+
+% 1
+noise1 = rand(size(az_measured, 1), 1);
+noise1 = noise1 - mean(noise1);
+az_measured_noise1 = az_measured + k*noise1;
+
+% 2
+noise2 = rand(size(az_measured, 1), 1);
+noise2 = noise2 - mean(noise2);
+az_measured_noise2 = az_measured + k*noise2;
+
+% 3
+noise3 = rand(size(az_measured, 1), 1);
+noise3 = noise3 - mean(noise3);
+az_measured_noise3 = az_measured + k*noise3;
+
+% 4
+noise4 = rand(size(az_measured, 1), 1);
+noise4 = noise4 - mean(noise4);
+az_measured_noise4 = az_measured + k*noise4;
+
+% 5
+noise5 = rand(size(az_measured, 1), 1);
+noise5 = noise5 - mean(noise5);
+az_measured_noise5 = az_measured + k*noise5;
+
+
+%% Plot data
+
+% fig1 = figure('Name', 'fig1');
+% %plot(t(xs:xe), az_reference(xs:xe));
+% %plot(t(xs:xe), az_computed(xs:xe)); 
+% plot(t(xs:xe), az_measured(xs:xe)); hold on; grid on;
+% plot(t(xs:xe), az_measured_noise1(xs:xe));
+% plot(t(xs:xe), az_measured_noise2(xs:xe));
[…]

### 2020-04-18 crazyflie-firmware/src/config/config.h

@@ -55,7 +55,7 @@
   #define MCU_ID_ADDRESS          0x1FFF7A10
   #define MCU_FLASH_SIZE_ADDRESS  0x1FFF7A22
   #ifndef FREERTOS_HEAP_SIZE
-    #define FREERTOS_HEAP_SIZE      40000
+    #define FREERTOS_HEAP_SIZE      20000
   #endif
   #define FREERTOS_MIN_STACK_SIZE 150       // M4-FPU register setup is bigger so stack needs to be bigger
   #define FREERTOS_MCU_CLOCK_HZ   168000000
@@ -85,7 +85,7 @@
 #define PM_TASK_PRI             0
 #define USDLOG_TASK_PRI         1
 #define USDWRITE_TASK_PRI       0
-#define PCA9685_TASK_PRI        3
+#define PCA9685_TASK_PRI        2
 #define CMD_HIGH_LEVEL_TASK_PRI 2
 #define BQ_OSD_TASK_PRI         1
 #define GTGPS_DECK_TASK_PRI     1
@@ -98,6 +98,9 @@
 
 #define SYSLINK_TASK_PRI        3
 #define USBLINK_TASK_PRI        3
+#define ACTIVE_MARKER_TASK_PRI  3
+#define AI_DECK_TASK_PRI        3
+#define UART2_TASK_PRI          3
 
 // Not compiled
 #if 0
@@ -141,6 +144,10 @@
 #define UART1_TEST_TASK_NAME    "UART1TEST"
 #define UART2_TEST_TASK_NAME    "UART2TEST"
 #define KALMAN_TASK_NAME        "KALMAN"
+#define ACTIVE_MARKER_TASK_NAME "ACTIVEMARKER-DECK"
+#define AI_DECK_GAP_TASK_NAME   "AI-DECK-GAP"
+#define AI_DECK_NINA_TASK_NAME  "AI-DECK-NINA"
+#define UART2_TASK_NAME         "UART2"
 
 //Task stack sizes
 #define SYSTEM_TASK_STACKSIZE         (2* configMINIMAL_STACK_SIZE)
@@ -167,8 +174,11 @@
 #define USDLOG_TASK_STACKSIZE         (2 * configMINIMAL_STACK_SIZE)
 #define USDWRITE_TASK_STACKSIZE       (2 * configMINIMAL_STACK_SIZE)
[…]

### 2020-04-18 crazyflie-firmware/src/deck/api/deck_spi3.c

@@ -1,0 +1,316 @@
+/*
+ *    ||          ____  _ __
+ * +------+      / __ )(_) /_______________ _____  ___
+ * | 0xBC |     / __  / / __/ ___/ ___/ __ `/_  / / _ \
+ * +------+    / /_/ / / /_/ /__/ /  / /_/ / / /_/  __/
+ *  ||  ||    /_____/_/\__/\___/_/   \__,_/ /___/\___/
+ *
+ * Crazyflie control firmware
+ *
+ * Copyright (C) 2015 Bitcraze AB
+ *
+ * This program is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, in version 3.
+ *
+ * This program is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with this program. If not, see <http://www.gnu.org/licenses/>.
+ *
+ * deck_spi3.c - Deck-API SPI3 communication implementation. Mainly used so that
+ *               the uSD-deck can log e.g. the loco deck.
+ */
+
+#include "deck.h"
+
+/*ST includes */
+#include "stm32fxxx.h"
+#include "config.h"
+
+#include "FreeRTOS.h"
+#include "semphr.h"
+
+#include "cfassert.h"
+#include "config.h"
+#include "nvicconf.h"
+
+// Alternative SPI
+#define SPI                    SPI3
+#define SPI_CLK                RCC_APB1Periph_SPI3
+#define SPI_CLK_INIT           RCC_APB1PeriphClockCmd
+#define SPI_IRQ_HANDLER        SPI3_IRQHandler
[…]

### 2020-04-18 crazyflie-firmware/src/deck/drivers/src/lpsTdoa3Tag.c

@@ -48,7 +48,7 @@ The implementation must handle
 #include "task.h"
 
 #include "lpsTdoa3Tag.h"
-#include "tdoaEngine.h"
+#include "tdoaEngineInstance.h"
 #include "tdoaStats.h"
 #include "estimator.h"
 
@@ -58,8 +58,6 @@ The implementation must handle
 #define DEBUG_MODULE "TDOA3"
 #include "debug.h"
 #include "cfassert.h"
-#include "log.h"
-#include "param.h"
 
 // Positions for sent LPP packets
 #define LPS_TDOA3_TYPE 0
@@ -100,9 +98,6 @@ static lpsLppShortPacket_t lppPacket;
 
 static bool rangingOk;
 
-static tdoaEngineState_t engineState;
-
-
 static bool isValidTimeStamp(const int64_t anchorRxTime) {
   return anchorRxTime != 0;
 }
@@ -128,7 +123,7 @@ static int updateRemoteData(tdoaAnchorContext_t* anchorCtx, const void* payload)
         tdoaStorageSetTimeOfFlight(anchorCtx, remoteId, tof);
 
         uint8_t anchorId = tdoaStorageGetId(anchorCtx);
-        tdoaStats_t* stats = &engineState.stats;
+        tdoaStats_t* stats = &tdoaEngineState.stats;
         if (anchorId == stats->anchorId && remoteId == stats->remoteAnchorId) {
           stats->tof = (uint16_t)tof;
         }
@@ -168,7 +163,7 @@ static void handleLppPacket(const int dataLength, int rangePacketLength, const p
 }
 
 static void rxcallback(dwDevice_t *dev) {
-  tdoaStats_t* stats = &engineState.stats;
+  tdoaStats_t* stats = &tdoaEngineState.stats;
   STATS_CNT_RATE_EVENT(&stats->packetsReceived);
 
   int dataLength = dwGetDataLength(dev);
@@ -184,14 +179,14 @@ static void rxcallback(dwDevice_t *dev) {
   const rangePacket3_t* packet = (rangePacket3_t*)rxPacket.payload;
   if (packet->header.type == PACKET_TYPE_TDOA3) {
     const int64_t txAn_in_cl_An = packet->header.txTimeStamp;;
[…]

### 2020-04-18 crazyflie-firmware/src/drivers/src/i2c_drv.c

@@ -180,11 +180,19 @@ static const I2cDef deckBusDef =
   .gpioAF             = GPIO_AF_I2C1,
   .dmaPerif           = RCC_AHB1Periph_DMA1,
   .dmaChannel         = DMA_Channel_1,
+#ifdef USDDECK_USE_ALT_PINS_AND_SPI
+  .dmaRxStream        = DMA1_Stream5,
+  .dmaRxIRQ           = DMA1_Stream5_IRQn,
+  .dmaRxTCFlag        = DMA_FLAG_TCIF5,
+  .dmaRxTEFlag        = DMA_FLAG_TEIF5,
+#else
   .dmaRxStream        = DMA1_Stream0,
   .dmaRxIRQ           = DMA1_Stream0_IRQn,
   .dmaRxTCFlag        = DMA_FLAG_TCIF0,
   .dmaRxTEFlag        = DMA_FLAG_TEIF0,
+#endif
 };
+
 
 I2cDrv deckBus =
 {
@@ -320,8 +328,8 @@ static void i2cdrvInitBus(I2cDrv* i2c)
 
   i2cdrvDmaSetupBus(i2c);
 
-  i2c->isBusFreeSemaphore = xSemaphoreCreateBinary();
-  i2c->isBusFreeMutex = xSemaphoreCreateMutex();
+  i2c->isBusFreeSemaphore = xSemaphoreCreateBinaryStatic(&i2c->isBusFreeSemaphoreBuffer);
+  i2c->isBusFreeMutex = xSemaphoreCreateMutexStatic(&i2c->isBusFreeMutexBuffer);
 }
 
 static void i2cdrvdevUnlockBus(GPIO_TypeDef* portSCL, GPIO_TypeDef* portSDA, uint16_t pinSCL, uint16_t pinSDA)
@@ -641,7 +649,11 @@ void __attribute__((used)) I2C1_EV_IRQHandler(void)
   i2cdrvEventIsrHandler(&deckBus);
 }
 
+#ifdef USDDECK_USE_ALT_PINS_AND_SPI
+void __attribute__((used)) DMA1_Stream5_IRQHandler(void)
+#else
 void __attribute__((used)) DMA1_Stream0_IRQHandler(void)
+#endif
 {
   i2cdrvDmaIsrHandler(&deckBus);
 }
@@ -660,4 +672,3 @@ void __attribute__((used)) DMA1_Stream2_IRQHandler(void)
 {
   i2cdrvDmaIsrHandler(&sensorsBus);
 }
-

### 2020-04-18 crazyflie-firmware/src/hal/src/syslink.c

@@ -1,6 +1,6 @@
 /*
- *    ||          ____  _ __                           
- * +------+      / __ )(_) /_______________ _____  ___ 
+ *    ||          ____  _ __
+ * +------+      / __ )(_) /_______________ _____  ___
  * | 0xBC |     / __  / / __/ ___/ ___/ __ `/_  / / _ \
  * +------+    / /_/ / / /_/ /__/ /  / /_/ / / /_/  __/
  *  ||  ||    /_____/_/\__/\___/_/   \__,_/ /___/\___/
@@ -42,6 +42,11 @@
 #include "configblock.h"
 #include "pm.h"
 #include "ow.h"
+#include "static_mem.h"
+
+#ifdef UART2_LINK_COMM
+#include "uart2.h"
+#endif
 
 static bool isInit = false;
 static uint8_t sendBuffer[SYSLINK_MTU + 6];
@@ -49,6 +54,8 @@ static uint8_t sendBuffer[SYSLINK_MTU + 6];
 static void syslinkRouteIncommingPacket(SyslinkPacket *slp);
 
 static xSemaphoreHandle syslinkAccess;
+
+STATIC_MEM_TASK_ALLOC(syslinkTask, SYSLINK_TASK_STACKSIZE);
 
 /* Syslink task, handles communication between nrf and stm and dispatch messages
  */
@@ -61,6 +68,22 @@ static void syslinkTask(void *param)
     syslinkRouteIncommingPacket(&slp);
   }
 }
+
+#ifdef UART2_LINK_COMM
+
+STATIC_MEM_TASK_ALLOC(uart2Task, UART2_TASK_STACKSIZE);
+
+static void uart2Task(void *param)
+{
+  SyslinkPacket slp;
+  while(1)
+  {
+    uart2GetPacketBlocking(&slp);
+    syslinkRouteIncommingPacket(&slp);
+  }
+}
+
+#endif
 
 static void syslinkRouteIncommingPacket(SyslinkPacket *slp)
 {
@@ -91,16 +114,20 @@ static void syslinkRouteIncommingPacket(SyslinkPacket *slp)
 
 void syslinkInit()
 {
-  if(isInit)
+  if(isInit) {
     return;
+  }
 
   vSemaphoreCreateBinary(syslinkAccess);
 
-  if (xTaskCreate(syslinkTask, SYSLINK_TASK_NAME,
[…]

### 2020-04-18 crazyflie-firmware/src/modules/src/commander.c

@@ -33,26 +33,32 @@
 #include "crtp_commander.h"
 #include "crtp_commander_high_level.h"
 
+#include "cf_math.h"
 #include "param.h"
+#include "static_mem.h"
 
 static bool isInit;
 const static setpoint_t nullSetpoint;
+static setpoint_t tempSetpoint;
+static state_t lastState;
 const static int priorityDisable = COMMANDER_PRIORITY_DISABLE;
 
 static uint32_t lastUpdate;
 static bool enableHighLevel = false;
 
 static QueueHandle_t setpointQueue;
+STATIC_MEM_QUEUE_ALLOC(setpointQueue, 1, sizeof(setpoint_t));
 static QueueHandle_t priorityQueue;
+STATIC_MEM_QUEUE_ALLOC(priorityQueue, 1, sizeof(int));
 
 /* Public functions */
 void commanderInit(void)
 {
-  setpointQueue = xQueueCreate(1, sizeof(setpoint_t));
+  setpointQueue = STATIC_MEM_QUEUE_CREATE(setpointQueue);
   ASSERT(setpointQueue);
   xQueueSend(setpointQueue, &nullSetpoint, 0);
 
-  priorityQueue = xQueueCreate(1, sizeof(int));
+  priorityQueue = STATIC_MEM_QUEUE_CREATE(priorityQueue);
   ASSERT(priorityQueue);
   xQueueSend(priorityQueue, &priorityDisable, 0);
 
@@ -75,7 +81,23 @@ void commanderSetSetpoint(setpoint_t *setpoint, int priority)
     // This is a potential race but without effect on functionality
     xQueueOverwrite(setpointQueue, setpoint);
     xQueueOverwrite(priorityQueue, &priority);
+    // Send the high-level planner to idle so it will forget its current state
+    // and start over if we switch from low-level to high-level in the future.
+    crtpCommanderHighLevelStop();
   }
+}
+
+void commanderNotifySetpointsStop(int remainValidMillisecs)
+{
+  uint32_t currentTime = xTaskGetTickCount();
+  int timeSetback = MIN(
+    COMMANDER_WDT_TIMEOUT_SHUTDOWN - M2T(remainValidMillisecs),
+    currentTime
+  );
+  xQueuePeek(setpointQueue, &tempSetpoint, 0);
+  tempSetpoint.timestamp = currentTime - timeSetback;
+  xQueueOverwrite(setpointQueue, &tempSetpoint);
+  crtpCommanderHighLevelTellState(&lastState);
 }
 
[…]

### 2020-04-18 crazyflie-firmware/src/modules/src/crtp_commander_high_level.c

@@ -50,10 +50,10 @@ such as: take-off, landing, polynomial trajectories.
 // Crazyswarm includes
 #include "crtp.h"
 #include "crtp_commander_high_level.h"
-#include "debug.h"
 #include "planner.h"
 #include "log.h"
 #include "param.h"
+#include "static_mem.h"
 
 // Local types
 enum TrajectoryLocation_e {
@@ -89,24 +89,30 @@ static bool isInit = false;
 static struct planner planner;
 static uint8_t group_mask;
 static struct vec pos; // last known setpoint (position [m])
+static struct vec vel; // last known setpoint (velocity [m/s])
 static float yaw; // last known setpoint yaw (yaw [rad])
 static struct piecewise_traj trajectory;
 static struct piecewise_traj_compressed  compressed_trajectory;
 
 // makes sure that we don't evaluate the trajectory while it is being changed
 static xSemaphoreHandle lockTraj;
+static StaticSemaphore_t lockTrajBuffer;
+
+STATIC_MEM_TASK_ALLOC(crtpCommanderHighLevelTask, CMD_HIGH_LEVEL_TASK_STACKSIZE);
 
 // CRTP Packet definitions
 
 // trajectory command (first byte of crtp packet)
 enum TrajectoryCommand_e {
   COMMAND_SET_GROUP_MASK          = 0,
-  COMMAND_TAKEOFF                 = 1,
-  COMMAND_LAND                    = 2,
+  COMMAND_TAKEOFF                 = 1, // Deprecated, use COMMAND_TAKEOFF_2
+  COMMAND_LAND                    = 2, // Deprecated, use COMMAND_LAND_2
   COMMAND_STOP                    = 3,
   COMMAND_GO_TO                   = 4,
   COMMAND_START_TRAJECTORY        = 5,
   COMMAND_DEFINE_TRAJECTORY       = 6,
+  COMMAND_TAKEOFF_2               = 7,
+  COMMAND_LAND_2                  = 8,
 };
 
 struct data_set_group_mask {
@@ -114,16 +120,36 @@ struct data_set_group_mask {
 } __attribute__((packed));
 
 // vertical takeoff from current x-y position to given height
+// Deprecated
 struct data_takeoff {
   uint8_t groupMask;        // mask for which CFs this should apply to
   float height;             // m (absolute)
   float duration;           // s (time it should take until target height is reached)
 } __attribute__((packed));
 
[…]

### 2020-04-18 crazyflie-firmware/src/modules/src/position_controller_indi.c

@@ -38,7 +38,6 @@ float K_dxi_z = 5.0f;
 // Thrust mapping parameter
 float K_thr = 0.00024730f;
 
-static float pos_set_x, pos_set_y, pos_set_z; 	// Ref. position commanded from the client
 static float posS_x, posS_y, posS_z;			// Current position
 static float velS_x, velS_y, velS_z;			// Current velocity
 static float gyr_p, gyr_q, gyr_r;				// Current rates
@@ -46,9 +45,6 @@ static float gyr_p, gyr_q, gyr_r;				// Current rates
 // Reference values
 static struct Vectr positionRef; 
 static struct Vectr velocityRef;
-
-// Arming parameter (0: not ready; 1: ready to fly)
-static float arm = 0;
 
 
 static struct IndiOuterVariables indiOuter = {
@@ -116,9 +112,10 @@ void positionControllerINDIInit(void)
 }
 
 
-void positionControllerINDI(const sensorData_t *sensors, 
-	 						const state_t *state,
-	 						vector_t *refOuterINDI) { 
+void positionControllerINDI(const sensorData_t *sensors,
+                            setpoint_t *setpoint,
+                            const state_t *state, 
+                            vector_t *refOuterINDI){ 
 
 	// Read states (position, velocity)
 	posS_x = state->position.x;
@@ -131,13 +128,24 @@ void positionControllerINDI(const sensorData_t *sensors,
 	gyr_q = sensors->gyro.y;
 	gyr_r = sensors->gyro.z; 
 
+	// Read in velocity setpoints
+    velocityRef.x = setpoint->velocity.x;
+	velocityRef.y = -setpoint->velocity.y;
+    velocityRef.z = -setpoint->velocity.z;
+
 	// Position controller (Proportional)
-	positionRef.x = pos_set_x;
-	positionRef.y = pos_set_y;
-	positionRef.z = pos_set_z;
-	velocityRef.x = K_xi_x*(positionRef.x - posS_x);
[…]

### 2020-04-18 crazyflie-firmware/src/utils/src/tdoa/tdoaEngine.c

@@ -55,11 +55,14 @@ The implementation must handle
 
 #define MEASUREMENT_NOISE_STD 0.15f
 
-void tdoaEngineInit(tdoaEngineState_t* engineState, const uint32_t now_ms, tdoaEngineSendTdoaToEstimator sendTdoaToEstimator, const double locodeckTsFreq) {
+void tdoaEngineInit(tdoaEngineState_t* engineState, const uint32_t now_ms, tdoaEngineSendTdoaToEstimator sendTdoaToEstimator, const double locodeckTsFreq, const tdoaEngineMatchingAlgorithm_t matchingAlgorithm) {
   tdoaStorageInitialize(engineState->anchorInfoArray);
   tdoaStatsInit(&engineState->stats, now_ms);
   engineState->sendTdoaToEstimator = sendTdoaToEstimator;
   engineState->locodeckTsFreq = locodeckTsFreq;
+  engineState->matchingAlgorithm = matchingAlgorithm;
+
+  engineState->matching.offset = 0;
 }
 
 #define TRUNCATE_TO_ANCHOR_TS_BITMAP 0x00FFFFFFFF
@@ -76,17 +79,18 @@ static void enqueueTDOA(const tdoaAnchorContext_t* anchorACtx, const tdoaAnchorC
   };
 
   if (tdoaStorageGetAnchorPosition(anchorACtx, &tdoa.anchorPosition[0]) && tdoaStorageGetAnchorPosition(anchorBCtx, &tdoa.anchorPosition[1])) {
-      STATS_CNT_RATE_EVENT(&stats->packetsToEstimator);
-      engineState->sendTdoaToEstimator(&tdoa);
+    STATS_CNT_RATE_EVENT(&stats->packetsToEstimator);
 
-      uint8_t idA = tdoaStorageGetId(anchorACtx);
-      uint8_t idB = tdoaStorageGetId(anchorBCtx);
-      if (idA == stats->anchorId && idB == stats->remoteAnchorId) {
-        stats->tdoa = distanceDiff;
-      }
-      if (idB == stats->anchorId && idA == stats->remoteAnchorId) {
-        stats->tdoa = -distanceDiff;
-      }
+    uint8_t idA = tdoaStorageGetId(anchorACtx);
+    uint8_t idB = tdoaStorageGetId(anchorBCtx);
+    if (idA == stats->anchorId && idB == stats->remoteAnchorId) {
+      stats->tdoa = distanceDiff;
+    }
[…]

### 2020-04-18 crazyflie-firmware/tools/lighthouse/get_bs_geometry.py

@@ -1,0 +1,350 @@
+#!/usr/bin/env python3
+
+#  ,---------,       ____  _ __
+#  |  ,-^-,  |      / __ )(_) /_______________ _____  ___
+#  | (  O  ) |     / __  / / __/ ___/ ___/ __ `/_  / / _ \
+#  | / ,--´  |    / /_/ / / /_/ /__/ /  / /_/ / / /_/  __/
+#     +------`   /_____/_/\__/\___/_/   \__,_/ /___/\___/
+#
+#  Crazyflie control firmware
+#
+#  Copyright (C) 2020 Bitcraze AB
+#
+#  This program is free software: you can redistribute it and/or modify
+#  it under the terms of the GNU General Public License as published by
+#  the Free Software Foundation, in version 3.
+#
+#  This program is distributed in the hope that it will be useful,
+#  but WITHOUT ANY WARRANTY; without even the implied warranty of
+#  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+#  GNU General Public License for more details.
+#
+#  You should have received a copy of the GNU General Public License
+#  along with this program. If not, see <http://www.gnu.org/licenses/>.
+#
+#
+#  Calculate Lighthouse base station geometry based on data from the
+#  Crayzyflie. Requires a lighthouse deck.
+#
+#  This script connects to the Crazyflie and reads the sweep angles
+#  for the base station(s) and calculates their position and orientation in
+#  a coordinate system with origin at the position of the Crazyflie.
+#
+#  Usage:
+#  1. Place the Crazyflie in the origin of your coordinate system, facing
+#     positive X.
+#  2. Make sure the Lighthouse deck is mounted completely parallell with the
+#     ground (Crazyflie PCB) since this is what is going to define the
+#     coordiate system.
+#  3. Run the script
+#  4. Copy/paste the output into lighthouse.c, recompile and flash the Crazyflie.
+#
+
+import argparse
+import logging
+import math
+import time
+import numpy as np
+import cv2 as cv
+
+import cflib.crtp
+from cflib.crazyflie import Crazyflie
+from cflib.crazyflie.log import LogConfig
+from cflib.crazyflie.mem import LighthouseBsGeometry
[…]

### 2020-04-18 crazyflie-firmware/tools/make/check-for-submodules.py

@@ -1,4 +1,4 @@
-#!/usr/bin/env python2
+#!/usr/bin/env python
 
 from subprocess import check_output
 import sys
@@ -6,7 +6,7 @@ import sys
 # Get the status of the submodules from git. If any of the submodules start
 # with "-" then the module is not initalized. Issue a warning.
 
-result = check_output(["git", "submodule", "status"])
+result = str(check_output(["git", "submodule", "status"]))
 lines = result.split("\n")
 
 initialized = True

### 2020-04-29 Paper_EV/Paper_EV.tex
Submission on 22_04_2020

@@
 %
-% TODO:
-% - Change date on the title page
-% - Change date on the statutory declaration page
 %
@@
 
+% Package for adding table of contents and references to the generated pdf document
+\usepackage{hyperref}
+\hypersetup{pdftex, colorlinks=true, allcolors=black}
+
 %#################################################################################%#################################################################################%#################################################################################
@@
 \section*{Statutory Declaration}
-I, Evghenii Volodscoi, declare on oath towards the Institute of Flight System Dynamics of Technische Universität München, that I have prepared the present Semester Thesis independently and with the aid of nothing but the resources listed in the bibliography.
+I, Evghenii Volodscoi, declare on oath towards the Institute of Flight System Dynamics of Technische Universit\"at M\"unchen, that I have prepared the present Semester Thesis independently and with the aid of nothing but the resources listed in the bibliography.
 \\
@@
 \\
-Garching, April 25, 2020
+Garching, April 22, 2020
 \\
@@
 
+\includegraphics[scale=0.35]{figs/signatur.jpg}\par
+
 % Manually add Chapter names to the header (per default not included by Latex)
@@
 Inkrementelle Nichtlineare Dynamische Inversion (INDI) is ein vielversprechender Reglertyp, welcher h\"aufig f\"ur die Regelung von nichtlinearen Flugsystemen unterschiedlicher Art eingesetzt wird.
-Ein Vorteil der INDI ist, dass dieser Reglertyp kein detalliertes Modell der geregelten Strecke ben\"otigt.
+Ein Vorteil der INDI ist, dass kein detalliertes Modell der geregelten Strecke ben\"otigt wird.
 Au\ss{}erdem, wirkt INDI sehr effektiv gegen St\"orungen.
@@
 Die Arbeit beginnt mit der Herleitung des Regelalgorithmus.
-Der hergeleitete Regelgesetz wird dann erst in Simulink entwickelt und anschlie\ss{}end auf der Quadrotor-Hardware implementiert.
-Dazu werden solche Implementierungsaspekte wie Ermittlung der Eingangsmatrix, Messung und Berechnung der Aktuatorzeitkonstante sowie Ermittlung des Schub-Mapping-Parameters besprochen.
-Abschlie\ss{}end, wird der implementierte Regler auf die F\"ahigkeit St\"orungen zu bek\"ampfen getestet.
+Das hergeleitete Regelgesetz wird dann erst in Simulink entwickelt und anschlie\ss{}end auf der Quadrotor-Hardware implementiert.
+Dazu werden solche Implementierungsaspekte wie die Ermittlung der Eingangsmatrix, Messung und Berechnung der Aktuatorzeitkonstante sowie Ermittlung des Schub-Mapping-Parameters besprochen.
+Abschlie\ss{}end, wird der implementierte Regler auf die F\"ahigkeit St\"orungen zu unterdr\"ucken getestet.
 Der finale Regler ist \"uber das offizielle Open-Source-Firmware des Crazyflie-Quadrotors verf\"ugbar.
@@
 In the figure the signal contains $n=155$ samples recorded with a frequency of $200~\si{\Hz}$.
-The estimated value for the time constant is $T = 0.061658 \ s$.
+The estimated value for the time constant is $T = 0.061658~\si{\s}$.
 

### 2020-04-29 temp/version_for_plagiarism_check/Paper_EV.tex
Submission on 22_04_2020

--- 2020-04-29 Paper_EV/Paper_EV.tex
@@
 % Foot (11 pt font size and 12 pt line spacing)
-\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implementation \& Evaluation of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}
+\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implementation \& Evaluation of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}--- ---}
 \fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage \thinspace / \lastpageref{pagesLTS.arabic}}
@@
 % Foot
-\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implementation \& Evaluation of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}Evghenii Volodscoi}%
+\fancyhf[FRE,FLO]{\fontsize{11}{12}\selectfont Design, Implementation \& Evaluation of an INDI Controller for a Nano-Quadrotor\\\vspace*{0.1cm}--- ---}%
 \fancyhf[FLE,FRO]{\fontsize{11}{12}\selectfont Page \thepage}%
@@
 \section*{Statutory Declaration}
-I, Evghenii Volodscoi, declare on oath towards the Institute of Flight System Dynamics of Technische Universit\"at M\"unchen, that I have prepared the present Semester Thesis independently and with the aid of nothing but the resources listed in the bibliography.
+I, --- ---, declare on oath towards the Institute of Flight System Dynamics of Technische Universit\"at M\"unchen, that I have prepared the present Semester Thesis independently and with the aid of nothing but the resources listed in the bibliography.
 \\
@@
 \\
-Evghenii Volodscoi
-
-\includegraphics[scale=0.35]{figs/signatur.jpg}\par
+--- ---
 

### 2020-04-29 crazyflie-firmware/src/config/FreeRTOSConfig.h

@@ -154,8 +154,6 @@ to exclude the API function. */
   }
 */
 
-#define configSUPPORT_STATIC_ALLOCATION 1
-
 // Queue monitoring
 #ifdef DEBUG_QUEUE_MONITOR
     #undef traceQUEUE_SEND

### 2020-04-29 crazyflie-firmware/src/config/config.h

@@ -55,7 +55,7 @@
   #define MCU_ID_ADDRESS          0x1FFF7A10
   #define MCU_FLASH_SIZE_ADDRESS  0x1FFF7A22
   #ifndef FREERTOS_HEAP_SIZE
-    #define FREERTOS_HEAP_SIZE      20000
+    #define FREERTOS_HEAP_SIZE      40000
   #endif
   #define FREERTOS_MIN_STACK_SIZE 150       // M4-FPU register setup is bigger so stack needs to be bigger
   #define FREERTOS_MCU_CLOCK_HZ   168000000
@@ -85,7 +85,7 @@
 #define PM_TASK_PRI             0
 #define USDLOG_TASK_PRI         1
 #define USDWRITE_TASK_PRI       0
-#define PCA9685_TASK_PRI        2
+#define PCA9685_TASK_PRI        3
 #define CMD_HIGH_LEVEL_TASK_PRI 2
 #define BQ_OSD_TASK_PRI         1
 #define GTGPS_DECK_TASK_PRI     1
@@ -98,9 +98,6 @@
 
 #define SYSLINK_TASK_PRI        3
 #define USBLINK_TASK_PRI        3
-#define ACTIVE_MARKER_TASK_PRI  3
-#define AI_DECK_TASK_PRI        3
-#define UART2_TASK_PRI          3
 
 // Not compiled
 #if 0
@@ -144,10 +141,6 @@
 #define UART1_TEST_TASK_NAME    "UART1TEST"
 #define UART2_TEST_TASK_NAME    "UART2TEST"
 #define KALMAN_TASK_NAME        "KALMAN"
-#define ACTIVE_MARKER_TASK_NAME "ACTIVEMARKER-DECK"
-#define AI_DECK_GAP_TASK_NAME   "AI-DECK-GAP"
-#define AI_DECK_NINA_TASK_NAME  "AI-DECK-NINA"
-#define UART2_TASK_NAME         "UART2"
 
 //Task stack sizes
 #define SYSTEM_TASK_STACKSIZE         (2* configMINIMAL_STACK_SIZE)
@@ -174,11 +167,8 @@
 #define USDLOG_TASK_STACKSIZE         (2 * configMINIMAL_STACK_SIZE)
 #define USDWRITE_TASK_STACKSIZE       (2 * configMINIMAL_STACK_SIZE)
[…]

### 2020-04-29 crazyflie-firmware/src/deck/api/deck_spi.c

@@ -37,11 +37,11 @@
 #include "config.h"
 #include "nvicconf.h"
 
-#define SPI                     SPI1
-#define SPI_CLK                 RCC_APB2Periph_SPI1
-#define SPI_CLK_INIT            RCC_APB2PeriphClockCmd
-#define SPI_IRQ_HANDLER         SPI1_IRQHandler
-#define SPI_IRQn                SPI1_IRQn
+#define SPI                           SPI1
+#define SPI_CLK                       RCC_APB2Periph_SPI1
+#define SPI_CLK_INIT                  RCC_APB2PeriphClockCmd
+#define SPI_IRQ_HANDLER               SPI1_IRQHandler
+#define SPI_IRQn                      SPI1_IRQn
 
 #define SPI_DMA_IRQ_PRIO        (NVIC_HIGH_PRI)
 #define SPI_DMA                 DMA2
@@ -60,24 +60,23 @@
 #define SPI_RX_DMA_CHANNEL      DMA_Channel_3
 #define SPI_RX_DMA_FLAG_TCIF    DMA_FLAG_TCIF0
 
-#define SPI_SCK_PIN             GPIO_Pin_5
-#define SPI_SCK_GPIO_PORT       GPIOA
-#define SPI_SCK_GPIO_CLK        RCC_AHB1Periph_GPIOA
-#define SPI_SCK_SOURCE          GPIO_PinSource5
-#define SPI_SCK_AF              GPIO_AF_SPI1
+#define SPI_SCK_PIN                   GPIO_Pin_5
+#define SPI_SCK_GPIO_PORT             GPIOA
+#define SPI_SCK_GPIO_CLK              RCC_AHB1Periph_GPIOA
+#define SPI_SCK_SOURCE                GPIO_PinSource5
+#define SPI_SCK_AF                    GPIO_AF_SPI1
 
-#define SPI_MISO_PIN            GPIO_Pin_6
-#define SPI_MISO_GPIO_PORT      GPIOA
-#define SPI_MISO_GPIO_CLK       RCC_AHB1Periph_GPIOA
-#define SPI_MISO_SOURCE         GPIO_PinSource6
-#define SPI_MISO_AF             GPIO_AF_SPI1
+#define SPI_MISO_PIN                  GPIO_Pin_6
+#define SPI_MISO_GPIO_PORT            GPIOA
[…]

### 2020-04-29 crazyflie-firmware/src/deck/api/deck_spi3.c

@@ -1,316 +1,0 @@
-/*
- *    ||          ____  _ __
- * +------+      / __ )(_) /_______________ _____  ___
- * | 0xBC |     / __  / / __/ ___/ ___/ __ `/_  / / _ \
- * +------+    / /_/ / / /_/ /__/ /  / /_/ / / /_/  __/
- *  ||  ||    /_____/_/\__/\___/_/   \__,_/ /___/\___/
- *
- * Crazyflie control firmware
- *
- * Copyright (C) 2015 Bitcraze AB
- *
- * This program is free software: you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation, in version 3.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program. If not, see <http://www.gnu.org/licenses/>.
- *
- * deck_spi3.c - Deck-API SPI3 communication implementation. Mainly used so that
- *               the uSD-deck can log e.g. the loco deck.
- */
-
-#include "deck.h"
-
-/*ST includes */
-#include "stm32fxxx.h"
-#include "config.h"
-
-#include "FreeRTOS.h"
-#include "semphr.h"
-
-#include "cfassert.h"
-#include "config.h"
-#include "nvicconf.h"
-
-// Alternative SPI
-#define SPI                    SPI3
-#define SPI_CLK                RCC_APB1Periph_SPI3
-#define SPI_CLK_INIT           RCC_APB1PeriphClockCmd
-#define SPI_IRQ_HANDLER        SPI3_IRQHandler
[…]

### 2020-04-29 crazyflie-firmware/src/drivers/interface/i2c_drv.h

@@ -70,9 +70,7 @@ typedef struct
   uint32_t messageIndex;                //< Index of bytes sent/received
   uint32_t nbrOfretries;                //< Retries done
   SemaphoreHandle_t isBusFreeSemaphore; //< Semaphore to block during transaction.
-  StaticSemaphore_t isBusFreeSemaphoreBuffer;
-  SemaphoreHandle_t isBusFreeMutex;     //< Mutex to protect bus
-  StaticSemaphore_t isBusFreeMutexBuffer;
+  SemaphoreHandle_t isBusFreeMutex;     //< Mutex to protect buss
   DMA_InitTypeDef DMAStruct;            //< DMA configuration structure used during transfer setup.
 } I2cDrv;
 
@@ -133,3 +131,4 @@ void i2cdrvCreateMessageIntAddr(I2cMessage *message,
                              uint8_t  *buffer);
 
 #endif
+

### 2020-04-29 crazyflie-firmware/src/drivers/src/adc_f103.c

@@ -38,7 +38,6 @@
 #include "pm.h"
 #include "nvicconf.h"
 #include "imu.h"
-#include "static_mem.h"
 
 // PORT A
 #define GPIO_VBAT        GPIO_Pin_3
@@ -53,9 +52,7 @@
 static bool isInit;
 volatile AdcGroup adcValues[ADC_MEAN_SIZE * 2];
 
-static xQueueHandle adcQueue;
-STATIC_MEM_QUEUE_ALLOC(adcQueue, 1, AdcGroup);
-STATIC_MEM_TASK_ALLOC(adcTask, ADC_TASK_STACKSIZE);
+xQueueHandle      adcQueue;
 
 static void adcDmaInit(void)
 {
@@ -205,9 +202,10 @@ void adcInit(void)
   NVIC_InitStructure.NVIC_IRQChannelCmd = ENABLE;
   NVIC_Init(&NVIC_InitStructure);
 
-  adcQueue = STATIC_MEM_QUEUE_CREATE(adcQueue);
+  adcQueue = xQueueCreate(1, sizeof(AdcGroup*));
 
-  STATIC_MEM_TASK_CREATE(adcTask, adcTask, ADC_TASK_NAME, NULL, ADC_TASK_NAME);
+  xTaskCreate(adcTask, ADC_TASK_NAME,
+              ADC_TASK_STACKSIZE, NULL, ADC_TASK_PRI, NULL);
 
   isInit = true;
 }

### 2020-04-29 crazyflie-firmware/src/drivers/src/i2c_drv.c

@@ -180,19 +180,11 @@ static const I2cDef deckBusDef =
   .gpioAF             = GPIO_AF_I2C1,
   .dmaPerif           = RCC_AHB1Periph_DMA1,
   .dmaChannel         = DMA_Channel_1,
-#ifdef USDDECK_USE_ALT_PINS_AND_SPI
-  .dmaRxStream        = DMA1_Stream5,
-  .dmaRxIRQ           = DMA1_Stream5_IRQn,
-  .dmaRxTCFlag        = DMA_FLAG_TCIF5,
-  .dmaRxTEFlag        = DMA_FLAG_TEIF5,
-#else
   .dmaRxStream        = DMA1_Stream0,
   .dmaRxIRQ           = DMA1_Stream0_IRQn,
   .dmaRxTCFlag        = DMA_FLAG_TCIF0,
   .dmaRxTEFlag        = DMA_FLAG_TEIF0,
-#endif
 };
-
 
 I2cDrv deckBus =
 {
@@ -328,8 +320,8 @@ static void i2cdrvInitBus(I2cDrv* i2c)
 
   i2cdrvDmaSetupBus(i2c);
 
-  i2c->isBusFreeSemaphore = xSemaphoreCreateBinaryStatic(&i2c->isBusFreeSemaphoreBuffer);
-  i2c->isBusFreeMutex = xSemaphoreCreateMutexStatic(&i2c->isBusFreeMutexBuffer);
+  i2c->isBusFreeSemaphore = xSemaphoreCreateBinary();
+  i2c->isBusFreeMutex = xSemaphoreCreateMutex();
 }
 
 static void i2cdrvdevUnlockBus(GPIO_TypeDef* portSCL, GPIO_TypeDef* portSDA, uint16_t pinSCL, uint16_t pinSDA)
@@ -649,11 +641,7 @@ void __attribute__((used)) I2C1_EV_IRQHandler(void)
   i2cdrvEventIsrHandler(&deckBus);
 }
 
-#ifdef USDDECK_USE_ALT_PINS_AND_SPI
-void __attribute__((used)) DMA1_Stream5_IRQHandler(void)
-#else
 void __attribute__((used)) DMA1_Stream0_IRQHandler(void)
-#endif
 {
   i2cdrvDmaIsrHandler(&deckBus);
 }
@@ -672,3 +660,4 @@ void __attribute__((used)) DMA1_Stream2_IRQHandler(void)
 {
   i2cdrvDmaIsrHandler(&sensorsBus);
 }
+

### 2020-04-29 crazyflie-firmware/src/drivers/src/nvic.c

@@ -25,8 +25,9 @@
  */
 #include "exti.h"
 #include "led.h"
+#include "i2cdev.h"
+#include "ws2812.h"
 #include "motors.h"
-#include "power_distribution.h"
 #include "cfassert.h"
 
 #include "uart1.h"
@@ -129,20 +130,16 @@ void DONT_DISCARD printHardFault(uint32_t* hardfaultArgs)
   UART_PRINT("DFSR = %x\n", (*((volatile unsigned int *)(0xE000ED30))));
   UART_PRINT("AFSR = %x\n", (*((volatile unsigned int *)(0xE000ED3C))));
 
+  motorsSetRatio(MOTOR_M1, 0);
+  motorsSetRatio(MOTOR_M2, 0);
+  motorsSetRatio(MOTOR_M3, 0);
+  motorsSetRatio(MOTOR_M4, 0);
+
   ledClearAll();
   ledSet(ERR_LED1, 1);
   ledSet(ERR_LED2, 1);
-  powerStop();
 
-  storeAssertHardfaultData(
-    stacked_r0,
-    stacked_r1,
-    stacked_r2,
-    stacked_r3,
-    stacked_r12,
-    stacked_lr,
-    stacked_pc,
-    stacked_psr);
+  storeAssertSnapshotData(__FILE__, __LINE__);
   while (1)
   {}
 }
@@ -152,12 +149,16 @@ void DONT_DISCARD printHardFault(uint32_t* hardfaultArgs)
 void DONT_DISCARD MemManage_Handler(void)
 {
   /* Go to infinite loop when Memory Manage exception occurs */
+  motorsSetRatio(MOTOR_M1, 0);
+  motorsSetRatio(MOTOR_M2, 0);
+  motorsSetRatio(MOTOR_M3, 0);
+  motorsSetRatio(MOTOR_M4, 0);
+
   ledClearAll();
   ledSet(ERR_LED1, 1);
   ledSet(ERR_LED2, 1);
-  powerStop();
 
-  storeAssertTextData("MemManage");
+  storeAssertSnapshotData(__FILE__, __LINE__);
   while (1)
   {}
 }
@@ -168,12 +169,16 @@ void DONT_DISCARD MemManage_Handler(void)
 void DONT_DISCARD BusFault_Handler(void)
 {
   /* Go to infinite loop when Bus Fault exception occurs */
[…]

### 2020-04-29 crazyflie-firmware/src/drivers/src/pca9685.c

@@ -160,7 +160,6 @@ bool pca9685setDurations(
 #include "task.h"
 #include "queue.h"
 #include "config.h"
-#include "static_mem.h"
 
 struct asyncRequest
 {
@@ -174,10 +173,7 @@ struct asyncRequest
 static struct asyncRequest reqPop;
 
 static TaskHandle_t task;
-STATIC_MEM_TASK_ALLOC(task, PCA9685_TASK_STACKSIZE);
-
-static xQueueHandle queue;
-STATIC_MEM_QUEUE_ALLOC(queue, 1, sizeof(struct asyncRequest));
+static QueueHandle_t queue;
 
 static void asyncTask(__attribute__((unused)) void *param)
 {
@@ -193,13 +189,20 @@ static void asyncTask(__attribute__((unused)) void *param)
 
 bool pca9685startAsyncTask()
 {
-  queue = STATIC_MEM_QUEUE_CREATE(queue);
+  queue = xQueueCreate(1, sizeof(struct asyncRequest));
   if (queue == 0) {
     return false;
   }
 
-  task = STATIC_MEM_TASK_CREATE(task, asyncTask, PCA9685_TASK_NAME, NULL, PCA9685_TASK_PRI);
-  return true;
+  BaseType_t xReturned = xTaskCreate(
+    &asyncTask,
+    PCA9685_TASK_NAME,
+    PCA9685_TASK_STACKSIZE,
+    NULL,
+    PCA9685_TASK_PRI - 1,
+    &task);
+
+  return xReturned == pdPASS;
 }
 
 bool pca9685setDutiesAsync(

### 2020-04-29 crazyflie-firmware/src/hal/src/proximity.c

@@ -37,7 +37,6 @@
 #include "log.h"
 
 #include "stm32fxxx.h"
-#include "static_mem.h"
 
 /* Flag indicating if the proximityInit() function has been called or not. */
 static bool isInit = false;
@@ -62,8 +61,6 @@ LOG_ADD(LOG_UINT32, distanceMed, &proximityDistanceMedian)
 LOG_ADD(LOG_UINT32, accuracy, &proximityAccuracy)
 LOG_GROUP_STOP(proximity)
 #endif
-
-STATIC_MEM_TASK_ALLOC(proximityTask, PROXIMITY_TASK_STACKSIZE);
 
 /**
  * This function returns the median value of an array.
@@ -176,7 +173,8 @@ void proximityInit(void)
 
 #if defined(PROXIMITY_ENABLED)
   /* Only start the task if the proximity subsystem is enabled in conf.h */
-  STATIC_MEM_TASK_CREATE(proximityTask, proximityTask, PROXIMITY_TASK_NAME, NULL, PROXIMITY_TASK_PRI);
+  xTaskCreate(proximityTask, PROXIMITY_TASK_NAME,
+              PROXIMITY_TASK_STACKSIZE, NULL, PROXIMITY_TASK_PRI, NULL);
 #endif
 
   isInit = true;

### 2020-04-29 crazyflie-firmware/src/hal/src/radiolink.c

@@ -1,6 +1,6 @@
 /*
- *    ||          ____  _ __
- * +------+      / __ )(_) /_______________ _____  ___
+ *    ||          ____  _ __                           
+ * +------+      / __ )(_) /_______________ _____  ___ 
  * | 0xBC |     / __  / / __/ ___/ ___/ __ `/_  / / _ \
  * +------+    / /_/ / / /_/ /__/ /  / /_/ / / /_/  __/
  *  ||  ||    /_____/_/\__/\___/_/   \__,_/ /___/\___/
@@ -42,7 +42,6 @@
 #include "led.h"
 #include "ledseq.h"
 #include "queuemonitor.h"
-#include "static_mem.h"
 
 #define RADIOLINK_TX_QUEUE_SIZE (1)
 #define RADIOLINK_CTRP_QUEUE_SIZE (5)
@@ -51,10 +50,7 @@
 #define RADIOLINK_P2P_QUEUE_SIZE (5)
 
 static xQueueHandle  txQueue;
-STATIC_MEM_QUEUE_ALLOC(txQueue, RADIOLINK_TX_QUEUE_SIZE, sizeof(SyslinkPacket));
-
 static xQueueHandle crtpPacketDelivery;
-STATIC_MEM_QUEUE_ALLOC(crtpPacketDelivery, RADIOLINK_CTRP_QUEUE_SIZE, sizeof(CRTPPacket));
 
 static bool isInit;
 
@@ -86,9 +82,9 @@ void radiolinkInit(void)
   if (isInit)
     return;
 
-  txQueue = STATIC_MEM_QUEUE_CREATE(txQueue);
+  txQueue = xQueueCreate(RADIOLINK_TX_QUEUE_SIZE, sizeof(SyslinkPacket));
   DEBUG_QUEUE_MONITOR_REGISTER(txQueue);
-  crtpPacketDelivery = STATIC_MEM_QUEUE_CREATE(crtpPacketDelivery);
+  crtpPacketDelivery = xQueueCreate(RADIOLINK_CTRP_QUEUE_SIZE, sizeof(CRTPPacket));
   DEBUG_QUEUE_MONITOR_REGISTER(crtpPacketDelivery);
 
   ASSERT(crtpPacketDelivery);

### 2020-04-29 crazyflie-firmware/src/hal/src/sensors_bmi088_bmp388.c

@@ -50,7 +50,6 @@
 #include "bmi088.h"
 #include "bmp3.h"
 #include "bstdr_types.h"
-#include "static_mem.h"
 
 #define GYRO_ADD_RAW_AND_VARIANCE_LOG_VALUES
 
@@ -102,18 +101,11 @@ static struct bmi088_dev bmi088Dev;
 static struct bmp3_dev   bmp388Dev;
 
 static xQueueHandle accelerometerDataQueue;
-STATIC_MEM_QUEUE_ALLOC(accelerometerDataQueue, 1, sizeof(Axis3f));
 static xQueueHandle gyroDataQueue;
-STATIC_MEM_QUEUE_ALLOC(gyroDataQueue, 1, sizeof(Axis3f));
 static xQueueHandle magnetometerDataQueue;
-STATIC_MEM_QUEUE_ALLOC(magnetometerDataQueue, 1, sizeof(Axis3f));
 static xQueueHandle barometerDataQueue;
-STATIC_MEM_QUEUE_ALLOC(barometerDataQueue, 1, sizeof(baro_t));
-
 static xSemaphoreHandle sensorsDataReady;
-static StaticSemaphore_t sensorsDataReadyBuffer;
 static xSemaphoreHandle dataReady;
-static StaticSemaphore_t dataReadyBuffer;
 
 static bool isInit = false;
 static sensorData_t sensorData;
@@ -160,8 +152,6 @@ static void sensorsCalculateBiasMean(BiasObj* bias, Axis3i32* meanOut);
 static void sensorsAddBiasValue(BiasObj* bias, int16_t x, int16_t y, int16_t z);
 static bool sensorsFindBiasValue(BiasObj* bias);
 static void sensorsAccAlignToGravity(Axis3f* in, Axis3f* out);
-
-STATIC_MEM_TASK_ALLOC(sensorsTask, SENSORS_TASK_STACKSIZE);
 
 // Communication routines
 
@@ -508,12 +498,12 @@ static void sensorsDeviceInit(void)
 
 static void sensorsTaskInit(void)
 {
-  accelerometerDataQueue = STATIC_MEM_QUEUE_CREATE(accelerometerDataQueue);
-  gyroDataQueue = STATIC_MEM_QUEUE_CREATE(gyroDataQueue);
-  magnetometerDataQueue = STATIC_MEM_QUEUE_CREATE(magnetometerDataQueue);
[…]

### 2020-04-29 crazyflie-firmware/src/hal/src/sensors_mpu9250_lps25h.c

@@ -49,7 +49,6 @@
 #include "ledseq.h"
 #include "sound.h"
 #include "filter.h"
-#include "static_mem.h"
 
 /**
  * Enable 250Hz digital LPF mode. However does not work with
@@ -105,18 +104,11 @@ typedef struct
 } BiasObj;
 
 static xQueueHandle accelerometerDataQueue;
-STATIC_MEM_QUEUE_ALLOC(accelerometerDataQueue, 1, sizeof(Axis3f));
 static xQueueHandle gyroDataQueue;
-STATIC_MEM_QUEUE_ALLOC(gyroDataQueue, 1, sizeof(Axis3f));
 static xQueueHandle magnetometerDataQueue;
-STATIC_MEM_QUEUE_ALLOC(magnetometerDataQueue, 1, sizeof(Axis3f));
 static xQueueHandle barometerDataQueue;
-STATIC_MEM_QUEUE_ALLOC(barometerDataQueue, 1, sizeof(baro_t));
-
 static xSemaphoreHandle sensorsDataReady;
-static StaticSemaphore_t sensorsDataReadyBuffer;
 static xSemaphoreHandle dataReady;
-static StaticSemaphore_t dataReadyBuffer;
 
 static bool isInit = false;
 static sensorData_t sensorData;
@@ -173,8 +165,6 @@ static void sensorsCalculateBiasMean(BiasObj* bias, Axis3i32* meanOut);
 static void sensorsAddBiasValue(BiasObj* bias, int16_t x, int16_t y, int16_t z);
 static bool sensorsFindBiasValue(BiasObj* bias);
 static void sensorsAccAlignToGravity(Axis3f* in, Axis3f* out);
-
-STATIC_MEM_TASK_ALLOC(sensorsTask, SENSORS_TASK_STACKSIZE);
 
 bool sensorsMpu9250Lps25hReadGyro(Axis3f *gyro)
 {
@@ -486,12 +476,12 @@ static void sensorsSetupSlaveRead(void)
 
 static void sensorsTaskInit(void)
 {
-  accelerometerDataQueue = STATIC_MEM_QUEUE_CREATE(accelerometerDataQueue);
-  gyroDataQueue = STATIC_MEM_QUEUE_CREATE(gyroDataQueue);
-  magnetometerDataQueue = STATIC_MEM_QUEUE_CREATE(magnetometerDataQueue);
[…]

### 2020-04-29 crazyflie-firmware/src/hal/src/usb.c

@@ -1,6 +1,6 @@
 /**
- *    ||          ____  _ __
- * +------+      / __ )(_) /_______________ _____  ___
+ *    ||          ____  _ __                           
+ * +------+      / __ )(_) /_______________ _____  ___ 
  * | 0xBC |     / __  / / __/ ___/ ___/ __ `/_  / / _ \
  * +------+    / /_/ / / /_/ /__/ /  / /_/ / / /_/  __/
  *  ||  ||    /_____/_/\__/\___/_/   \__,_/ /___/\___/
@@ -46,7 +46,6 @@
 #include "usb_dcd.h"
 
 #include "crtp.h"
-#include "static_mem.h"
 
 
 __ALIGN_BEGIN USB_OTG_CORE_HANDLE    USB_OTG_dev __ALIGN_END ;
@@ -54,11 +53,8 @@ __ALIGN_BEGIN USB_OTG_CORE_HANDLE    USB_OTG_dev __ALIGN_END ;
 static bool isInit = false;
 static bool doingTransfer = false;
 
-// This should probably be reduced to a CRTP packet size
 static xQueueHandle usbDataRx;
-STATIC_MEM_QUEUE_ALLOC(usbDataRx, 5, sizeof(USBPacket)); /* Buffer USB packets (max 64 bytes) */
 static xQueueHandle usbDataTx;
-STATIC_MEM_QUEUE_ALLOC(usbDataTx, 1, sizeof(USBPacket)); /* Buffer USB packets (max 64 bytes) */
 
 /* Endpoints */
 #define IN_EP                       0x81  /* EP1 for data IN */
@@ -156,7 +152,7 @@ static void resetUSB(void) {
     while (xQueueReceiveFromISR(usbDataTx, &outPacket, &xTaskWokenByReceive) == pdTRUE)
       ;
   }
-
+  
   USB_OTG_FlushTxFifo(&USB_OTG_dev, IN_EP);
 }
 
@@ -380,9 +376,10 @@ void usbInit(void)
             &cf_usb_cb,
             &USR_cb);
 
-  usbDataRx = STATIC_MEM_QUEUE_CREATE(usbDataRx);
+  // This should probably be reduced to a CRTP packet size
+  usbDataRx = xQueueCreate(5, sizeof(USBPacket)); /* Buffer USB packets (max 64 bytes) */
   DEBUG_QUEUE_MONITOR_REGISTER(usbDataRx);
[…]

### 2020-04-29 crazyflie-firmware/src/hal/src/usblink.c

@@ -1,6 +1,6 @@
 /*
- *    ||          ____  _ __
- * +------+      / __ )(_) /_______________ _____  ___
+ *    ||          ____  _ __                           
+ * +------+      / __ )(_) /_______________ _____  ___ 
  * | 0xBC |     / __  / / __/ ___/ ___/ __ `/_  / / _ \
  * +------+    / /_/ / / /_/ /__/ /  / /_/ / / /_/  __/
  *  ||  ||    /_____/_/\__/\___/_/   \__,_/ /___/\___/
@@ -39,20 +39,17 @@
 #include "queue.h"
 #include "queuemonitor.h"
 #include "semphr.h"
-#include "static_mem.h"
 
 #include "usb.h"
 
 static bool isInit = false;
 static xQueueHandle crtpPacketDelivery;
-STATIC_MEM_QUEUE_ALLOC(crtpPacketDelivery, 16, sizeof(CRTPPacket));
 static uint8_t sendBuffer[64];
 
 static int usblinkSendPacket(CRTPPacket *p);
 static int usblinkSetEnable(bool enable);
 static int usblinkReceiveCRTPPacket(CRTPPacket *p);
 
-STATIC_MEM_TASK_ALLOC(usblinkTask, USBLINK_TASK_STACKSIZE);
 
 static struct crtpLinkOperations usblinkOp =
 {
@@ -129,10 +126,11 @@ void usblinkInit()
   // Initialize the USB peripheral
   usbInit();
 
-  crtpPacketDelivery = STATIC_MEM_QUEUE_CREATE(crtpPacketDelivery);
+  crtpPacketDelivery = xQueueCreate(16, sizeof(CRTPPacket));
   DEBUG_QUEUE_MONITOR_REGISTER(crtpPacketDelivery);
 
-  STATIC_MEM_TASK_CREATE(usblinkTask, usblinkTask, USBLINK_TASK_NAME, NULL, USBLINK_TASK_PRI);
+  xTaskCreate(usblinkTask, USBLINK_TASK_NAME,
+              USBLINK_TASK_STACKSIZE, NULL, USBLINK_TASK_PRI, NULL);
 
   isInit = true;
 }
@@ -146,3 +144,4 @@ struct crtpLinkOperations * usblinkGetLink()
 {
   return &usblinkOp;
 }
+

### 2020-04-29 crazyflie-firmware/src/modules/interface/commander.h

@@ -46,13 +46,6 @@ uint32_t commanderGetInactivityTime(void);
 void commanderSetSetpoint(setpoint_t *setpoint, int priority);
 int commanderGetActivePriority(void);
 
-/* Inform the commander that streaming setpoints are about to stop.
- * Parameter controls the amount of time the last setpoint will remain valid.
- * This gives the PC time to send the next command, e.g. with the high-level
- * commander, before we enter timeout mode.
- */
-void commanderNotifySetpointsStop(int remainValidMillisecs);
-
 void commanderGetSetpoint(setpoint_t *setpoint, const state_t *state);
 
 #endif /* COMMANDER_H_ */

### 2020-04-29 crazyflie-firmware/src/modules/interface/math3d.h

@@ -179,7 +179,7 @@ static inline float vnorm1(struct vec v) {
 }
 
 //
-// comparisons, including partial orderings
+// comparisons
 //
 
 // compare two vectors for exact equality.
@@ -227,7 +227,7 @@ static inline struct vec vadd3(struct vec a, struct vec b, struct vec c) {
 // add 4 vectors.
 static inline struct vec vadd4(struct vec a, struct vec b, struct vec c, struct vec d) {
 	// TODO: make sure it compiles to optimal code
-	return vadd(vadd(a, b), vadd(c, d));
+	return vadd(vadd(vadd(a, b), c), d);
 }
 // subtract b and c from a.
 static inline struct vec vsub2(struct vec a, struct vec b, struct vec c) {
@@ -235,7 +235,7 @@ static inline struct vec vsub2(struct vec a, struct vec b, struct vec c) {
 }
 
 //
-// conversion to/from raw float and double arrays; array-like access.
+// conversion to/from raw float and double arrays.
 //
 
 // load a vector from a double array.
@@ -253,10 +253,6 @@ static inline struct vec vloadf(float const *f) {
 // store a vector into a float array.
 static inline void vstoref(struct vec v, float *f) {
 	f[0] = v.x; f[1] = v.y; f[2] = v.z;
-}
-// index a vector like a 3-element array.
-static inline float vindex(struct vec v, int i) {
-	return ((float const *)&v.x)[i];
 }
 
 
@@ -448,46 +444,6 @@ static inline void set_block33_rowmaj(float *block, int stride, struct mat33 con
 		block += stride;
 	}
 }
-
-//
-// special functions to ease the pain of writing vector math in C.
-//
-
-// add three matrices.
-static inline struct mat33 madd3(struct mat33 a, struct mat33 b, struct mat33 c) {
-	return madd(madd(a, b), c);
-}
-
-//
-// 3D rotation constructors & operators
-//
-
-// construct equivalent rotation matrix for axis-angle rotation.
-// assumes input axis is normalized, angle in radians.
-static inline struct mat33 maxisangle(struct vec axis, float angle) {
-	// Rodrigues formula
-	struct mat33 const K = mcrossmat(axis);
-	return madd3(
-		meye(),
-		mscl(sinf(angle), K),
-		mscl(1.0f - cosf(angle), mmul(K, K))
-	);
-}
-// rotation about x axis by given angle (radians)
[…]

### 2020-04-29 crazyflie-firmware/src/modules/interface/planner.h

@@ -87,16 +87,13 @@ bool plan_is_stopped(struct planner *p);
 struct traj_eval plan_current_goal(struct planner *p, float t);
 
 // start a takeoff trajectory.
-int plan_takeoff(struct planner *p, struct vec curr_pos, float curr_yaw, float hover_height, float hover_yaw, float duration, float t);
+int plan_takeoff(struct planner *p, struct vec pos, float yaw, float height, float duration, float t);
 
 // start a landing trajectory.
-int plan_land(struct planner *p, struct vec curr_pos, float curr_yaw, float hover_height, float hover_yaw, float duration, float t);
+int plan_land(struct planner *p, struct vec pos, float yaw, float height, float duration, float t);
 
 // move to a given position, then hover there.
 int plan_go_to(struct planner *p, bool relative, struct vec hover_pos, float hover_yaw, float duration, float t);
-
-// same as above, but with current state provided from outside.
-int plan_go_to_from(struct planner *p, const struct traj_eval *curr_eval, bool relative, struct vec hover_pos, float hover_yaw, float duration, float t);
 
 // start trajectory
 int plan_start_trajectory(struct planner *p, const struct piecewise_traj* trajectory, bool reversed);

### 2020-04-29 crazyflie-firmware/src/modules/interface/static_mem.h

@@ -1,142 +1,0 @@
-/**
- * ,---------,       ____  _ __
- * |  ,-^-,  |      / __ )(_) /_______________ _____  ___
- * | (  O  ) |     / __  / / __/ ___/ ___/ __ `/_  / / _ \
- * | / ,--'  |    / /_/ / / /_/ /__/ /  / /_/ / / /_/  __/
- *    +------`   /_____/_/\__/\___/_/   \__,_/ /___/\___/
- *
- * Crazyflie control firmware
- *
- * Copyright (C) 2019 Bitcraze AB
- *
- * This program is free software: you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation, in version 3.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program. If not, see <http://www.gnu.org/licenses/>.
- *
- * @file static_mem.h
- * @brief Utility macros to create static memory for OS objects such as
- * queues, semaphores and so on.
- *
- * @copyright Copyright (c) 2019
- *
- */
-
-#pragma once
-
-/**
- * @brief Creation of queues using static memory.
- *
- * STATIC_MEM_QUEUE_ALLOC() and STATIC_MEM_QUEUE_CREATE() are used togehter to set up
- * and create a queue. STATIC_MEM_QUEUE_ALLOC() defines a number of static variables,
- * that are required by the queue. STATIC_MEM_QUEUE_CREATE() creates the OS queue object
- * using the previously defined variables.
- *
- * Example:
- * static xQueueHandle myQueue;
- * STATIC_MEM_QUEUE_ALLOC(myQueue, 5, sizeof(int));
- * // ...
- * void init() {
- *   myQueue = STATIC_MEM_QUEUE_CREATE(myQueue);
- *   // myQueue can now be used in OS calls
- * }
- *
- * Note: the queue handle may have the same name as used in the macros, but it is
- * not necessary.
- */
-
-/**
- * @brief Creates a number of variables required for a queue using static memory.
- *
[…]

### 2020-04-29 crazyflie-firmware/src/modules/src/commander.c

@@ -33,32 +33,26 @@
 #include "crtp_commander.h"
 #include "crtp_commander_high_level.h"
 
-#include "cf_math.h"
 #include "param.h"
-#include "static_mem.h"
 
 static bool isInit;
 const static setpoint_t nullSetpoint;
-static setpoint_t tempSetpoint;
-static state_t lastState;
 const static int priorityDisable = COMMANDER_PRIORITY_DISABLE;
 
 static uint32_t lastUpdate;
 static bool enableHighLevel = false;
 
 static QueueHandle_t setpointQueue;
-STATIC_MEM_QUEUE_ALLOC(setpointQueue, 1, sizeof(setpoint_t));
 static QueueHandle_t priorityQueue;
-STATIC_MEM_QUEUE_ALLOC(priorityQueue, 1, sizeof(int));
 
 /* Public functions */
 void commanderInit(void)
 {
-  setpointQueue = STATIC_MEM_QUEUE_CREATE(setpointQueue);
+  setpointQueue = xQueueCreate(1, sizeof(setpoint_t));
   ASSERT(setpointQueue);
   xQueueSend(setpointQueue, &nullSetpoint, 0);
 
-  priorityQueue = STATIC_MEM_QUEUE_CREATE(priorityQueue);
+  priorityQueue = xQueueCreate(1, sizeof(int));
   ASSERT(priorityQueue);
   xQueueSend(priorityQueue, &priorityDisable, 0);
 
@@ -81,23 +75,7 @@ void commanderSetSetpoint(setpoint_t *setpoint, int priority)
     // This is a potential race but without effect on functionality
     xQueueOverwrite(setpointQueue, setpoint);
     xQueueOverwrite(priorityQueue, &priority);
-    // Send the high-level planner to idle so it will forget its current state
-    // and start over if we switch from low-level to high-level in the future.
-    crtpCommanderHighLevelStop();
   }
-}
-
-void commanderNotifySetpointsStop(int remainValidMillisecs)
-{
-  uint32_t currentTime = xTaskGetTickCount();
-  int timeSetback = MIN(
-    COMMANDER_WDT_TIMEOUT_SHUTDOWN - M2T(remainValidMillisecs),
-    currentTime
-  );
-  xQueuePeek(setpointQueue, &tempSetpoint, 0);
-  tempSetpoint.timestamp = currentTime - timeSetback;
-  xQueueOverwrite(setpointQueue, &tempSetpoint);
-  crtpCommanderHighLevelTellState(&lastState);
 }
 
[…]

### 2020-04-29 crazyflie-firmware/src/modules/src/controller_pid.c

@@ -43,20 +43,6 @@ bool controllerPidTest(void)
   return pass;
 }
 
-static float capAngle(float angle) {
-  float result = angle;
-
-  while (result > 180.0f) {
-    result -= 360.0f;
-  }
-
-  while (result < -180.0f) {
-    result += 360.0f;
-  }
-
-  return result;
-}
-
 void controllerPid(control_t *control, setpoint_t *setpoint,
                                          const sensorData_t *sensors,
                                          const state_t *state,
@@ -66,11 +52,13 @@ void controllerPid(control_t *control, setpoint_t *setpoint,
     // Rate-controled YAW is moving YAW angle setpoint
     if (setpoint->mode.yaw == modeVelocity) {
        attitudeDesired.yaw += setpoint->attitudeRate.yaw * ATTITUDE_UPDATE_DT;
+      while (attitudeDesired.yaw > 180.0f)
+        attitudeDesired.yaw -= 360.0f;
+      while (attitudeDesired.yaw < -180.0f)
+        attitudeDesired.yaw += 360.0f;
     } else {
       attitudeDesired.yaw = setpoint->attitude.yaw;
     }
-
-    attitudeDesired.yaw = capAngle(attitudeDesired.yaw);
   }
 
   if (RATE_DO_EXECUTE(POSITION_RATE, tick)) {

### 2020-04-29 crazyflie-firmware/src/modules/src/crtp_commander.c

@@ -27,7 +27,6 @@
 
 #include "crtp_commander.h"
 
-#include "cfassert.h"
 #include "commander.h"
 #include "crtp.h"
 
@@ -48,64 +47,7 @@ void crtpCommanderInit(void)
   isInit = true;
 }
 
-enum crtpSetpointGenericChannel {
-  SET_SETPOINT_CHANNEL = 0,
-  META_COMMAND_CHANNEL = 1,
-};
 
-/* Channel 1 of the generic commander port is used for "meta-commands"
- * that alter the behavior of the commander itself, e.g. mode switching.
- * Although we use the generic commander port due to increasing pressure on the
- * 4-bit space of ports numbers, meta-commands that are unrelated to
- * streaming generic setpoint control modes are permitted.
- *
- * The packet format for meta-commands is:
- * +------+==========================+
- * | TYPE |     DATA                 |
- * +------+==========================+
- *
- * TYPE is an 8-bit value. The remainder of the data depends on the command.
- * The maximum data size is 29 bytes.
- */
-
-/* To add a new packet:
- *   1 - Add a new type in the metaCommand_e enum.
- *   2 - Implement a decoder function with good documentation about the data
- *       structure and the intent of the packet.
- *   3 - Add the decoder function to the metaCommandDecoders array.
- *   4 - Create a new params group for your handler if necessary
- *   5 - Pull-request your change :-)
- */
-
-/* ---===== 1 - metaCommand_e enum =====--- */
-enum metaCommand_e {
-  metaNotifySetpointsStop = 0,
-  nMetaCommands,
-};
-
-typedef void (*metaCommandDecoder_t)(const void *data, size_t datalen);
-
-/* ---===== 2 - Decoding functions =====--- */
-
-/* notifySetpointsStop meta-command. See commander.h function
- * commanderNotifySetpointsStop() for description and motivation.
- */
-struct notifySetpointsStopPacket {
-  uint32_t remainValidMillisecs;
-} __attribute__((packed));
-void notifySetpointsStopDecoder(const void *data, size_t datalen)
-{
-  ASSERT(datalen == sizeof(struct notifySetpointsStopPacket));
-  const struct notifySetpointsStopPacket *values = data;
[…]

### 2020-04-29 crazyflie-firmware/src/modules/src/estimator_complementary.c

@@ -36,7 +36,6 @@
 #include "position_estimator.h"
 #include "sensors.h"
 #include "stabilizer_types.h"
-#include "static_mem.h"
 
 #define ATTITUDE_UPDATE_RATE RATE_250_HZ
 #define ATTITUDE_UPDATE_DT 1.0/ATTITUDE_UPDATE_RATE
@@ -47,14 +46,12 @@
 static bool latestTofMeasurement(tofMeasurement_t* tofMeasurement);
 
 // Measurements of TOF from laser sensor
-#define TOF_QUEUE_LENGTH (1)
 static xQueueHandle tofDataQueue;
-STATIC_MEM_QUEUE_ALLOC(tofDataQueue, TOF_QUEUE_LENGTH, sizeof(tofMeasurement_t));
-
+#define TOF_QUEUE_LENGTH (1)
 
 void estimatorComplementaryInit(void)
 {
-  tofDataQueue = STATIC_MEM_QUEUE_CREATE(tofDataQueue);
+  tofDataQueue = xQueueCreate(TOF_QUEUE_LENGTH, sizeof(tofMeasurement_t));
 
   sensfusion6Init();
 }
@@ -130,3 +127,4 @@ bool estimatorComplementaryEnqueueTOF(const tofMeasurement_t *tof)
   // A distance (distance) [m] to the ground along the z_B axis.
   return overwriteMeasurement(tofDataQueue, (void *)tof);
 }
+

### 2020-04-29 crazyflie-firmware/src/modules/src/estimator_kalman.c

@@ -67,7 +67,6 @@
 #include "task.h"
 #include "semphr.h"
 #include "sensors.h"
-#include "static_mem.h"
 
 #include "system.h"
 #include "log.h"
@@ -96,7 +95,7 @@
 
 // Distance-to-point measurements
 static xQueueHandle distDataQueue;
-STATIC_MEM_QUEUE_ALLOC(distDataQueue, 10, sizeof(distanceMeasurement_t));
+#define DIST_QUEUE_LENGTH (10)
 
 static inline bool stateEstimatorHasDistanceMeasurement(distanceMeasurement_t *dist) {
   return (pdTRUE == xQueueReceive(distDataQueue, dist, 0));
@@ -104,7 +103,7 @@ static inline bool stateEstimatorHasDistanceMeasurement(distanceMeasurement_t *d
 
 // Direct measurements of Crazyflie position
 static xQueueHandle posDataQueue;
-STATIC_MEM_QUEUE_ALLOC(posDataQueue, 10, sizeof(positionMeasurement_t));
+#define POS_QUEUE_LENGTH (10)
 
 static inline bool stateEstimatorHasPositionMeasurement(positionMeasurement_t *pos) {
   return (pdTRUE == xQueueReceive(posDataQueue, pos, 0));
@@ -112,7 +111,7 @@ static inline bool stateEstimatorHasPositionMeasurement(positionMeasurement_t *p
 
 // Direct measurements of Crazyflie pose
 static xQueueHandle poseDataQueue;
-STATIC_MEM_QUEUE_ALLOC(poseDataQueue, 10, sizeof(poseMeasurement_t));
+#define POSE_QUEUE_LENGTH (10)
 
 static inline bool stateEstimatorHasPoseMeasurement(poseMeasurement_t *pose) {
   return (pdTRUE == xQueueReceive(poseDataQueue, pose, 0));
@@ -120,15 +119,16 @@ static inline bool stateEstimatorHasPoseMeasurement(poseMeasurement_t *pose) {
 
 // Measurements of a UWB Tx/Rx
 static xQueueHandle tdoaDataQueue;
-STATIC_MEM_QUEUE_ALLOC(tdoaDataQueue, 10, sizeof(tdoaMeasurement_t));
+#define UWB_QUEUE_LENGTH (10)
 
[…]

### 2020-04-29 crazyflie-firmware/src/modules/src/extrx.c

@@ -41,7 +41,6 @@
 #define DEBUG_MODULE  "EXTRX"
 #include "debug.h"
 #include "log.h"
-#include "static_mem.h"
 
 #define ENABLE_CPPM
 #define ENABLE_EXTRX_LOG
@@ -69,8 +68,6 @@ static void extRxTask(void *param);
 static void extRxDecodeCppm(void);
 static void extRxDecodeChannels(void);
 
-STATIC_MEM_TASK_ALLOC(extRxTask, EXTRX_TASK_STACKSIZE);
-
 void extRxInit(void)
 {
 
@@ -86,7 +83,9 @@ void extRxInit(void)
   uart1Init();
 #endif
 
-  STATIC_MEM_TASK_CREATE(extRxTask, extRxTask, EXTRX_TASK_NAME, NULL, EXTRX_TASK_PRI);
+
+  xTaskCreate(extRxTask, EXTRX_TASK_NAME,
+              EXTRX_TASK_STACKSIZE, NULL, EXTRX_TASK_PRI, NULL);
 }
 
 static void extRxTask(void *param)

### 2020-04-29 crazyflie-firmware/src/modules/src/log.c

@@ -48,7 +48,6 @@
 #include "console.h"
 #include "cfassert.h"
 #include "debug.h"
-#include "static_mem.h"
 
 #if 0
 #define LOG_DEBUG(fmt, ...) DEBUG_PRINT("D/log " fmt, ## __VA_ARGS__)
@@ -94,14 +93,12 @@ struct log_ops {
 struct log_block {
   int id;
   xTimerHandle timer;
-  StaticTimer_t timerBuffer;
   struct log_ops * ops;
 };
 
 static struct log_ops logOps[LOG_MAX_OPS];
 static struct log_block logBlocks[LOG_MAX_BLOCKS];
 static xSemaphoreHandle logLock;
-static StaticSemaphore_t logLockBuffer;
 
 struct ops_setting {
     uint8_t logType;
@@ -167,8 +164,6 @@ static int logStopBlock(int id);
 static void logReset();
 static acquisitionType_t acquisitionTypeFromLogType(uint8_t logType);
 
-STATIC_MEM_TASK_ALLOC(logTask, LOG_TASK_STACKSIZE);
-
 void logInit(void)
 {
   int i;
@@ -209,7 +204,7 @@ void logInit(void)
   }
 
   // Big lock that protects the log datastructures
-  logLock = xSemaphoreCreateMutexStatic(&logLockBuffer);
+  logLock = xSemaphoreCreateMutex();
 
   for (i=0; i<logsLen; i++)
   {
@@ -225,7 +220,8 @@ void logInit(void)
   logReset();
 
   //Start the log task
-  STATIC_MEM_TASK_CREATE(logTask, logTask, LOG_TASK_NAME, NULL, LOG_TASK_PRI);
+  xTaskCreate(logTask, LOG_TASK_NAME,
+              LOG_TASK_STACKSIZE, NULL, LOG_TASK_PRI, NULL);
 
   isInit = true;
 }
@@ -434,8 +430,8 @@ static int logCreateBlock(unsigned char id, struct ops_setting * settings, int l
     return ENOMEM;
 
   logBlocks[i].id = id;
-  logBlocks[i].timer = xTimerCreateStatic("logTimer", M2T(1000), pdTRUE,
-    &logBlocks[i], logBlockTimed, &logBlocks[i].timerBuffer);
+  logBlocks[i].timer = xTimerCreate( "logTimer", M2T(1000),
+                                     pdTRUE, &logBlocks[i], logBlockTimed );
[…]

### 2020-04-29 crazyflie-firmware/src/modules/src/outlierFilter.c

@@ -30,7 +30,7 @@
 #include "log.h"
 #include "debug.h"
 
-#define BUCKET_ACCEPTANCE_LEVEL 3
+#define BUCKET_ACCEPTANCE_LEVEL 2
 #define MAX_BUCKET_FILL 10
 #define FILTER_CLOSE_DELAY_COUNT 30
 

### 2020-04-29 crazyflie-firmware/src/modules/src/param.c

@@ -36,7 +36,6 @@
 #include "crc.h"
 #include "console.h"
 #include "debug.h"
-#include "static_mem.h"
 
 #if 0
 #define PARAM_DEBUG(fmt, ...) DEBUG_PRINT("D/param " fmt, ## __VA_ARGS__)
@@ -100,8 +99,6 @@ static CRTPPacket p;
 
 static bool isInit = false;
 
-STATIC_MEM_TASK_ALLOC(paramTask, PARAM_TASK_STACKSIZE);
-
 void paramInit(void)
 {
   int i;
@@ -150,7 +147,8 @@ void paramInit(void)
 
 
   //Start the param task
-  STATIC_MEM_TASK_CREATE(paramTask, paramTask, PARAM_TASK_NAME, NULL, PARAM_TASK_PRI);
+	xTaskCreate(paramTask, PARAM_TASK_NAME,
+	            PARAM_TASK_STACKSIZE, NULL, PARAM_TASK_PRI, NULL);
 
   //TODO: Handle stored parameters!
 
@@ -667,3 +665,4 @@ unsigned int paramGetUint(int varid)
 {
   return (unsigned int)paramGetInt(varid);
 }
+

### 2020-04-29 crazyflie-firmware/src/modules/src/planner.c

@@ -40,14 +40,14 @@ implementation of planning state machine
 
 static struct traj_eval plan_eval(struct planner *p, float t);
 
-static void plan_takeoff_or_landing(struct planner *p, struct vec curr_pos, float curr_yaw, float hover_height, float hover_yaw, float duration)
+static void plan_takeoff_or_landing(struct planner *p, struct vec pos, float yaw, float height, float duration)
 {
-	struct vec hover_pos = curr_pos;
-	hover_pos.z = hover_height;
+	struct vec takeoff_pos = pos;
+	takeoff_pos.z = height;
 
 	piecewise_plan_7th_order_no_jerk(&p->planned_trajectory, duration,
-		curr_pos,  curr_yaw,  vzero(), 0, vzero(),
-		hover_pos, hover_yaw, vzero(), 0, vzero());
+		pos,         yaw, vzero(), 0, vzero(),
+		takeoff_pos,   0, vzero(), 0, vzero());
 }
 
 // ----------------- //
@@ -131,13 +131,13 @@ struct traj_eval plan_eval(struct planner *p, float t)
 	}
 }
 
-int plan_takeoff(struct planner *p, struct vec curr_pos, float curr_yaw, float hover_height, float hover_yaw, float duration, float t)
+int plan_takeoff(struct planner *p, struct vec pos, float yaw, float height, float duration, float t)
 {
 	if (p->state != TRAJECTORY_STATE_IDLE) {
 		return 1;
 	}
 
-	plan_takeoff_or_landing(p, curr_pos, curr_yaw, hover_height, hover_yaw, duration);
+	plan_takeoff_or_landing(p, pos, yaw, height, duration);
 	p->reversed = false;
 	p->state = TRAJECTORY_STATE_FLYING;
 	p->type = TRAJECTORY_TYPE_PIECEWISE;
@@ -146,13 +146,14 @@ int plan_takeoff(struct planner *p, struct vec curr_pos, float curr_yaw, float h
 	return 0;
 }
 
-int plan_land(struct planner *p, struct vec curr_pos, float curr_yaw, float hover_height, float hover_yaw, float duration, float t)
+int plan_land(struct planner *p, struct vec pos, float yaw, float height, float duration, float t)
 {
-	if (p->state == TRAJECTORY_STATE_LANDING) {
+	if (   p->state == TRAJECTORY_STATE_IDLE
+		|| p->state == TRAJECTORY_STATE_LANDING) {
[…]

### 2020-04-29 crazyflie-firmware/src/modules/src/position_controller_indi.c

@@ -38,6 +38,7 @@ float K_dxi_z = 5.0f;
 // Thrust mapping parameter
 float K_thr = 0.00024730f;
 
+static float pos_set_x, pos_set_y, pos_set_z; 	// Ref. position commanded from the client
 static float posS_x, posS_y, posS_z;			// Current position
 static float velS_x, velS_y, velS_z;			// Current velocity
 static float gyr_p, gyr_q, gyr_r;				// Current rates
@@ -45,6 +46,9 @@ static float gyr_p, gyr_q, gyr_r;				// Current rates
 // Reference values
 static struct Vectr positionRef; 
 static struct Vectr velocityRef;
+
+// Arming parameter (0: not ready; 1: ready to fly)
+static float arm = 0;
 
 
 static struct IndiOuterVariables indiOuter = {
@@ -112,10 +116,9 @@ void positionControllerINDIInit(void)
 }
 
 
-void positionControllerINDI(const sensorData_t *sensors,
-                            setpoint_t *setpoint,
-                            const state_t *state, 
-                            vector_t *refOuterINDI){ 
+void positionControllerINDI(const sensorData_t *sensors, 
+	 						const state_t *state,
+	 						vector_t *refOuterINDI) { 
 
 	// Read states (position, velocity)
 	posS_x = state->position.x;
@@ -128,24 +131,13 @@ void positionControllerINDI(const sensorData_t *sensors,
 	gyr_q = sensors->gyro.y;
 	gyr_r = sensors->gyro.z; 
 
-	// Read in velocity setpoints
-    velocityRef.x = setpoint->velocity.x;
-	velocityRef.y = -setpoint->velocity.y;
-    velocityRef.z = -setpoint->velocity.z;
-
 	// Position controller (Proportional)
-	if (setpoint->mode.x == modeAbs) {
-		positionRef.x = setpoint->position.x;
-		velocityRef.x = K_xi_x*(positionRef.x - posS_x);
-	}
-	if (setpoint->mode.y == modeAbs) {
[…]

### 2020-04-29 crazyflie-firmware/src/modules/src/power_distribution_stock.c

@@ -117,11 +117,11 @@ PARAM_ADD(PARAM_UINT16, m1, &motorPowerSet.m1)
 PARAM_ADD(PARAM_UINT16, m2, &motorPowerSet.m2)
 PARAM_ADD(PARAM_UINT16, m3, &motorPowerSet.m3)
 PARAM_ADD(PARAM_UINT16, m4, &motorPowerSet.m4)
-PARAM_GROUP_STOP(motorPowerSet)
+PARAM_GROUP_STOP(ring)
 
 LOG_GROUP_START(motor)
-LOG_ADD(LOG_UINT32, m1, &motorPower.m1)
-LOG_ADD(LOG_UINT32, m2, &motorPower.m2)
-LOG_ADD(LOG_UINT32, m3, &motorPower.m3)
-LOG_ADD(LOG_UINT32, m4, &motorPower.m4)
+LOG_ADD(LOG_INT32, m4, &motorPower.m4)
+LOG_ADD(LOG_INT32, m1, &motorPower.m1)
+LOG_ADD(LOG_INT32, m2, &motorPower.m2)
+LOG_ADD(LOG_INT32, m3, &motorPower.m3)
 LOG_GROUP_STOP(motor)

### 2020-04-29 crazyflie-firmware/src/modules/src/sound_cf2.c

@@ -198,9 +198,9 @@ static Melody starwars = {.bpm = 120, .delay = 1, .notes = {{A3, Q}, {A3, Q}, {A
     {A3, Q}, {F3, ES}, {C4, S}, {A3, H}, {0, H},
     REPEAT}};
 static Melody valkyries = {.bpm = 140, .delay = 1, .notes = {{Gb3, Q}, {B3, Q},
-    {Gb3, S}, {B3, E},  {D4, Q}, {B3, Q}, {D4, Q}, {B3, S}, {D4, E}, {Gb4, Q},
-    {D4, Q}, {Gb4, Q}, {D4, S}, {Gb4, E}, {A4, Q}, {A3, Q}, {D4, Q}, {A3, S},
-    {D4, E}, {Gb4, H},
+    {Gb3, S}, {B3, E},  {D4, Q}, {B3, Q}, {D4, Q}, {B3, S}, {D4, E}, {Gb4, Q},  
+    {D4, Q}, {Gb4, Q}, {D4, S}, {Gb4, E}, {A4, Q}, {A3, Q}, {D4, Q}, {A3, S},  
+    {D4, E}, {Gb4, H}, 
     REPEAT}};
 
 typedef void (*BuzzerEffect)(uint32_t timer, uint32_t * mi, Melody * melody);
@@ -317,7 +317,6 @@ static EffectCall effects[] = {
 };
 
 static xTimerHandle timer;
-static StaticTimer_t timerBuffer;
 static uint32_t counter = 0;
 
 static void soundTimer(xTimerHandle timer)
@@ -344,7 +343,7 @@ void soundInit(void)
 
   neffect = sizeof(effects) / sizeof(effects[0]) - 1;
 
-  timer = xTimerCreateStatic("SoundTimer", M2T(10), pdTRUE, NULL, soundTimer, &timerBuffer);
+  timer = xTimerCreate("SoundTimer", M2T(10), pdTRUE, NULL, soundTimer);
   xTimerStart(timer, 100);
 
   isInit = true;

### 2020-04-29 crazyflie-firmware/src/modules/src/system.c

@@ -65,18 +65,14 @@
 #include "deck.h"
 #include "extrx.h"
 #include "app.h"
-#include "static_mem.h"
 
 /* Private variable */
 static bool selftestPassed;
 static bool canFly;
 static bool isInit;
 
-STATIC_MEM_TASK_ALLOC(systemTask, SYSTEM_TASK_STACKSIZE);
-
 /* System wide synchronisation */
 xSemaphoreHandle canStartMutex;
-static StaticSemaphore_t canStartMutexBuffer;
 
 /* Private functions */
 static void systemTask(void *arg);
@@ -84,7 +80,10 @@ static void systemTask(void *arg);
 /* Public functions */
 void systemLaunch(void)
 {
-  STATIC_MEM_TASK_CREATE(systemTask, systemTask, SYSTEM_TASK_NAME, NULL, SYSTEM_TASK_PRI);
+  xTaskCreate(systemTask, SYSTEM_TASK_NAME,
+              SYSTEM_TASK_STACKSIZE, NULL,
+              SYSTEM_TASK_PRI, NULL);
+
 }
 
 // This must be the first module to be initialized!
@@ -93,7 +92,7 @@ void systemInit(void)
   if(isInit)
     return;
 
-  canStartMutex = xSemaphoreCreateMutexStatic(&canStartMutexBuffer);
+  canStartMutex = xSemaphoreCreateMutex();
   xSemaphoreTake(canStartMutex, portMAX_DELAY);
 
   usblinkInit();

### 2020-04-29 crazyflie-firmware/src/modules/src/tdoaEngineInstance.c

@@ -1,57 +1,0 @@
-/**
- * ,---------,       ____  _ __
- * |  ,-^-,  |      / __ )(_) /_______________ _____  ___
- * | (  O  ) |     / __  / / __/ ___/ ___/ __ `/_  / / _ \
- * | / ,--´  |    / /_/ / / /_/ /__/ /  / /_/ / / /_/  __/
- *    +------`   /_____/_/\__/\___/_/   \__,_/ /___/\___/
- *
- * Crazyflie control firmware
- *
- * Copyright (C) 2020 Bitcraze AB
- *
- * This program is free software: you can redistribute it and/or modify
- * it under the terms of the GNU General Public License as published by
- * the Free Software Foundation, in version 3.
- *
- * This program is distributed in the hope that it will be useful,
- * but WITHOUT ANY WARRANTY; without even the implied warranty of
- * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
- * GNU General Public License for more details.
- *
- * You should have received a copy of the GNU General Public License
- * along with this program. If not, see <http://www.gnu.org/licenses/>.
- *
- *
- * tdoaEngineInstance.c - holds the tdoa engine state instance
- */
-
-#include "tdoaEngineInstance.h"
-#include "log.h"
-#include "param.h"
-
-tdoaEngineState_t tdoaEngineState;
-
-LOG_GROUP_START(tdoaEngine)
-STATS_CNT_RATE_LOG_ADD(stRx, &tdoaEngineState.stats.packetsReceived)
-STATS_CNT_RATE_LOG_ADD(stEst, &tdoaEngineState.stats.packetsToEstimator)
-STATS_CNT_RATE_LOG_ADD(stTime, &tdoaEngineState.stats.timeIsGood)
-STATS_CNT_RATE_LOG_ADD(stFound, &tdoaEngineState.stats.suitableDataFound)
-STATS_CNT_RATE_LOG_ADD(stCc, &tdoaEngineState.stats.clockCorrectionCount)
-STATS_CNT_RATE_LOG_ADD(stHit, &tdoaEngineState.stats.contextHitCount)
-STATS_CNT_RATE_LOG_ADD(stMiss, &tdoaEngineState.stats.contextMissCount)
-
-LOG_ADD(LOG_FLOAT, cc, &tdoaEngineState.stats.clockCorrection)
[…]

### 2020-04-29 crazyflie-firmware/src/utils/interface/cf_math.h

@@ -39,6 +39,3 @@
 
 #define DEG_TO_RAD (PI/180.0f)
 #define RAD_TO_DEG (180.0f/PI)
-
-#define MIN(a, b) ((b) < (a) ? (b) : (a))
-#define MAX(a, b) ((b) > (a) ? (b) : (a))

### 2020-04-29 crazyflie-firmware/test/deck/drivers/src/test_lps_tdoa2_tag.c

@@ -1,0 +1,1224 @@
+// File under test lpsTwrTag.h
+#include "lpsTdoa2Tag.h"
+
+#include <string.h>
+#include <stdlib.h>
+#include "unity.h"
+
+#include "mock_libdw1000.h"
+#include "mock_cfassert.h"
+#include "mock_estimator.h"
+#include "mock_locodeck.h"
+
+#include "dw1000Mocks.h"
+#include "freertosMocks.h"
+#include "physicalConstants.h"
+
+// The local clock uses 40 bits
+#define TIMER_TAG_MAX_VALUE 0x000000FFFFFFFFFFul
+
+// Timestamps received in messages from anchors are 32 bits
+#define TIMER_ANCHOR_MAX_VALUE 0x00000000FFFFFFFFul
+
+static dwDevice_t dev;
+static lpsTdoa2AlgoOptions_t options = {
+  .anchorAddress = {
+    0xbccf000000000000,
+    0xbccf000000000001,
+    0xbccf000000000002,
+    0xbccf000000000003,
+    0xbccf000000000004,
+    0xbccf000000000005,
+    0xbccf000000000006,
+    0xbccf000000000007,
+  },
+  .anchorPosition = {
+    {.x = 0.99, .y = 1.49, .z = 1.80},
+    {.x = 0.99, .y = 3.29, .z = 1.80},
+    {.x = 4.67, .y = 2.54, .z = 1.80},
+    {.x = 0.59, .y = 2.27, .z = 0.20},
+    {.x = 4.70, .y = 3.38, .z = 0.20},
+    {.x = 4.70, .y = 1.14, .z = 0.20},
+    {.x = 4.70, .y = 3.38, .z = 0.20},
+    {.x = 4.70, .y = 1.14, .z = 0.20},
+  },
+};
+
+static const uint64_t NS = 0;
+static const uint32_t dataLengthNoLpp = MAC802154_HEADER_LENGTH + sizeof(rangePacket2_t);
+
+static void mockMessageFromAnchor(uint8_t anchorIndex, uint64_t rxTime, uint8_t sequenceNrs[], uint64_t timestamps[], uint64_t distances[]);
+static void mockMessageFromAnchorNotComingBackToReceive(uint8_t anchorIndex, uint64_t rxTime, uint8_t sequenceNrs[], uint64_t timestamps[], uint64_t distances[]);
[…]

### 2020-04-29 crazyflie-firmware/tools/lighthouse/get_bs_position.py

@@ -71,13 +71,13 @@ for i in range(openvr.k_unMaxTrackedDeviceCount):
                 sys.exit(1)
 
 # Rotation matrixes to convert to the CF coordinate system
-openvr_to_cf = np.array([
+opencv_to_cf = np.array([
     [0.0, 0.0, -1.0],
     [-1.0, 0.0, 0.0],
     [0.0, 1.0, 0.0],
 ])
 
-cf_to_openvr = np.array([
+cf_to_opencv = np.array([
     [0.0, -1.0, 0.0],
     [0.0, 0.0, 1.0],
     [-1.0, 0.0, 0.0],
@@ -89,10 +89,10 @@ for pose in bs_poses:
         continue
 
     position = [pose[0][3] - offset[0], pose[1][3] - offset[1], pose[2][3] - offset[2]]
-    position_cf = np.dot(openvr_to_cf, position)
+    position_cf = np.dot(opencv_to_cf, position)
 
     rotation = [pose[0][:3], pose[1][:3], pose[2][:3]]
-    rotation_cf = np.dot(openvr_to_cf, np.dot(rotation, cf_to_openvr))
+    rotation_cf = np.dot(opencv_to_cf, np.dot(rotation, cf_to_opencv))
 
     print("{.origin = {", end='')
     for i in position_cf:

### 2020-04-29 crazyflie-firmware/tools/make/versionTemplate.py

@@ -15,20 +15,9 @@ header = """/* This file is automatically generated by {0}!
  */
 """
 
-def check_output(*args):
-    """A wrapper for subprocess.check_output() to handle differences in python 2 and 3.
-    Returns a string.
-    """
-    result = subprocess.check_output(*args)
-
-    if isinstance(result, bytes):
-        return result.decode('utf-8')
-    else:
-        return result
-
 
 def extract_information_from_git(base):
-    revision = check_output(["git", "-C", base, "rev-parse", "HEAD"]).strip()
+    revision = subprocess.check_output(["git", "-C", base, "rev-parse", "HEAD"]).strip()
 
     version['revision'] = revision[0:12]
     version['irevision0'] = "0x" + revision[0:8]
@@ -36,7 +25,7 @@ def extract_information_from_git(base):
     version['productionRelease'] = 'false'
 
     try:
-        identify = check_output(
+        identify = subprocess.check_output(
             ["git", "-C", base, "describe", "--abbrev=12", "--tags", "HEAD"])
         identify = identify.split('-')
 
@@ -59,12 +48,12 @@ def extract_information_from_git(base):
     if version['local_revision'] != '0':
         version['tag'] = version['tag'] + ' +' + version['local_revision']
 
-    branch = check_output(
+    branch = subprocess.check_output(
         ["git", "-C", base, "rev-parse", "--abbrev-ref", "HEAD"]).strip()
     version['branch'] = branch
 
     subprocess.call(["git", "-C", base, "update-index", "-q", "--refresh"])
-    changes = check_output(
+    changes = subprocess.check_output(
         ["git", "-C", base, "diff-index", "--name-only", "HEAD", "--"]).strip()
     if len(changes):
         version['modified'] = 'true'
